### 2019-04-19 template/articles/article_fan.tex
First Template File Created

\input{../../preambles/article_fan_pre_main.tex}

\begin{document}

\title{Paper Name}

\author{Fan Wang\thanks{Department of Economics, University of Houston (email: fwang26@uh.edu)}}

\maketitle
\begin{abstract}
\singlespacing This is my abstract \end{abstract}
\vfill
\pagebreak{}

\section{Introduction}

\section{Main}

\section{Conclusion}

\pagebreak
\input{../../cite/endcite_fan_main.tex}
\pagebreak

\appendix
\section{Data Figures and Tables}

\end{document}

### 2019-04-19 sections/data/data_one.tex
Section based compilation

\label{subsec:dataone}

The survey also captures some aspects of the pecuniary \FCFs for acquiring each loan. There was a significant reduction in these costs after 2001 for \NLC \BBBB. Most of the drop is due to the prevalence of the Million Baht Fund program. Loans from the Million Baht Fund had fees and transportation costs similar to \BBBB \LLCLY, which is likely due to its localized and village-committee based administration.

Fees and transportation costs for the BAAC also went down over time. These might have been driven down by improvements in the BAAC itself or reductions in transportation and communication costs. Table \ref{tab:FCBorrDetailType} shows that costs at the BAAC, however, are still twice as large as the average costs reported for \BBBB from relatives or moneylenders. Strikingly, the fees and transport costs on the few reported commercial bank loans are on average seven times larger than those for BAAC loans, and almost 35 times larger than the costs for Million Baht Fund loans or \LLC loans.

### 2019-04-19 sections/data/data_two.tex
Section based compilation

\label{subsec:datatwo}

In the literature on \LLC credit markets, repayment rates for \LLC \BBBB have often been found to be high \autocite{morduch_microfinance_1999}. Recently, evidence from a number of microfinance studies shows that repayment rates for \NLC \BBBB have also been found to be high \autocite{buera_macroeconomics_2012}. Consistent with these findings, in the Townsend Thai Monthly Survey villages, both \NLC and \LLC repayments are high. These on-time repayment rates are directly calculated from the data: every month, new loans that households take out are recorded and the month in which repayment should be completed is also recorded; then every month, repayment amounts of each loan is tracked until full repayment.

Specifically, the eventual full repayment rate for \NLC loans is 97\% and for \LLC loans is 95\%. Interestingly, households that do not fully pay back their loans still pay a significant proportion of their debts, as shown in Table \ref{tab:Repay_notFull}. Taking partial repayments into consideration, I find that 98.2\% of every Baht of principal lent is paid back for \NLC loans, and 96.5\% of every Baht of principal lent is paid back for \LLC loans.

### 2019-04-19 sections/esti/esti_one.tex
Section based compilation

\label{subsec:estione}

Besides the age at school closure, the impact of school closure on educational attainment may also differ by the number of years of exposure to the policy: short-run effects of closure on a child's educational attainment progression could be dampened or amplified over the medium and long run.\footnote{After an individual completes schooling, duration effects will become constant. In studies with cross-sectional data taken long after a policy has been implemented, \textcite{duflo_2001_school} for example, the duration effect is irrelevant because all educational attainment data is observed long after sample individuals have completed schooling. In our data, a significant proportion of individuals have not completed schooling, allowing us to have meaningful duration effects.}  In order to identify both age and duration effects with our cross-sectional data, we exploit the variation in the year of school closure. Under the assumption that the impact of the policy is not specific to the calendar year of closure, we can estimate Equation \ref{eq:startsLengths} to obtain the impact of the policy as a function of both starting age and the length of exposure.

In Equation \ref{eq:startsLengths}, we use similar notations as in Equation \ref{eq:startsOnly}, the difference is that the policy's effects are now captured by $\hat{\lambda_{zl}}$ that varies by age-at-closure variable \(t_{i}\) and years-of-exposure variable $\tau_{i}$:

\begin{singlespace}\vspace*{-\baselineskip}
\begin{eqnarray}
E_{pvia} & = & \phi+\beta_{v}+\rho_{pa} \nonumber \\
&  & + \hat{\lambda_{zl}} \cdot \mathbb{1}\left\{ (l_{l}\leq\tau_{i}\leq u_{l} ) \cap  ( l_{z}\leq t_{i}\leq u_{z} ) \right\} \cdot c_{v} \label{eq:startsLengths}\\
&  & +X_i\cdot\gamma\nonumber +\epsilon_{i}\nonumber
\end{eqnarray}
\end{singlespace}\noindent\ignorespaces
where, as before, \(c_{v}\) is a binary variable indicating if individual \(i\) is from a village \(v\) with school consolidation (i.e. treatment village). As in Equation \ref{eq:startsOnly}, we group children in villages with school closure into $Z$ groups based on their age at closure, with lower and upper bounds for each group, $l_{z}$ and $u_{z}$. To capture duration effects, we further divide each of the Z groups of children into $L$ groups based on the length of exposure $\tau_i$, defined as the gap between individual $i$'s age in 2011 and $i$'s age at year of school closure, $t_{i}$.\footnote{$\tau_i = \min(a_i, a_i - t_i)$: \(\tau_i\) is the gap between age in 2011 and $t_{i}$ if individual $i$ was borne before the year of closure, and it is the age of the child in 2011 if the child was borne after school closure. } Each $l$ length of exposure group includes those with $\tau_i$ falling within lower and upper bounds, $l_{l}$ and $l_{u}$. The exposure groups allow us to separately estimate the short, medium and long run effects of the consolidation policy on educational attainment. There are $Z\cdot L$ groups of interest for this regression.\footnote{Ideally, we would estimate the policy effects for each $t_i$ and $\tau_i$ combination separately, but we have constructed the $Z$ and $L$ groups due to limited sample size.}

### 2019-04-19 sections/esti/esti_two.tex
Section based compilation

\label{subsec:estitwo}

We include in the model  measurement errors that allow us to estimate the parameters using maximum likelohood methods.
As described previously, households observe $\Omega = \big(Y, p^{N}_{yv}, X\big)$, and the distributions of $R_{yv}$. In terms of choices and outcomes, the econometrician only observes $F^{*}$ and $N^{*}$, which differ from the true optimal nutritional choice $N$ by measurement error $\eta$ and true height outcome $h_{24}$ by $\iota$:
\begin{equation}
\log(N^{*}) = \log(N(Y, X, \epsilon; p^{N}_{yv},\mu_{R_{yv}},\sigma_{R_{yv}})) + \eta
\end{equation}
\begin{equation}
\log(h_{24}^{*}) = \log(h_{24}(N(Y, X, \epsilon; p^{N}_{yv},\mu_{R_{yv}},\sigma_{R_{yv}}), X, \epsilon)) + \iota
\end{equation}
We assume that $\eta$ and $\iota$ are normally distributed, and that $\epsilon$, $\eta$ and $\iota$ are independent. The standard deviation of $\eta$ is $\sigma_{\eta}$ and the mean is $\mu_{\eta}=-\frac{\sigma_{\eta}^2}{2}$. The standard deviation for $\iota$ is $\sigma_{\iota}$ with mean $\mu_{\iota}=-\frac{\sigma_{\iota}^2}{2}$. The log likelihood is based on the difference between model optimal nutritional choices and observed nutritional choices, as well as the model height outcome and observed heights at 24 months of age:

\begin{equation}
\label{eq:likelihood}
\max_{\theta\in\Theta} \sum_{y=1970}^{1975}\sum_{v} \bigg\{ \sum_{i=1}^{n_{yv}} \log \bigg( \int_{\epsilon} \phi_{\iota}
\big(
\ln h_{24,i}^{*}-
\ln h_{24}(
\substack{
Y_{i}, X_{i}, \epsilon_i; \\
\theta,\mu_{R_{yv}}, \sigma_{R_{yv}}
}
)
\big)
\cdot \phi_{\eta}\big(\ln N^{*}_{i} -
\ln N(
\substack{
Y_{i}, X_{i}, \epsilon_i; \\
\theta,\mu_{R_{yv}}, \sigma_{R_{yv}}
}
)
\big) dF(\epsilon_i) \bigg)\bigg\}
\end{equation}
where
\begin{equation}
\theta=\{\underbrace{\rho, \gamma, \lambda}_{\text{Preference}}, \overbrace{\delta}^{\substack{\text{Atole} \\ \text{disc.}}}, \underbrace{A, \alpha , \beta, \sigma_{\epsilon} }_{\substack{\text{Production} \\ \text{Function}}}, \sigma_{\eta},\sigma_{\iota}\}
\end{equation}
Equation \ref{eq:likelihood} is determined by $\theta$ as well as a set of $\big(\mu_{R_{yv}}, \sigma_{R_{yv}}\big)$ that are village- and time-specific. This means that in estimating the model, we do not impose assumptions about where the current height distribution is with respect to the stationary height distribution. We solve for optimal choices given the observed individual specific $\Omega_i$ and the observed $\mu_{R_{yv}}, \sigma_{R_{yv}}$ for each year $y$ in village $v$.

### 2019-04-19 sections/introconclude/abstract.tex
Section based compilation

% JEL CODES
\newcommand{\jelcodes}{D15, D25, G21, O16, O17}
\newcommand{\keywords}{Informal credit, microfinance, structural estimation}
% Informal credit, Family loans, Social capital, Limited enforcement, Default risk
% Microfinance, Entrepreneurship, Social Networks
% Microfinance, entrepreneurship, general equilibrium effectiveness
%% 2018-12-13 05:38
\newcommand{\abstractA}{I develop a dynamic equilibrium model in which risky entrepreneurs sort among local-informal and outside-formal borrowing and savings opportunities. A local interest rate clears the informal credit market, but villages are small-open economies with respect to the formal market. Identical policies that shift the interest rate, fixed cost or collateral constraint of formal access have non-linear and non-separable effects depending on the costs of informal access. I develop computational methods for solving and estimating dynamic equilibrium models with discrete and continuous choices that leverage scalable parallel cloud computing resources. I take the model to villages in Thailand which implemented formal credit access expansion policies, and estimate changes in the costs and constraints of access from changes in credit market participation. I find that lower fixed costs increased the proportion of households borrowing formally, and that relaxed collateral constraints lowered informal interest rates. In terms of welfare, I find low wealth but productive households benefited from policies that expanded credit access, but average gains are smaller than would be predicted by models that do not consider the substantial informal credit market. Moreover, approximately 18\% of households suffered welfare losses because of diminished opportunities for informal saving.}

\newcommand{\abstractB}{I develop and estimate a dynamic equilibrium model of risky entrepreneurs' borrowing and savings decisions incorporating both formal and local-informal credit markets. Households have access to an exogenous formal credit market and to an informal credit market in which the interest rate is endogenously determined by the local demand and supply of credit. I estimate the model via Simulated Maximum Likelihood using Thai village data during an episode of formal credit market expansion. My estimates suggest that a 49 percent reduction in fixed costs increased the proportion of households borrowing formally by \FIPNafterFCPropIncRnd\xspace percent, and that a doubling of the collateralized borrowing limits lowered informal interest rates by \IRNafterFCPropIncRnd\xspace percent. I find that more productive households benefited from the policies that expanded borrowing access, but less productive households lost in terms of welfare due to diminished savings opportunities. Gains are overall smaller than would be predicted by models that do not consider the informal credit market. \textbf{JEL codes}: \jelcodes}

### 2019-04-19 sections/introconclude/conclude.tex
Section based compilation

In recent decades, \NLC financial services have expanded significantly in developing countries. This paper evaluates the impacts of improving access to the \NLC credit market on rural households, taking into consideration the impacts of changing \NLC credit market conditions on the \LLC credit market.

I built a risky entrepreneur model assuming that villages are small open economies with respect to \NLC credit market options, but households can also borrow and save in an equilibrium local credit market. I showed that \NLC credit market expansions through interest rates subsidies, access fixed costs reductions, and collateral constraint relaxations have heterogeneous and non-separable effects on households. These effects differ depending on informal credit market conditions. In the Thai case, villages already had extensive \LLC \BBBB and \SSSS activities, and the effects of \NLC credit market expansions on household welfare were hence limited.

### 2019-04-19 sections/introconclude/intro.tex
Section based compilation

\newcommand{\introfootone}{For example, \textcite{gine_access_2011, KARAIVANOV2018100} use the initial waves of the Townsend Thai village survey to study how household firms choose between formal and informal borrowing in two-period models. \textcite{gine_access_2011} distinguishes formal and informal borrowing by interest rates, fixed costs, and collateral constraints.}

It is well known that in village economies, local informal financial arrangements exist in the absence of external formal credit market options \autocite{udry_risk_1994, townsend_risk_1994}. As formal borrowing and savings opportunities have expanded, informal credit markets have persisted. But dynamic models that study the effects of financial deepening on development do not explicitly consider informal financial options, and studies that test the fit of informal risk-sharing models to data generally do not consider formal options explicitly.\footnote{See \textcite{townsend_financial_2010, BKSannualReview} for reviews.} On the other hand, studies which explicitly analyze the interaction of formal and informal credit markets generally do so in non-dynamic settings.\footnote{\introfootone} It is difficult to fully analyze the effects of financial deepening which determines asset distributions, however, when these distributions are fixed. In this paper, I develop and estimate a dynamic equilibrium risky entrepreneur model that incorporates formal as well as informal borrowing and savings choices. In this model, households are infinitely-lived, risk-averse, and have varying productivity and \CZH.

### 2019-04-19 sections/introconclude/literature.tex
Section based compilation

The analysis in this paper contributes to several strands of the literature. First, there has been substantial research on the impacts of greater financial access on developing economies \autocite{greenwood_financial_1990, banerjee_occupational_1993, lloyd-ellis_enterprise_2000, gine_evaluation_2004, greenwood_financing_2010, kaboski_structural_2011, moll_productivity_2014, buera_macroeconomics_2012, NBERw20821}. Despite the importance of informal financial arrangements \autocite{udry_risk_1994, townsend_risk_1994}, these dynamic models of financial deepening--formal credit market expansion--generally do not explicitly consider informal financial options.\footnote{\textcite{banerjee_credit_2017} allow households to borrow from formal and informal sectors at exogenous rates to finance within period capital investments, and households can save across periods at an exogenous negative savings rate.} Additionally, studies that test the fit of informal risk-sharing models to data do not model formal options explicitly \autocite{alem_evaluation_2014, karaivanov_dynamic_2014, KinnanThai}. In this paper, I model risky entrepreneurs' choices over formal and informal credit market options in an exogenous incomplete markets setting.\footnote{While there are different ways for rural households to transfer financial resources, \textcite{karaivanov_dynamic_2014} find that a model with exogenously incomplete borrowing and savings options fit consumption and investment data in rural Thai villages better than constrained efficient credit/insurance models. The model in effect augments equilibrium models of risky entrepreneurs (see review: \textcite{quadrini_entrepreneurship_2009}) with additional exogenous borrowing and savings options.} Similar to \textcite{kaboski_structural_2011}, I treat villages as small open economies where formal prices are exogenously determined, but I extend the framework to explicitly consider informal choices and equilibrium interest rates determined within each local informal credit market. My approach here focuses on the \textit{micro-equilibrium} effects of formal credit market expansion on village credit markets. This is different from \textcite{buera_macroeconomics_2012, BrezaKinnanNBERw24329}, which study the macro equilibrium effects of large microfinance roll-outs on prices, including interest rates and wages, in the aggregate economy.

Second, this paper contributes to works that study the interaction between formal and informal credit markets. Third, there is a significant and growing empirical literature that analyzes separate dimensions of credit market policies. Fourth, there is a literature that studies how the provision of formal insurance could crowd-out informal insurance \autocite{attanasio_consumption_2000,krueger_public_2011,ChandrasekharKinnanLarreguy}.

The structure of the paper is as follows. Section \ref{sec:modelmodel} develops the model. Section \ref{sec:simusimu} describes model mechanisms and demonstrates the equilibrium effects of shifting various  dimensions of formal and informal credit market access costs. In Section \ref{sec:Data-and-Background}, I describe the data and background. Section \ref{sec:estiesti} describes estimation results and counterfactuals. I offer the conclusion in Section \ref{sec:concludeconclude}. Additional details for the solution and estimation methods are in Sections \ref{sec:solualgo}.

### 2019-04-19 sections/model/model_one.tex
Section based compilation

\label{subsec:modelone}

Given $\mu_{R_{yv}}$, $\sigma_{R_{yv}}$, and price $p^{N}_{yv}$, each household solves the following maximization problem:

\begin{equation}
\max_{c,N} c+\rho\cdot c^{2}+  \Bigg\{ \gamma\cdot H_{24}+\lambda \cdot \int_{R_{yv}} \left(H_{24}-R_{yv}\right)\mathbb{1}\left\{ H_{24}\ge R_{yv}\right\}dF(R_{yv}) \Bigg\}
\end{equation}
where:
\[
c=Y - p^{N}_{yv} \cdot N
\]
\[
H_{24}(N,X,\epsilon)=\exp(A+ X\cdot\alpha+\epsilon)\cdot N^{\beta}
\]
The realized household utility $u_{yv}$ is a function of parameters and $Y, p^{N}_{yv}, X, F(R_{yv}),\epsilon$. Households make choices given $\Omega = \big(Y, p^{N}_{yv}, X\big)$, the i.i.d. productivity shock $\epsilon$, and $F(R_{yv})$. At the birth of a child, a household chooses the optimal amount of nutrition for the child over the next 24 months given the joint relative distribution of the reference health outcome and their own child's helath given that child's productivity shock and nutritional intake. The parents choose knowing that more nutritional intake--at a decreasing rate of return--will increase the probability that their child will catch up to or exceed the reference health.

### 2019-04-19 sections/model/model_two.tex
Section based compilation

\label{subsec:modeltwo}

At the beginning of each period, for each household, the household \PDT \(\A\), \SKE \(\SHK\), and \PYS \(\K\), which is chosen previously by the household based on expected productivity, jointly determine the \ICM of the household in the current period:\footnote{The model focuses on financial (safe asset) and \PYS  (risky asset) choices. Labor supply for the household firm is inelastic and captured by \(\A\).}
\begin{equation}
  \label{eq:ProductionFunction}
  \Y=\exp\left(\A+\SHK\right)\cdot \K^{\PALPHA}
\end{equation}

### 2019-04-19 sections_sandbox/estimate_sandbox.tex
Section based compilation

\documentclass[12pt,english]{article}
\input{../fragments/preamble_main.tex}
\begin{document}

\input{../sections/esti/esti_main.tex}
% \input{../sections/esti/esti_one.tex}
% \input{../sections/esti/esti_two.tex}

\input{../fragments/cite/cite_end.tex}
\end{document}

### 2019-04-19 singlefile_article/article_fan.tex
Section based compilation

\documentclass[12pt,english]{article}

\input{../fragments/preamble_one.tex}
\input{../fragments/preamble_two.tex}

% Special String Shorthands
\input{../fragments/shorthand/short_text.tex}
\input{../fragments/shorthand/short_math.tex}

% Numbers as Newcommands
\input{../fragments/stats/stats_one.tex}

% Citation
\input{../fragments/cite/cite_preamble.tex}
\bibliography{../_bib/ref_one, ../_bib/ref_two, ../_bib/ref_three, ../_bib/ref_four, ../_bib/ref_five}

\makeatother

\begin{document}

\title{Paper Name}

\author{Fan Wang\thanks{Department of Economics, University of Houston (email: fwang26@uh.edu)}}

\maketitle
\begin{abstract}
\singlespacing This is my abstract \end{abstract}
\vfill
\pagebreak{}

\section{Introduction}

According to \textcite{becker_human_1986}, ipsum dolor sit amet, consectetur adipiscing elit. Integer placerat nunc orci, id pellentesque lacus ullamcorper at. Mauris venenatis gravida magna non dapibus. Nullam vel consequat purus, id luctus dui. Suspendisse vel auctor nulla. Proin ipsum felis, efficitur eu eleifend vitae, efficitur pellentesque mauris \autocite{case_lasting_2005, conti_understanding_2010}.

\section{Model}

Let $\tau$ be the fraction of poorest children receiving price discounts and $\delta$ be the percentage price discount that children receive. $Z\left(\tau,\delta\right)$ is the total cost of a subsidy in grams of protein for 1970, 1972, 1974 and 1976 cohorts, given reference point distribution $\Gamma$ for each cohort:

\begin{equation}
\label{eq:targetcost}
Z\left(\tau,\delta\right) =
\sum\limits_{
	\substack{
	\mathrm{cohort} \\ \in{\left\{70,72,74,76\right\}}}
	}
\left\{\delta\cdot
\int_{\epsilon}
\int_{Y_{min}}^{F_{Y}^{-1}\left(\tau\right)}
\int_{X}
N\Big(
\substack{
	Y,X,\epsilon; \\
	\delta, \Gamma_{\mathrm{cohort}}
}
\Big)f\left(X|Y\right)f\left(Y\right)f\left(\epsilon\right)\mathrm{d}X\mathrm{d}Y\mathrm{d}\epsilon\right\}
\end{equation}
As described earlier, we fix the joint distribution of the state space variables across cohorts, and so only the reference point distribution $\Gamma$ is cohort-specific in Equation \ref{eq:targetcost}. We start $\Gamma_{1970}$ as mentioned using the actual reference points in year 1970 from Atole villages, and solve for subsequent reference point distributions following Equation \ref{eq:hmeasure}.

\section{Data}

Let $\tau$ be the fraction of poorest children receiving price discounts and $\delta$ be the percentage price discount that children receive. $Z\left(\tau,\delta\right)$ is the total cost of a subsidy in grams of protein for 1970, 1972, 1974 and 1976 cohorts, given reference point distribution $\Gamma$ for each cohort:

\begin{equation}
\label{eq:targetcost}
Z\left(\tau,\delta\right) =
\sum\limits_{
	\substack{
	\mathrm{cohort} \\ \in{\left\{70,72,74,76\right\}}}
	}
\left\{\delta\cdot
\int_{\epsilon}
\int_{Y_{min}}^{F_{Y}^{-1}\left(\tau\right)}
\int_{X}
N\Big(
\substack{
	Y,X,\epsilon; \\
	\delta, \Gamma_{\mathrm{cohort}}
}
\Big)f\left(X|Y\right)f\left(Y\right)f\left(\epsilon\right)\mathrm{d}X\mathrm{d}Y\mathrm{d}\epsilon\right\}
\end{equation}
As described earlier, we fix the joint distribution of the state space variables across cohorts, and so only the reference point distribution $\Gamma$ is cohort-specific in Equation \ref{eq:targetcost}. We start $\Gamma_{1970}$ as mentioned using the actual reference points in year 1970 from Atole villages, and solve for subsequent reference point distributions following Equation \ref{eq:hmeasure}.

\section{Conclusion}

\pagebreak
\input{../fragments/cite/cite_end.tex}
\pagebreak

\appendix
\section{Data Figures and Tables}

\end{document}

### 2019-04-19 sections_blank/tabfig/main_esti.tex
Empty File

% \FIGESTIFIT{../graphs/estimation}
% \input{../preamble/group_d_data_pick/PARAMS.tex} # top of draft used by data tables as well
% \input{../preamble/group_d_data_pick/DATASIMUPROBJ.tex}  # top of draft used by data tables as well
% \FIGESTIMATES
\input{../preamble/group_d_data_pick/var/PARAMSFY1000early.tex}
% 2. Get SD
\input{../preamble/group_d_data_pick/var/PARAMSFY10early.tex}
% 3. Get SD for FB
\input{../preamble/group_d_data_pick/var/PARAMSFY500early.tex}
% 4a. sds
\input{../preamble/group_d_data_pick/var/PARAMSLV15.tex}
% 4a. sds
\input{../preamble/group_d_data_pick/var/PARAMSLV105.tex}
% 4a. mu A
\input{../preamble/group_d_data_pick/var/PARAMSLV500.tex}
% 4a. Kappa 99-01 mean + sd for all kappa
\input{../preamble/group_d_data_pick/var/PARAMSLV10.tex}
% 4c. Kappa 02-09, overrid mean 02-09
\input{../preamble/group_d_data_pick/var/PARAMSLV1000.tex}
% 4b. beta NE mean
\input{../preamble/group_d_data_pick/var/PARAMSLV100.tex}
\input{../preamble/group_d_data_pick/var/PARAMSLV50.tex}
% finalized Production function estimates o11 and real
\input{../preamble/group_d_data_pick/prod_var/PARAMS_adist_o11_rel.tex}

\FIGESTIMATESFY{Parameter Estimates}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% FRACTIONS Borrowing
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Borrow Frac Central
\input{../preamble/group_d_data_pick/pcky_var/CKY1000_mpoly.tex}
% Borrow Frac Northeast
\input{../preamble/group_d_data_pick/pcky_var/CKY15_msimu.tex}
% Informal Borrow Shares
\input{../preamble/group_d_data_pick/pcky_var/CKY15_msimu_ibbf_ne.tex}
\input{../preamble/group_d_data_pick/pcky_var/CKY15_msimu_ibbf_ce.tex}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% CKY AMOUNTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% K Amount NE and CE and Y for CE both from SIMU 15
\input{../preamble/group_d_data_pick/pcky_var/CKY15_msimu_kne.tex}
\input{../preamble/group_d_data_pick/pcky_var/CKY15_msimu_kce.tex}
\input{../preamble/group_d_data_pick/pcky_var/CKY15_msimu_yce.tex}
\input{../preamble/group_d_data_pick/pcky_var/CKY1_msimu_cne_v2.tex}
% Y Amount NE from mpoly 100
% \input{../preamble/group_d_data_pick/pcky_var/CKY100_mpoly_yne.tex}
\input{../preamble/group_d_data_pick/pcky_var/CKY500_mpoly_yne_v2.tex}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Probabilities Means
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Probabilities
\input{../preamble/group_d_data_pick/pcky_raw/PROB1.tex}
% replace prob confidence interval
\input{../preamble/group_d_data_pick/pcky_var/PROB500.tex}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% ACTUAL DATA
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\input{../preamble/group_d_data_pick/pcky_data.tex}

\FITPRBKY{Model Fits}

### 2019-04-19 sections_combine/draft_main_blank.tex
Empty File

\documentclass[12pt,english]{article}
\input{../fragments/preamble_main.tex}
\begin{document}

\title{Blank File}
\author{Fan Wang\thanks{Department of Economics, University of Houston (email: fwang26@uh.edu), \url{https://fanwangecon.github.io/research.html}}}
\maketitle

\input{../sections_blank/introconclude/abstract.tex}
\begin{abstract}
\singlespacing \abstractB
\end{abstract}
\vfill
\pagebreak{}

\section{Introduction}
\input{../sections_blank/introconclude/intro.tex}
\paragraph{Related Literature}
\input{../sections_blank/introconclude/literature.tex}

\section{Data}
\subsection{Data One}
\input{../sections_blank/data/data_one.tex}
\subsection{Data Two}
\input{../sections_blank/data/data_two.tex}
\subsection{Data Three}
\input{../sections_blank/data/data_two.tex}

\section{Model}
\subsection{Model One}
\input{../sections_blank/model/model_one.tex}
\subsection{Model Two}
\input{../sections_blank/model/model_two.tex}
\subsection{Model Three}
\input{../sections_blank/model/model_two.tex}

\section{Estimate}
\subsection{Estimation One}
\input{../sections_blank/esti/esti_one.tex}
\subsection{Estimation Two}
\input{../sections_blank/esti/esti_two.tex}
\subsection{Estimation Three}
\input{../sections_blank/esti/esti_two.tex}

\section{Conclusion}
\input{../sections_blank/introconclude/conclude.tex}

\pagebreak
\input{../fragments/cite/cite_end.tex}
\pagebreak

\appendix

\end{document}

### 2019-04-21 sections/introconclude/intro.tex
bib test sync zotero overleaf

@@
-\newcommand{\introfootone}{For example, \textcite{gine_access_2011, KARAIVANOV2018100} use the initial waves of the Townsend Thai village survey to study how household firms choose between formal and informal borrowing in two-period models.
+\newcommand{\introfootone}{For example, \textcite{gine_access_2011, karaivanov_disadvantages_2018} use the initial waves of the Townsend Thai village survey to study how household firms choose between formal and informal borrowing in two-period models.
 \textcite{gine_access_2011} distinguishes formal and informal borrowing by interest rates, fixed costs, and collateral constraints.}
@@
 As formal borrowing and savings opportunities have expanded, informal credit markets have persisted.
-But dynamic models that study the effects of financial deepening on development do not explicitly consider informal financial options, and studies that test the fit of informal risk-sharing models to data generally do not consider formal options explicitly.\footnote{See \textcite{townsend_financial_2010, BKSannualReview} for reviews.} On the other hand, studies which explicitly analyze the interaction of formal and informal credit markets generally do so in non-dynamic settings.\footnote{\introfootone} It is difficult to fully analyze the effects of financial deepening which determines asset distributions, however, when these distributions are fixed.
+But dynamic models that study the effects of financial deepening on development do not explicitly consider informal financial options, and studies that test the fit of informal risk-sharing models to data generally do not consider formal options explicitly.\footnote{See \textcite{townsend_financial_2010, buera_entrepreneurship_2015} for reviews.} On the other hand, studies which explicitly analyze the interaction of formal and informal credit markets generally do so in non-dynamic settings.\footnote{\introfootone} It is difficult to fully analyze the effects of financial deepening which determines asset distributions, however, when these distributions are fixed.
 In this paper, I develop and estimate a dynamic equilibrium risky entrepreneur model that incorporates formal as well as informal borrowing and savings choices.

### 2019-04-21 sections/introconclude/literature.tex
bib test sync zotero overleaf

@@
 The analysis in this paper contributes to several strands of the literature.
-First, there has been substantial research on the impacts of greater financial access on developing economies \autocite{greenwood_financial_1990, banerjee_occupational_1993, lloyd-ellis_enterprise_2000, gine_evaluation_2004, greenwood_financing_2010, kaboski_structural_2011, moll_productivity_2014, buera_macroeconomics_2012, NBERw20821}.
-Despite the importance of informal financial arrangements \autocite{udry_risk_1994, townsend_risk_1994}, these dynamic models of financial deepening--formal credit market expansion--generally do not explicitly consider informal financial options.\footnote{\textcite{banerjee_credit_2017} allow households to borrow from formal and informal sectors at exogenous rates to finance within period capital investments, and households can save across periods at an exogenous negative savings rate.} Additionally, studies that test the fit of informal risk-sharing models to data do not model formal options explicitly \autocite{alem_evaluation_2014, karaivanov_dynamic_2014, KinnanThai}.
+First, there has been substantial research on the impacts of greater financial access on developing economies \autocite{greenwood_financial_1990, banerjee_occupational_1993, lloyd-ellis_enterprise_2000, gine_evaluation_2004, greenwood_financing_2010, kaboski_structural_2011, moll_productivity_2014, buera_macroeconomics_2012, dabla-norris_distinguishing_2018}.
+Despite the importance of informal financial arrangements \autocite{udry_risk_1994, townsend_risk_1994}, these dynamic models of financial deepening--formal credit market expansion--generally do not explicitly consider informal financial options.\footnote{\textcite{banerjee_credit_2017} allow households to borrow from formal and informal sectors at exogenous rates to finance within period capital investments, and households can save across periods at an exogenous negative savings rate.} Additionally, studies that test the fit of informal risk-sharing models to data do not model formal options explicitly \autocite{alem_evaluation_2014, karaivanov_dynamic_2014, kinnan_distinguishing_2017}.
 In this paper, I model risky entrepreneurs' choices over formal and informal credit market options in an exogenous incomplete markets setting.\footnote{While there are different ways for rural households to transfer financial resources, \textcite{karaivanov_dynamic_2014} find that a model with exogenously incomplete borrowing and savings options fit consumption and investment data in rural Thai villages better than constrained efficient credit/insurance models.
@@
 My approach here focuses on the \textit{micro-equilibrium} effects of formal credit market expansion on village credit markets.
-This is different from \textcite{buera_macroeconomics_2012, BrezaKinnanNBERw24329}, which study the macro equilibrium effects of large microfinance roll-outs on prices, including interest rates and wages, in the aggregate economy.
+This is different from \textcite{buera_macroeconomics_2012, breza_measuring_2018}, which study the macro equilibrium effects of large microfinance roll-outs on prices, including interest rates and wages, in the aggregate economy.
 
@@
 Third, there is a significant and growing empirical literature that analyzes separate dimensions of credit market policies.
-Fourth, there is a literature that studies how the provision of formal insurance could crowd-out informal insurance \autocite{attanasio_consumption_2000,krueger_public_2011,ChandrasekharKinnanLarreguy}.
+Fourth, there is a literature that studies how the provision of formal insurance could crowd-out informal insurance \autocite{attanasio_consumption_2000,krueger_public_2011,chandrasekhar_information_2011}.
 

### 2019-04-21 sections/esti/esti_one.tex
overleaf zotero sync again

@@
 Besides the age at school closure, the impact of school closure on educational attainment may also differ by the number of years of exposure to the policy: short-run effects of closure on a child's educational attainment progression could be dampened or amplified over the medium and long run.\footnote{After an individual completes schooling, duration effects will become constant.
-In studies with cross-sectional data taken long after a policy has been implemented, \textcite{duflo_2001_school} for example, the duration effect is irrelevant because all educational attainment data is observed long after sample individuals have completed schooling.
+In studies with cross-sectional data taken long after a policy has been implemented, \textcite{duflo_school_2001} for example, the duration effect is irrelevant because all educational attainment data is observed long after sample individuals have completed schooling.
 In our data, a significant proportion of individuals have not completed schooling, allowing us to have meaningful duration effects.}  In order to identify both age and duration effects with our cross-sectional data, we exploit the variation in the year of school closure.

### 2019-06-25 _other/pandoc/fansample.tex
pandoc example

\documentclass[12pt,english]{article}
\usepackage[utf8]{inputenc}

% url package
\usepackage{hyperref}

% Bibliography package
\usepackage[authordate, backend=biber]{biblatex-chicago}
\bibliography{fansample}

% Titling and Author
\title{Sandbox Testing Latex}
\author{Fan Wang (University of Houston)}
\date{\today}

\begin{document}

\maketitle

\section{Equation Test}

Inline: $\sigma_y = \sqrt{ \sum_{y} P(Y=y) \cdot \left( y - \mu_y \right)^2}$

$$\Omega^{\max} = \exp(z^{\max}) \cdot \left(\Lambda^{\max}\right)^{\alpha}$$

\begin{equation}
\label{eq:1}
\sum_{i=0}^{\infty} a_i x^i
\end{equation}

\section{Citation Testing}

\textcite{becker_human_1986} is a paper on Human Capital.

\section{URL Test}

\begin{itemize}
	\item \href{http://fanwangecon.github.io}{Fan Wang Site}
	\item \href{https://fanwangecon.github.io/CodeDynaAsset/}{Fan Wang Dynamic Asset Code Repository}
\end{itemize}

\pagebreak

\section{Pandoc}

\subsection{Install and convert Tex to Word}

For editing latex files in word.

\begin{enumerate}
	\item install pandoc: \href{https://pandoc.org/installing.html}{Pandoc Site Installation Link}
	\item open up command line
	\item \textit{cd into where tex file is}: cd \path{C:/Users/fan/Tex4Econ/_other/pandoc}
	\item \textit{run this for tex to word}: pandoc -s fansample.tex -o fansample.docx
\end{enumerate}

\subsection{Convert from Tex to Word with bibliography}

\begin{enumerate}
	\item \textit{run this for word to tex}: pandoc --bibliography=fansample.bib -o fansample.docx fansample.tex
\end{enumerate}

\subsection{Convert from back to Tex from Word}

\begin{enumerate}
	\item \textit{run this for word to tex}: pandoc -s fansample.docx -o fansampleBACKDOCX.tex
\end{enumerate}

\printbibliography

\end{document}

### 2019-06-25 _other/pandoc/fansampleBACKDOCX.tex
pandoc example

\PassOptionsToPackage{unicode=true}{hyperref} % options for packages loaded elsewhere
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provides euro and other symbols
\else % if luatex or xelatex
  \usepackage{unicode-math}
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage[]{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\usepackage{hyperref}
\hypersetup{
            pdftitle={Sandbox Testing Latex},
            pdfauthor={Fan Wang (University of Houston)},
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

% set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother

\title{Sandbox Testing Latex}
\author{Fan Wang (University of Houston)}
\date{}

\begin{document}
\maketitle

\hypertarget{equation-test}{%
\section{Equation Test}\label{equation-test}}

Inline:
\(\sigma_{y} = \sqrt{\sum_{y}^{}P(Y = y) \cdot \left( y - \mu_{y} \right)^{2}}\)

\[\Omega^{\max} = \exp(z^{\max}) \cdot \left( \Lambda^{\max} \right)^{\alpha}\]

\[\sum_{i = 0}^{\infty}a_{i}x^{i}\]

\hypertarget{citation-testing}{%
\section{Citation Testing}\label{citation-testing}}

is a paper on Human Capital.

\hypertarget{url-test}{%
\section{URL Test}\label{url-test}}

\begin{itemize}
\item
  \href{http://fanwangecon.github.io}{Fan Wang Site}
\item
  \href{https://fanwangecon.github.io/CodeDynaAsset/}{Fan Wang Dynamic
  Asset Code Repository}
\end{itemize}

\hypertarget{pandoc}{%
\section{Pandoc}\label{pandoc}}

\hypertarget{install-and-convert-tex-to-word}{%
\subsection{Install and convert Tex to
Word}\label{install-and-convert-tex-to-word}}

For editing latex files in word.

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  install pandoc: \href{https://pandoc.org/installing.html}{Pandoc Site
  Installation Link}
\item
  open up command line
\item
  \emph{cd into where tex file is}: cd
\item
  \emph{run this for tex to word}: pandoc -s fansample.tex -o
  fansample.docx
\end{enumerate}

\hypertarget{convert-from-tex-to-word-and-markdown}{%
\subsection{Convert from tex to word and
markdown}\label{convert-from-tex-to-word-and-markdown}}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  \emph{run this for tex to word}: pandoc -s fansample.tex -o
  fansample.docx
\item
  \emph{run this for tex to md}: pandoc -s fansample.tex -o fansample.md
\end{enumerate}

\hypertarget{convert-from-back-to-tex-from-word-and-markdown}{%
\subsection{Convert from back to tex from word and
markdown}\label{convert-from-back-to-tex-from-word-and-markdown}}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  run this to convert tex to word: pandoc -s fansample.tex -o
  fansample.docx
\item
  run this to convert tex to markdown: pandoc -s fansample.tex -o
  fansample.md
\end{enumerate}

\hypertarget{convert-with-bibliography}{%
\subsection{Convert with Bibliography}\label{convert-with-bibliography}}

Suppose the file pandoc --bibliography=BiblatexChinaClosureWestern.bib
-o Draft20180210.docx Draft20180210.tex

\end{document}

### 2019-06-25 _other/pandoc/fansample.tex
update pandoc instructions, more citation details.

@@
 \textcite{becker_human_1986} is a paper on Human Capital.
+Early childhood health and economic circumstances could have lasting effects on adult socioeconomic outcomes \autocite{case_lasting_2005}.\footnote{"In this article, we develop a framework for analyzing the causal effects of interventions in the presence of latent factors that could affect outcomes, even in the absence of interventions" \autocite{conti_understanding_2010}.}
 
@@
 
-For editing latex files in word.
+For editing latex files in word to benefit from tracked changes.
 
@@
 
-\subsection{Convert from back to Tex from Word}
+\subsection{Convert from Word from Tex}
 

### 2019-06-25 _other/pandoc/fansampleBACKDOCX.tex
pandoc converted to doc from updated tex

@@
 
-is a paper on Human Capital.
+Becker and Tomes (1986) is a paper on Human Capital. Early childhood
+health and economic circumstances could have lasting effects on adult
+socioeconomic outcomes (Case, Fertig, and Paxson 2005).\footnote{"In
+  this article, we develop a framework for analyzing the causal effects
+  of interventions in the presence of latent factors that could affect
+  outcomes, even in the absence of interventions" (Conti and Heckman
+  2010).}
 
@@
 
-\hypertarget{convert-from-tex-to-word-and-markdown}{%
-\subsection{Convert from tex to word and
-markdown}\label{convert-from-tex-to-word-and-markdown}}
+\hypertarget{convert-from-tex-to-word-with-bibliography}{%
+\subsection{Convert from Tex to Word with
+bibliography}\label{convert-from-tex-to-word-with-bibliography}}
 
@@
 \item
-  \emph{run this for tex to word}: pandoc -s fansample.tex -o
-  fansample.docx
-\item
-  \emph{run this for tex to md}: pandoc -s fansample.tex -o fansample.md
+  \emph{run this for word to tex}: pandoc --bibliography=fansample.bib
+  -o fansample.docx fansample.tex
 \end{enumerate}
 
-\hypertarget{convert-from-back-to-tex-from-word-and-markdown}{%
-\subsection{Convert from back to tex from word and
-markdown}\label{convert-from-back-to-tex-from-word-and-markdown}}
+\hypertarget{convert-from-word-from-tex}{%
+\subsection{Convert from Word from
+Tex}\label{convert-from-word-from-tex}}
 
@@
 \item
-  run this to convert tex to word: pandoc -s fansample.tex -o
-  fansample.docx
-\item
-  run this to convert tex to markdown: pandoc -s fansample.tex -o
-  fansample.md
+  \emph{run this for word to tex}: pandoc -s fansample.docx -o
+  fansampleBACKDOCX.tex
 \end{enumerate}
 
-\hypertarget{convert-with-bibliography}{%
-\subsection{Convert with Bibliography}\label{convert-with-bibliography}}
+Becker, Gary S, and Nigel Tomes. 1986. ``Human Capital and the Rise and
+Fall of Families.'' \emph{Journal of Labor Economics} 4 (3): S1--39.
+\url{http://ideas.repec.org/a/ucp/jlabec/v4y1986i3ps1-39.html}.
 
-Suppose the file pandoc --bibliography=BiblatexChinaClosureWestern.bib
--o Draft20180210.docx Draft20180210.tex
+Case, Anne, Angela Fertig, and Christina Paxson. 2005. ``The Lasting
+Impact of Childhood Health and Circumstance.'' \emph{Journal of Health
+Economics} 24 (2): 365--89.
+\url{https://doi.org/10.1016/j.jhealeco.2004.09.008}.
+
+Conti, Gabriella, and James J Heckman. 2010. ``Understanding the Early
+Origins of the Education--Health Gradient.'' \emph{Perspectives on
+Psychological Science} 5 (5): 585--605.
+\url{https://doi.org/10.1177/1745691610383502}.
 

### 2019-08-15 _other/tikz/timeline.tex
tikz timeline and sample latex table

\documentclass{article}

\usepackage{tikz}
\usetikzlibrary{decorations.pathreplacing}

\definecolor{myLightGray}{RGB}{191,191,191}
\definecolor{myGray}{RGB}{160,160,160}
\definecolor{myDarkGray}{RGB}{144,144,144}
\definecolor{myDarkRed}{RGB}{167,114,115}
\definecolor{myRed}{RGB}{255,58,70}
\definecolor{myGreen}{RGB}{0,255,71}

\begin{document}

\begin{tikzpicture}[scale=1]
\node[align=center] at (1,0.5) {Susceptible\\stage};
\node[align=center] at (2.25,1.85) {Time of\\infection};
\draw [thick,->] (2.25,1.4) -- (2.25,0.15);
\node[align=center] at (3.15,0.85) {Latent\\period};
\draw [thick,decorate,decoration={brace,amplitude=6pt,raise=0pt}] (2.5,0.15) -- (3.75,0.15);
\draw [thick,->] (4,0.85) -- (4,0.15);
\node[align=center] at (6.25,0.6) {Infectious period};
\draw [thick,->] (8.25,0.85) -- (8.25,0.15);
\node[align=center] at (9.15,0.5) {Immune\\stage};
\draw [thick,decorate,decoration={brace,amplitude=6pt,raise=0pt}] (4.25,0.15) -- (8,0.15);
\draw [thick,->] (0,0) -- (10,0);
\draw [thick,->] (4.6,-0.85) -- (4.6,-0.15);
\draw [thick,->] (7.65,-0.4) -- (7.65,-0.15);
\draw [thick,decorate,decoration={brace,amplitude=6pt,raise=0pt,mirror}] (4.75,-0.15) -- (7.5,-0.15);
\node[align=center] at (6.25,-0.85) {Symptomatic\\period};
\node[align=center] at (4.6,-1.3) {Onset of\\symptoms};
\end{tikzpicture}

\begin{tikzpicture}[%
    every node/.style={
        font=\footnotesize,
        text height=1ex,
        text depth=.25ex,
    },
]
% draw horizontal line   
\draw[->] (0,0) -- (8.5,0);

% draw vertical lines
\foreach \x in {0,1,...,8}{
    \draw (\x cm,3pt) -- (\x cm,0pt);
}

% place axis labels
\node[anchor=north] at (1,0) {$t-1$};
\node[anchor=north] at (4,0) {$t$};
\node[anchor=north] at (5,0) {$t$};
\node[anchor=north] at (7,0) {$t+2$};

% draw scale above
\fill[myLightGray] (1,0.25) rectangle (2,0.4);
\fill[myDarkGray] (2,0.25) rectangle (3,0.4);
\fill[myDarkRed] (3,0.25) rectangle (4,0.4);
\fill[myRed] (4,0.25) rectangle (5,0.4);
\draw[myRed,dashed,thick,-latex] (5.05,0.325) -- (6.05,0.325);

% draw scale below
\fill[myLightGray] (3,-0.4) rectangle (4,-0.55);
\fill[myGray] (4,-0.4) rectangle (5,-0.55);
\fill[myGreen] (5,-0.4) rectangle (6,-0.55);
\draw[myGreen,dashed,thick,-latex] (6.05,-0.475) -- (7.05,-0.475);

% draw curly braces and add their labels
\draw[decorate,decoration={brace,amplitude=5pt}] (3,0.45) -- (5,0.45)
    node[anchor=south,midway,above=4pt] {Training period};
\draw[decorate,decoration={brace,amplitude=5pt}] (6,-0.6) -- (5,-0.6)
    node[anchor=north,midway,below=4pt] {Testing period};

% Add Lines
\node[align=center] at (2.25,1.85) {Realization of Shocks};
\draw [thick,->] (2,1.4) -- (2,0.15);

\end{tikzpicture}

\begin{tikzpicture}
\draw (0,0) -- (13,0);
\foreach \x in {0,2,4,6,8,12,13}
  \draw (\x cm,3pt) -- (\x cm,-3pt);
\draw (0,0) node[below=3pt] (a) {$(i)$} node[above=3pt] {};
\draw (2,0) node[below=3pt] (b) {} node[above=3pt] {$(ii)$};
\draw (4,0)  node[below=3pt]  {$(iii)$} node[above=3pt] (c) {};
\draw (6,0) node[below=3pt](d) {} node[above=3pt] {$(iv)$};
\draw (8,0) node[below=3pt](e) {$(v)$} node[above=3pt] {};
\draw (12,0) node[above=3pt] (f) {$(vi)$} node[below=3pt] {};
\draw[latex-latex]
  (e.north) -- (f.north);
\draw[latex-latex,blue]
  (e.north) to[bend left] (f.north);
\draw[latex-latex,red]
  (e.north) to[out=60,in=150] (f.north);
\end{tikzpicture}\qquad
\begin{tikzpicture}
\draw (0,0) -- (13,0);
\foreach \x in {0,2,4,6,8,12,13}
  \draw (\x cm,3pt) -- (\x cm,-3pt);
\draw (0,0) node[below=3pt] (a) {$(i)$} node[above=3pt] {};
\draw (2,0) node[below=3pt] (b) {} node[above=3pt] {$(ii)$};
\draw (4,0)  node[below=3pt]  {$(iii)$} node[above=3pt] (c) {};
\draw (6,0) node[below=3pt](d) {} node[above=3pt] {$(iv)$};
\draw (8,0) node[below=3pt](e) {$(v)$} node[above=3pt] {};
\draw (12,0) node[above=3pt] (f) {$(vi)$} node[below=3pt] {};
\draw[latex-latex]
  (e.north|-f.north) -- (f.north);
\draw[latex-latex,blue]
  (e.north|-f.north) to[bend left] (f.north);
\draw[latex-latex,red]
  (e.north|-f.north) to[out=60,in=120] (f.north);
\end{tikzpicture}

\end{document}

### 2019-09-12 _support/spacing/font.tex
spacing

--- 2019-06-25 _other/pandoc/fansample.tex
@@
 % Titling and Author
-\title{Sandbox Testing Latex}
+\title{Latex Font}
 \author{Fan Wang (University of Houston)}
@@
 
-\maketitle
-
-\section{Equation Test}
-
-Inline: $\sigma_y = \sqrt{ \sum_{y} P(Y=y) \cdot \left( y - \mu_y \right)^2}$
-
-$$\Omega^{\max} = \exp(z^{\max}) \cdot \left(\Lambda^{\max}\right)^{\alpha}$$
-
-\begin{equation}
-\label{eq:1}
-\sum_{i=0}^{\infty} a_i x^i
-\end{equation}
-
-\section{Citation Testing}
-
-\textcite{becker_human_1986} is a paper on Human Capital.
-
-\section{URL Test}
-
-\begin{itemize}
-	\item \href{http://fanwangecon.github.io}{Fan Wang Site}
-	\item \href{https://fanwangecon.github.io/CodeDynaAsset/}{Fan Wang Dynamic Asset Code Repository}
-\end{itemize}
-
-\pagebreak
-
-\section{Pandoc}
-
-\subsection{Install and convert Tex to Word}
-
-For editing latex files in word.
-
-\begin{enumerate}
-	\item install pandoc: \href{https://pandoc.org/installing.html}{Pandoc Site Installation Link}
-	\item open up command line
-	\item \textit{cd into where tex file is}: cd \path{C:/Users/fan/Tex4Econ/_other/pandoc}
-	\item \textit{run this for tex to word}: pandoc -s fansample.tex -o fansample.docx
-\end{enumerate}
-
-\subsection{Convert from Tex to Word with bibliography}
-
-\begin{enumerate}
-	\item \textit{run this for word to tex}: pandoc --bibliography=fansample.bib -o fansample.docx fansample.tex
-\end{enumerate}
-
-\subsection{Convert from back to Tex from Word}
-
-\begin{enumerate}
-	\item \textit{run this for word to tex}: pandoc -s fansample.docx -o fansampleBACKDOCX.tex
-\end{enumerate}
-
-\printbibliography
+There are different font families in latex.
+\textbf{mathpazo} is a family type with nice math equations, but the texts and equations take up more space, potentially exceeding journals' submission limits.
 

### 2019-09-12 _support/spacing/reduce.tex
spacing

\documentclass[12pt,english]{article}
\usepackage[utf8]{inputenc}
\usepackage{mathptmx}

\usepackage{amsfonts}

\usepackage{listings}
\lstset{%
	basicstyle=\small\ttfamily,
	language=[LaTeX]{TeX}
}
% url package
\usepackage{hyperref}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Reduce Spacing for Title
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{titlesec}
\titlespacing\section{0pt}{2pt}{0pt}
\titlespacing\subsection{0pt}{2pt}{0pt}
\titlespacing\subsubsection{0pt}{2pt}{0pt}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Reduce Spacing for Math Equations
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\makeatletter
\g@addto@macro\normalsize{%
  \setlength\abovedisplayskip{1pt}
  \setlength\belowdisplayskip{1pt}
  \setlength\abovedisplayshortskip{1pt}
  \setlength\belowdisplayshortskip{1pt}
}

% Titling and Author
\title{Reduce Latex Spacing}
\author{Fan Wang (University of Houston)}
\date{\today}

\everypar{\looseness=-1}
\linepenalty=1000

\begin{document}\fontsize{9.5}{14}\rm

Various journals have requirements for paper lengths. Your paper is longer. How do you reduce paper length without changing much text to satisfy submission requirements? abc efg sdlfjk lsdkjf lkjdfer.

\section{Font}

Are you using a non-standard font. \textbf{mathpazo} is a family type with nice math equations, but the texts and equations take up more space, potentially exceeding journals' submission limits. Switching from mathpazo to the default font could save pages.

A good font is \textbf{mathptmx}.

also use \textbf{microtype} for fine improvements.

\section{Heading Spacing}

\href{https://tex.stackexchange.com/questions/53338/reducing-spacing-after-headings}{reducing spacing after headings}

\begin{lstlisting}
\usepackage{titlesec}
\titlespacing\section{0pt}{0pt}{0pt}
\titlespacing\subsection{0pt}{0pt}{0pt}
\titlespacing\subsubsection{0pt}{0pt}{0pt}
\end{lstlisting}

\section{Equation Spacing}

\subsection{Equation with Reduced Spacing}
Given $\mu_{R_{yv}}$, $\sigma_{R_{yv}}$, and price $p^{N}_{yv}$, each household solves the following maximization problem:
\begin{equation}
\max_{c,N} c+\rho\cdot c^{2}+  \Bigg\{ \gamma\cdot H_{24}+\lambda \cdot \int_{R_{yv}} \left(H_{24}-R_{yv}\right)\mathbb{1}\left\{ H_{24}\ge R_{yv}\right\}dF(R_{yv}) \Bigg\}
\end{equation}
where:
\[
c=Y - p^{N}_{yv} \cdot N
\]
\[
H_{24}(N,X,\epsilon)=\exp(A+ X\cdot\alpha+\epsilon)\cdot N^{\beta}
\]
The realized household utility $u_{yv}$ is a function of parameters and $Y, p^{N}_{yv}, X, F(R_{yv}),\epsilon$. Households make choices given $\Omega = \big(Y, p^{N}_{yv}, X\big)$, the i.i.d. productivity shock $\epsilon$, and $F(R_{yv})$. At the birth of a child, a household chooses the optimal amount of nutrition for the child over the next 24 months given the joint relative distribution of the reference health outcome and their own child's helath given that child's productivity shock and nutritional intake. The parents choose knowing that more nutritional intake-at a decreasing rate of return-will increase the probability that their child will catch-up to or exceed the reference health. \footnote{We assume that parents do not consider the nutritional choices of other parents for their own maximization in order to focus purely on the effect of the change in the reference point.}

\subsection{Code to Reduce Equation Spacing}
\begin{lstlisting}
\makeatletter
\g@addto@macro\normalsize{%
  \setlength\abovedisplayskip{40pt}
  \setlength\belowdisplayskip{40pt}
  \setlength\abovedisplayshortskip{40pt}
  \setlength\belowdisplayshortskip{40pt}
}
\makeatother
\begin{document}
text
\begin{gather}
  1 + 1 = 2
\end{gather}
text
\begin{equation}
  1 + 1 = 2
\end{equation}
\end{document}
\end{lstlisting}

\section{Margins}

You can change margins a little bit, but better not.

\begin{lstlisting}
\geometry{
a4paper,
noheadfoot=true,
left=1.0in,
right=1.0in,
top=1.0in,
bottom=1.0in,
}
\end{lstlisting}

\section{Paragraphs}

\begin{lstlisting}
\everypar{\looseness=-1}
\linepenalty=1000
\end{lstlisting}

\section{Figures}

\begin{lstlisting}
\renewcommand\floatpagefraction{.9}
\renewcommand\dblfloatpagefraction{.9} % for two column documents
\renewcommand\topfraction{.9}
\renewcommand\dbltopfraction{.9} % for two column documents
\renewcommand\bottomfraction{.9}
\renewcommand\textfraction{.1}   
\setcounter{totalnumber}{50}
\setcounter{topnumber}{50}
\setcounter{bottomnumber}{50}
\end{lstlisting}

\end{document}

### 2019-09-12 _support/spacing/ff_summ_percentiles.R

@@ -1,0 +1,85 @@
+ff_summ_percentiles <- function(df, col2varname = FALSE, bl_statsasrows = TRUE) {
+    #' Summarize each variable in a dataset
+    #'
+    #' @description
+    #' Generate similar statistics as what is generated by distributional statistics
+    #' calculator from dynamic asset webpage's distributional codes: \url{https://fanwangecon.github.io/CodeDynaAsset/}
+    #'
+    #' @param df dataframe input dataframe of interest
+    #' @param col2varname boolean if true drop var names
+    #' @param bl_statsasrows boolean if true then rotate table
+    #' @return a dataframe with summary statistics.
+    #' @author Fan Wang, \url{http://fanwangecon.github.io}
+    #' @references \url{https://fanwangecon.github.io/R4Econ/}
+    #' @export
+    #' @import dplyr tidyr tibble
+    #' @examples
+    #' ff_summ_percentiles(iris)
+    #' ff_summ_percentiles(iris, TRUE)
+
+    names(df) <- gsub("_", ".", names(df))
+
+    tb_summ_stats <- df %>% ungroup() %>% summarise_if(is.numeric,
+        funs(n = n(), NAobs = sum(is.na(.) == 1),
+            ZEROobs = sum(. == 0), mean = mean(.,
+                na.rm = TRUE), min = min(., na.rm = TRUE),
+            max = max(., na.rm = TRUE), sd = sd(.,
+                na.rm = TRUE), cv = sd(., na.rm = TRUE)/mean(.,
+                na.rm = TRUE), p01 = quantile(.,
+                probs = c(0.01), na.rm = TRUE), p05 = quantile(.,
+                probs = c(0.05), na.rm = TRUE), p10 = quantile(.,
+                probs = c(0.1), na.rm = TRUE), p25 = quantile(.,
+                probs = c(0.25), na.rm = TRUE), p50 = quantile(.,
+                probs = c(0.5), na.rm = TRUE), p75 = quantile(.,
+                probs = c(0.75), na.rm = TRUE), p90 = quantile(.,
+                probs = c(0.9), na.rm = TRUE), p95 = quantile(.,
+                probs = c(0.95), na.rm = TRUE), p99 = quantile(.,
+                probs = c(0.99), na.rm = TRUE))) %>%
+        gather(variable, value) %>% separate(variable,
+        c("var", "stats"), sep = "_") %>% spread(stats,
[…]

### 2019-09-12 sections_sandbox/estimate_sandbox.tex

@@
 
+\begin{table}[htbp]                                 \centering                                 \def\sym#1{\ifmmode^{#1}\else\(^{#1}\)\fi}                                 \caption{Summary Statistics Various Variables\label{summcovarmain}}                                 \begin{adjustbox}{max width=1\textwidth}                                 \begin{tabular}{m{8cm} >{\centering\arraybackslash}m{1.8cm} >{\centering\arraybackslash}m{1.8cm} >{\centering\arraybackslash}m{1.8cm} >{\centering\arraybackslash}m{1.8cm} >{\centering\arraybackslash}m{1.8cm}}                                 \toprule                                                                                         & \multicolumn{5}{C{9cm}}{Atole and Fresco Differences} \\                                                 \cmidrule(l{5pt}r{5pt}){2-6}                                                   & \multicolumn{1}{C{1.8cm}}{\small \textbf{All}} & \multicolumn{2}{C{3.6cm}}{\small \textbf{Group Averages}} & \multicolumn{2}{C{3.6cm}}{\small \textbf{p-Values Testing}} \\                                                  \cmidrule(l{5pt}r{5pt}){2-2} \cmidrule(l{5pt}r{5pt}){3-4} \cmidrule(l{5pt}r{5pt}){5-6}                                                  & \multicolumn{1}{C{1.8cm}}{\textit{\small mean (sd)}} & \multicolumn{1}{C{1.8cm}}{\textit{\small Fresco Villages}} & \multicolumn{1}{C{1.8cm}}{\textit{\small Atole Villages}} & \multicolumn{1}{C{1.8cm}}{\textit{\small Gap}} & \multicolumn{1}{C{1.8cm}}{\textit{\small P-value}} \\
+\midrule
+                                         \multicolumn{6}{L{18.8cm}}{\vspace*{-5mm}\hspace*{-5mm}\textbf{\textit{\normalsize Panel A: Gender Income Price (N=503, main sample)}}} \\                                          &            &            &            &            &            \\
+Male                &        0.52&        0.52&        0.52&       -0.00&        0.92\\
+                    &\vspace*{-2mm}{\footnotesize (0.50) }&\vspace*{-2mm}{\footnotesize (0.50) }&\vspace*{-2mm}{\footnotesize (0.50) }&            &            \\
+Income (peso)       &      515.57&      503.68&      526.00&       22.32&        0.59\\
+                    &\vspace*{-2mm}{\footnotesize (460.9) }&\vspace*{-2mm}{\footnotesize (464.4) }&\vspace*{-2mm}{\footnotesize (458.4) }&            &            \\
+Mth 15-24 Protein Price (peso/10k grams)&       52.58&       52.47&       52.68&        0.21&        0.54\\
+                    &\vspace*{-2mm}{\footnotesize (3.87) }&\vspace*{-2mm}{\footnotesize (3.93) }&\vspace*{-2mm}{\footnotesize (3.81) }&            &            \\
+\midrule
+
+\midrule
+                                         \multicolumn{6}{L{18.8cm}}{\vspace*{-5mm}\hspace*{-5mm}\textbf{\textit{\normalsize Panel B: Gender Income (N=1115, hgt observed once in first 24 months)}}} \\                                          &            &            &            &            &            \\
+Male                &        0.53&        0.53&        0.53&        0.00&        0.98\\
+                    &\vspace*{-2mm}{\footnotesize (0.50) }&\vspace*{-2mm}{\footnotesize (0.50) }&\vspace*{-2mm}{\footnotesize (0.50) }&            &            \\
+Income (peso)       &      449.49&      444.63&      454.06&        9.43&        0.72\\
+                    &\vspace*{-2mm}{\footnotesize (432.3) }&\vspace*{-2mm}{\footnotesize (446.4) }&\vspace*{-2mm}{\footnotesize (419.0) }&            &            \\
+\midrule
+
+\midrule
+                                         \multicolumn{6}{L{18.8cm}}{\vspace*{-5mm}\hspace*{-5mm}\textbf{\textit{\normalsize Panel C: Height}}} \\                                          &            &            &            &            &            \\
+Month 0 (cm)  {\footnotesize N=503}&       49.64&       49.79&       49.52&       -0.27&        0.19\\
+                    &\vspace*{-2mm}{\footnotesize (2.29) }&\vspace*{-2mm}{\footnotesize (2.29) }&\vspace*{-2mm}{\footnotesize (2.29) }&            &            \\
+Month 6 (cm)  {\footnotesize N=463}&       62.72&       62.49&       62.93&        0.44&        0.05\\
+                    &\vspace*{-2mm}{\footnotesize (2.46) }&\vspace*{-2mm}{\footnotesize (2.50) }&\vspace*{-2mm}{\footnotesize (2.42) }&            &            \\
+Month 12 (cm) {\footnotesize N=475}&       68.81&       68.45&       69.13&        0.68&        0.01\\
+                    &\vspace*{-2mm}{\footnotesize (2.99) }&\vspace*{-2mm}{\footnotesize (3.13) }&\vspace*{-2mm}{\footnotesize (2.83) }&            &            \\
+Month 18 (cm) {\footnotesize N=482}&       73.37&       72.88&       73.80&        0.92&        0.00\\
+                    &\vspace*{-2mm}{\footnotesize (3.23) }&\vspace*{-2mm}{\footnotesize (3.26) }&\vspace*{-2mm}{\footnotesize (3.15) }&            &            \\
+Month 24 (cm) {\footnotesize N=503}&       77.66&       76.94&       78.29&        1.36&        0.00\\
+                    &\vspace*{-2mm}{\footnotesize (3.47) }&\vspace*{-2mm}{\footnotesize (3.49) }&\vspace*{-2mm}{\footnotesize (3.33) }&            &            \\
+\midrule
+
+\midrule
+                                         \multicolumn{6}{L{18.8cm}}{\vspace*{-5mm}\hspace*{-5mm}\textbf{\textit{\normalsize Panel D: Average Daily Nutritional Intake}}} \\                                          &            &            &            &            &            \\
+Month 15 (grams/day) {\footnotesize N=464}&       17.43&       14.29&       20.07&        5.78&        0.00\\
+                    &\vspace*{-2mm}{\footnotesize (10.5) }&\vspace*{-2mm}{\footnotesize (9.14) }&\vspace*{-2mm}{\footnotesize (10.9) }&            &            \\
+Month 18 (grams/day) {\footnotesize N=461}&       21.52&       18.27&       24.41&        6.14&        0.00\\
+                    &\vspace*{-2mm}{\footnotesize (11.4) }&\vspace*{-2mm}{\footnotesize (9.61) }&\vspace*{-2mm}{\footnotesize (12.0) }&            &            \\
+Month 21 (grams/day) {\footnotesize N=475}&       24.45&       20.17&       27.99&        7.82&        0.00\\
+                    &\vspace*{-2mm}{\footnotesize (11.4) }&\vspace*{-2mm}{\footnotesize (9.03) }&\vspace*{-2mm}{\footnotesize (11.9) }&            &            \\
+Month 24 (grams/day) {\footnotesize N=462}&       26.99&       22.51&       31.07&        8.56&        0.00\\
+                    &\vspace*{-2mm}{\footnotesize (12.0) }&\vspace*{-2mm}{\footnotesize (9.02) }&\vspace*{-2mm}{\footnotesize (13.0) }&            &            \\
+Avg Mth 15-24 (grams/day) {\footnotesize N=503}&       22.54&       18.81&       25.80&        6.99&        0.00\\
+                    &\vspace*{-2mm}{\footnotesize (8.98) }&\vspace*{-2mm}{\footnotesize (6.43) }&\vspace*{-2mm}{\footnotesize (9.62) }&            &            \\
+Avg Mth 15-24 (kcal/day)   {\footnotesize N=503}&      691.78&      681.78&      700.55&       18.77&        0.38\\
+                    &\vspace*{-2mm}{\footnotesize (236.5) }&\vspace*{-2mm}{\footnotesize (236.2) }&\vspace*{-2mm}{\footnotesize (236.9) }&            &            \\
+\midrule
+\bottomrule
+                                                         \addlinespace[-0.5em]                                 \multicolumn{6}{L{18.8cm}}{                                                                                   \footnotesize                                         \justify                                          Summary Statistics} \\
+\end{tabular}
+\end{adjustbox}
+\end{table}
+
 \input{../fragments/cite/cite_end.tex}

### 2019-11-03 _nontex/git/g_subtree/fs_subtree.Rmd
misc repo

---
title: "Git folder within Git Folder--Git Subtree Project and Draft"
output:
  pdf_document: default
  word_document: default
  html_document: default
  html_notebook: default
urlcolor: blue
always_allow_html: yes
---

Go back to [fan](http://fanwangecon.github.io/)'s [Miscellaneous Repository](http://fanwangecon.github.io/Tex4Econ/_nontex/).

# Git subtree

**Search**

- git submodule
- Git subtree
- import subtree to existing repository
- import repo to existing repository as subtree

**Issue**

- There is a main folder, which is a git folder (code etc folder), shared in dropbox
- There is a remote repository (paper draft).
- Pull remote paper draft into git folder for whole project so remote repo for draft folder looks like a regular folder in dropbox in the shared master git repo folder with co-authors.

**Solution**

How to sync both folders properly? Traditional option is submodule, do not use that, use **subtree**, which is a standard feature for git since *v1.7.11*.

## Create subtree in existing repository

1. There is some git repository: *"C:/Users/fan/Documents/Dropbox (UH-ECON)/Project Emily Minority Survey/"*
    - make sure the repository does has been synced, no uncommited changes
2. Add remote git url for draft folder
    - *git remote add github_draft git@github.com:FanWangEcon/ChinaSchoolClosure.git*
3. Suppose folder *Drafts_RR* is not in the repository yet, create subtree under that
    - *git subtree add --prefix=Drafts_RR/ github_draft master*: pull from master branch of remote repo github_draft defined in step 2, add remote repo files to Drafts_RR folder
4. now updates in github_draft repo are synced inside the github repo. but github_draft remains independently syncable with overleaf. So overleaf does not have to be synced to much larger non-tex folder.

## Sync Subtree Changes with Folder and Sub folder.

1. make some changes in subfolder
2. sync with the github repo first, commit changes in the master folder first.
3. sync with subtre subfolder
    - *cd "C:/Users/fan/Documents/Dropbox (UH-ECON)/Project Emily Minority Survey/"*
    - *git subtree push --prefix=Drafts_RR github_draft master*

### Commands Together

```{bash, eval = FALSE}

# Project git folder in dropbox
cd "C:/Users/fan/Documents/Dropbox (UH-ECON)/Project Emily Minority Survey/Drafts_RR"

# Add new paper draft remote url to project git remote urls
# github main is project repo url, github_draft is overleaf synced folder
git remote -v
git remote add github_draft git@github.com:FanWangEcon/ChinaSchoolClosure.git
git remote -v

# Add subtree, Drafts_RR should not exist yet
git subtree add --prefix=Drafts_RR github_draft

git subtree add --prefix "C:/Users/fan/Documents/Dropbox (UH-ECON)/Project Emily Minority Survey/Drafts_RR" git@github.com:FanWangEcon/ChinaSchoolClosure.git master --squash

git subtree split --prefix=Drafts_RR/ -b ChinaSchoolClosure
Do not use submodule
```

### Console outputs

```{bash, eval = FALSE}
 $ git subtree add --prefix=Drafts_RR/ github_draft master
 git fetch github_draft master
 Enter passphrase for key '/c/Users/fan/.ssh/id_rsa':
 warning: no common commits
 remote: Enumerating objects: 235, done.
 remote: Counting objects: 100% (235/235), done.
 remote: Compressing objects: 100% (177/177), done.
 remote: Total 235 (delta 110), reused 133 (delta 50), pack-reused 0
 Receiving objects: 100% (235/235), 3.02 MiB | 3.58 MiB/s, done.
 Resolving deltas: 100% (110/110), done.
 From github.com:FanWangEcon/ChinaSchoolClosure
  * branch            master     -> FETCH_HEAD
  * [new branch]      master     -> github_draft/master
 Added dir 'Drafts_RR'
 fan@LAPTOP-55QHS6DU MINGW64 ~/Documents/Dropbox (UH-ECON)/Project Emily Minority Survey (master)
 $ ls
  Code/         Drafts/                  Images/                           notes.md        'Possible Questions and Answers.docx'   > andbox/                                  Tables/
  CodeEdccRR/   Drafts_RR/               Log/                              onenote1.pdf     presentation/                          > choolConsolidation_main_sexHan_wlt.pdf  'Tables Old'/
  comments/    'eth disparities irb'/   'Model Variables Graph Factory'/   onenote2.pdf    'R&R comments.docx'                     choolConsolidationDraft_V1.pdf
  Data/         Feedback/               'Notes and drafts, language'/      Planning.xmind   README.md                              Submissions/
  desktop.ini  'Government Documents'/  'Notes and Papers'/                policies/       'Reference papers'/                     summer2014visitors/

 fan@LAPTOP-55QHS6DU MINGW64 ~/Documents/Dropbox (UH-ECON)/Project Emily Minority Survey (master)
 $ ls Drafts_RR
 _bib/  _fig/  _tab/  draft_main.pdf  draft_main.tex  fragments/  preamble_main.tex  sections/
```

### Links

- [Git Tools - Submodules](https://git-scm.com/book/en/v2/Git-Tools-Submodules)
- [Working with submodules](https://github.blog/2016-02-01-working-with-submodules/)
- [4 Git Submodules Alternatives You Should Know](https://codeburst.io/4-git-submodules-alternatives-you-should-know-592095859b0)
- [Git subtree: the alternative to Git submodule](https://www.atlassian.com/git/tutorials/git-subtree)
    + instructions came from here
- [What is Git subtree?](https://tsh.io/blog/git-subtree-or-how-i-stopped-worrying-and-learned-to-love-external-dependencies/)
- [git subtrees: a tutorial](https://medium.com/@v/git-subtrees-a-tutorial-6ff568381844)

### 2019-11-03 _support/foothead/repage/repage_response_referee.tex
pagination and line gaps

\documentclass[12pt,english]{article}
\usepackage[utf8]{inputenc}
\usepackage{blindtext}
\usepackage{listings}
\usepackage{csquotes}

% url package
\usepackage[colorlinks = true,
            linkcolor = blue,
            urlcolor  = blue]{hyperref}

% Titling and Autho
\begin{document}

\begingroup
  \centering
  \LARGE Repage Document add Responses to Referees to End of File \\[1.5em]
  \large \href{http://fanwangecon.github.io/}{Fan Wang} (\href{http://fanwangecon.github.io/Tex4Econ}{Tex4Econ}) \\[1.5em]
  \large \today \par
\endgroup

\begin{abstract}
We paginate the main body of the file, re-paginate appendix with letter section headings, then re-paginate a post appendix section with numeric section headings. Final section could be appended file response to referees, which is included with main file to allow for consistent table and graph referencing and citations, but then should be split out as separate file afterwards.
\end{abstract}

\section{Introduction}

\paragraph{Searchs}
\begin{itemize}
  \item latex reset page number
\end{itemize}

\paragraph{Code} Core Latex

\begin{lstlisting}
  % Reset Appendix
  \pagenumbering{arabic}
  \setcounter{page}{1}
  % Reset Response to Referee
  \setcounter{section}{0}
  \renewcommand{\thesection}{\arabic{section}}
\end{lstlisting}

\paragraph{Links}
\begin{enumerate}
  \item \href{https://tex.stackexchange.com/questions/259085/restart-page-numbering-for-memoir-appendix}{Restart page numbering for memoir appendix}
\end{enumerate}

\section{Data\label{sec:data}}
\Blindtext
\section{Estimation\label{sec:esti}}
\Blindtext
\section{Conclusion}
\blindtext

\pagebreak
\clearpage

\appendix

\pagenumbering{arabic}
\setcounter{page}{1}

\section{Data Details\label{app:data}}
\blindtext
\section{Derivations}
\blindtext
\section{Robustness Checks}
\Blindtext
\pagebreak
\clearpage

\setcounter{section}{0}
\renewcommand{\thesection}{\arabic{section}}

\section{Responses to Editor}
\begin{quotation}
\textbf{AE: }\enquote{\blindtext}
\end{quotation}

In Sections \ref{sec:data} and \ref{app:data}. \blindtext

\subsection{Editor Question One}
\begin{quotation}
\textbf{AE: }\enquote{\blindtext}
\end{quotation}

\blindtext
\clearpage
\pagebreak

\section{Responses to Referee One}
\begin{quotation}
\textbf{R1: }\enquote{\blindtext}
\end{quotation}

\blindtext

\subsection{Referee One Question One}
\begin{quotation}
\textbf{R1: }\enquote{\blindtext}
\end{quotation}

\Blindtext

\subsection{Referee One Question Two}
\begin{quotation}
\textbf{R1: }\enquote{\blindtext}
\end{quotation}

\Blindtext

\end{document}

\end{document}

### 2019-11-05 template/fantemplate_basic_imgtabref/draft.tex
template file with img, table and ref and zip for overleaf

\documentclass[12pt,english]{article}

\input{fragments/preamble_packages.tex}
\input{fragments/preamble_layout.tex}
\input{fragments/preamble_citation.tex}
\bibliography{bib/ref_one, bib/ref_two}

\makeatother

\begin{document}

\title{Overleaf Package Template File}

\author{\href{http://fanwangecon.github.io/}{Fan Wang} \thanks{See \href{https://fanwangecon.github.io/Tex4Econ/}{Tex4Econ} for more latex examples.}}

\maketitle
\begin{abstract}
\singlespacing \href{https://papers.ssrn.com/sol3/papers.cfm?abstract_id=3140132}{We estimate} the impact of educational infrastructure consolidation on educational attainment using the case of China’s rural primary school closure policies in the early 2000s. The rationale for consolidation policies is that economies of scale will enable higher quality education, but distance to school increases for children in villages with school closures. We use data from a large household survey covering 728 villages in 7 provinces in China, and exploit variation in villages’ year of school closure and children’s ages at closure to identify the causal impact of school closure. For children exposed to closure during their primary school ages, we find an average decrease of 0.60 years of schooling for girls after age 15, but no significant effect for boys. Negative effects strengthen with time since closure. There is no evidence of a differential trend in educational attainment between individuals in villages with school closure and those in villages without, as indicated by an analysis using older cohorts beyond primary school age when closure occurred. Different effects by gender may be related to greater sensitivity of girls’ enrollment to distance and greater responsiveness of boys’ enrollment to quality.\end{abstract}
\vfill
\pagebreak{}

\section{Introduction}

According to \textcite{becker_human_1986}, ipsum dolor sit amet, consectetur adipiscing elit. Integer placerat nunc orci, id pellentesque lacus ullamcorper at. Mauris venenatis gravida magna non dapibus. Nullam vel consequat purus, id luctus dui. Suspendisse vel auctor nulla. Proin ipsum felis, efficitur eu eleifend vitae, efficitur pellentesque mauris \autocite{case_lasting_2005, conti_understanding_2010}.

\section{\href{https://papers.ssrn.com/sol3/papers.cfm?abstract_id=3140132}{Data}}

Village closure information is taken from a village head survey, which was collected in conjunction with household surveys. Village heads were asked if the village currently had a primary school, and asked about the year of school closure if the village school had been closed. Based on the village heads survey, there are four categories of closure status. The first category includes 193 villages that did not have village schools in 2011 and experienced school closure between 1999 and 2010. In the second category, which included 22 villages, a school closure year between 1999 and 2010 was reported, but village heads also reported that the village currently had a school in 2011. In this case, it is plausible that new schools were built in these 22 villages after school closure.\footnote{Generally students went to schools in township centers after village school closure, but in these 22 villages, it is possible that a new consolidated school was built inside these villages.} In the third category, 430 villages had village schools in 2011 and did not experience school closure.\footnote{We do not have survey information on the opening year of the schools. The vast majority of these schools should have been established in the 1980s and early 1990s when the central government aimed to have a school in each village to provide education to rural children.} Finally, the fourth category includes 48 villages that had never had a primary school and 35 that do not currently have a school but had a village primary school at some point between 1954 and 1999. In the following analysis, we designate the first and second categories as school closure. The third and fourth categories are coded as non-closure.\footnote{We will test the robustness of regression results to dropping the second and fourth categories from the closure and non-closure groups.}

\section{\href{https://papers.ssrn.com/sol3/papers.cfm?abstract_id=3167023}{Model}\label{sec:data}}

Let $\tau$ be the fraction of poorest children receiving price discounts and $\delta$ be the percentage price discount that children receive. $Z\left(\tau,\delta\right)$ is the total cost of a subsidy in grams of protein for 1970, 1972, 1974 and 1976 cohorts, given reference point distribution $\Gamma$ for each cohort:

\begin{equation}
\label{eq:targetcost}
Z\left(\tau,\delta\right) =
\sum\limits_{
	\substack{
	\mathrm{cohort} \\ \in{\left\{70,72,74,76\right\}}}
	}
\left\{\delta\cdot
\int_{\epsilon}
\int_{Y_{min}}^{F_{Y}^{-1}\left(\tau\right)}
\int_{X}
N\Big(
\substack{
	Y,X,\epsilon; \\
	\delta, \Gamma_{\mathrm{cohort}}
}
\Big)f\left(X|Y\right)f\left(Y\right)f\left(\epsilon\right)\mathrm{d}X\mathrm{d}Y\mathrm{d}\epsilon\right\}
\end{equation}

\section{\href{https://papers.ssrn.com/sol3/papers.cfm?abstract_id=3140132}{Estimation}}

In Section \ref{sec:data}, we categorized villages by their school closure status. Among the 193 villages that did not have village schools in 2011 and experienced school closure between 1999 and 2010, there were 45 villages where the closed village school was a teaching-point. Among the 430 villages that had village schools in 2011 and did not experience school closure, there were 44 villages where the village school in 2011 was a teaching-point. Teaching-point village primary schools offer up to 4 years of within-village primary education partly with the aim of reducing travel distance for students. While teaching-points might offer proximity and small-school benefits for young village students, when quality is defined  narrowly in terms of the physical facility quality and teacher qualifications, teaching-points are of lower quality compared to other primary schools. In this section, we analyze the heterogeneity of closure effects by teaching-points status.

We estimate:
\begin{singlespace}\vspace*{-\baselineskip}
	\begin{eqnarray}
	\label{eq:tp}
	E_{pvia} & = & \phi + \beta_{v}  + \rho_{pa} + \rho^{\tau}_{a} \cdot \text{TP}_{v}
	\nonumber \\
	&  & + \sum_{\tau \in \left\{0, 1\right\}}
	\left(
	\sum_{z=1}^Z \tilde{\lambda^{\tau}_{z}} \cdot \mathbb{1} \left\{ l_{z}\leq t_{i}\leq u_{z} \right\}
	\cdot c_{v}
	\right)
	\cdot \mathbb{1} \left\{ \text{TP}_{v} = \tau \right\}
	\\
	&  &
	+ X_i \cdot \gamma + X_i \cdot \text{TP}_{v} \cdot \gamma^{\tau} \nonumber\\
	&  & + \epsilon_{i}  \nonumber
	\end{eqnarray}
\end{singlespace}\noindent\ignorespaces
where $\text{TP}_v = 1$ if the village had a teaching-point school in 2011 or had a teaching-point school that was closed before 2001. Equation \ref{eq:tp} allows teaching-point villages to have differential age patterns and covariate effects.

\section{Results}

\input{"tab/tab3_fm_pna_texbody"}

Table \ref{regone} presents estimates of \(\lambda \) in Equation \ref{eq:targetcost}. The first panel presents overall results, while the sex-specific results are shown in the second and third panels. In each panel, we compare three subsets of children below age 14 against baseline group -- those between 14 and 21 at the time of school closure. Columns 1 and 2 include all individuals between 1 and 44 years of age in 2011, columns 3 and 4 restrict to individuals between 10 and 34, and columns 5 and 6 restrict further to individuals between 15 and 34 years of age. The even-numbered columns drop villages that never had a school from the villages without closure group (category 4 as defined in data section). All regressions include several individual and household controls.\footnote{All regressions include controls for households size, a dummy for if the individual is Han and a categorical variable for the relative wealth. The relative wealth variable is based on the survey question that asked households if they are better or worse off than village average. We do not have income measures for all families. The village income per capita variable shown in summary Table \ref{regone} is from the village-head survey and not based on household incomes.} All standard errors are clustered at the village-level. Column 1 contains our focal main result, other columns contain results for robustness checks which we discuss later.

\begin{figure}[h]
	\centering
	\caption{\small Effect of School Closure on Educational Attainment (Number of Grades Completed by 2011) by 15 Age-at-Closure Group.}
	\includegraphics[width=1.0\textwidth, center]{"img/GM14S2B15_cvnc_1no".png}
	\captionsetup{width=1.0\textwidth}
	\caption*{\footnotesize Each $a$--$b$ group shows impact of closure on grades completed by 2011 for children who were between $a$ and $b$ years of age at the time of school closure. These results correspond to results from column 1 of Table \ref{regone} which had 5 age-at-closure groups. \label{figoneb}}
\end{figure}

As noted earlier, school closures typically imply disruption, greater distance, and better quality school facilities for affected students. Our prior analyses showed that the impact of closure on attainment is not of short-term duration, indicating that there is limited short-term disruption effects of closure on attainment. To investigate mechanisms behind the impacts of school closure on educational attainment, we analyze how the two possible factors --  distance to school and quality of school -- are linked to enrollment status at the time of the survey. Here, we focus only on children between 5 to 12 years of age in 2011, ages at which nearly all children attend primary school in 2011.\footnote{Although previously in regressions on educational attainment we include children who were age 13 at year of closure into the group that may still attend primary school and therefore be exposed to school closure, we only include children who are in the age range that is definitely for primary school in the enrollment regression here.} For these children, we have information about distance to primary school and primary school quality.\footnote{For older individuals in the survey who are included in the earlier attainment regressions, we do not have measures for the quality of school when they were attending primary school.} We use children from both villages with and without school closure in these regressions. The data for these analyses come from columns 2 and 3 of Table \ref{figoneb}.

Primary school enrollment in 2011 is high but not full. For children at 5 years of age, the enrollment rate is 10 percent. At age 6 and 7, the enrollment rate increases to 47 percent and then 83 percent. Enrollment peaks at 94.4 percent at age 11.\footnote{After primary school, at age 13, 15 and 17, enrollment rates drops to 92, 82, and 55 percent respectively.} In the following regressions, we analyze the relationship between distance, quality and school enrollment.

We regress enrollment on distance to closest primary school and quality of these schools. Regressions control for county fixed effects, province-specific age fixed effects, village per capita income, village per capita land size, village population size, household relative wealth, the number of household members and household ethnicity. Despite the controls, the coefficients we obtain for distance to school and quality of school would not be causal if there are unobserved village-level attributes that affect enrollment and that are also correlated with distance and quality. Our inclusion of village-level controls and county fixed effects, however, seeks to reduce the risk of omitted variables bias our estimates.

\section{\href{https://papers.ssrn.com/sol3/papers.cfm?abstract_id=3316939}{Conclusion}}

In solving and estimating this model, I developed a set of solution and estimation algorithms. The solution algorithm captures the impacts of variations in the four fixed costs, three interest rates, and one collateral constraint on the household-specific feasible risky and safe asset choice sets, the average costs (returns) of borrowing (savings) across the seven credit market participation categories, and conditional and marginal asset distributions. The estimation algorithm chooses initial values for estimation by exploring the global properties of the estimation objective function through polynomial approximations. The solution and estimation algorithms can reduce estimation time by taking advantage of scalable cloud computing resources.

\pagebreak
\begingroup
\setstretch{1.0}
%\setstretch{1.1}
\setlength\bibitemsep{0pt}
\printbibliography
\endgroup
\pagebreak

\end{document}

### 2019-11-05 template/fantemplate_basic_imgtabref/tab/tab3_fm_pna_texbody.tex
template file with img, table and ref and zip for overleaf

\begin{table}[ht]                 \centering                 \caption{Effect of School Closure on Educational Attainment\label{regone}}\begin{adjustbox}{max width=1\textwidth}\begin{tabular}{m{10cm} >{\centering\arraybackslash}m{1.85cm} >{\centering\arraybackslash}m{1.85cm} >{\centering\arraybackslash}m{1.85cm} >{\centering\arraybackslash}m{1.85cm} >{\centering\arraybackslash}m{1.85cm} >{\centering\arraybackslash}m{1.85cm}}                 \toprule                                  & \multicolumn{6}{L{11.1cm}}{Outcome: grades completed by year 2011} \\                 \cmidrule(l{5pt}r{5pt}){2-7}                  & \multicolumn{2}{L{3.7cm}}{\small } & \multicolumn{2}{L{3.7cm}}{\small 10 $\le$ 2011 Age $\le$ 34} & \multicolumn{2}{L{3.7cm}}{\small  15 $\le$ 2011 Age $\le$ 34} \\                  \cmidrule(l{5pt}r{5pt}){2-3} \cmidrule(l{5pt}r{5pt}){4-5} \cmidrule(l{5pt}r{5pt}){6-7}                  & \multicolumn{1}{C{1.85cm}}{1} & \multicolumn{1}{C{1.85cm}}{2} & \multicolumn{1}{C{1.85cm}}{3} & \multicolumn{1}{C{1.85cm}}{4} & \multicolumn{1}{C{1.85cm}}{5} & \multicolumn{1}{C{1.85cm}}{6} \\         
\midrule
\multicolumn{7}{L{22.95cm}}{\vspace*{-5mm}\hspace*{-8mm}\textbf{Panel Male and Female}} \\&                     &                     &                     &                     &                     &                     \\
\vspace*{0mm}\hspace*{5mm} x Age at closure 0-5&       -0.23         &       -0.30         &                     &                     &                     &                     \\
                    &\vspace*{-2mm}{\footnotesize (0.17) }         &\vspace*{-2mm}{\footnotesize (0.19) }         &                     &                     &                     &                     \\
\vspace*{0mm}\hspace*{5mm} x Age at closure 6-9&       -0.29\sym{*}  &       -0.38\sym{**} &       -0.39\sym{**} &       -0.53\sym{***}&                     &                     \\
                    &\vspace*{-2mm}{\footnotesize (0.16) }         &\vspace*{-2mm}{\footnotesize (0.18) }         &\vspace*{-2mm}{\footnotesize (0.18) }         &\vspace*{-2mm}{\footnotesize (0.20) }         &                     &                     \\
\vspace*{0mm}\hspace*{5mm} x Age at closure 10-13&       -0.42\sym{***}&       -0.47\sym{***}&       -0.46\sym{***}&       -0.53\sym{***}&       -0.49\sym{***}&       -0.55\sym{***}\\
                    &\vspace*{-2mm}{\footnotesize (0.14) }         &\vspace*{-2mm}{\footnotesize (0.16) }         &\vspace*{-2mm}{\footnotesize (0.14) }         &\vspace*{-2mm}{\footnotesize (0.15) }         &\vspace*{-2mm}{\footnotesize (0.15) }         &\vspace*{-2mm}{\footnotesize (0.16) }         \\
\vspace*{0mm}\hspace*{5mm} x Age at closure 22-29&        0.11         &        0.18         &       0.027         &        0.12         &     -0.0062         &       0.079         \\
                    &\vspace*{-2mm}{\footnotesize (0.17) }         &\vspace*{-2mm}{\footnotesize (0.18) }         &\vspace*{-2mm}{\footnotesize (0.17) }         &\vspace*{-2mm}{\footnotesize (0.19) }         &\vspace*{-2mm}{\footnotesize (0.17) }         &\vspace*{-2mm}{\footnotesize (0.19) }         \\
\midrule
Observations        &       18804         &       15918         &       12072         &       10289         &        9998         &        8538         \\
\midrule \multicolumn{7}{L{22.95cm}}{\vspace*{-5mm}\hspace*{-8mm}\textbf{\textit{\normalsize Exclusions and controls:}}} \\  & & & & & & \\ \vspace*{0mm}\hspace*{2mm}Village FE, province-age FE and controls&         Yes         &          No         &         Yes         &          No         &         Yes         &          No         \\
\vspace*{0mm}\hspace*{2mm}Exclude villages that never had schools&         Yes         &         Yes         &         Yes         &         Yes         &         Yes         &          No         \\
\bottomrule                  \addlinespace[-0.5em]                 \multicolumn{7}{L{23.875cm}}{\footnotesize\justify\dag Includes village fixed effects, province-specific age FEs, controls for ethnicity, household size and relative household wealth.\\ \ddag Odd columns check robustness by dropping category 2 closure and category 4 non-closure status villages discussed in Section \ref{sec:data}.\\ Statistical significance:* 0.10 ** 0.05 *** 0.01. Robust standard error clustered at village level. Each column (in each panel) represents a separate regression. Compare children with different starting age of exposure (and length of exposure) to children in baseline group who should not be impacted by school closure. Columns 3 to 6 restrict regressions to subsets of individuals who are closer together in 2011 age, testing the robustness of results to excluding younger and older individuals (see Table \ref{summthree}). Regression sample includes villagers who were below 29 at year of closure for villages that experienced closure between 1999 and 2010. Individuals included in regressions from all columns are below 45 years of age in year 2011.}\\          \end{tabular}\end{adjustbox}\end{table}

### 2019-11-07 template/fantemplate_basic_roman/draft.tex
roman 12 double space template tex

--- 2019-11-05 template/fantemplate_basic_imgtabref/draft.tex
@@
 
-\begin{document}
+\begin{document}\fontsize{12}{14}\rm
 
-\title{Overleaf Package Template File}
+\title{Research Proposal Template}
 
@@
 \maketitle
-\begin{abstract}
-\singlespacing \href{https://papers.ssrn.com/sol3/papers.cfm?abstract_id=3140132}{We estimate} the impact of educational infrastructure consolidation on educational attainment using the case of China’s rural primary school closure policies in the early 2000s.
-The rationale for consolidation policies is that economies of scale will enable higher quality education, but distance to school increases for children in villages with school closures.
-We use data from a large household survey covering 728 villages in 7 provinces in China, and exploit variation in villages’ year of school closure and children’s ages at closure to identify the causal impact of school closure.
-For children exposed to closure during their primary school ages, we find an average decrease of 0.60 years of schooling for girls after age 15, but no significant effect for boys.
-Negative effects strengthen with time since closure.
-There is no evidence of a differential trend in educational attainment between individuals in villages with school closure and those in villages without, as indicated by an analysis using older cohorts beyond primary school age when closure occurred.
-Different effects by gender may be related to greater sensitivity of girls’ enrollment to distance and greater responsiveness of boys’ enrollment to quality.\end{abstract}
-\vfill
-\pagebreak{}
-
-\section{Introduction}
 
@@
 
-\section{\href{https://papers.ssrn.com/sol3/papers.cfm?abstract_id=3140132}{Data}}
-
-Village closure information is taken from a village head survey, which was collected in conjunction with household surveys.
-Village heads were asked if the village currently had a primary school, and asked about the year of school closure if the village school had been closed.
-Based on the village heads survey, there are four categories of closure status.
-The first category includes 193 villages that did not have village schools in 2011 and experienced school closure between 1999 and 2010.
-In the second category, which included 22 villages, a school closure year between 1999 and 2010 was reported, but village heads also reported that the village currently had a school in 2011.
-In this case, it is plausible that new schools were built in these 22 villages after school closure.\footnote{Generally students went to schools in township centers after village school closure, but in these 22 villages, it is possible that a new consolidated school was built inside these villages.} In the third category, 430 villages had village schools in 2011 and did not experience school closure.\footnote{We do not have survey information on the opening year of the schools.
-The vast majority of these schools should have been established in the 1980s and early 1990s when the central government aimed to have a school in each village to provide education to rural children.} Finally, the fourth category includes 48 villages that had never had a primary school and 35 that do not currently have a school but had a village primary school at some point between 1954 and 1999.
-In the following analysis, we designate the first and second categories as school closure.
-The third and fourth categories are coded as non-closure.\footnote{We will test the robustness of regression results to dropping the second and fourth categories from the closure and non-closure groups.}
-
-\section{\href{https://papers.ssrn.com/sol3/papers.cfm?abstract_id=3167023}{Model}\label{sec:data}}
+\section{\href{https://papers.ssrn.com/sol3/papers.cfm?abstract_id=3167023}{Research Design}\label{sec:design}}
 
@@
 \end{equation}
-
-\section{\href{https://papers.ssrn.com/sol3/papers.cfm?abstract_id=3140132}{Estimation}}
 
@@
 
-\section{Results}
+\section{Literature and Relevance}
 
-\input{"tab/tab3_fm_pna_texbody"}
+Village closure information is taken from a village head survey, which was collected in conjunction with household surveys.
+Village heads were asked if the village currently had a primary school, and asked about the year of school closure if the village school had been closed.
+Based on the village heads survey, there are four categories of closure status.
+The first category includes 193 villages that did not have village schools in 2011 and experienced school closure between 1999 and 2010.
+In the second category, which included 22 villages, a school closure year between 1999 and 2010 was reported, but village heads also reported that the village currently had a school in 2011.
+In this case, it is plausible that new schools were built in these 22 villages after school closure.\footnote{Generally students went to schools in township centers after village school closure, but in these 22 villages, it is possible that a new consolidated school was built inside these villages.} In the third category, 430 villages had village schools in 2011 and did not experience school closure.\footnote{We do not have survey information on the opening year of the schools.
+The vast majority of these schools should have been established in the 1980s and early 1990s when the central government aimed to have a school in each village to provide education to rural children.} Finally, the fourth category includes 48 villages that had never had a primary school and 35 that do not currently have a school but had a village primary school at some point between 1954 and 1999.
+In the following analysis, we designate the first and second categories as school closure.
+The third and fourth categories are coded as non-closure.\footnote{We will test the robustness of regression results to dropping the second and fourth categories from the closure and non-closure groups.}
+
+\section{Feasibility and Local Support}
 
@@
 
-\section{\href{https://papers.ssrn.com/sol3/papers.cfm?abstract_id=3316939}{Conclusion}}
-
-In solving and estimating this model, I developed a set of solution and estimation algorithms.
-The solution algorithm captures the impacts of variations in the four fixed costs, three interest rates, and one collateral constraint on the household-specific feasible risky and safe asset choice sets, the average costs (returns) of borrowing (savings) across the seven credit market participation categories, and conditional and marginal asset distributions.
-The estimation algorithm chooses initial values for estimation by exploring the global properties of the estimation objective function through polynomial approximations.
-The solution and estimation algorithms can reduce estimation time by taking advantage of scalable cloud computing resources.
-
 \pagebreak

### 2019-11-18 template/fantemplate_paper_rr_response/draft.tex
response to referee template

--- 2019-11-05 template/fantemplate_basic_imgtabref/draft.tex
@@
 \input{fragments/preamble_citation.tex}
+
+% Responses to Referees
+\usepackage{blindtext}
+\newcommand{\aptxspc}{1.8}
+\newcommand{\rrquote}{1.1}
+\newcommand{\rrxspc}{1.5}
+
 \bibliography{bib/ref_one, bib/ref_two}
@@
 
-\title{Overleaf Package Template File}
+\title{Paper with Response to Referee\\Multiple Sections Separate Page Numberings and Bibliography}
 
@@
 
-According to \textcite{becker_human_1986}, ipsum dolor sit amet, consectetur adipiscing elit.
+According to ipsum dolor sit amet, consectetur adipiscing elit.
 Integer placerat nunc orci, id pellentesque lacus ullamcorper at.
@@
 
+\appendix
+
+\pagenumbering{arabic}
+\setcounter{page}{1}
+
+\section{Data Details\label{app:data}}
+\blindtext
+\section{Derivations}
+\blindtext
+\section{Robustness Checks}
+\Blindtext
+\pagebreak
+\clearpage
+
+\setcounter{section}{0}
+\renewcommand{\thesection}{\arabic{section}}
+\pagenumbering{arabic}
+\setcounter{page}{1}
+
+\begin{refsection}
+\section{Responses to Editors and Referees}
+\begin{spacing}{\rrxspc}
+We appreciate the insightful questions and helpful suggestions raised by the Associate editor, referee one, and referee two and three.
+An important paper discussed related issued \autocite{becker_human_1986, case_lasting_2005}.
+\blindtext
+\end{spacing}
+
+\section{Responses to Editor}
+\begin{spacing}{\rrquote}
+\end{spacing}
+\begin{quotation}
+\textbf{AE: }\enquote{\blindtext}
+\end{quotation}
+
+In Sections \ref{sec:data} and \ref{app:data}. \blindtext
+
+\subsection{Editor Question One}
+\begin{spacing}{\rrquote}
+\begin{quotation}
+\textbf{AE: }\enquote{\blindtext}
+\end{quotation}
+\end{spacing}
+
+\begin{spacing}{\rrxspc}
+\blindtext
+\end{spacing}
+\clearpage
+\pagebreak
+
+\section{Responses to Referee One}
+\begin{spacing}{\rrquote}
+\begin{quotation}
+\textbf{R1: }\enquote{\blindtext}
+\end{quotation}
+\end{spacing}
+
+\begin{spacing}{\rrxspc}
+\blindtext
+\end{spacing}
+
+\subsection{Referee One Question One}
+\begin{spacing}{\rrquote}
+\begin{quotation}
+\textbf{R1: }\enquote{\blindtext}
+\end{quotation}
+\end{spacing}
+
+\begin{spacing}{\rrxspc}
+\Blindtext
+\end{spacing}
+
+\subsection{Referee One Question Two}
+\begin{spacing}{\rrquote}
+\begin{quotation}
+\textbf{R1: }\enquote{\blindtext}
+\end{quotation}
+\end{spacing}
+
+\begin{spacing}{\rrxspc}
+\Blindtext
+\end{spacing}
+
+\pagebreak
+\begingroup
+\setstretch{1.0}
+%\setstretch{1.1}
+\setlength\bibitemsep{0pt}
+\printbibliography[heading=subbibliography]
+\endgroup
+\pagebreak
+\end{refsection}
+
 \end{document}

### 2019-12-03 _other/tikz/fplot/functionplot.tex
tikz equations 2d linear graphs optimal allocation

\documentclass{article}

\usepackage{caption}
\usepackage{amsmath}
\usepackage{tikz}
\usepackage{pgfplots}
\usepackage{hyperref}
\usepackage{geometry}
\geometry{
	a3paper,
	noheadfoot=true,
	left=1.0in,
	right=1.0in,
	top=0.50in,
	bottom=0.50in
}
\usetikzlibrary{decorations.pathreplacing}
\usepgfplotslibrary{external}

\definecolor{myLightGray}{RGB}{191,191,191}
\definecolor{myGray}{RGB}{160,160,160}
\definecolor{myDarkGray}{RGB}{144,144,144}
\definecolor{myDarkRed}{RGB}{167,114,115}
\definecolor{myRed}{RGB}{255,58,70}
\definecolor{myGreen}{RGB}{0,255,71}

\begin{document}

\section{Tikz Four Lines}

% slopes of lines a b c d
\def\ssa{0.8}
\def\ssb{1.0}
\def\ssc{1.1}
\def\ssd{0.6}
% y-intercepts of lines a b c d
\def\iia{+1.0}
\def\iib{+0.0}
\def\iic{-1.0}
\def\iid{-1.5}
% Other parameters
\def\rescale{4}
% color definitions
\def\cla{blue}
\def\clb{black}
\def\clc{red}
\def\cld{red}

\subsection{Four Relative Allocation Lines}
\begin{tikzpicture}
    \draw[->] (-3,0) -- (4,0) node[right] {$N_m$};
    \draw[->] (0,-3) -- (0,4) node[above] {$N_{m^{\prime}}$};
    \draw[line width=0.25mm,domain=-2:4,smooth,variable=\x, \cla] plot ({\x},{\iia+\x*\ssa});
    \draw[line width=0.25mm,domain=-2:4,smooth,variable=\x, \clb] plot ({\x},{\iib+\x*\ssb});
    \draw[line width=0.25mm,domain=-2:4,smooth,variable=\x, \clc] plot ({\x},{\iic+\x*\ssc});
    \draw[line width=0.25mm,domain=-2:4,smooth,variable=\x, \cld] plot ({\x},{\iid+\x*\ssd});    
\end{tikzpicture}

\subsection{Inequality Constrained Relative Allocation $Y > 0$}
\begin{tikzpicture}
    \draw[->] (-3,0) -- (4,0) node[right] {$N_m$};
    \draw[->] (0,-3) -- (0,4) node[above] {$N_{m^{\prime}}$};
    \draw[line width=0.25mm,domain=(-\iia/\ssa):4,smooth,variable=\x, \cla] plot ({\x},{\iia+\x*\ssa});
    \draw[line width=0.25mm,domain=(-\iib/\ssb):4,smooth,variable=\x, \clb] plot ({\x},{\iib+\x*\ssb});
    \draw[line width=0.25mm,domain=(-\iic/\ssc):4,smooth,variable=\x, \clc] plot ({\x},{\iic+\x*\ssc});
    \draw[line width=0.25mm,domain=(-\iid/\ssd):4,smooth,variable=\x, \cld] plot ({\x},{\iid+\x*\ssd});
\end{tikzpicture}

\subsection{Tikz Lines Sum UP when $Y > 0$--Linear Spline}
\begin{tikzpicture}
    \draw[->] (-3,0) -- (4,0) node[right] {$N_m$};
    \draw[->] (0,-3) -- (0,4) node[above] {$N$};
    \draw[line width=0.25mm,domain=(-\iia/\ssa):4,smooth,variable=\x, \cla] plot ({\x},{(\iia+\x*\ssa)/\rescale});
    \draw[line width=0.25mm,domain=(-\iib/\ssb):4,smooth,variable=\x, \clb] plot ({\x},{((\iia+\iib)+\x*(\ssa+\ssb))/\rescale});
    \draw[line width=0.25mm,domain=(-\iic/\ssc):4,smooth,variable=\x, \clc] plot ({\x},{((\iia+\iib+\iic)+\x*(\ssa+\ssb+\ssc))/\rescale});
    \draw[line width=0.25mm,domain=(-\iid/\ssd):4,smooth,variable=\x, \cld] plot ({\x},{((\iia+\iib+\iic+\iid)+\x*(\ssa+\ssb+\ssc+\ssd))/\rescale});
\end{tikzpicture}

\subsection{Tikz Linear Spline Invert}
\begin{tikzpicture}
    \draw[->] (-3,0) -- (4,0) node[right] {$N$};
    \draw[->] (0,-3) -- (0,4) node[above] {$N_m$};
    \draw[line width=0.25mm,domain=-2:4,smooth,variable=\x, \cla] plot ({\x},{ ((\x/\rescale-\iia)/\ssa)) });
    \draw[line width=0.25mm,domain=-2:4,smooth,variable=\x, \clb] plot ({\x},{ ((\x/\rescale-\iia)/\ssa)) + ((\x/\rescale-\iib)/\ssb)) });
    \draw[line width=0.25mm,domain=-2:4,smooth,variable=\x, \clc] plot ({\x},{ ((\x/\rescale-\iia)/\ssa)) + ((\x/\rescale-\iib)/\ssb)) + ((\x/\rescale-\iic)/\ssc)) });
    \draw[line width=0.25mm,domain=-2:4,smooth,variable=\x, \cld] plot ({\x},{ ((\x/\rescale-\iia)/\ssa)) + ((\x/\rescale-\iib)/\ssb)) + ((\x/\rescale-\iic)/\ssc)) + ((\x/\rescale-\iid)/\ssd)) });
\end{tikzpicture}
\pagebreak
\pagebreak

\section{Tikz Axis}

From: \href{https://tex.stackexchange.com/questions/360229/plotting-6-linear-functions-in-one-graph}{Plotting 6 Linear functions in one graph}

\begin{tikzpicture}
    \begin{axis}[xlabel=$x$,ylabel=$y$,
    xmin=-10,xmax=10,ymin=-10,ymax=10, axis lines=center, axis equal]
        \addplot[domain=-10:10, color=blue,]{18*x-9};
        \addplot[domain=-10:10, color=red,]{-17*x+8};
        \addplot[domain=-10:10, color=yellow,]{-12*x+6};
        \addplot[domain=-10:10, color=green,]{4*x-2};
        \addplot[domain=-10:10, color=pink,]{-3*x+1};
        \addplot[domain=-10:10, color=orange,]{pi/2*x};
    \end{axis}
\end{tikzpicture}

\end{document}

### 2019-12-03 _support/reference/biblatex_basic/biblatex_test.tex
biblatex basic citation

\documentclass[12pt,english]{article}

\usepackage[colorlinks=true, linkcolor=blue, citecolor=blue, plainpages=false, pdfpagelabels=true, urlcolor=blue]{hyperref}
\usepackage[bottom]{footmisc}

\usepackage{filecontents}
% This creates a bib file called ref.bib in the same folder as the current tex file
\begin{filecontents}{ref.bib}
@article{becker_human_1986,
	title = {Human Capital and the Rise and Fall of Families},
	volume = {4},
	url = {http://ideas.repec.org/a/ucp/jlabec/v4y1986i3ps1-39.html},
	pages = {S1--39},
	number = {3},
	journaltitle = {Journal of Labor Economics},
	author = {Becker, Gary S and Tomes, Nigel},
	urldate = {2012-02-15},
	date = {1986}
}
@article{case_lasting_2005,
	title = {The lasting impact of childhood health and circumstance},
	volume = {24},
	issn = {0167-6296},
	url = {http://www.ncbi.nlm.nih.gov/pubmed/15721050},
	doi = {10.1016/j.jhealeco.2004.09.008},
	pages = {365--389},
	number = {2},
	journaltitle = {Journal of health economics},
	shortjournal = {J Health Econ},
	author = {Case, Anne and Fertig, Angela and Paxson, Christina},
	urldate = {2012-06-13},
	date = {2005-03},
	pmid = {15721050},
	keywords = {Adult, child, Child Welfare, Cohort Studies, Great Britain, Health Status Indicators, Humans, Social Class}
}
@article{conti_understanding_2010,
	title = {Understanding the Early Origins of the Education–Health Gradient},
	volume = {5},
	issn = {1745-6916, 1745-6924},
	url = {http://pps.sagepub.com/content/5/5/585.abstract},
	doi = {10.1177/1745691610383502},
	pages = {585--605},
	number = {5},
	journaltitle = {Perspectives on Psychological Science},
	author = {Conti, Gabriella and Heckman, James J},
	urldate = {2012-02-16},
	date = {2010-09-01},
	keywords = {health, education, genetics, treatment effects}
}
\end{filecontents}

\usepackage[authordate,
backend=bibtex,
doi=false,
isbn=false,
sorting=nyt,
maxbibnames=10,
maxcitenames=3,
sortcites=False]{biblatex-chicago}
\bibliography{ref}

\begin{document}

\title{Basic Bibliography and Reference Testing}
\author{\href{http://fanwangecon.github.io/}{Fan Wang} \thanks{See \href{https://fanwangecon.github.io/Tex4Econ/}{Tex4Econ} for more latex examples.}}

\maketitle

According to \textcite{becker_human_1986}, ipsum dolor sit amet, consectetur adipiscing elit. Integer placerat nunc orci, id pellentesque lacus ullamcorper at. Mauris venenatis gravida magna non dapibus. Nullam vel consequat purus, id luctus dui. Suspendisse vel auctor nulla. Proin ipsum felis, efficitur eu eleifend vitae, efficitur pellentesque mauris \autocite{case_lasting_2005, conti_understanding_2010}.

\paragraph{\href{https://papers.ssrn.com/sol3/papers.cfm?abstract_id=3140132}{Data}}

Village closure information is taken from a village head survey, which was collected in conjunction with household surveys. Village heads were asked if the village currently had a primary school, and asked about the year of school closure if the village school had been closed. Based on the village heads survey, there are four categories of closure status. The first category includes 193 villages that did not have village schools in 2011 and experienced school closure between 1999 and 2010. In the second category, which included 22 villages, a school closure year between 1999 and 2010 was reported, but village heads also reported that the village currently had a school in 2011. In this case, it is plausible that new schools were built in these 22 villages after school closure.\footnote{Generally students went to schools in township centers after village school closure, but in these 22 villages, it is possible that a new consolidated school was built inside these villages.}

\pagebreak
\begingroup
%\setstretch{1.1}
\setlength\bibitemsep{0pt}
\printbibliography
\endgroup
\pagebreak

\end{document}

### 2019-12-03 _support/reference/labelref/labelref_test.tex
references differ hyperlinks by sections

--- 2019-12-03 _support/reference/biblatex_basic/biblatex_test.tex
@@
 
+\usepackage{setspace}
 \usepackage[colorlinks=true, linkcolor=blue, citecolor=blue, plainpages=false, pdfpagelabels=true, urlcolor=blue]{hyperref}
 \usepackage[bottom]{footmisc}
+\usepackage{blindtext}
 
@@
 	date = {1986}
-}
-@article{case_lasting_2005,
-	title = {The lasting impact of childhood health and circumstance},
-	volume = {24},
-	issn = {0167-6296},
-	url = {http://www.ncbi.nlm.nih.gov/pubmed/15721050},
-	doi = {10.1016/j.jhealeco.2004.09.008},
-	pages = {365--389},
-	number = {2},
-	journaltitle = {Journal of health economics},
-	shortjournal = {J Health Econ},
-	author = {Case, Anne and Fertig, Angela and Paxson, Christina},
-	urldate = {2012-06-13},
-	date = {2005-03},
-	pmid = {15721050},
-	keywords = {Adult, child, Child Welfare, Cohort Studies, Great Britain, Health Status Indicators, Humans, Social Class}
 }
@@
 \maketitle
+\begin{abstract}
+\singlespacing In this \href{https://papers.ssrn.com/sol3/papers.cfm?abstract_id=3140132}{paper}, we look at how to reference sections and reference section page numbers.
+And we also include in the bibliography links to on which page the references were mentioned.
+Hyperref is used to show links in subsections in different ways, some clickable, some not.\end{abstract}
+\vfill
+\pagebreak{}
+
+\maketitle
 
@@
 Suspendisse vel auctor nulla.
-Proin ipsum felis, efficitur eu eleifend vitae, efficitur pellentesque mauris \autocite{case_lasting_2005, conti_understanding_2010}.
+Proin ipsum felis, efficitur eu eleifend vitae, efficitur pellentesque mauris \autocite{becker_human_1986}.
 
@@
 
+\section{Introduction\label{sec:intro}}
+\blindtext\footnote{\autocite{conti_understanding_2010}}.
+
+\section{Data\label{sec:data}}
+\Blindtext
+
+\section{Estimation\label{sec:estimate}}
+\Blindtext
+
+\section{Conclusion\label{sec:conclude}}
+
+In Section \ref{sec:intro} (Page \pageref{sec:intro}), we introduced the paper.
+In Section \ref{sec:data} (Page \pageref{sec:data}), we discussed the data.
+In Section \ref{sec:estimate} (Page \pageref{sec:estimate}), we discussed the estimation results.
+\blindtext
+
+\pagebreak
+\appendix
+
+\section{References here not Colored or Linked}
+\begingroup
+{\hypersetup{hidelinks=true}
+Now we change settings for the appendix, so that the page numbers do not light up. Earlier they did.
+
+In Section \ref{sec:intro} (Page \pageref{sec:intro}), we introduced the paper.
+In Section \ref{sec:data} (Page \pageref{sec:data}), we discussed the data.
+In Section \ref{sec:estimate} (Page \pageref{sec:estimate}), we discussed the estimation results.
+}
+\endgroup
+
+\section{References here have Red Color}
+\begingroup
+{\hypersetup{colorlinks=true, linkcolor=red, citecolor=red, plainpages=false, pdfpagelabels=true, urlcolor=red}
+	Now we change settings for the appendix, so that the page numbers do not light up. Earlier they did.
+	In Section \ref{sec:intro} (Page \pageref{sec:intro}), we introduced the paper.
+In Section \ref{sec:data} (Page \pageref{sec:data}), we discussed the data.
+In Section \ref{sec:estimate} (Page \pageref{sec:estimate}), we discussed the estimation results.
+For more help on the hyperref package's options, see: \href{http://mirror.utexas.edu/ctan/macros/latex/contrib/hyperref/doc/options.pdf}{hyperref package options}.
+}
+\endgroup
+
 \pagebreak

### 2019-12-08 _other/tikz/fplot/functionplot.tex
Completed Inverting Linear Spline

@@
 
+\usepackage{multicol}
 \usepackage{caption}
@@
 	right=1.0in,
-	top=0.50in,
-	bottom=0.50in
+	top=1.0in,
+	bottom=1.0in
 }
@@
 
-\section{Tikz Four Lines}
-
-% slopes of lines a b c d
+%%%%%%%%%%%%%%%%%%%%%
+%%% Line Values
+%%%%%%%%%%%%%%%%%%%%%
+% A. slopes of lines a b c d
 \def\ssa{0.8}
@@
 \def\ssd{0.6}
-% y-intercepts of lines a b c d
+% B. y-intercepts of lines a b c d
 \def\iia{+1.0}
@@
 \def\rescale{4}
-% color definitions
+
+%%%%%%%%%%%%%%%%%%%%%
+%%% Line Formatting
+%%%%%%%%%%%%%%%%%%%%%
+% A. color definitions
 \def\cla{blue}
@@
 \def\clc{red}
-\def\cld{red}
+\def\cld{green}
+
+%%%%%%%%%%%%%%%%%%%%%
+%%% Draw Lines
+%%%%%%%%%%%%%%%%%%%%%
+\begin{multicols}{3}
+[
+\section{Tikz Four Lines}
+Draw four lines, sum them up linear spline, then invert
+]
 
@@
 
-\subsection{Inequality Constrained Relative Allocation $Y > 0$}
+\subsection{Inequality Constrained $Y > 0$}
 \begin{tikzpicture}
@@
 
-\subsection{Tikz Lines Sum UP when $Y > 0$--Linear Spline}
+\subsection{Sum $Y > 0$}
 \begin{tikzpicture}
@@
     \draw[->] (0,-3) -- (0,4) node[above] {$N$};
-    \draw[line width=0.25mm,domain=(-\iia/\ssa):4,smooth,variable=\x, \cla] plot ({\x},{(\iia+\x*\ssa)/\rescale});
-    \draw[line width=0.25mm,domain=(-\iib/\ssb):4,smooth,variable=\x, \clb] plot ({\x},{((\iia+\iib)+\x*(\ssa+\ssb))/\rescale});
-    \draw[line width=0.25mm,domain=(-\iic/\ssc):4,smooth,variable=\x, \clc] plot ({\x},{((\iia+\iib+\iic)+\x*(\ssa+\ssb+\ssc))/\rescale});
-    \draw[line width=0.25mm,domain=(-\iid/\ssd):4,smooth,variable=\x, \cld] plot ({\x},{((\iia+\iib+\iic+\iid)+\x*(\ssa+\ssb+\ssc+\ssd))/\rescale});
+    \draw[line width=0.25mm,domain=(-\iia/\ssa):4,smooth,variable=\x, \cla] 
+        plot ({\x},{(\iia+\x*\ssa)});
+    \draw[line width=0.25mm,domain=(-\iib/\ssb):4,smooth,variable=\x, \clb] 
+        plot ({\x},{((\iia+\iib)+\x*(\ssa+\ssb))});
+    \draw[line width=0.25mm,domain=(-\iic/\ssc):4,smooth,variable=\x, \clc] 
+        plot ({\x},{((\iia+\iib+\iic)+\x*(\ssa+\ssb+\ssc))});
+    \draw[line width=0.25mm,domain=(-\iid/\ssd):4,smooth,variable=\x, \cld] 
+        plot ({\x},{((\iia+\iib+\iic+\iid)+\x*(\ssa+\ssb+\ssc+\ssd))});
 \end{tikzpicture}
 
-\subsection{Tikz Linear Spline Invert}
+\subsection{Sum $Y > 0$ Rescale}
+\begin{tikzpicture}
+    \draw[->] (-3,0) -- (4,0) node[right] {$N_m$};
+    \draw[->] (0,-3) -- (0,4) node[above] {$N$};
+    \draw[line width=0.25mm,domain=(-\iia/\ssa):4,smooth,variable=\x, \cla] 
+        plot ({\x},{(\iia+\x*\ssa)/\rescale});
+    \draw[line width=0.25mm,domain=(-\iib/\ssb):4,smooth,variable=\x, \clb] 
+        plot ({\x},{((\iia+\iib)+\x*(\ssa+\ssb))/\rescale});
+    \draw[line width=0.25mm,domain=(-\iic/\ssc):4,smooth,variable=\x, \clc] 
+        plot ({\x},{((\iia+\iib+\iic)+\x*(\ssa+\ssb+\ssc))/\rescale});
+    \draw[line width=0.25mm,domain=(-\iid/\ssd):4,smooth,variable=\x, \cld] 
+        plot ({\x},{((\iia+\iib+\iic+\iid)+\x*(\ssa+\ssb+\ssc+\ssd))/\rescale});
+\end{tikzpicture}
+
+\subsection{$Y > 0$--Linear Spline}
+\begin{tikzpicture}
+    \draw[->] (-3,0) -- (4,0) node[right] {$N_m$};
+    \draw[->] (0,-3) -- (0,4) node[above] {$N$};
+    \draw[line width=0.25mm,domain=(-\iia/\ssa):(-\iib/\ssb),smooth,variable=\x, \cla] 
+        plot ({\x},{(\iia+\x*\ssa)/\rescale});
+    \draw[line width=0.25mm,domain=(-\iib/\ssb):(-\iic/\ssc),smooth,variable=\x, \clb] 
+        plot ({\x},{((\iia+\iib)+\x*(\ssa+\ssb))/\rescale});
+    \draw[line width=0.25mm,domain=(-\iic/\ssc):(-\iid/\ssd),smooth,variable=\x, \clc] 
+        plot ({\x},{((\iia+\iib+\iic)+\x*(\ssa+\ssb+\ssc))/\rescale});
+    \draw[line width=0.25mm,domain=(-\iid/\ssd):4,smooth,variable=\x, \cld] 
+        plot ({\x},{((\iia+\iib+\iic+\iid)+\x*(\ssa+\ssb+\ssc+\ssd))/\rescale});
+\end{tikzpicture}
+
+% (((\iia+\iib)+((-\iib/\ssb))*(\ssa+\ssb))/\rescale)
+\subsection{Summed Lines Invert}
 \begin{tikzpicture}
@@
     \draw[->] (0,-3) -- (0,4) node[above] {$N_m$};
-    \draw[line width=0.25mm,domain=-2:4,smooth,variable=\x, \cla] plot ({\x},{ ((\x/\rescale-\iia)/\ssa)) });
-    \draw[line width=0.25mm,domain=-2:4,smooth,variable=\x, \clb] plot ({\x},{ ((\x/\rescale-\iia)/\ssa)) + ((\x/\rescale-\iib)/\ssb)) });
-    \draw[line width=0.25mm,domain=-2:4,smooth,variable=\x, \clc] plot ({\x},{ ((\x/\rescale-\iia)/\ssa)) + ((\x/\rescale-\iib)/\ssb)) + ((\x/\rescale-\iic)/\ssc)) });
-    \draw[line width=0.25mm,domain=-2:4,smooth,variable=\x, \cld] plot ({\x},{ ((\x/\rescale-\iia)/\ssa)) + ((\x/\rescale-\iib)/\ssb)) + ((\x/\rescale-\iic)/\ssc)) + ((\x/\rescale-\iid)/\ssd)) });
-\end{tikzpicture}
-\pagebreak
-\pagebreak
-
-\section{Tikz Axis}
-
-From: \href{https://tex.stackexchange.com/questions/360229/plotting-6-linear-functions-in-one-graph}{Plotting 6 Linear functions in one graph}
-
-\begin{tikzpicture}
-    \begin{axis}[xlabel=$x$,ylabel=$y$,
-    xmin=-10,xmax=10,ymin=-10,ymax=10, axis lines=center, axis equal]
-        \addplot[domain=-10:10, color=blue,]{18*x-9};
-        \addplot[domain=-10:10, color=red,]{-17*x+8};
-        \addplot[domain=-10:10, color=yellow,]{-12*x+6};
-        \addplot[domain=-10:10, color=green,]{4*x-2};
-        \addplot[domain=-10:10, color=pink,]{-3*x+1};
-        \addplot[domain=-10:10, color=orange,]{pi/2*x};
-    \end{axis}
+    \clip (-3,-3) rectangle (7,4);
+    \draw[line width=0.25mm,
+            domain=((\iia+(-\iia/\ssa)*\ssa)/\rescale):4,
+            smooth,variable=\x, \cla]
+        plot ({\x},{ ((\x*\rescale-\iia)/\ssa)});
+    \draw[line width=0.25mm,
+            domain=(((\iia+\iib)+(-\iib/\ssb)*(\ssa+\ssb))/\rescale):4,
+            smooth,variable=\x, \clb]
+        plot ({\x},{ ((\x*\rescale-(\iia+\iib))/(\ssa+\ssb)) });
+    \draw[line width=0.25mm,
+            domain=(((\iia+\iib+\iic)+(-\iic/\ssc)*(\ssa+\ssb+\ssc))/\rescale):4,
+            smooth,variable=\x, \clc]
+        plot ({\x},{ ((\x*\rescale-(\iia+\iib+\iic))/(\ssa+\ssb+\ssc)) });
+    \draw[line width=0.25mm,
+            domain=(((\iia+\iib+\iic+\iid)+(-\iid/\ssd)*(\ssa+\ssb+\ssc+\ssd))/\rescale):4,
+            smooth,variable=\x, \cld]
+        plot ({\x},{ ((\x*\rescale-(\iia+\iib+\iic+\iid))/(\ssa+\ssb+\ssc+\ssd)) });
 \end{tikzpicture}
 
+\subsection{Spline Invert}
+\begin{tikzpicture}
+    \draw[->] (-3,0) -- (4,0) node[right] {$N$};
+    \draw[->] (0,-3) -- (0,4) node[above] {$N_m$};
+    \clip (-3,-3) rectangle (7,4);
+    \draw[line width=0.25mm,
+            domain=((\iia+(-\iia/\ssa)*\ssa)/\rescale):(((\iia+\iib)+(-\iib/\ssb)*(\ssa+\ssb))/\rescale),
+            smooth,variable=\x, \cla]
+        plot ({\x},{ ((\x*\rescale-\iia)/\ssa)});
+    \draw[line width=0.25mm,
+            domain=(((\iia+\iib)+(-\iib/\ssb)*(\ssa+\ssb))/\rescale):(((\iia+\iib+\iic)+(-\iic/\ssc)*(\ssa+\ssb+\ssc))/\rescale),
+            smooth,variable=\x, \clb]
+        plot ({\x},{ ((\x*\rescale-(\iia+\iib))/(\ssa+\ssb)) });
+    \draw[line width=0.25mm,
+            domain=(((\iia+\iib+\iic)+(-\iic/\ssc)*(\ssa+\ssb+\ssc))/\rescale):(((\iia+\iib+\iic+\iid)+(-\iid/\ssd)*(\ssa+\ssb+\ssc+\ssd))/\rescale),
+            smooth,variable=\x, \clc]
+        plot ({\x},{ ((\x*\rescale-(\iia+\iib+\iic))/(\ssa+\ssb+\ssc)) });
+    \draw[line width=0.25mm,
+            domain=(((\iia+\iib+\iic+\iid)+(-\iid/\ssd)*(\ssa+\ssb+\ssc+\ssd))/\rescale):4,
+            smooth,variable=\x, \cld]
+        plot ({\x},{ ((\x*\rescale-(\iia+\iib+\iic+\iid))/(\ssa+\ssb+\ssc+\ssd)) });
+\end{tikzpicture}
+
+\end{multicols}
+
 \end{document}

### 2019-12-09 _other/tikz/fplot/functionplot.tex
tikz example for relative positioning

@@
 \definecolor{myGreen}{RGB}{0,255,71}
+
+% Titling and Author
+\title{Latex Tikz Test, Linear Equation Plotting, Linear Spline}
+\author{\href{https://fanwangecon.github.io/}{Fan Wang}\thanks{https://fanwangecon.github.io, repository: \href{https://fanwangecon.github.io/Tex4Econ/}{Tex4Econ}}}
+\date{\today}
 
@@
 \section{Tikz Four Lines}
-Draw four lines, sum them up linear spline, then invert
+Draw four lines, sum them up linear spline, then invert.
+A3 page has 29.7 cm width.
+Below, width is 7 cm for each plot, so 21 cm all together generally.
+Margins are 1 inch on each side, so about 5 cm together.
 ]

### 2019-12-09 _other/tikz/positioning/fs_tikz_position.tex
tikz example for relative positioning

\documentclass{article}

\usepackage{blindtext}
\usepackage{multicol}
\usepackage{caption}
\usepackage{amsmath}
\usepackage{tikz}
\usepackage{pgfplots}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=cyan,
}
\usepackage{geometry}
\geometry{
	a4paper,
	noheadfoot=true,
	left=1.0in,
	right=1.0in,
	top=1.0in,
	bottom=1.0in
}

% url package
\usepackage{hyperref}

% Titling and Author
\title{Latex Tikz Test, Relative Position on Page and Alignment}
\author{\href{https://fanwangecon.github.io/}{Fan Wang}\thanks{https://fanwangecon.github.io, repository: \href{https://fanwangecon.github.io/Tex4Econ/}{Tex4Econ}}}
\date{\today}

\begin{document}

\maketitle

\section{Relative Positioning}

\subsection{First line}
Using the code below, we draw from $x=0$ and $y=0$, to $x=1$ and $y=2$, the second point:
\begin{verbatim}
\draw (0,0) --(1,2);
\end{verbatim}
\bigskip
\begin{tikzpicture}
\draw (0,0) --(1,2);
\end{tikzpicture}

\subsection{Center Align Half Width Lines}
For lines below, we draw several partial page lines and align to page center:
\begin{verbatim}
\begin{center}
\begin{tikzpicture}
\draw (0,2) -- (0.25*\textwidth,2);
\draw (0,1) -- (0.5*\textwidth,1);
\end{tikzpicture}
\end{center}
\end{verbatim}
\bigskip
\begin{center}
\begin{tikzpicture}
\draw (0,2) -- (0.25*\textwidth,2);
\draw (0,1) -- (0.5*\textwidth,1);
\end{tikzpicture}
\end{center}

\subsection{Big line that fills page within margin}
Tikz coordinates are in cm. On A4 page, we have $21.0$ cm width by $29.7$ cm height. Each inch is $2.54$ cm. So with $1.0$ cm border on the left and on the right, we have $21-2.54\cdot2=15.92$, $15.92$ cm.
For lines below, we draw several full and partial page width lines:
\begin{verbatim}
\begin{center}
\begin{tikzpicture}
\draw (0,6) -- (7,6);
\draw (0,5) -- (15.92,5);
\draw (0,4) -- (0.45*\textwidth,4);
\draw (0,3) -- (0.5*\textwidth,3);
\draw (0,2) -- (0.9*\textwidth,2);
\draw (0,1) -- (\textwidth,1);
\end{tikzpicture}
\end{center}
\end{verbatim}
Note that we center the lines. Centering does not disrupt the coordinates, but just places entire tikz in the middle of page considering all plotted lines
\bigskip
\begin{center}
\begin{tikzpicture}
\draw (0,6) -- (7,6);
\draw (0,5) -- (15.92,5);
\draw (0,4) -- (0.45*\textwidth,4);
\draw (0,3) -- (0.5*\textwidth,3);
\draw (0,2) -- (0.9*\textwidth,2);
\draw (0,1) -- (\textwidth,1);
\end{tikzpicture}
\end{center}

\bigskip
For additional, information, see \href{https://tex.stackexchange.com/questions/58292/a-line-of-length-textwidth-in-tikz}{A line of length textwidth in TikZ}

\subsection{Box in the Middle of Page}
Now draw half width relative position box in the middle of pageFor lines below, we draw several full and partial page width lines:
\begin{verbatim}
\begin{center}
\begin{tikzpicture}
\draw (0,0) -- 
(0,0.5*\textwidth) -- 
(0.5*\textwidth, 0.5*\textwidth) -- 
(0.5*\textwidth, 0) -- (0, 0);
\end{tikzpicture}
\end{center}
\end{verbatim}
Note that the box is centered.
\bigskip
\begin{center}
\begin{tikzpicture}
\draw (0,0) -- (0,0.5*\textwidth) -- (0.5*\textwidth, 0.5*\textwidth) -- (0.5*\textwidth, 0) -- (0, 0);
\end{tikzpicture}
\end{center}

\end{document}

### 2019-12-22 _other/tikz/annotate/fs_tikz_annotate.tex
layout, multi-line, etc

--- 2019-12-09 _other/tikz/positioning/fs_tikz_position.tex
@@
 \usepackage{caption}
-\usepackage{amsmath}
+\usepackage{bm}
 \usepackage{tikz}
@@
 \usepackage{hyperref}
+\usepackage{subcaption}
 
 % Titling and Author
-\title{Latex Tikz Test, Relative Position on Page and Alignment}
+\title{Latex Tikz Examples, Annotate on Graph}
 \author{\href{https://fanwangecon.github.io/}{Fan Wang}\thanks{https://fanwangecon.github.io, repository: \href{https://fanwangecon.github.io/Tex4Econ/}{Tex4Econ}}}
@@
 
-\section{Relative Positioning}
+\section{Annotate Text in Figure}
 
-\subsection{First line}
-Using the code below, we draw from $x=0$ and $y=0$, to $x=1$ and $y=2$, the second point:
-\begin{verbatim}
-\draw (0,0) --(1,2);
-\end{verbatim}
-\bigskip
-\begin{tikzpicture}
-\draw (0,0) --(1,2);
-\end{tikzpicture}
+\subsection{Slope and Intercept Annotate}
 
-\subsection{Center Align Half Width Lines}
-For lines below, we draw several partial page lines and align to page center:
+Draw axis below, and a line, middle of page, and annotate the slope of the intercept with arrows. Annotate with box without color.
+
 \begin{verbatim}
@@
 \begin{tikzpicture}
-\draw (0,2) -- (0.25*\textwidth,2);
-\draw (0,1) -- (0.5*\textwidth,1);
-\end{tikzpicture}
-\end{center}
+\draw[->] (-1,0) -- (6,0) node[right] {$N_m$};
+\draw[->] (0,-1) -- (0,6) node[above] {$N_{m^{\prime}}$};
 
-\subsection{Big line that fills page within margin}
-Tikz coordinates are in cm.
-On A4 page, we have $21.0$ cm width by $29.7$ cm height.
-Each inch is $2.54$ cm.
-So with $1.0$ cm border on the left and on the right, we have $21-2.54\cdot2=15.92$, $15.92$ cm.
-For lines below, we draw several full and partial page width lines:
-\begin{verbatim}
-\begin{center}
-\begin{tikzpicture}
-\draw (0,6) -- (7,6);
-\draw (0,5) -- (15.92,5);
-\draw (0,4) -- (0.45*\textwidth,4);
-\draw (0,3) -- (0.5*\textwidth,3);
-\draw (0,2) -- (0.9*\textwidth,2);
-\draw (0,1) -- (\textwidth,1);
-\end{tikzpicture}
-\end{center}
-\end{verbatim}
-Note that we center the lines. Centering does not disrupt the coordinates, but just places entire tikz in the middle of page considering all plotted lines
-\bigskip
-\begin{center}
-\begin{tikzpicture}
-\draw (0,6) -- (7,6);
-\draw (0,5) -- (15.92,5);
-\draw (0,4) -- (0.45*\textwidth,4);
-\draw (0,3) -- (0.5*\textwidth,3);
-\draw (0,2) -- (0.9*\textwidth,2);
-\draw (0,1) -- (\textwidth,1);
-\end{tikzpicture}
-\end{center}
+% A. Clip area so that line below is only drawn inside finite box
+\clip (-3,-1) rectangle (6,6);
 
-\bigskip
-For additional, information, see \href{https://tex.stackexchange.com/questions/58292/a-line-of-length-textwidth-in-tikz}{A line of length textwidth in TikZ}
+% B. Draw a line with intercept and slope
+\draw[line width=0.50mm,domain=-1:6,smooth,variable=\x, blue] plot ({\x},{1+\x*1.25});
 
-\subsection{Box in the Middle of Page}
-Now draw half width relative position box in the middle of pageFor lines below, we draw several full and partial page width lines:
-\begin{verbatim}
-\begin{center}
-\begin{tikzpicture}
-\draw (0,0) -- 
-(0,0.5*\textwidth) -- 
-(0.5*\textwidth, 0.5*\textwidth) -- 
-(0.5*\textwidth, 0) -- (0, 0);
-\end{tikzpicture}
-\end{center}
-\end{verbatim}
-Note that the box is centered.
-\bigskip
-\begin{center}
-\begin{tikzpicture}
-\draw (0,0) -- (0,0.5*\textwidth) -- (0.5*\textwidth, 0.5*\textwidth) -- (0.5*\textwidth, 0) -- (0, 0);
+% C. Draw Line pointing to Intercept of line
+\draw[->, line width=0.75mm] (-1.7,2.2) -- (-0.1,1.1);
+
+% D. Draw a transparent text box that wraps text
+\node[text width=3cm] at (-1.4,3.25) {\large{$\bm{\alpha_i}$ (this is the position of the \textbf{x-intercept}), wrap text.}};
+
 \end{tikzpicture}

### 2019-12-22 _other/tikz/positioning/fs_tikz_position.tex
layout, multi-line, etc

@@
 \usepackage{hyperref}
+\usepackage{subcaption}
 
 % Titling and Author
-\title{Latex Tikz Test, Relative Position on Page and Alignment}
+\title{Latex Tikz Examples, Relative Position on Page and Alignment}
 \author{\href{https://fanwangecon.github.io/}{Fan Wang}\thanks{https://fanwangecon.github.io, repository: \href{https://fanwangecon.github.io/Tex4Econ/}{Tex4Econ}}}
@@
 
+\subsection{Four Boxes Same Page in Larger Box}
+There are four plots that I would like to draw together, four panels of tikz. We are defining height and width by textwidth, in this case textwidth is the width of each subfigure.
+
+\begin{itemize}
+    \item tikz page panels subplots
+    \item latex subfigure
+\end{itemize}
+
+\begin{verbatim}
+\def\fhratio{0.50}
+\def\fwratio{1.0}
+\begin{subfigure}[b]{0.49\textwidth}
+    \begin{center}
+    \begin{tikzpicture}
+    \draw (0,0) -- 
+        (0,\fhratio*\textwidth) -- 
+        (\fwratio*\textwidth, \fhratio*\textwidth) -- 
+        (\fwratio*\textwidth, 0) -- (0, 0);
+    \draw 
+        (0.3*\fwratio*\textwidth,0.3*\fhratio*\textwidth) -- 
+        (0.7*\fwratio*\textwidth,0.7*\fhratio*\textwidth);
+    \end{tikzpicture}
+    \end{center}
+    \caption{Panel A}
+    \label{fig:panela}
+\end{subfigure}
+\end{figure}
+\end{verbatim}
+Repeat this four timnes in a figure:
+\def\fhratio{0.50}
+\def\fwratio{1.0}
+\begin{figure}[h]
+    \centering
+    \begin{subfigure}[b]{0.49\textwidth}
+        \begin{center}
+        \begin{tikzpicture}
+        \draw (0,0) -- (0,\fhratio*\textwidth) -- (\fwratio*\textwidth, \fhratio*\textwidth) -- (\fwratio*\textwidth, 0) -- (0, 0);
+        \draw (0.3*\fwratio*\textwidth,0.3*\fhratio*\textwidth) --(0.7*\fwratio*\textwidth,0.7*\fhratio*\textwidth);
+        \end{tikzpicture}
+        \end{center}
+        \caption{Panel A}
+        \label{fig:panela}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.49\textwidth}
+        \begin{center}
+        \begin{tikzpicture}
+        \draw (0,0) -- (0,\fhratio*\textwidth) -- (\fwratio*\textwidth, \fhratio*\textwidth) -- (\fwratio*\textwidth, 0) -- (0, 0);
+        \draw (0.3*\fwratio*\textwidth,0.3*\fhratio*\textwidth) --(0.7*\fwratio*\textwidth,0.7*\fhratio*\textwidth);
+        \end{tikzpicture}
+        \end{center}
+        \caption{Panel B}
+        \label{fig:panelb}
+    \end{subfigure}
+    \bigskip
+    \\
+    \begin{subfigure}[b]{0.49\textwidth}
+        \begin{center}
+        \begin{tikzpicture}
+        \draw (0,0) -- (0,\fhratio*\textwidth) -- (\fwratio*\textwidth, \fhratio*\textwidth) -- (\fwratio*\textwidth, 0) -- (0, 0);
+        \draw (0.3*\fwratio*\textwidth,0.3*\fhratio*\textwidth) --(0.7*\fwratio*\textwidth,0.7*\fhratio*\textwidth);
+        \end{tikzpicture}
+        \end{center}
+        \caption{Panel C}
+        \label{fig:panelc}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.49\textwidth}
+        \begin{center}
+        \begin{tikzpicture}
+        \draw (0,0) -- (0,\fhratio*\textwidth) -- (\fwratio*\textwidth, \fhratio*\textwidth) -- (\fwratio*\textwidth, 0) -- (0, 0);
+        \draw (0.3*\fwratio*\textwidth,0.3*\fhratio*\textwidth) --(0.7*\fwratio*\textwidth,0.7*\fhratio*\textwidth);
+        \end{tikzpicture}
+        \end{center}
+        \caption{Panel D}
+        \label{fig:paneld}
+    \end{subfigure}    
+    \caption{Figure with Four Subfigures Each Containing Tikz Figure}\label{fig:tikztogether}
+\end{figure}
+
 \end{document}

### 2019-12-22 _other/tikz/tree/fs_tikz_gametree.tex
layout, multi-line, etc

\documentclass{article}

\usepackage{blindtext}
\usepackage{multicol}
\usepackage{caption}
\usepackage{amsmath}
\usepackage{tikz}
\usepackage{pgfplots}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=cyan,
}
\usepackage{geometry}
\geometry{
	a4paper,
	noheadfoot=true,
	left=1.0in,
	right=1.0in,
	top=1.0in,
	bottom=1.0in
}

% url package
\usepackage{hyperref}
\usepackage{subcaption}

% Titling and Author
\title{Latex Tikz Examples, Discrete and Continuous Strategy Trees}
\author{\href{https://fanwangecon.github.io/}{Fan Wang}\thanks{https://fanwangecon.github.io, repository: \href{https://fanwangecon.github.io/Tex4Econ/}{Tex4Econ}}}
\date{\today}

\begin{document}

\maketitle

% A.1 Node styles
\tikzset{
    % Two node styles for game trees: solid and hollow
    solid node/.style={circle,draw,inner sep=1.5,fill=black},
    hollow node/.style={circle,draw,inner sep=1.5,fill=white}
}

\begin{center}
\begin{tikzpicture}[scale=1.5,font=\footnotesize]

% A.2 Level Styles
    % Specify spacing for each level of the tree
    \tikzstyle{level 1}=[level distance=17mm,sibling distance=25mm]
    \tikzstyle{level 2}=[level distance=15mm,sibling distance=15mm]

% B Level 1 point
\node(0)[solid node,label=above:{$P1$}]{}

% C Level 2 Node (child nodes)
% C.1 First child node, left
child{
    % C.1.a Node line color
    [red]
    % C.1.b Node dot 
    node(1)[solid node, label=below:{red dot}]{}
    % C.1.c now go to edge
    edge from parent 
        % C.1.c Node along edge
        node[sloped, above, black, text width=3cm]{Minimum Choice showing up along this red line}
    }
% C.2 Middle Child node, do not show line, invisible
child{
    % Main node of level 2 middle node, same y-axis height as node left and right
    % Y-shift to move level 3 child node lower
    [purple] node(2)[solid node, xshift=30, yshift=-50, label=right:{hello}]{}
    % D.1 Left level 3 (from middle level 2)
    child{
        [black] 
        node[hollow node,label=below:{$(a,b)$}]{} 
        edge from parent 
            node[left]{$C$}
        }
    child{
        [black]
        node[hollow node,label=below:{$(c,d)$}]{} 
        edge from parent 
            node[right]{$D$}
        }
    edge from parent 
        %note that you need to adjust the yshift if you change the level distance
        node[left, black, xshift=-5, yshift=0, text width = 1mm]{$\alpha$\\$\beta$\\$\sigma$} 
    }
child{
    [black]
    node(3)[solid node, label=right:{hi there}, green]{}
    edge from parent 
        node[right, xshift=0, yshift=15, text width=2cm]{Some text for this edge}
    };
% information set
\draw[dashed, bend right] 
    (1) to (3);
\draw[dashed, bend left, line width=0.5mm, blue] 
    (0) to 
        node[right, text width=1.25cm, xshift=5, yshift=-10] 
            {\tiny{label right of blue dashed line}}
        (2);
\end{tikzpicture}
\end{center}

% \begin{istgame}[font=\scriptsize]
% \setistgrowdirection{east}
% \cntmdistance{20mm}{20mm}
% \cntmAistb{q_1=0}[at end,below]{q_1=1,000}[at end,above]
% \istrootcntmA(0){1}
%   \istbA[draw=none]
%   \endist
% \cntmAistb{q_2=0}[at end,below]{q_2=1,000}[at end,above]
% \istrootcntmA(1)(0-1)<[xshift=3pt]90>{2}
%   \istbA[draw=none]{}{\pi_1,\pi_2}
%   \endist
% \end{istgame}

\end{document}

### 2019-12-22 nontex/install/linux/fn_ubuntu.Rmd
tutorial for installations

---
title: "Atom, Git, Github, etc Set-up for Linux"
output:
  pdf_document:
    df_print: paged
    number_sections: true
  html_notebook:
    number_sections: true
  word_document:
    number_sections: true
  html_document:
    number_sections: true
urlcolor: blue
always_allow_html: yes
---

Go back to [fan](http://fanwangecon.github.io/)'s [Miscellaneous Repository](http://fanwangecon.github.io/Tex4Econ/nontex/).

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval = FALSE)
```

# Atom Install

Can be directly installed from Ubuntu store.

```{bash}
# install atom
sudo apt-get install atom
```

- *personal access token*: d8a293d30ef620a8b27ab0ad6294cdd8942a0b6f
- *Gist id*: 754fa9ca57eb7ddc1ee89775f934b59f

# Git Install

1. install git
2. once rsa set up, sync repo

```{bash}
# install git
sudo apt-get install git
# generate repo directory and sync
mkdir ~/PyFan
cd ~/PyFan
git init
git config --global user.name "Fan Wang"
git config --global user.email wangfanbsg75@live.com
git remote add github git@github.com:FanWangEcon/PyFan.git
git pull github master
```

# Github and local repo

1. generate rsa
    - ssh-keygen -t rsa -C "wangfanbsg75@live.com", when prompted, do not enter "file in which save the key", when prompted for passphrase, enter "WHATEVERPASSWORDIS"
2. copy key
3. log on to github ssh section, generate new ssh rsa key

```{bash}
ssh-keygen -t rsa -C "wangfanbsg75@live.com"
cat ~/.ssh/id_rsa.pub
```

# Conda Install

conda install linux

1. wget to download from url to download folder
2. bash to install
3. follow instructions, type yes
4. source ~/.bashrc

```{bash}
# could be saved in current folder: pwd
# could be saved in download folder: ~/Downloads
wget https://repo.anaconda.com/archive/Anaconda3-2019.10-Linux-x86_64.sh
# install file
bash "Anaconda3-2019.10-Linux-x86_64.sh"
# refresh
source ~/.bashrc
```

### 2019-12-22 nontex/install/windows/fn_installations.Rmd
tutorial for installations

---
title: "Python and R set-up and Installations on New Computer"
output:
  pdf_document:
    df_print: paged
    number_sections: true
  html_notebook:
    number_sections: true
  word_document:
    number_sections: true
  html_document:
    number_sections: true
urlcolor: blue
always_allow_html: yes
---

Go back to [fan](http://fanwangecon.github.io/)'s [Miscellaneous Repository](http://fanwangecon.github.io/Tex4Econ/nontex/).

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval = FALSE)
```

# Conda

Use conda across platforms, so that locally on windows and ubuntu and remotely on aws, can have the same software setup environment.

Search for Anaconda Prompt, right click, choose run as administrator.

Check software versions.

```{bash}
conda list anaconda
python -V
```

## First Time Conda Install

Download and install for all users. Afterwards, Anaconda does not automatically get added to Windows Path. Need to use Anaconda Prompt to access programs. To access Anaconda packages from windows prompt, from git bash, from R, etc, need to Add Anaconda to Windows Path

See Anaconda Installation Directory, in anaconda prompt:
```{bash}
where anaconda
# C:/ProgramData/Anaconda3/Scripts/anaconda.exe
where python
# C:/ProgramData/Anaconda3/python.exe
where jupyter
# C:/ProgramData/Anaconda3/Scripts/jupyter.exe
where jupyter-kernelspec
# if R installed already
where r
```

To Add Anaconda to Path, In Windows
1. search for: Environment Variables
2. Edit Environment Variables
3. Add new to Path (lower half):
    - C:/ProgramData/Anaconda3/Scripts/
    - C:/ProgramData/Anaconda3/
4. Now open up regular windows command Prompt, Type in:
    - conda --version
    - also Close and Open up Git Bash: conda --version

## Conda Update

Open up Anaconda Navigator, it will update navigator automatically. If there are errors, might have to clean first.

```{bash}
# # if there are bugs
# conda clean --packages
# normal update
conda update --all
```

## Conda Test Python

```{r}
python "C:/Users/fan/PyFan/ProjectSupport/Testing/Numpy/Functions.py"
python "C:/Users/fan/PyFan/ProjectSupport/graph/subplot.py"
```

## Additional Packages

```{r}
conda install statsmodels
conda install datashape
conda install seaborn
conda install -c conda-forge interpolation
conda install -c conda-forge awscli
conda install -c anaconda boto3
conda install -c r r-irkernel
```

# R Installation

Try to install R from within Conda. The procedure here is the same for windows as well as linux machines.

## Fully uninstall r

open up RStudio, and see where paths are.
also open up R from command prompt, see where paths are.

```{R}
.libPath()
```

Open up install and uninstall programs, find R and Rstudio, and uninstall them. Then delete all files found path paths shown by *.libPath()*, looking at these:
    - *C:/Users/fan/Documents/R/win-library/3.6*
    - *C:/Program Files/R/R-3.6.1/library*

## Install R (outside of Conda)

1. [download R](https://cran.r-project.org/bin/windows/base/)
2. [download R-studio](https://cran.r-project.org/bin/windows/base/)
3. Open R-studio and auto-detect R
4. Install packages

```{r}
# Install R-tools
install.packages("installr")
library("installr")
install.Rtools()

# main packagevps
install.packages(c("tidyr", "tidyverse", "tidymodels"))
# development packages
install.packages(c("devtools", "irkernel", "pkgdown", "roxygen2"))
# other packages
install.packages(c("AER", "minpack.lm", "knitr", "kableExtra", "matlab"))

# Install my package
devtools::install_github("fanwangecon/R4Econ")
```

## Set up R-Environment in Conda

Conda environments are language agnostic. pip is a package manager for Python. venv is an environment manager for Python. conda is both a package and environment manager and is language agnostic. Inside Anaconda Prompt:

Key packages are generally available in conda's default channel (official distribution) and also the more frequently updated conda-forge channel. Prioritize conda-forge to get the latest packages. after adding *conda-forge* to channels, that will be prioritized, so when creating a new environment, conda will install first from conda-forge if package exists there. Try the *r_env* generation line with and without first adding *conda-forge* to channel, and see that the packages installed will have different versions, reflecting versions in the default channel and in the *conda-forge* channels.

```{bash}
# Set up Channel
conda config --add channels conda-forge
# install key r packages within a r-environment
conda env remove -n r_env
conda create -n r_env r-essentials r-base r-tidyr r-tidyverse r-devtools r-irkernel r-pkgdown r-roxygen2
# see all installed environments
conda env list
# activate an environment to use it, if in base, r does not exist, isolated in r_env
conda activate r_env
# see packages in environment
conda list
# to quit
conda deactivate
```

- **Location**: Installed environments are shown appear in the *envs* folder of *C:/ProgramData/Anaconda3/envs/*. Can be easily deleted without disrupting the main base installation for conda. This is very important. During installation, could easily run into problems, and need to re-install. Much better to only re-install a folder. Note that when R is installed in *envs*, it will not show up under add or remove programs for uninstallation from there, has to be uninstalled, deleted directly here.
- **Use only in Env**: Note that if we installed r inside r_env, if we type *r* under the base environment, we can not enter r. We can only enter r within r_env. With PATH properly set-up, this happens under Conda Prompt, Windows Prompt, etc.
- **Multiple Pythons**: With the above installation for R, one benefit is that if R requires a different version of Python than what the base environment uses, the r_env could have a different python version. So type *python* in the base environment as well as inside the *r_env*. This also means potentially there could be duplicated installations I think. Look at the python versions under *conda list* in the base and in the r-environment.
- **File Size**: Note that this creates a large installation folder, *C:/ProgramData/Anaconda3/envs/r_env/*, without additional packages, is 1.3 GB in size

## Install Additional Packages inside the R-environment

These are packages that I use, these should be installed inside the environment. Or they could be installed later from inside r-studio. Installing inside r-studio is a lot better.

This did not work, *tidymodels* failed to install. Perhaps because of directory issues. *tidymodels* required *rstanarm*, and *rstanarm* failed to install.

```{bash}
### One line
conda install -c conda-forge r-aer r-minpack.lm r-knitr r-kableExtra r-matlab
# conda install -c conda-forge r-rstanarm

#######################################
### Estimation
#######################################
# Estimation Tools
# tidymodels does not work fron conda install
# Linear Regression Package
# https://anaconda.org/conda-forge/r-aer
# Nonlinear Regression Package
# https://anaconda.org/conda-forge/r-minpack.lm
conda install -c conda-forge r-aer r-minpack.lm
# enter r and use devtools
# install.packages("tidymodels")

#######################################
### Visualiation
#######################################
conda install -c conda-forge r-knitr r-kableExtra

#######################################
### Utilities
#######################################
# Allowing for Invoking Matlab Files from Inside R
conda install -c conda-forge r-matlab
```

Install additional packages from inside R. The devtools install will install packages inside *envs/r_env/Lib/R*.

```{r}
#######################################
### Own Package
#######################################
devtools::install_github("fanwangecon/R4Econ")
# install_dev("cli")
```

## R-Studio Set-up Download from Rstudio

1. Download R-studio, and install, as normal (not from conda, directly from rstudio website latest windows version)
2. Open up anaconda prompt, enter *r_env* environment: *activate r_env*
3. cd into rstudio exe file folder: cd "C:/Program Files/RStudio/bin"
4. start r-studio from inside *r_env*: rstudio.exe
5. inside r-studio, check: *.libPaths()*
    - "C:/ProgramData/Anaconda3/envs/r_env/Lib/R/library"

```{bash}
activate r_env
cd "C:/Program Files/RStudio/bin"
rstudio.exe

cd "C:/ProgramData/Anaconda3/envs/r_env/Lib/R/library"
"C:/Program Files/RStudio/bin/rstudio.exe"
```

## Install Packages from R-Studio

Install addition files inside Rstudio. Easier to debug potentially. Install rtools as described [here](https://thecoatlessprofessor.com/programming/cpp/installing-rtools-for-compiled-code-via-rcpp/): [rtools download](https://cran.r-project.org/bin/windows/Rtools/). Alternatively:

```{r}
install.packages("installr")
library("installr")
# Note that this will generate several pop-up windows
install.Rtools()
# choose to only install 64 bit toolchain
# this installs g++ which is needed for rstanarm
# Add these below to windows path
# c:/Rtools/bin;
# c:/Rtools/mingw_62/bin;

if (!require(devtools)) {
  install.packages("devtools")
  library(devtools)
}
library(devtools)
install_github("stan-dev/rstanarm", args = "--preclean")

setwd('C:/ProgramData/Anaconda3/envs/r_env/Lib/R/library')

install.packages("stan-dev/rstanarm", dependencies=TRUE, INSTALL_opts = c('--no-lock'))

# other packages
install.packages(c("tidymodels", "AER", "minpack.lm", "knitr", "kableExtra", "matlab"))

# Install my package
devtools::install_github("fanwangecon/R4Econ")
```

### Test Files

Test the following file to see if we can execute a R file. Do it inside *r_env* and inside a *r* session.

```{r}
# A simple file with summary statistics using tidyverse
source('C:/Users/fan/R4Econ/summarize/dist/fst_hist_onevar.R')
# Another simple file with summary statistics using tidyverse
source('C:/Users/fan/R4Econ/support/tibble/fs_tib_basics.R')
# A file involving estimation
source('C:/Users/fan/R4Econ/optimization/cesloglin/fst_ces_plan_linlog.R')
```

# Other Programs to Install

## Development Programs

- [git for windows](https://git-scm.com/download/win): after install, try "cd ~/PyFan"
- [atom](https://atom.io/)
- [pycharm](https://www.jetbrains.com/pycharm/)

## Key Programs

- Adobe Acrobat
    + go to adobe website, log in using fwang26@uh.edu
    + go to my account, choose view and download my apps, choose acrobat & PDF, download Acrobat DC
    + UH account can only be activated on two accounts at once, so need to kick other computers out temporarily potentially

## Utilities

- 7-zip

### 2019-12-22 nontex/install/linux/fn_ubuntu.Rmd
edit improve linux and windows installation files.

@@
 source ~/.bashrc
+# show all installed packages under current envir
+conda list
+# see where key files are installed
+which python
+which conda
+# use conda-forge as main channel and update all
+conda config --add channels conda-forge
+conda update --all
 ```
+
+## Install PyCharm
+
+PyCharm can be installed from Ubuntu apps.
+
+```{bash}
+<!-- for Debian -->
+sudo tar xfz pycharm-*.tar.gz -C /opt/
+cd /opt/pycharm-*/bin
+./pycharm.sh
+```
+
+# R install
+
+R could be installed first as below.
+Or follow the [instructions on this page](https://fanwangecon.github.io/Tex4Econ/nontex/install/windows/fn_installations.html) to install from conda an environment for R, with associated R-studio.
+
+```{bash}
+apt-get update
+apt-get install r-base r-base-dev
+```

### 2019-12-22 nontex/install/windows/fn_installations.Rmd
edit improve linux and windows installation files.

@@
 # conda clean --packages
+# use conda-forge as main channel, more updated packages
+conda config --add channels conda-forge
 # normal update
@@
 ```{r}
+# windows
 python "C:/Users/fan/PyFan/ProjectSupport/Testing/Numpy/Functions.py"
 python "C:/Users/fan/PyFan/ProjectSupport/graph/subplot.py"
+# linux
+python ~/PyFan/ProjectSupport/Testing/Numpy/Functions.py
+python ~/PyFan/ProjectSupport/graph/subplot.py
 ```
@@
 
-1. [download R](https://cran.r-project.org/bin/windows/base/)
-2. [download R-studio](https://cran.r-project.org/bin/windows/base/)
+1. [download R](https://cloud.r-project.org/)
+2. [download R-studio](https://rstudio.com/products/rstudio/download/)
 3. Open R-studio and auto-detect R
 4. Install packages
+
+note that installation will not work if the machine's version of R is not up to date, this could be the case with default R versions for some linux installations.
 
@@
 install.Rtools()
+# c:/Rtools/bin;
+# c:/Rtools/mingw_32/bin;
+# c:/Rtools/mingw_64/bin;
 
@@
 
-This did not work, *tidymodels* failed to install. Perhaps because of directory issues. *tidymodels* required *rstanarm*, and *rstanarm* failed to install.
+This did not work in windows, *tidymodels* failed to install. Perhaps because of directory issues. *tidymodels* required *rstanarm*, and *rstanarm* failed to install.
 
@@
 
+For linux, note that rstudio offers Ubuntu as well as Debian versions that can be installed with wget:
+
+```{bash}
+<!-- for ubuntu -->
+wget "https://download1.rstudio.org/desktop/bionic/amd64/rstudio-1.2.5033-amd64.deb"
+sudo apt install ./rstudio-1.2.5033-amd64.deb
+<!-- for debian -->
+wget "https://download1.rstudio.org/desktop/debian9/x86_64/rstudio-1.2.5033-amd64.deb"
+sudo apt install ./rstudio-1.2.5033-amd64.deb
+conda install -c r rstudio
+cd "C:/Program Files/RStudio/bin"
+rstudio.exe
+
+cd "C:/ProgramData/Anaconda3/envs/r_env/Lib/R/library"
+"C:/Program Files/RStudio/bin/rstudio.exe"
+```
+
 ## Install Packages from R-Studio
@@
 # c:/Rtools/bin;
-# c:/Rtools/mingw_62/bin;
+# c:/Rtools/mingw_64/bin;
 

### 2019-12-22 nontex/install/git/fs_git_setup.Rmd
git multi repo no passphrase initialize

---
title: "Git and Github Example and Tutorial, Sync with Multiple Repositories, Store Password"
output:
  pdf_document:
    df_print: paged
    number_sections: true
  html_notebook:
    number_sections: true
  word_document:
    number_sections: true
  html_document:
    number_sections: true
urlcolor: blue
always_allow_html: yes
---

Go back to [fan](http://fanwangecon.github.io/)'s [Tex4Econ and Miscellaneous Repository](http://fanwangecon.github.io/Tex4Econ/).

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval = FALSE)
```

# Download Programs

1. Install [git for windows](https://git-scm.com/download/win): after install, try "cd ~/PyFan"
2. Install [atom](https://atom.io/)
3. Might need to install [putty](https://www.putty.org/) possibly

# git and Github Security Set-up

1. open up git bash
2. generate rsa
    - *ssh-keygen -t rsa -C "wangfanbsg75@live.com"*
    - when prompted, do not enter "file in which save the key", when prompted for passphrase, enter "WHATEVERPASSWORDIS"
3. copy key
    - WINDOWS: *clip < ~/.ssh/id_rsa.pub*
    - LINUX: *cat ~/.ssh/id_rsa.pub*
4. log on to github ssh section, generate new ssh rsa key
    - SSH and GPG keys, choose New SSH key, paste in clipped text.

```{bash}
# inside git bash
ssh-keygen -t rsa -C "wangfanbsg75@live.com"
# this copies the text in the .pub file generated
clip < ~/.ssh/id_rsa.pub
```

# Start and Sync Key Repositories

Inside git bash (open as *administrator*), Sync Several Key Repositories that should be synced on all computers:

1. fanwangecon.github.io: Github root repo
2. PyFan: Private Repo with Python Support Files
3. [Tex4Econ](https://github.com/FanWangEcon/Tex4Econ): Latex, installation, and various other support files, public repo.
4. [R4Econ](https://github.com/FanWangEcon/R4Econ): Public repo, R package, R research programs
5. [M4Econ](https://github.com/FanWangEcon/M4Econ): Public repo, Matlab package, Matlab examples and research files
6. [Py4Econ](https://github.com/FanWangEcon/Py4Econ): Public repo, Python package, Python research programs
7. Teaching: Private teaching repository

Other repositories can be synced when needed on an ad-hoc basis. The repositories above are essential repositories.

## Repo Folders and Global config

Remember git bash or bash should be in windows opened as *administrator*.

```{bash}
# cd to root folder
cd ~
# generate all needed key repositories
mkdir fanwangecon.github.io PyFan Tex4Econ R4Econ M4Econ Py4Econ Teaching

# Set global config settings, in ~/.gitconfig
git config --global user.name "Fan Wang"
git config --global user.email wangfanbsg75@live.com
```

## Initalize and add remote repo for each:

```{bash}
# Initialize Repositories
cd ~/fanwangecon.github.io
git init
git remote add github git@github.com:fanwangecon/fanwangecon.github.io.git
cd ~/PyFan
git init
git remote add github git@github.com:fanwangecon/PyFan
cd ~/Tex4Econ
git init
git remote add github git@github.com:fanwangecon/Tex4Econ
cd ~/R4Econ
git init
git remote add github git@github.com:fanwangecon/R4Econ
cd ~/M4Econ
git init
git remote add github git@github.com:fanwangecon/M4Econ
cd ~/Py4Econ
git init
git remote add github git@github.com:fanwangecon/Py4Econ
cd ~/Teaching
git init
git remote add github git@github.com:fanwangecon/Teaching
```

## Sync Repo in SSH Secure Session

Pull latested from multiple repositories. Just Paste the following lines.

1. start ssh-agent secure session
2. pull from multiple Repositories upon start of working session.
3. commit changes as work on one computer
4. upon leaving a computer with commited changes, push all

Start and end ssh session:

```{bash}
# To avoid having to enter password each time, start background authentication agent.
eval "$(ssh-agent)"
ssh-add ~/.ssh/id_rsa

# to stop the ssh session
kill $SSH_AGENT_PID
```

Pull from repos:

```{bash}
# Initialize Repositories, do these one by one first
cd ~/fanwangecon.github.io
git pull github master
cd ~/PyFan
git pull github master
cd ~/Tex4Econ
git pull github master
cd ~/R4Econ
git pull github master
cd ~/M4Econ
git pull github master
cd ~/Py4Econ
git pull github master
cd ~/Teaching
git pull github master
```

Push from repos committed changes

```{bash}
# Initialize Repositories, do these one by one first
cd ~/fanwangecon.github.io
git push -u github master
cd ~/PyFan
git push -u github master
cd ~/Tex4Econ
git push -u github master
cd ~/R4Econ
git push -u github master
cd ~/M4Econ
git push -u github master
cd ~/Py4Econ
git push -u github master
cd ~/Teaching
git push -u github master
```

### 2019-12-22 nontex/install/linux/fn_ubuntu.Rmd
git multi repo no passphrase initialize

@@
 ---
-title: "Atom, Git, Github, etc Set-up for Linux"
+title: "Example and Tutorial for Atom, Git, Github, etc Set-up for Linux"
 output:
@@
 
-Go back to [fan](http://fanwangecon.github.io/)'s [Miscellaneous Repository](http://fanwangecon.github.io/Tex4Econ/nontex/).
+Go back to [fan](http://fanwangecon.github.io/)'s [Tex4Econ and Miscellaneous Repository](http://fanwangecon.github.io/Tex4Econ/).
 
@@
 mkdir ~/PyFan
+# mkdir fanwangecon.github.io PyFan Tex4Econ R4Econ M4Econ Py4Econ Teaching
 cd ~/PyFan
 git init
+# git config only needs to happen once, info stored under ~/.gitconfig
 git config --global user.name "Fan Wang"

### 2019-12-22 nontex/install/windows/fn_installations.Rmd
git multi repo no passphrase initialize

@@
 ---
-title: "Python and R set-up and Installations on New Computer"
+title: "New Windows Computer Data-Science Set-up: Python (anaconda, pycharm), R (r-studio) and other Programs Installations"
 output:
@@
 See Anaconda Installation Directory, in anaconda prompt:
+
 ```{bash}
@@
 where r
+
+###############################
+# Add these to Windows PATH:
+###############################
+# C:/ProgramData/Anaconda3/Scripts
+# C:/ProgramData/Anaconda3
 ```
@@
 ```{r}
-conda install statsmodels
-conda install datashape
-conda install seaborn
-conda install -c conda-forge interpolation
-conda install -c conda-forge awscli
+conda install statsmodels datashape seaborn
+# conda install statsmodels
+# conda install datashape
+# conda install seaborn
+
+conda install -c conda-forge interpolation awscli
+# conda install -c conda-forge interpolation
+# conda install -c conda-forge awscli
+
 conda install -c anaconda boto3
+
 conda install -c r r-irkernel
@@
 install.Rtools()
-# c:/Rtools/bin;
-# c:/Rtools/mingw_32/bin;
-# c:/Rtools/mingw_64/bin;
+# c:\Rtools\bin;
+# c:\Rtools\mingw_32\bin;
+# c:\Rtools\mingw_64\bin;
 
@@
 source('C:/Users/fan/R4Econ/optimization/cesloglin/fst_ces_plan_linlog.R')
+
+# C:\Users\fan\R4Econ\summarize\dist\fst_hist_onevar.Rmd
+# C:\Users\fan\R4Econ\support\tibble\fs_tib_basics.Rmd
+# C:\Users\fan\R4Econ\optimization\cesloglin\fst_ces_plan_linlog.Rmd
 ```
@@
 
-- [git for windows](https://git-scm.com/download/win): after install, try "cd ~/PyFan"
-- [atom](https://atom.io/)
 - [pycharm](https://www.jetbrains.com/pycharm/)

### 2019-12-23 nontex/install/linux/fn_ubuntu.tex
new gist for atom sync, latex installation

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
\PassOptionsToPackage{dvipsnames,svgnames*,x11names*}{xcolor}
%
\documentclass[
]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={Example and Tutorial for Atom, Git, Github, etc Set-up for Linux},
  colorlinks=true,
  linkcolor=Maroon,
  filecolor=Maroon,
  citecolor=Blue,
  urlcolor=blue,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage[margin=1in]{geometry}
\usepackage{color}
\usepackage{fancyvrb}
\newcommand{\VerbBar}{|}
\newcommand{\VERB}{\Verb[commandchars=\\\{\}]}
\DefineVerbatimEnvironment{Highlighting}{Verbatim}{commandchars=\\\{\}}
% Add ',fontsize=\small' for more characters per line
\usepackage{framed}
\definecolor{shadecolor}{RGB}{248,248,248}
\newenvironment{Shaded}{\begin{snugshade}}{\end{snugshade}}
\newcommand{\AlertTok}[1]{\textcolor[rgb]{0.94,0.16,0.16}{#1}}
\newcommand{\AnnotationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\AttributeTok}[1]{\textcolor[rgb]{0.77,0.63,0.00}{#1}}
\newcommand{\BaseNTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\BuiltInTok}[1]{#1}
\newcommand{\CharTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\CommentTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
\newcommand{\CommentVarTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\ConstantTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\ControlFlowTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
\newcommand{\DataTypeTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{#1}}
\newcommand{\DecValTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\DocumentationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\ErrorTok}[1]{\textcolor[rgb]{0.64,0.00,0.00}{\textbf{#1}}}
\newcommand{\ExtensionTok}[1]{#1}
\newcommand{\FloatTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\FunctionTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\ImportTok}[1]{#1}
\newcommand{\InformationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\KeywordTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
\newcommand{\NormalTok}[1]{#1}
\newcommand{\OperatorTok}[1]{\textcolor[rgb]{0.81,0.36,0.00}{\textbf{#1}}}
\newcommand{\OtherTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{#1}}
\newcommand{\PreprocessorTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
\newcommand{\RegionMarkerTok}[1]{#1}
\newcommand{\SpecialCharTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\SpecialStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\StringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\VariableTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\VerbatimStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\WarningTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{5}

\title{Example and Tutorial for Atom, Git, Github, etc Set-up for Linux}
\author{}
\date{\vspace{-2.5em}}

\begin{document}
\maketitle

Go back to \href{http://fanwangecon.github.io/}{fan}'s
\href{http://fanwangecon.github.io/Tex4Econ/}{Tex4Econ and Miscellaneous
Repository}.

\hypertarget{atom-install}{%
\section{Atom Install}\label{atom-install}}

Can be directly installed from Ubuntu store.

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{# install atom}
\FunctionTok{sudo}\NormalTok{ apt-get install atom}
\end{Highlighting}
\end{Shaded}

\begin{itemize}
\item
  \emph{personal access token}: d8a293d30ef620a8b27ab0ad6294cdd8942a0b6f
\item
  \emph{Gist id}: 754fa9ca57eb7ddc1ee89775f934b59f
\item
  \emph{personal access token}: b36b4d26ff2b5b626a1d7f66e3bc60c582a85c21
\item
  \emph{Gist id}: a883a7ba62661dbe9b907d24b651b780
\end{itemize}

\hypertarget{git-install}{%
\section{Git Install}\label{git-install}}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  install git
\item
  once rsa set up, sync repo
\end{enumerate}

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{# install git}
\FunctionTok{sudo}\NormalTok{ apt-get install git}
\CommentTok{# generate repo directory and sync}
\FunctionTok{mkdir}\NormalTok{ ~/PyFan}
\CommentTok{# mkdir fanwangecon.github.io PyFan Tex4Econ R4Econ M4Econ Py4Econ Teaching}
\BuiltInTok{cd}\NormalTok{ ~/PyFan}
\FunctionTok{git}\NormalTok{ init}
\CommentTok{# git config only needs to happen once, info stored under ~/.gitconfig}
\FunctionTok{git}\NormalTok{ config --global user.name }\StringTok{"Fan Wang"}
\FunctionTok{git}\NormalTok{ config --global user.email wangfanbsg75@live.com}
\FunctionTok{git}\NormalTok{ remote add github git@github.com:FanWangEcon/PyFan.git}
\FunctionTok{git}\NormalTok{ pull github master}
\end{Highlighting}
\end{Shaded}

\hypertarget{github-and-local-repo}{%
\section{Github and local repo}\label{github-and-local-repo}}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  generate rsa

  \begin{itemize}
  \tightlist
  \item
    ssh-keygen -t rsa -C
    ``\href{mailto:wangfanbsg75@live.com}{\nolinkurl{wangfanbsg75@live.com}}'',
    when prompted, do not enter ``file in which save the key'', when
    prompted for passphrase, enter ``WHATEVERPASSWORDIS''
  \end{itemize}
\item
  copy key
\item
  log on to github ssh section, generate new ssh rsa key
\end{enumerate}

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{ssh-keygen}\NormalTok{ -t rsa -C }\StringTok{"wangfanbsg75@live.com"}
\FunctionTok{cat}\NormalTok{ ~/.ssh/id_rsa.pub}
\end{Highlighting}
\end{Shaded}

\hypertarget{conda-install}{%
\section{Conda Install}\label{conda-install}}

conda install linux

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  wget to download from url to download folder
\item
  bash to install
\item
  follow instructions, type yes
\item
  source \textasciitilde/.bashrc
\end{enumerate}

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{# could be saved in current folder: pwd}
\CommentTok{# could be saved in download folder: ~/Downloads}
\FunctionTok{wget}\NormalTok{ https://repo.anaconda.com/archive/Anaconda3-2019.10-Linux-x86_64.sh}
\CommentTok{# install file}
\FunctionTok{bash} \StringTok{"Anaconda3-2019.10-Linux-x86_64.sh"}
\CommentTok{# refresh}
\BuiltInTok{source}\NormalTok{ ~/.bashrc}
\CommentTok{# show all installed packages under current envir}
\ExtensionTok{conda}\NormalTok{ list}
\CommentTok{# see where key files are installed}
\FunctionTok{which}\NormalTok{ python}
\FunctionTok{which}\NormalTok{ conda}
\CommentTok{# use conda-forge as main channel and update all}
\ExtensionTok{conda}\NormalTok{ config --add channels conda-forge}
\ExtensionTok{conda}\NormalTok{ update --all}
\end{Highlighting}
\end{Shaded}

\hypertarget{install-pycharm}{%
\subsection{Install PyCharm}\label{install-pycharm}}

PyCharm can be installed from Ubuntu apps.

\begin{Shaded}
\begin{Highlighting}[]
\OperatorTok{<}\NormalTok{!}\ExtensionTok{--}\NormalTok{ for Debian --}\OperatorTok{>}
\FunctionTok{sudo}\NormalTok{ tar xfz pycharm-*.tar.gz -C /opt/}
\BuiltInTok{cd}\NormalTok{ /opt/pycharm-*/bin}
\ExtensionTok{./pycharm.sh}
\end{Highlighting}
\end{Shaded}

\hypertarget{r-install}{%
\section{R install}\label{r-install}}

R could be installed first as below. Or follow the
\href{https://fanwangecon.github.io/Tex4Econ/nontex/install/windows/fn_installations.html}{instructions
on this page} to install from conda an environment for R, with
associated R-studio.

\begin{Shaded}
\begin{Highlighting}[]
\ExtensionTok{apt-get}\NormalTok{ update}
\ExtensionTok{apt-get}\NormalTok{ install r-base r-base-dev}
\end{Highlighting}
\end{Shaded}

\end{document}

### 2019-12-23 nontex/install/windows/fn_installations.Rmd
new gist for atom sync, latex installation

@@
 
+# Install Latex
+
+Use a combination of overleaf and local compile.
+The goal is to have the same installation set-up for windows as well as linux.
+And hopefully, locally compilable file also can be compiled on overleaf (only use packages also available on overleaf).
+
+There are several pieces of things to install:
+
+1. latex compiler: pdflatex, etc
+2. tex distributions: MikTex, texlive
+    + these folders, once various packages are installed, could be very large, many GB
+3. latex packages from distributions
+3. editor (gui): Atom, texStudio, etc
+
+## Uninstall
+
+- uninstall *MiKTeX*: delete from programs, then delete remaining folder in Program Files.
+- uninstall *texlive*: go to *c:/texlive*, delete the folder
+
+## Install
+
+*Install on Windows*
+
+- [Install Texstudio](https://www.texstudio.org/)
+- [Install texlive](https://www.tug.org/texlive/acquire-netinstall.html)
+
+*Install on Ubuntu*
+
+install texlive and texstudio ubuntu/debian.
+
+```{bash}
+sudo apt-get update
+sudo apt-get install texlive-full
+sudo apt-get install texstudio
+```
+
+## Compile in Atom
+
+Install the [latex](https://github.com/thomasjo/atom-latex) package on atom.
+
+```{bash}
+# set TeX path
+# C:\texlive\2019\bin\win32
+```
+
 # Other Programs to Install

### 2019-12-23 nontex/install/windows/fn_installations.tex
new gist for atom sync, latex installation

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
\PassOptionsToPackage{dvipsnames,svgnames*,x11names*}{xcolor}
%
\documentclass[
]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={New Windows Computer Data-Science Set-up: Python (anaconda, pycharm), R (r-studio) and other Programs Installations},
  colorlinks=true,
  linkcolor=Maroon,
  filecolor=Maroon,
  citecolor=Blue,
  urlcolor=blue,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage[margin=1in]{geometry}
\usepackage{color}
\usepackage{fancyvrb}
\newcommand{\VerbBar}{|}
\newcommand{\VERB}{\Verb[commandchars=\\\{\}]}
\DefineVerbatimEnvironment{Highlighting}{Verbatim}{commandchars=\\\{\}}
% Add ',fontsize=\small' for more characters per line
\usepackage{framed}
\definecolor{shadecolor}{RGB}{248,248,248}
\newenvironment{Shaded}{\begin{snugshade}}{\end{snugshade}}
\newcommand{\AlertTok}[1]{\textcolor[rgb]{0.94,0.16,0.16}{#1}}
\newcommand{\AnnotationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\AttributeTok}[1]{\textcolor[rgb]{0.77,0.63,0.00}{#1}}
\newcommand{\BaseNTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\BuiltInTok}[1]{#1}
\newcommand{\CharTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\CommentTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
\newcommand{\CommentVarTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\ConstantTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\ControlFlowTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
\newcommand{\DataTypeTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{#1}}
\newcommand{\DecValTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\DocumentationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\ErrorTok}[1]{\textcolor[rgb]{0.64,0.00,0.00}{\textbf{#1}}}
\newcommand{\ExtensionTok}[1]{#1}
\newcommand{\FloatTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\FunctionTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\ImportTok}[1]{#1}
\newcommand{\InformationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\KeywordTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
\newcommand{\NormalTok}[1]{#1}
\newcommand{\OperatorTok}[1]{\textcolor[rgb]{0.81,0.36,0.00}{\textbf{#1}}}
\newcommand{\OtherTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{#1}}
\newcommand{\PreprocessorTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
\newcommand{\RegionMarkerTok}[1]{#1}
\newcommand{\SpecialCharTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\SpecialStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\StringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\VariableTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\VerbatimStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\WarningTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{5}

\title{New Windows Computer Data-Science Set-up: Python (anaconda, pycharm), R
(r-studio) and other Programs Installations}
\author{}
\date{\vspace{-2.5em}}

\begin{document}
\maketitle

Go back to \href{http://fanwangecon.github.io/}{fan}'s
\href{http://fanwangecon.github.io/Tex4Econ/}{Tex4Econ and Miscellaneous
Repository}.

\hypertarget{conda}{%
\section{Conda}\label{conda}}

Use conda across platforms, so that locally on windows and ubuntu and
remotely on aws, can have the same software setup environment.

Search for Anaconda Prompt, right click, choose run as administrator.

Check software versions.

\begin{Shaded}
\begin{Highlighting}[]
\ExtensionTok{conda}\NormalTok{ list anaconda}
\ExtensionTok{python}\NormalTok{ -V}
\end{Highlighting}
\end{Shaded}

\hypertarget{first-time-conda-install}{%
\subsection{First Time Conda Install}\label{first-time-conda-install}}

Download and install for all users. Afterwards, Anaconda does not
automatically get added to Windows Path. Need to use Anaconda Prompt to
access programs. To access Anaconda packages from windows prompt, from
git bash, from R, etc, need to Add Anaconda to Windows Path

See Anaconda Installation Directory, in anaconda prompt:

\begin{Shaded}
\begin{Highlighting}[]
\ExtensionTok{where}\NormalTok{ anaconda}
\CommentTok{# C:/ProgramData/Anaconda3/Scripts/anaconda.exe}
\ExtensionTok{where}\NormalTok{ python}
\CommentTok{# C:/ProgramData/Anaconda3/python.exe}
\ExtensionTok{where}\NormalTok{ jupyter}
\CommentTok{# C:/ProgramData/Anaconda3/Scripts/jupyter.exe}
\ExtensionTok{where}\NormalTok{ jupyter-kernelspec}
\CommentTok{# if R installed already}
\ExtensionTok{where}\NormalTok{ r}

\CommentTok{###############################}
\CommentTok{# Add these to Windows PATH:}
\CommentTok{###############################}
\CommentTok{# C:/ProgramData/Anaconda3/Scripts}
\CommentTok{# C:/ProgramData/Anaconda3}
\end{Highlighting}
\end{Shaded}

To Add Anaconda to Path, In Windows 1. search for: Environment Variables
2. Edit Environment Variables 3. Add new to Path (lower half): -
C:/ProgramData/Anaconda3/Scripts/ - C:/ProgramData/Anaconda3/ 4. Now
open up regular windows command Prompt, Type in: - conda --version -
also Close and Open up Git Bash: conda --version

\hypertarget{conda-update}{%
\subsection{Conda Update}\label{conda-update}}

Open up Anaconda Navigator, it will update navigator automatically. If
there are errors, might have to clean first.

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{# # if there are bugs}
\CommentTok{# conda clean --packages}
\CommentTok{# use conda-forge as main channel, more updated packages}
\ExtensionTok{conda}\NormalTok{ config --add channels conda-forge}
\CommentTok{# normal update}
\ExtensionTok{conda}\NormalTok{ update --all}
\end{Highlighting}
\end{Shaded}

\hypertarget{conda-test-python}{%
\subsection{Conda Test Python}\label{conda-test-python}}

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{# windows}
\NormalTok{python }\StringTok{"C:/Users/fan/PyFan/ProjectSupport/Testing/Numpy/Functions.py"}
\NormalTok{python }\StringTok{"C:/Users/fan/PyFan/ProjectSupport/graph/subplot.py"}
\CommentTok{# linux}
\NormalTok{python }\OperatorTok{~}\ErrorTok{/}\NormalTok{PyFan}\OperatorTok{/}\NormalTok{ProjectSupport}\OperatorTok{/}\NormalTok{Testing}\OperatorTok{/}\NormalTok{Numpy}\OperatorTok{/}\NormalTok{Functions.py}
\NormalTok{python }\OperatorTok{~}\ErrorTok{/}\NormalTok{PyFan}\OperatorTok{/}\NormalTok{ProjectSupport}\OperatorTok{/}\NormalTok{graph}\OperatorTok{/}\NormalTok{subplot.py}
\end{Highlighting}
\end{Shaded}

\hypertarget{additional-packages}{%
\subsection{Additional Packages}\label{additional-packages}}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{conda install statsmodels datashape seaborn}
\CommentTok{# conda install statsmodels}
\CommentTok{# conda install datashape}
\CommentTok{# conda install seaborn}

\NormalTok{conda install }\OperatorTok{-}\NormalTok{c conda}\OperatorTok{-}\NormalTok{forge interpolation awscli}
\CommentTok{# conda install -c conda-forge interpolation}
\CommentTok{# conda install -c conda-forge awscli}

\NormalTok{conda install }\OperatorTok{-}\NormalTok{c anaconda boto3}

\NormalTok{conda install }\OperatorTok{-}\NormalTok{c r r}\OperatorTok{-}\NormalTok{irkernel}
\end{Highlighting}
\end{Shaded}

\hypertarget{r-installation}{%
\section{R Installation}\label{r-installation}}

Try to install R from within Conda. The procedure here is the same for
windows as well as linux machines.

\hypertarget{fully-uninstall-r}{%
\subsection{Fully uninstall r}\label{fully-uninstall-r}}

open up RStudio, and see where paths are. also open up R from command
prompt, see where paths are.

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{.libPath}\NormalTok{()}
\end{Highlighting}
\end{Shaded}

Open up install and uninstall programs, find R and Rstudio, and
uninstall them. Then delete all files found path paths shown by
\emph{.libPath()}, looking at these: -
\emph{C:/Users/fan/Documents/R/win-library/3.6} - \emph{C:/Program
Files/R/R-3.6.1/library}

\hypertarget{install-r-outside-of-conda}{%
\subsection{Install R (outside of
Conda)}\label{install-r-outside-of-conda}}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  \href{https://cloud.r-project.org/}{download R}
\item
  \href{https://rstudio.com/products/rstudio/download/}{download
  R-studio}
\item
  Open R-studio and auto-detect R
\item
  Install packages
\end{enumerate}

note that installation will not work if the machine's version of R is
not up to date, this could be the case with default R versions for some
linux installations.

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{# Install R-tools}
\KeywordTok{install.packages}\NormalTok{(}\StringTok{"installr"}\NormalTok{)}
\KeywordTok{library}\NormalTok{(}\StringTok{"installr"}\NormalTok{)}
\KeywordTok{install.Rtools}\NormalTok{()}
\CommentTok{# c:\textbackslash{}Rtools\textbackslash{}bin;}
\CommentTok{# c:\textbackslash{}Rtools\textbackslash{}mingw_32\textbackslash{}bin;}
\CommentTok{# c:\textbackslash{}Rtools\textbackslash{}mingw_64\textbackslash{}bin;}

\CommentTok{# main packagevps}
\KeywordTok{install.packages}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\StringTok{"tidyr"}\NormalTok{, }\StringTok{"tidyverse"}\NormalTok{, }\StringTok{"tidymodels"}\NormalTok{))}
\CommentTok{# development packages}
\KeywordTok{install.packages}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\StringTok{"devtools"}\NormalTok{, }\StringTok{"irkernel"}\NormalTok{, }\StringTok{"pkgdown"}\NormalTok{, }\StringTok{"roxygen2"}\NormalTok{))}
\CommentTok{# other packages}
\KeywordTok{install.packages}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\StringTok{"AER"}\NormalTok{, }\StringTok{"minpack.lm"}\NormalTok{, }\StringTok{"knitr"}\NormalTok{, }\StringTok{"kableExtra"}\NormalTok{, }\StringTok{"matlab"}\NormalTok{))}

\CommentTok{# Install my package}
\NormalTok{devtools}\OperatorTok{::}\KeywordTok{install_github}\NormalTok{(}\StringTok{"fanwangecon/R4Econ"}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\hypertarget{set-up-r-environment-in-conda}{%
\subsection{Set up R-Environment in
Conda}\label{set-up-r-environment-in-conda}}

Conda environments are language agnostic. pip is a package manager for
Python. venv is an environment manager for Python. conda is both a
package and environment manager and is language agnostic. Inside
Anaconda Prompt:

Key packages are generally available in conda's default channel
(official distribution) and also the more frequently updated conda-forge
channel. Prioritize conda-forge to get the latest packages. after adding
\emph{conda-forge} to channels, that will be prioritized, so when
creating a new environment, conda will install first from conda-forge if
package exists there. Try the \emph{r\_env} generation line with and
without first adding \emph{conda-forge} to channel, and see that the
packages installed will have different versions, reflecting versions in
the default channel and in the \emph{conda-forge} channels.

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{# Set up Channel}
\ExtensionTok{conda}\NormalTok{ config --add channels conda-forge}
\CommentTok{# install key r packages within a r-environment}
\ExtensionTok{conda}\NormalTok{ env remove -n r_env}
\ExtensionTok{conda}\NormalTok{ create -n r_env r-essentials r-base r-tidyr r-tidyverse r-devtools r-irkernel r-pkgdown r-roxygen2}
\CommentTok{# see all installed environments}
\ExtensionTok{conda}\NormalTok{ env list}
\CommentTok{# activate an environment to use it, if in base, r does not exist, isolated in r_env}
\ExtensionTok{conda}\NormalTok{ activate r_env}
\CommentTok{# see packages in environment}
\ExtensionTok{conda}\NormalTok{ list}
\CommentTok{# to quit}
\ExtensionTok{conda}\NormalTok{ deactivate}
\end{Highlighting}
\end{Shaded}

\begin{itemize}
\tightlist
\item
  \textbf{Location}: Installed environments are shown appear in the
  \emph{envs} folder of \emph{C:/ProgramData/Anaconda3/envs/}. Can be
  easily deleted without disrupting the main base installation for
  conda. This is very important. During installation, could easily run
  into problems, and need to re-install. Much better to only re-install
  a folder. Note that when R is installed in \emph{envs}, it will not
  show up under add or remove programs for uninstallation from there,
  has to be uninstalled, deleted directly here.
\item
  \textbf{Use only in Env}: Note that if we installed r inside r\_env,
  if we type \emph{r} under the base environment, we can not enter r. We
  can only enter r within r\_env. With PATH properly set-up, this
  happens under Conda Prompt, Windows Prompt, etc.
\item
  \textbf{Multiple Pythons}: With the above installation for R, one
  benefit is that if R requires a different version of Python than what
  the base environment uses, the r\_env could have a different python
  version. So type \emph{python} in the base environment as well as
  inside the \emph{r\_env}. This also means potentially there could be
  duplicated installations I think. Look at the python versions under
  \emph{conda list} in the base and in the r-environment.
\item
  \textbf{File Size}: Note that this creates a large installation
  folder, \emph{C:/ProgramData/Anaconda3/envs/r\_env/}, without
  additional packages, is 1.3 GB in size
\end{itemize}

\hypertarget{install-additional-packages-inside-the-r-environment}{%
\subsection{Install Additional Packages inside the
R-environment}\label{install-additional-packages-inside-the-r-environment}}

These are packages that I use, these should be installed inside the
environment. Or they could be installed later from inside r-studio.
Installing inside r-studio is a lot better.

This did not work in windows, \emph{tidymodels} failed to install.
Perhaps because of directory issues. \emph{tidymodels} required
\emph{rstanarm}, and \emph{rstanarm} failed to install.

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{### One line}
\ExtensionTok{conda}\NormalTok{ install -c conda-forge r-aer r-minpack.lm r-knitr r-kableExtra r-matlab}
\CommentTok{# conda install -c conda-forge r-rstanarm}

\CommentTok{#######################################}
\CommentTok{### Estimation}
\CommentTok{#######################################}
\CommentTok{# Estimation Tools}
\CommentTok{# tidymodels does not work fron conda install}
\CommentTok{# Linear Regression Package}
\CommentTok{# https://anaconda.org/conda-forge/r-aer}
\CommentTok{# Nonlinear Regression Package}
\CommentTok{# https://anaconda.org/conda-forge/r-minpack.lm}
\ExtensionTok{conda}\NormalTok{ install -c conda-forge r-aer r-minpack.lm}
\CommentTok{# enter r and use devtools}
\CommentTok{# install.packages("tidymodels")}

\CommentTok{#######################################}
\CommentTok{### Visualiation}
\CommentTok{#######################################}
\ExtensionTok{conda}\NormalTok{ install -c conda-forge r-knitr r-kableExtra}

\CommentTok{#######################################}
\CommentTok{### Utilities}
\CommentTok{#######################################}
\CommentTok{# Allowing for Invoking Matlab Files from Inside R}
\ExtensionTok{conda}\NormalTok{ install -c conda-forge r-matlab}
\end{Highlighting}
\end{Shaded}

Install additional packages from inside R. The devtools install will
install packages inside \emph{envs/r\_env/Lib/R}.

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{#######################################}
\CommentTok{### Own Package}
\CommentTok{#######################################}
\NormalTok{devtools}\OperatorTok{::}\KeywordTok{install_github}\NormalTok{(}\StringTok{"fanwangecon/R4Econ"}\NormalTok{)}
\CommentTok{# install_dev("cli")}
\end{Highlighting}
\end{Shaded}

\hypertarget{r-studio-set-up-download-from-rstudio}{%
\subsection{R-Studio Set-up Download from
Rstudio}\label{r-studio-set-up-download-from-rstudio}}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Download R-studio, and install, as normal (not from conda, directly
  from rstudio website latest windows version)
\item
  Open up anaconda prompt, enter \emph{r\_env} environment:
  \emph{activate r\_env}
\item
  cd into rstudio exe file folder: cd ``C:/Program Files/RStudio/bin''
\item
  start r-studio from inside \emph{r\_env}: rstudio.exe
\item
  inside r-studio, check: \emph{.libPaths()}

  \begin{itemize}
  \tightlist
  \item
    ``C:/ProgramData/Anaconda3/envs/r\_env/Lib/R/library''
  \end{itemize}
\end{enumerate}

\begin{Shaded}
\begin{Highlighting}[]
\ExtensionTok{activate}\NormalTok{ r_env}
\BuiltInTok{cd} \StringTok{"C:/Program Files/RStudio/bin"}
\ExtensionTok{rstudio.exe}

\BuiltInTok{cd} \StringTok{"C:/ProgramData/Anaconda3/envs/r_env/Lib/R/library"}
\StringTok{"C:/Program Files/RStudio/bin/rstudio.exe"}
\end{Highlighting}
\end{Shaded}

For linux, note that rstudio offers Ubuntu as well as Debian versions
that can be installed with wget:

\begin{Shaded}
\begin{Highlighting}[]
\OperatorTok{<}\NormalTok{!}\ExtensionTok{--}\NormalTok{ for ubuntu --}\OperatorTok{>}
\FunctionTok{wget} \StringTok{"https://download1.rstudio.org/desktop/bionic/amd64/rstudio-1.2.5033-amd64.deb"}
\FunctionTok{sudo}\NormalTok{ apt install ./rstudio-1.2.5033-amd64.deb}
\OperatorTok{<}\NormalTok{!}\ExtensionTok{--}\NormalTok{ for debian --}\OperatorTok{>}
\FunctionTok{wget} \StringTok{"https://download1.rstudio.org/desktop/debian9/x86_64/rstudio-1.2.5033-amd64.deb"}
\FunctionTok{sudo}\NormalTok{ apt install ./rstudio-1.2.5033-amd64.deb}
\ExtensionTok{conda}\NormalTok{ install -c r rstudio}
\BuiltInTok{cd} \StringTok{"C:/Program Files/RStudio/bin"}
\ExtensionTok{rstudio.exe}

\BuiltInTok{cd} \StringTok{"C:/ProgramData/Anaconda3/envs/r_env/Lib/R/library"}
\StringTok{"C:/Program Files/RStudio/bin/rstudio.exe"}
\end{Highlighting}
\end{Shaded}

\hypertarget{install-packages-from-r-studio}{%
\subsection{Install Packages from
R-Studio}\label{install-packages-from-r-studio}}

Install addition files inside Rstudio. Easier to debug potentially.
Install rtools as described
\href{https://thecoatlessprofessor.com/programming/cpp/installing-rtools-for-compiled-code-via-rcpp/}{here}:
\href{https://cran.r-project.org/bin/windows/Rtools/}{rtools download}.
Alternatively:

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{install.packages}\NormalTok{(}\StringTok{"installr"}\NormalTok{)}
\KeywordTok{library}\NormalTok{(}\StringTok{"installr"}\NormalTok{)}
\CommentTok{# Note that this will generate several pop-up windows}
\KeywordTok{install.Rtools}\NormalTok{()}
\CommentTok{# choose to only install 64 bit toolchain}
\CommentTok{# this installs g++ which is needed for rstanarm}
\CommentTok{# Add these below to windows path}
\CommentTok{# c:/Rtools/bin;}
\CommentTok{# c:/Rtools/mingw_64/bin;}

\ControlFlowTok{if}\NormalTok{ (}\OperatorTok{!}\KeywordTok{require}\NormalTok{(devtools)) \{}
  \KeywordTok{install.packages}\NormalTok{(}\StringTok{"devtools"}\NormalTok{)}
  \KeywordTok{library}\NormalTok{(devtools)}
\NormalTok{\}}
\KeywordTok{library}\NormalTok{(devtools)}
\KeywordTok{install_github}\NormalTok{(}\StringTok{"stan-dev/rstanarm"}\NormalTok{, }\DataTypeTok{args =} \StringTok{"--preclean"}\NormalTok{)}

\KeywordTok{setwd}\NormalTok{(}\StringTok{'C:/ProgramData/Anaconda3/envs/r_env/Lib/R/library'}\NormalTok{)}

\KeywordTok{install.packages}\NormalTok{(}\StringTok{"stan-dev/rstanarm"}\NormalTok{, }\DataTypeTok{dependencies=}\OtherTok{TRUE}\NormalTok{, }\DataTypeTok{INSTALL_opts =} \KeywordTok{c}\NormalTok{(}\StringTok{'--no-lock'}\NormalTok{))}

\CommentTok{# other packages}
\KeywordTok{install.packages}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\StringTok{"tidymodels"}\NormalTok{, }\StringTok{"AER"}\NormalTok{, }\StringTok{"minpack.lm"}\NormalTok{, }\StringTok{"knitr"}\NormalTok{, }\StringTok{"kableExtra"}\NormalTok{, }\StringTok{"matlab"}\NormalTok{))}

\CommentTok{# Install my package}
\NormalTok{devtools}\OperatorTok{::}\KeywordTok{install_github}\NormalTok{(}\StringTok{"fanwangecon/R4Econ"}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\hypertarget{test-files}{%
\subsubsection{Test Files}\label{test-files}}

Test the following file to see if we can execute a R file. Do it inside
\emph{r\_env} and inside a \emph{r} session.

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{# A simple file with summary statistics using tidyverse}
\KeywordTok{source}\NormalTok{(}\StringTok{'C:/Users/fan/R4Econ/summarize/dist/fst_hist_onevar.R'}\NormalTok{)}
\CommentTok{# Another simple file with summary statistics using tidyverse}
\KeywordTok{source}\NormalTok{(}\StringTok{'C:/Users/fan/R4Econ/support/tibble/fs_tib_basics.R'}\NormalTok{)}
\CommentTok{# A file involving estimation}
\KeywordTok{source}\NormalTok{(}\StringTok{'C:/Users/fan/R4Econ/optimization/cesloglin/fst_ces_plan_linlog.R'}\NormalTok{)}

\CommentTok{# C:\textbackslash{}Users\textbackslash{}fan\textbackslash{}R4Econ\textbackslash{}summarize\textbackslash{}dist\textbackslash{}fst_hist_onevar.Rmd}
\CommentTok{# C:\textbackslash{}Users\textbackslash{}fan\textbackslash{}R4Econ\textbackslash{}support\textbackslash{}tibble\textbackslash{}fs_tib_basics.Rmd}
\CommentTok{# C:\textbackslash{}Users\textbackslash{}fan\textbackslash{}R4Econ\textbackslash{}optimization\textbackslash{}cesloglin\textbackslash{}fst_ces_plan_linlog.Rmd}
\end{Highlighting}
\end{Shaded}

\hypertarget{install-latex}{%
\section{Install Latex}\label{install-latex}}

Use a combination of overleaf and local compile. The goal is to have the
same installation set-up for windows as well as linux. And hopefully,
locally compilable file also can be compiled on overleaf (only use
packages also available on overleaf).

There are several pieces of things to install:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  latex compiler: pdflatex, etc
\item
  tex distributions: MikTex, texlive

  \begin{itemize}
  \tightlist
  \item
    these folders, once various packages are installed, could be very
    large, many GB
  \end{itemize}
\item
  latex packages from distributions
\item
  editor (gui): Atom, texStudio, etc
\end{enumerate}

\hypertarget{uninstall}{%
\subsection{Uninstall}\label{uninstall}}

\begin{itemize}
\tightlist
\item
  uninstall \emph{MiKTeX}: delete from programs, then delete remaining
  folder in Program Files.
\item
  uninstall \emph{texlive}: go to \emph{c:/texlive}, delete the folder
\end{itemize}

\hypertarget{install}{%
\subsection{Install}\label{install}}

\emph{Install on Windows}

\begin{itemize}
\tightlist
\item
  \href{https://www.texstudio.org/}{Install Texstudio}
\item
  \href{https://www.tug.org/texlive/acquire-netinstall.html}{Install
  texlive}
\end{itemize}

\emph{Install on Ubuntu}

install texlive and texstudio ubuntu/debian.

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{sudo}\NormalTok{ apt-get update}
\FunctionTok{sudo}\NormalTok{ apt-get install texlive-full}
\FunctionTok{sudo}\NormalTok{ apt-get install texstudio}
\end{Highlighting}
\end{Shaded}

\hypertarget{compile-in-atom}{%
\subsection{Compile in Atom}\label{compile-in-atom}}

Install the \href{https://github.com/thomasjo/atom-latex}{latex} package
on atom.

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{# set TeX path}
\CommentTok{# C:\textbackslash{}texlive\textbackslash{}2019\textbackslash{}bin\textbackslash{}win32}
\end{Highlighting}
\end{Shaded}

\hypertarget{other-programs-to-install}{%
\section{Other Programs to Install}\label{other-programs-to-install}}

\hypertarget{development-programs}{%
\subsection{Development Programs}\label{development-programs}}

\begin{itemize}
\tightlist
\item
  \href{https://www.jetbrains.com/pycharm/}{pycharm}
\end{itemize}

\hypertarget{key-programs}{%
\subsection{Key Programs}\label{key-programs}}

\begin{itemize}
\tightlist
\item
  Adobe Acrobat

  \begin{itemize}
  \tightlist
  \item
    go to adobe website, log in using
    \href{mailto:fwang26@uh.edu}{\nolinkurl{fwang26@uh.edu}}
  \item
    go to my account, choose view and download my apps, choose acrobat
    \& PDF, download Acrobat DC
  \item
    UH account can only be activated on two accounts at once, so need to
    kick other computers out temporarily potentially
  \end{itemize}
\end{itemize}

\hypertarget{utilities}{%
\subsection{Utilities}\label{utilities}}

\begin{itemize}
\tightlist
\item
  7-zip
\end{itemize}

\end{document}

### 2019-12-23 nontex/install/windows/fn_installations.Rmd
update installation files

@@
 ---
-title: "New Windows Computer Data-Science Set-up: Python (anaconda, pycharm), R (r-studio) and other Programs Installations"
+title: "New Computer Data-Science Set-up: Python (anaconda, pycharm), R (r-studio) and other Programs Installations"
 output:
@@
 ```
+
+# Objective
+
+For the following types of programming tasks, install relevant programs, that are cross platform compatible. Test at the end that example programs work.
+
+1. Python
+    + Anaconda Dist
+    + Pycharm
+    + atom hydrogen
+2. R
+    + R
+    + Rstudio
+    + atom hydrogen
+3. Matlab
+    + Matlab
+4. Latex and PDF
+    + atom latex
+    + texstudio
+    + texlive
+    + okular pdf
+
+Test at the end:
+
+1. Do sample *py* files work?
+    + work from command line?
+    + work from atom (hydrogen)
+2. Do sample *rmd* files work?
+    + work from r-studio
+    + work from atom (hydrogen), r file
+3. Do tex templates compile?
+    + tikz files
+    + template files with bib
 
@@
 # use conda-forge as main channel, more updated packages
+conda config --get channels
 conda config --add channels conda-forge
+conda config --get channels
+# remove conda-forge from channels (do so for main env install)
+conda config --remove channels conda-forge
 # normal update
@@
 ## Conda Test Python
+
+Fist test python under command line:
 
@@
 python ~/PyFan/ProjectSupport/graph/subplot.py
+```
+
+## Jupyter and Atom Hydrogen
+
+For both Jupyter as well as Atom, always open from command prompt, open from *Anaconda Prompt* with admin rights.
+
+First, open up *Jupyter Notebook*, does the python kernel work? If does not, uninstall and re-install Anaconda.
+
+```{bash}
+# start jupyter lab, from prompt
+jupyter lab
+```
+
+Now test python within atom:
+
+1. install hydrogen in atom. Follow [instructions](http://nteract.io/atom).
+    - terminal in windows or linux after installation: *apm install hydrogen*
+    - apm is the atom package manager.
+2. go to the programs above and try to run.
+
+```{bash}
+# Once atom is installed, can use apm to install packages
+apm install hydrogen
+# Inside Conda open up atom
+atom
+# open up any py from from within, try 1+1, does it work?
 ```
@@
 
-conda install -c r r-irkernel
+# conda install -c r r-irkernel
 ```
@@
 1. [download R](https://cloud.r-project.org/)
+    + for debian: [Johannes Ranke](https://cran.r-project.org/bin/linux/debian/)
 2. [download R-studio](https://rstudio.com/products/rstudio/download/)
@@
 note that installation will not work if the machine's version of R is not up to date, this could be the case with default R versions for some linux installations.
+For Debian for example, need to update the *source.list* to include sources that have more recent versions of R.
+
+Additionally, need to install *libcurl4-openssl-dev* and *libssl-dev* from command prompt first inside Debian.
+
+```{bash}
+# Go to get latesdebian latest r sources.list
+cat /etc/apt/sources.list
+# Install this First (should already be installed)
+sudo apt install dirmngr
+
+# Debian R is maintained by Johannes Ranke, copied from https://cran.r-project.org/bin/linux/debian/:
+apt-key adv --keyserver keys.gnupg.net --recv-key 'E19F5F87128899B192B1A2C2AD5F960A256A04AF'
+# Add to source.list, for debian stretch (9)
+# sudo su added for security issue as super-user
+sudo su -c "sudo echo 'deb http://cloud.r-project.org/bin/linux/debian stretch-cran35/' >> /etc/apt/sources.list"
+# if added wrong lines, delete 3rd line
+sudo sed '3d' /etc/apt/sources.list
+
+# Update and Install R, should say updated from cloud.r
+sudo apt-get update
+sudo apt-get install r-base r-base-dev
+
+# Also install these, otherwise r-packages do not install:
+sudo apt-get install libcurl4-openssl-dev
+sudo apt-get install libssl-dev
+```
 
 ```{r}
-# Install R-tools
+# Install R-tools, RTOOLS is for WINDOWS
 install.packages("installr")
@@
 install.Rtools()
-# c:\Rtools\bin;
-# c:\Rtools\mingw_32\bin;
-# c:\Rtools\mingw_64\bin;
+# c:/Rtools/bin;
+# c:/Rtools/mingw_32/bin;
+# c:/Rtools/mingw_64/bin;
 
 # main packagevps
+# tidymodel installation on linux difficult
 install.packages(c("tidyr", "tidyverse", "tidymodels"))
@@
 devtools::install_github("fanwangecon/R4Econ")
+
+# Kernel
+install.packages(c('repr', 'IRdisplay', 'evaluate', 'crayon', 'pbdZMQ', 'devtools', 'uuid', 'digest'))
+devtools::install_github('IRkernel/IRkernel')
+IRkernel::installspec()
 ```
@@
 ```{bash}
-# Set up Channel
+# Set up Channel, for R, to get latest r-packages
+# do not set-up channels to prioritize conda-forge for main env.
 conda config --add channels conda-forge
@@
 wget "https://download1.rstudio.org/desktop/bionic/amd64/rstudio-1.2.5033-amd64.deb"
+<!-- for debian -->
 sudo apt install ./rstudio-1.2.5033-amd64.deb
-<!-- for debian -->
 wget "https://download1.rstudio.org/desktop/debian9/x86_64/rstudio-1.2.5033-amd64.deb"
@@
 
+# for r-kernel to work in Atom
+install.packages(c('repr', 'IRdisplay', 'evaluate', 'crayon', 'pbdZMQ', 'devtools', 'uuid', 'digest'))
+devtools::install_github('IRkernel/IRkernel')
+IRkernel::installspec()
+
 # Install my package
@@
 
-# C:\Users\fan\R4Econ\summarize\dist\fst_hist_onevar.Rmd
-# C:\Users\fan\R4Econ\support\tibble\fs_tib_basics.Rmd
-# C:\Users\fan\R4Econ\optimization\cesloglin\fst_ces_plan_linlog.Rmd
+# C:/Users/fan/R4Econ/summarize/dist/fst_hist_onevar.Rmd
+# C:/Users/fan/R4Econ/support/tibble/fs_tib_basics.Rmd
+# C:/Users/fan/R4Econ/optimization/cesloglin/fst_ces_plan_linlog.Rmd
 ```
@@
 
-## Compile in Atom
+## Compile in Atom and Texstudio
 
-Install the [latex](https://github.com/thomasjo/atom-latex) package on atom.
+Install the following two packages in atom:
+
+1. [latex](https://github.com/thomasjo/atom-latex) package on atom.
+2. [language-latex](https://atom.io/packages/language-latex) package on atom
+
+In Atom Latex setting, note that on different platforms, paths to texlive are different:
+
+- Path:
+    + Windows: *C:/texlive/2019/bin/win32*
+    + Chromebook Linux: */usr/bin/latex*
+- Which PDF viewer to use:
+    + download Okular and use [Okular](https://okular.kde.org/)
 
@@
 # set TeX path
-# C:\texlive\2019\bin\win32
+# C:/texlive/2019/bin/win32
+
+# Latex, after installation
+# see where texlive appears under root folder directories
+sudo find / -name "texlive"
+# see latex version, if texlive is used
+latex -v
+# see main exe directory
+which latex
+# /usr/bin/latex
 ```
+
+Go to Tex4Econ and compile various template files and other types of files there to see if tex is working.
+
+Compile the same files in texstudio.
 
@@
 
-- Adobe Acrobat
+**PDF**
+
+- PDF Okular
+    + Linux: *sudo apt-get install okular*
+    + Windows: install okular from windows app store
+- PDF Adobe Acrobat
     + go to adobe website, log in using fwang26@uh.edu
@@
 
+**VPN**
+
+- [Proton VPN](https://protonvpn.com/): unlimited usage free version available.
+
 ## Utilities

### 2019-12-24 nontex/install/linux/fn_ubuntu.Rmd
new gist for atom sync, latex installation
update installation better linux R

@@
 - *Gist id*: 754fa9ca57eb7ddc1ee89775f934b59f
+
+- *personal access token*: b36b4d26ff2b5b626a1d7f66e3bc60c582a85c21
+- *Gist id*: a883a7ba62661dbe9b907d24b651b780
 
@@
 ```{bash}
+# To remove conda Fully
+rm -rf ~/anaconda3
+
 # could be saved in current folder: pwd
@@
 source ~/.bashrc
+
 # show all installed packages under current envir
@@
 # use conda-forge as main channel and update all
-conda config --add channels conda-forge
+/* conda config --add channels conda-forge */
 conda update --all
+```
+
+Additional statistics and related models to install:
+
+```{r}
+conda install -y statsmodels datashape seaborn
+# conda install statsmodels
+# conda install datashape
+# conda install seaborn
+
+conda install -c conda-forge -y interpolation awscli
+# conda install -c conda-forge interpolation
+# conda install -c conda-forge awscli
+
+conda install -c anaconda -y boto3
+
+# conda install -c r r-irkernel
 ```

### 2019-12-24 nontex/install/windows/fn_installations.Rmd
update installation better linux R

@@
 
+To install conda in Debian, follow [these instructions](https://fanwangecon.github.io/Tex4Econ/nontex/install/linux/fn_ubuntu.html).
+
 See Anaconda Installation Directory, in anaconda prompt:
@@
 ```{bash}
+# To remove conda Fully
+rm -rf ~/anaconda3
+
 where anaconda
@@
 conda update --all
+
+# install additional packages
+conda install -y statsmodels datashape seaborn
+conda install -c conda-forge -y interpolation awscli
+conda install -c anaconda -y boto3
 ```
@@
 # open up any py from from within, try 1+1, does it work?
-```
-
-## Additional Packages
-
-```{r}
-conda install statsmodels datashape seaborn
-# conda install statsmodels
-# conda install datashape
-# conda install seaborn
-
-conda install -c conda-forge interpolation awscli
-# conda install -c conda-forge interpolation
-# conda install -c conda-forge awscli
-
-conda install -c anaconda boto3
-
-# conda install -c r r-irkernel
+# also use script, try ctrl + shift + b, run whole file (not hydrogen)
 ```
@@
 
-## Fully uninstall r
+## Fully Uninstall r
 
-open up RStudio, and see where paths are.
+Open up RStudio, and see where paths are.
 also open up R from command prompt, see where paths are.
@@
     - *C:/Program Files/R/R-3.6.1/library*
+
+For Linux:
+
+- if used apt-get to install, R installed under main user drive, deactivate conda, and check which conda
+
+```{bash}
+# Exit Conda
+conda deactivate
+# where is R installed outside of Conda
+which R
+# /usr/bin/R
+# To remove all
+sudo apt-get remove r-base
+sudo apt-get remove r-base-core
+
+# Inside Conda base
+conda activate
+# Conda r_env
+conda activate r_env
+# Where is it installed?
+which R
+# /home/wangfanbsg75/anaconda3/bin/R
+conda uninstall r-base
+```
 
@@
 ```{bash}
+# If inside Debian, due to some tidymodel install issues, do this`
+conda install -c r r
+conda install -c r r-essentials
+conda install -c r r-igraph
+conda install -c conda-forge igraph
+
 # Go to get latesdebian latest r sources.list
@@
 
-# Also install these, otherwise r-packages do not install:
+# Also install these, otherwise r-packages do not install
+# libxml2 seems need for tidymodels
 sudo apt-get install libcurl4-openssl-dev
 sudo apt-get install libssl-dev
+sudo apt-get install libxml2-dev
 ```
 
+Which R?
+
+- *export RSTUDIO_WHICH_R=/usr/bin/R*
+- *export RSTUDIO_WHICH_R=/home/wangfanbsg75/anaconda3/bin/R*
+
 ```{r}
+# Can enter R from Command Prompt Conda ENV, much faster than from r-studio
 # Install R-tools, RTOOLS is for WINDOWS
@@
 # tidymodel installation on linux difficult
-install.packages(c("tidyr", "tidyverse", "tidymodels"))
+install.packages(c("tidyverse", "tidymodels", "tidyr"))
 # development packages
-install.packages(c("devtools", "irkernel", "pkgdown", "roxygen2"))
+install.packages(c("devtools", "IRkernel", "pkgdown", "roxygen2", "kableExtra"))
 # other packages
-install.packages(c("AER", "minpack.lm", "knitr", "kableExtra", "matlab"))
+install.packages(c("AER", "minpack.lm", "knitr", "matlab"))
 
-# Install my package
+# Install my package, need to prepare package to work for ubuntu
+# if install does not work, load locally
 devtools::install_github("fanwangecon/R4Econ")
@@
 install.packages(c('repr', 'IRdisplay', 'evaluate', 'crayon', 'pbdZMQ', 'devtools', 'uuid', 'digest'))
-devtools::install_github('IRkernel/IRkernel')
 IRkernel::installspec()
@@
 ```{bash}
-# Set up Channel, for R, to get latest r-packages
-# do not set-up channels to prioritize conda-forge for main env.
-conda config --add channels conda-forge
+# outside of conda, install some depencies
+sudo apt-get install libcurl4-openssl-dev
+sudo apt-get install libssl-dev
+sudo apt-get install libxml2-dev
+
 # install key r packages within a r-environment
 conda env remove -n r_env
-conda create -n r_env r-essentials r-base r-tidyr r-tidyverse r-devtools r-irkernel r-pkgdown r-roxygen2
+# start empty environment
+conda create -n r_env
+# activate env and check, nothing yet
+conda activate r_env
+conda list
+
+# check channel and add env specific channel
+conda config --get channels
+# to get latest r, use conda-forge, which has more recent Rs
+# conda config --env --add channels conda-forge
+# channels for base
+conda config --get channels
+# channels for cur env
+conda config --get channels --env
+
+# install files
+conda install -n r_env -c r r r-essentials r-tidyverse r-tidymodels -y
+
+# trouble with igraph installation, install here from conda
+# conda install -n r_env r-essentials r-base r-tidyr r-tidyverse r-devtools r-irkernel r-pkgdown r-roxygen2
+conda install -n r_env -c r r-igraph
+conda install -n r_env -c conda-forge igraph
+conda install -n r_env -c r r-rstantools r-rstan r-rstanarm -y
+
 # see all installed environments
@@
 
-This did not work in windows, *tidymodels* failed to install. Perhaps because of directory issues. *tidymodels* required *rstanarm*, and *rstanarm* failed to install.
+*tidymodel* has installation issues sometimes.
+
+In *r_env*, type in *R*, and then install from inside terminal's R:
 
 ```{bash}
-### One line
-conda install -c conda-forge r-aer r-minpack.lm r-knitr r-kableExtra r-matlab
-# conda install -c conda-forge r-rstanarm
+# enter into env
+conda activate r_env
+# enter R or type in rstudio
+# sicne R is only install inside r_env, has to enter rstudio from r_env
+R
+rstudio
 
-#######################################
-### Estimation
-#######################################
-# Estimation Tools
-# tidymodels does not work fron conda install
-# Linear Regression Package
-# https://anaconda.org/conda-forge/r-aer
-# Nonlinear Regression Package
-# https://anaconda.org/conda-forge/r-minpack.lm
-conda install -c conda-forge r-aer r-minpack.lm
-# enter r and use devtools
-# install.packages("tidymodels")
+# main packagevps
+# tidymodel installation on linux difficult
+install.packages(c("rstantools", "rstan", "rstanarm"))
+install.packages(c("tidyr", "tidyverse", "tidymodels"))
 
-#######################################
-### Visualiation
-#######################################
-conda install -c conda-forge r-knitr r-kableExtra
+# tidymodels
+# development packages
+install.packages(c("devtools", "IRkernel", "pkgdown", "roxygen2", "kableExtra"))
+# other packages
+install.packages(c("AER", "minpack.lm", "knitr", "matlab"))
 
-#######################################
-### Utilities
-#######################################
-# Allowing for Invoking Matlab Files from Inside R
-conda install -c conda-forge r-matlab
+# Install my package, need to prepare package to work for ubuntu
+# if install does not work, load locally
+devtools::install_github("fanwangecon/R4Econ")
+
+# Kernel
+install.packages(c('repr', 'IRdisplay', 'evaluate', 'crayon', 'pbdZMQ', 'devtools', 'uuid', 'digest'))
+IRkernel::installspec()
 ```
@@
 - [Proton VPN](https://protonvpn.com/): unlimited usage free version available.
+- Express VPN
 
@@
 - 7-zip
+- evernote
+- keepass

### 2019-12-29 nontex/install/linux/fn_ubuntu.Rmd
start vim set-up and knowledge file

@@
 sudo apt-get install atom
+# install various atom packages that are necessary
+apm install vim-mode-plus
 ```
@@
 ```{bash}
-apt-get update
-apt-get install r-base r-base-dev
+# Debian R is maintained by Johannes Ranke, copied from https://cran.r-project.org/bin/linux/debian/:
+apt-key adv --keyserver keys.gnupg.net --recv-key 'E19F5F87128899B192B1A2C2AD5F960A256A04AF'
+# Add to source.list, for debian stretch (9)
+# sudo su added for security issue as super-user
+sudo su -c "sudo echo 'deb http://cloud.r-project.org/bin/linux/debian stretch-cran35/' >> /etc/apt/sources.list"
+# if added wrong lines, delete 3rd line
+sudo sed '3d' /etc/apt/sources.list
+
+# Update and Install R, should say updated from cloud.r
+sudo apt-get update
+sudo apt-get install r-base r-base-dev
 ```
+
+# Install Other Programs and Packages
+
+Other key programs and packages to install.
+
+- vim: faster editor, on lower resource machines, atom is slow and typing could feel laggy.
+- htop: for resource monitoring
+
+```
+sudo apt-get install vim
+sudo apt-get install htop
+```

### 2019-12-29 nontex/install/linux/fn_vim.Rmd
start vim set-up and knowledge file

---
title: "Example and Tutorial for Vim Editor (Linux)"
output:
  pdf_document:
    df_print: paged
    number_sections: true
  html_notebook:
    number_sections: true
  word_document:
    number_sections: true
  html_document:
    number_sections: true
urlcolor: blue
always_allow_html: yes
---

Go back to [fan](http://fanwangecon.github.io/)'s [Tex4Econ and Miscellaneous Repository](http://fanwangecon.github.io/Tex4Econ/).

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval = FALSE)
```

# Vim Installations

Vim ships with Debian.

Additional packages to install:

```{bash}
vim
```

Also install neo-vim

```{bash}
sudo apt-get install neovim
```

## Plug-ins

Follow the [instructions here](https://github.com/junegunn/vim-plug/wiki/tutorial) for installations. Two steps:

1. generate ~/.vim and ~/.vimrc folders
2. curl plug.vim to ~/.vim/autoload
3. update ~/.vimrc file with ininstructions regarding which files to install.
4. open vim, type: *:PlugInstall* or *:PlugUpdate*, should start seeing updating packages.
5. type: *:scriptnames* to see loaded plugins
6. just comment out or delete plug lines for packages no longer needed.
7. how to install a particular package? See [vimawesome](https://vimawesome.com/plugin/onedark-vim)

```{bash}
# curl plug.vim
curl -fLo ~/.vim/autoload/plug.vim --create-dirs \
    https://raw.githubusercontent.com/junegunn/vim-plug/master/plug.vim

# create vimrc file
cd $HOME
vim .vimrc

# paste into file the text below.
```

Example .vimrc file with only one package one dark atom visual for vim:

```{bash}
if empty(glob('~/.vim/autoload/plug.vim'))
        silent !curl -fLo ~/.vim/autoload/plug.vim --create-dirs
                \ https://raw.githubusercontent.com/junegunn/vim-plug/master/plug.vim
        autocmd VimEnter * PlugInstall --sync | source $MYVIMRC
endif

" Plugins will be downloaded under the specified directory.
call plug#begin('~/.vim/plugged')

" Declare the list of plugins.
Plug 'joshdick/onedark.vim'

" List ends here. Plugins become visible to Vim after this call.
call plug#end()

"""""""""""""""""""""""""""""""""""""""""""""""""
" Settings
"""""""""""""""""""""""""""""""""""""""""""""""""
syntax on
colorscheme onedark
```

# Vim Basics

```{bash}
# to open vim
vim -v
# to exit vim
:q!
# open up file from google drive
vim "/mnt/chromeos/GoogleDrive/MyDrive/Reading Papers/Reading/Referee/pa_2019_oct_journal/jor_12345_comments.Rmd"
# start editing, type i to enter insert mode
i
# when editing is done, to exit and save, write and quit
# esc first
:wq
```

# Vim Cursor Movements

Move cursor to the beginning of a line? This should not be done in edit mode, esc, use movement commands, then back to insert mode. There are six most basic movements, *wbjk()0$*:

```{bash}
# forward one word
w
# back one word to begin
b
# back to word to end
e

# forward one line, achieved by also pressing downward arrow
j
# backward one line, achieved by pressing upward arrow
k
# left arrow
h
# right arrow
l

# Jump forward one Sentence
)
# Jump backward one Sentence
(

# Begin of line
0
# End of Line
$

# Begin of File
gg
# End of File
G
```

In combination, the basic commands can be used in combination

```{bash}
# move to the beginning of the next line
j0
# move to the end of the next line
j$
```

# Vim Editing

Delete a line.

```{bash}
# select text with cursor, then d for delete
d
```

# Very Convinent Functions

Some functionalities take much more efforts to complete in many other editors, but are very easy in vim:

```{bash}
# combine lines: bunch of lines, with carriage break, one block of text, reflow/join
# 1. select block
Vjjjj
# 2. reflow/join
J
```

## Combo Operations

1. Delete:
    - delete current word and go into insert mode: *ciw*
    - Delete current word: *dw*
    - Delete from cursor until end of sentence: *dis*
    - Delete from cursor to end of line: *d$* or *D*
    - Delete until end of paragraph: *dip*

# Vim Errors

Vim seems frozen (hard for vim to freeze, it is not really frozen). This is likely due to pressing *ctrl + s*, then need to press *ctrl + q*.

vim error: "E297: Write error in swap file"

```
# Trying to save
:w
# E297 can not save, override changes elswhere, and force save what is on screen.
:e!
```

# Vim Set-Up

Use [one-dark atom theme](https://github.com/joshdick/onedark.vim), otherwise color hard to read.

```{bash}

```

### 2019-12-30 _other/tikz/annotate/fs_tikz_annotate.tex
annotate plan and more vim guide

@@
 
+\subsection{Anote Slope, X intercept and Y intercept}
+
+Draw a line, then point to its slope, x and y intercepts.
+
+\begin{enumerate}
+  \item Define the slope and y-intercept: $a_i, b_i$
+  \item Define and calculate the x-intercept: $c_i = -\frac{a_i}{b_i}$
+  \item Define the text that should appear for each element: $a_{desca}$
+  \item Drawing lines pointing to $a$, $b$ or $c$ points:
+  \begin{itemize}
+    \item direction: $d_i \in \left\{NE, SE, SW, NW\right\}$
+    \item rotation: $0 <= e_i <= 90$, which direction points to text
+    \item dist one: $f_i > 0 $, straight distance from origin
+    \item dist two: $g_i > 0 $, distance of line
+    \item point start: $h^o_i, h^o_i$, starting point based on the four pieces of information
+    \item point end: $h^d_i, h^d_i$, ending point based on the four pieces of information
+  \end{itemize}
+\end{enumerate}
+
+So end up drawing using $a$, $b$ for line, $h^o$ for one point $h*d$ line small segment.
+
+\begin{verbatim}
+\end{verbatim}
+\bigskip
+\begin{center}
+\begin{tikzpicture}
+\draw[->] (-1,0) -- (6,0) node[right] {$N_m$};
+\draw[->] (0,-1) -- (0,6) node[above] {$N_{m^{\prime}}$};
+
+% A. Clip area so that line below is only drawn inside finite box
+\clip (-3,-1) rectangle (6,6);
+
+% B. Draw a line with intercept and slope
+\draw[line width=0.50mm,domain=-1:6,smooth,variable=\x, blue] plot ({\x},{1+\x*1.25});
+
+% C. Draw Line pointing to Intercept of line
+\draw[->, line width=0.75mm] (-1.7,2.2) -- (-0.1,1.1);
+
+% D. Draw a transparent text box that wraps text
+\node[text width=3cm] at (-1.4,3.25) {\large{$\bm{\alpha_i}$ (this is the position of the \textbf{x-intercept}), wrap text.}};
+
+\end{tikzpicture}
+\end{center}
+
 \end{document}

### 2019-12-30 nontex/install/linux/fn_vim.Rmd
annotate plan and more vim guide

@@
 
-Vim ships with Debian.
-
-Additional packages to install:
+Vim ships with Debian. Also install neo-vim:
 
@@
 vim
-```
-
-Also install neo-vim
-
-```{bash}
 sudo apt-get install neovim
@@
 
-## Plug-ins
+Just installing onedark, neovim seems to work better than vim.
+Vim has delete lag, and extra white space rows at the bottom of the screen that could take up very large screen segment.
+Neovim with onedark does not have this issue, could be due to some basic setting differences.
 
-Follow the [instructions here](https://github.com/junegunn/vim-plug/wiki/tutorial) for installations. Two steps:
+## Install Vim-Plug Plug-ins manager for Vim
+
+Follow the [instructions here](https://github.com/junegunn/vim-plug/wiki/tutorial) for installations. Several steps:
 
@@
 2. curl plug.vim to ~/.vim/autoload
-3. update ~/.vimrc file with ininstructions regarding which files to install.
+3. update ~/.vimrc file with instructions regarding which files to install.
 4. open vim, type: *:PlugInstall* or *:PlugUpdate*, should start seeing updating packages.
@@
 Plug 'joshdick/onedark.vim'
+
+" List ends here. Plugins become visible to Vim after this call.
+call plug#end()
+
+"""""""""""""""""""""""""""""""""""""""""""""""""
+" Settings
+"""""""""""""""""""""""""""""""""""""""""""""""""
+syntax on
+colorscheme onedark
+```
+
+## Install Vim-Plug Plug-ins manager for Neovim
+
+Follow the [instructions here](https://github.com/junegunn/vim-plug/wiki/tutorial) for installations. Very similar steps as above for Vim:
+
+1. curl *plug.vim* to *.local/share/nvim*. Directory different than vim
+2. create nvim folder under .config, vimrc contents should be in this file: *~/.config/nvim/init.vim*
+3. enter nvim and *:PlugInstall*
+
+```{bash}
+# Neovim (~/.local/share/nvim/site/autoload)
+curl -fLo ~/.local/share/nvim/site/autoload/plug.vim --create-dirs \
+    https://raw.githubusercontent.com/junegunn/vim-plug/master/plug.vim
+
+# create vimrc file
+mkdir ~/.config/nvim
+nvim ~/.config/nvim/init.vim
+
+# paste into file the text below.
+```
+
+Vimrc file with atom styling:
+```
+" Plugins will be downloaded under the specified directory.
+call plug#begin('~/.local/share/nvim/site/plugged')
+
+" Declare the list of plugins.
+Plug 'joshdick/onedark.vim'
+Plug 'vim-airline/vim-airline'
 
@@
 
+# Forward one page and back one page
+# ctrl+f, ctrl+b
+
 # Begin of line
@@
 d
+# delete until end of line, outside insert mode
+D
 ```

### 2019-12-30 nontex/install/linux/fn_vim.Rmd
vim goyo limelight and other colors tests

@@
 
+## Install Neovim in Conda (Windows)
+
+```
+# install scoop and use scoop
+scoop install neovim
+
+# follow vim-plug instructions
+md ~\AppData\Local\nvim\autoload
+$uri = 'https://raw.githubusercontent.com/junegunn/vim-plug/master/plug.vim'
+(New-Object Net.WebClient).DownloadFile(
+  $uri,
+  $ExecutionContext.SessionState.Path.GetUnresolvedProviderPathFromPSPath(
+    "~\AppData\Local\nvim\autoload\plug.vim"
+  )
+)
+```
+
+Create init.vim file:
+
+```
+cd ~\AppData\Local\nvim\
+nvim init.vim
+```
+
+paste these in *:set paste*:
+
+```
+" Plugins will be downloaded under the specified directory.
+call plug#begin('~/AppData/Local/nvim/site/plugged')
+
+" Declare the list of plugins.
+Plug 'vim-airline/vim-airline'
+
+" Visual Settings
+Plug 'junegunn/goyo.vim'
+Plug 'junegunn/limelight.vim'
+
+" Color theme plugins
+Plug 'joshdick/onedark.vim'
+Plug 'morhetz/gruvbox'
+Plug 'junegunn/seoul256.vim'
+Plug 'jaredgorski/spacecamp'
+Plug 'lifepillar/vim-solarized8'
+
+" List ends here. Plugins become visible to Vim after this call.
+call plug#end()
+
+"""""""""""""""""""""""""""""""""""""""""""""""""
+" Color Settings
+"""""""""""""""""""""""""""""""""""""""""""""""""
+
+syntax on
+
+" onedark:
+colorscheme onedark
+
+" seoul256:
+" seoul256 (dark), 236 is darkest
+" let g:seoul256_background = 236
+" colorscheme seoul256
+
+" spacecamp:
+" colorscheme spacecamp
+
+" vim-solarized8:
+" set background=dark
+" colorscheme solarized8
+```
+
 # Vim Basics

### 2019-12-30 nontex/install/linux/fn_vim.Rmd
vim Goyo and Limelight settings

@@
 " Declare the list of plugins.
+Plug 'vim-airline/vim-airline'
+
+" Visual Settings
+Plug 'junegunn/goyo.vim'
+Plug 'junegunn/limelight.vim'
+
+" Color theme plugins
 Plug 'joshdick/onedark.vim'
-Plug 'vim-airline/vim-airline'
 
@@
 """""""""""""""""""""""""""""""""""""""""""""""""
-" Settings
+" Color Settings
 """""""""""""""""""""""""""""""""""""""""""""""""
 syntax on
+
+" For Goyo
+let g:goyo_width=85
+
+" For LimeLight
+" Color name (:help cterm-colors) or ANSI code
+let g:limelight_conceal_ctermfg = 'gray'
+let g:limelight_conceal_ctermfg = 240
+" Color name (:help gui-colors) or RGB color
+let g:limelight_conceal_guifg = 'DarkGray'
+let g:limelight_conceal_guifg = '#777777'
+" highlight line
+let g:limelight_bop = '^.*$'
+let g:limelight_eop = '\n'
+let g:limelight_paragraph_span = 0
+
 colorscheme onedark
+
+"""""""""""""""""""""""""""""""""""""""""""""""""
+" UI Settings
+"""""""""""""""""""""""""""""""""""""""""""""""""
+" Keep cursor in the middle of the page, useful for editing text
+set so=999
+" Turn limelight on by default
+" autocmd VimEnter * Limelight
+" Turn Goyo on by default
+autocmd VimEnter * Goyo
 ```
@@
     - Delete until end of paragraph: *dip*
+    - Delete all text in file: *ggdG*
 

### 2019-12-30 nontex/install/linux/fn_vim.Rmd
vim windows set-up complete

@@
 
+colorscheme onedark
+
+"""""""""""""""""""""""""""""""""""""""""""""""""
+" Visual Settings
+"""""""""""""""""""""""""""""""""""""""""""""""""
 " For Goyo
@@
 let g:limelight_paragraph_span = 0
-
-colorscheme onedark
 
@@
 
+" Markdown
+Plug 'godlygeek/tabular'
+Plug 'plasticboy/vim-markdown'
+
 " Visual Settings
@@
 Plug 'junegunn/limelight.vim'
+Plug 'reedes/vim-pencil'
 
@@
 Plug 'lifepillar/vim-solarized8'
+Plug 'reedes/vim-colors-pencil'
 
@@
 """""""""""""""""""""""""""""""""""""""""""""""""
-
 syntax on
@@
 " colorscheme solarized8
+
+" vim-colors-pencil:
+" let g:pencil_higher_contrast_ui = 0
+" colorscheme pencil
+" set background=dark
+
+"""""""""""""""""""""""""""""""""""""""""""""""""
+" Visual Settings
+"""""""""""""""""""""""""""""""""""""""""""""""""
+" For Goyo
+let g:goyo_width=85
+
+" For LimeLight
+" Color name (:help cterm-colors) or ANSI code
+let g:limelight_conceal_ctermfg = 'gray'
+let g:limelight_conceal_ctermfg = 240
+" Color name (:help gui-colors) or RGB color
+let g:limelight_conceal_guifg = 'DarkGray'
+let g:limelight_conceal_guifg = '#777777'
+" if Limelight should highlight line rather than paragraph
+" let g:limelight_bop = '^.*$'
+" let g:limelight_eop = '\n'
+let g:limelight_paragraph_span = 0
+
+"""""""""""""""""""""""""""""""""""""""""""""""""
+" UI Settings
+"""""""""""""""""""""""""""""""""""""""""""""""""
+" Keep cursor in the middle of the page, useful for editing text
+set so=999
+" Turn limelight on by default
+" autocmd VimEnter * Limelight
+" Turn Goyo on by default
+autocmd VimEnter * Goyo
+
+"""""""""""""""""""""""""""""""""""""""""""""""""
+" Markdown **, * etc settings
+"""""""""""""""""""""""""""""""""""""""""""""""""
+" set concealcursor=n
+" set conceallevel=3
+" hi Asterisks NONE
+" hi AsteriskBold  cterm=bold gui=bold
+" syn match Asterisks contained "**" conceal
+" syn match AsteriskBold "\\\@<!\*\*[^"*|]\+\*\*" contains=Asterisks
+autocmd VimEnter * highlight Normal ctermbg=black
+" ctermfg=grey
+
+"""""""""""""""""""""""""""""""""""""""""""""""""
+" Other Settings
+"""""""""""""""""""""""""""""""""""""""""""""""""
+set paste               " to enable pasting in windows
+```
+
+```
+nvim "C:/Users/d674a/Tex4Econ/_other/equation/multilines.tex"
 ```

### 2019-12-31 nontex/install/git/fs_git_setup.Rmd
bash file for git pull and push

@@
 4. upon leaving a computer with commited changes, push all
+5. create bash file to make it easier to repeat steps
 
@@
 ```
+
+to create bash file to store these (from git bash in windows):
+
+```{bash}
+# store bash file in ~\PyFan\bin
+mkdir ~/PyFan/bin
+cd ~/PyFan/bin
+
+# create bash file
+vim pull_repos
+vim push_repos
+
+# paste the text below over, comfirm bash loc with: which bash
+#!/usr/bin/bash
+echo start fan github pull
+# Security
+eval "$(ssh-agent)"
+ssh-add ~/.ssh/id_rsa
+# Pull from Persistent Repos
+cd ~/fanwangecon.github.io
+git pull github master
+# Stop Secured SSH
+kill $SSH_AGENT_PID
+
+# change permission to make file an executable
+chmod u+x ~/PyFan/bin/pull_repos
+chmod u+x ~/PyFan/bin/push_repos
+# execute script
+bash ~/PyFan/bin/pull_repos
+```

### 2019-12-31 nontex/install/windows/fn_installations.Rmd
vim goyo limelight and other colors tests
bash file for git pull and push

@@
     - apm is the atom package manager.
-2. go to the programs above and try to run.
+2. Pull/Sync with Git and open mulitple projects in atom, follow [guide here](https://fanwangecon.github.io/Tex4Econ/nontex/install/git/fs_git_setup.html).
+3. go to the programs above and try to run.
 
@@
 apm install hydrogen
+apm install project-manager
 # Inside Conda open up atom
 atom
+# open multiple projects from atom at the same time, after repos synced
+atom ~/fanwangecon.github.io ~/Pyfan ~/Teaching ~/Tex4Econ ~/R4Econ ~/M4Econ ~/Py4Econ
 # open up any py from from within, try 1+1, does it work?
@@
 
+## Package Managers
+
+- [scoop](https://github.com/lukesampson/scoop/wiki/Quick-Start)
+
+```
+# in powershell
+# enter cmd
+# type powershell in cmd to enter powershell from cmd
+powershell
+# permission
+set-executionpolicy remotesigned -scope currentuser
+# install
+iwr -useb get.scoop.sh | iex
+```
+
 ## Development Programs

### 2020-01-01 _other/tikz/tree/fs_tikz_gametree.tex
Updates from Overleaf

@@
 }
+
+\section{Grow Tree towards Different Directions}
+
+\begin{center}
+\begin{tikzpicture}[scale=1.5,font=\footnotesize]
+\tikzstyle{level 1}=[level distance=10mm,sibling distance=10mm]
+\tikzstyle{level 2}=[level distance=12mm,sibling distance=7mm]
+\tikzstyle{level 3}=[level distance=6mm,sibling distance=6mm]
+\tikzstyle{level 4}=[level distance=4mm,sibling distance=4mm]
+% B Level 1 point
+\node(0)[solid node,label=left:{$P1$}]{} 
+[grow=right]
+child{
+    [red]
+    node(1)[solid node, label=below:{red dot}]{}
+    }
+child{
+    [purple]
+    node(2)[solid node]{}
+    [grow=right]
+    child
+    child{
+        [black]
+        node(4)[hollow node, green]{}
+        [grow=right]
+        child
+        child{
+            [grow=right]
+            child
+            child
+            child
+            }
+        }
+    child
+    child
+    child{
+            [black]
+            node(5)[hollow node, red]{}
+            [grow=up]
+            child
+            child
+        }
+    }
+child{
+    [black]
+    node(3)[solid node, label=above:{hi there}, green]{}
+    };
+\end{tikzpicture}
+\end{center}
+
+\section{Continuous and Discrete}
 

### 2020-01-01 _other/tikz/tree/fs_tikz_gametree.tex
tikz tree, vim set up, other setup updates

@@
 
+\section{Grow Three to the Right, Discrete and Continuous Muliple}
+
+There are three choices, choose consumption share first, which also means the residual goes to overall investment share.
+
+\begin{enumerate}
+  \item \textbf{continous}, choose consumption, or aggregate investment, rightward bend span, three node, center longer to match bend
+  \item \textbf{continous}, choose investment in capital, type 1 asset, residual goes to type two asset, rightward span, three node, center longer to match bend
+  \item \textbf{discrete}, within type 2 asset, choose a achieve the desired level of type two, rightward, five nodes, equi-distance
+\end{enumerate}
+
+\subsection{Nodes Only}
+
+When developing trees, to simply the problem, first just draw nodes and branches, no text, no benidng, no coloring.
+
+\def\famm{5mm}
+\begin{center}
+\begin{tikzpicture}[scale=1.5,font=\footnotesize]W
+\tikzstyle{level 1}=[level distance=\famm,sibling distance=\famm]
+\tikzstyle{level 2}=[level distance=\famm,sibling distance=\famm]
+\tikzstyle{level 3}=[level distance=\famm,sibling distance=\famm]
+% B Level 1 point
+\node(0)[solid node,label=left:{$P1$}]{}
+[grow=right]
+child
+child{
+    [grow=right]
+    child
+    child{
+        [grow=right]
+        child
+        child
+        child
+        child
+        child
+        }
+    child
+    }
+child;
+\end{tikzpicture}
+\end{center}
+
 % \begin{istgame}[font=\scriptsize]

### 2020-01-01 nontex/install/git/fs_git_setup.Rmd
tikz tree, vim set up, other setup updates

@@
 ```{bash}
-# Initialize Repositories, do these one by one first
+# Pull from Repositories, do these one by one first
 cd ~/fanwangecon.github.io
@@
 ```{bash}
-# Initialize Repositories, do these one by one first
+# Push to Repositories, do these one by one first
 cd ~/fanwangecon.github.io

### 2020-01-01 nontex/install/linux/fn_vim.Rmd
tikz tree, vim set up, other setup updates

@@
 
-## Install Neovim in Conda (Windows)
+## Install Neovim in Windows
+
+Install and access neovim all from windows powershell. Type in *powershell* in regular command prompt for example.
+
+### Install Neovim and Vim-Plug in Windows
 
@@
 
-Create init.vim file:
+### Set up init.vim File in Windows
+
+Inside powershell, create init.vim file:
 
@@
 " if Limelight should highlight line rather than paragraph
-" let g:limelight_bop = '^.*$'
+let g:limelight_bop = '^.*$'
 " let g:limelight_eop = '\n'
@@
 " syn match AsteriskBold "\\\@<!\*\*[^"*|]\+\*\*" contains=Asterisks
-autocmd VimEnter * highlight Normal ctermbg=black
+" autocmd VimEnter * highlight Normal ctermbg=black
 " ctermfg=grey
@@
 ```
+
+### Full Screen Vim Window in Windows
+
+It is nice to have full screen, no distraction work experience.
+To set command prompt to full screen (to get rid of scrolling bar on the right in full screen), use windows command prompt which allows for full screen, right click on window top border, choose property, then choose layout, then set height and width of window size and buffer size to be the same.
+This will allow for full screen experience.
 

### 2020-01-01 nontex/install/windows/fn_installations.Rmd
tikz tree, vim set up, other setup updates

@@
 apm install project-manager
+apm install sublime-style-column-selection
+
 # Inside Conda open up atom
 atom
+
 # open multiple projects from atom at the same time, after repos synced
@@
 3. latex packages from distributions
-3. editor (gui): Atom, texStudio, etc
+3. editor (gui): Atom, Sublime text, texStudio, etc
 
@@
 
-## Development Programs
+## Editors
 
-- [pycharm](https://www.jetbrains.com/pycharm/)
+In addition to Atom.
+
+### Notepad++
+
+[Notepad++](https://notepad-plus-plus.org/downloads/v7.8.2/). Many old projects have xml folder structures for Notepad++.
+
+- Silently update file changes made in other editors: Settings, Preferences, MISC., File Status Auto Detection, Update Silently.
+### Sublime
+
+[Sublime](https://www.sublimetext.com/3)
+
+there are some issues with atom.
+When a file is edited inside Vim, when changes are saved, a [temp file is created in atom](https://github.com/atom/atom/issues/17186).
+Sublime would, however, still show the file with the changes.
+This makes dual screen editing very difficult.
+Sublime text is used for this situation.
+
+*Sublime Setup*:
+
+- [r and rmd setup](https://weibeld.net/r/rmd_sublime_package.html)
+
+### PyCharm
+
+[pycharm](https://www.)jetbrains.com/pycharm/)
 

### 2020-01-03 nontex/install/linux/fn_vim.Rmd
VSCode with R and Linux Setup

@@
 let g:limelight_bop = '^.*$'
-let g:limelight_eop = '\n'
+" let g:limelight_eop = '\n'
 let g:limelight_paragraph_span = 0
@@
 autocmd VimEnter * Goyo
+" autocmd VimEnter * AirlineToggle
+" In Goyo, if airline is turned on, do nto show scratch area
+" autocmd! User GoyoEnter nested set eventignore=FocusGained
+" autocmd! User GoyoLeave nested set eventignore=
 ```
@@
 
-# Vim Editing
-
-Delete a line.
-
-```{bash}
-# select text with cursor, then d for delete
-d
-# delete until end of line, outside insert mode
-D
-```
-
 # Very Convinent Functions
@@
 
+## Vim go to Spot in Text Quickly
+
+```
+# ESC
+# Search for word
+/abc
+# esc
+# next occurance of word
+n
+# last occurance
+N
+# first occurance overall
+ggn
+# last occurance overall
+G
+# clear search highlighting
+:noh
+```
+
+back to previous point
+
+```
+~.
+```
+
 ## Combo Operations
@@
     - Delete all text in file: *ggdG*
+
+## Vim Statistics
+
+- word count: *g, ctrl+g*
 
@@
 
-# Vim Set-Up
+# Vim Set-Up Others
 
-Use [one-dark atom theme](https://github.com/joshdick/onedark.vim), otherwise color hard to read.
+## Chromebook
 
-```{bash}
+pressing esc key is an issue, too far away. On chromebook, remap the search key which is in the spot of the caps lock key to esc. and remap the esc key to search key.
 
-```
+1. search for keyboard under settings
+2. launcher to escape, and escape to launcher

### 2020-01-03 nontex/install/windows/fn_installations.Rmd
VSCode with R and Linux Setup

@@
 
+*note*: Github people seem to have slowed down updating Atom since microsoft acquisition
+
 # Conda
@@
 ###############################
-# C:/ProgramData/Anaconda3/Scripts
-# C:/ProgramData/Anaconda3
+# C:\ProgramData\Anaconda3\Scripts
+# C:\ProgramData\Anaconda3
 ```
@@
 ```{bash}
-# # if there are bugs
+# if there are bugs
 # conda clean --packages
@@
 
-```{r}
+```{bash}
 # windows
@@
 apm install sublime-style-column-selection
+apm install minimap
+
+# vim distraction free editing
+apm install vim-mode-plus
+apm install zen
 
@@
 
-```
+```{bash}
 # in powershell
@@
 
-In addition to Atom.
+In addition to Atom, which is pretty slow, and harder to run on lower spec computers.
+
+### VSCode
+
+VSCode is much more light-weight than Atom, does not have hydrogen.
+
+```{bash}
+# Debian Install
+curl https://packages.microsoft.com/keys/microsoft.asc | gpg --dearmor > microsoft.gpg
+sudo install -o root -g root -m 644 microsoft.gpg /usr/share/keyrings/microsoft-archive-keyring.gpg
+sudo sh -c 'echo "deb [arch=amd64 signed-by=/usr/share/keyrings/microsoft-archive-keyring.gpg] https://packages.microsoft.com/repos/vscode stable main" > /etc/apt/sources.list.d/vscode.list'
+sudo apt-get install apt-transport-https
+sudo apt-get update
+sudo apt-get install code # or code-insiders
+
+# Change Font (https://www.reddit.com/r/Crostini/comments/cesxr0/vscode_ui_and_fonts_too_small_heres_how_to_fix_it/)
+# modify: /usr/share/applications/code.desktop
+nvim /usr/share/applications/code.desktop
+#replace this line: Exec=/usr/share/code/code --unity-launch %F
+Exec=sommelier -X --scale=0.8 --dpi=160 /usr/share/code/code "--unity-launch %F"
+#replace this line: Exec=/usr/share/code/code --new-window %F
+Exec=sommelier -X --scale=0.8 --dpi=160 /usr/share/code/code "--new-window %F"
+
+# Open File
+# low density mode to see cleary
+code
+```
+
+Extensions to Download for VSCode:
+
+2. [Microsoft Python Extension](https://marketplace.visualstudio.com/items?itemName=ms-python.python)
+
+```{bash}
+ext install ms-python.python
+ext install latex-workshop
+```
+
+#### VSCode Shortcuts
+
+- Open up Settings: *Ctrl + ,*
+- Preview Markdown in VSCode: *Ctrl + Shift + V*
+- Open up left pane: *Ctrl + B*
+- Wrap Text: *alt + Z*, switch between wrap or not to save screen space for example.
+
+#### VSCode Benefits
+
+1. open a file, if have workspace where the file is in, automatically expand tree and show where file is on left pane.
+
+#### VSCode and R
+
+VSCode works pretty well it seems with Rmd files.
+Rmd files are useful to work through algorithm, examples in preparation for writing usable functions.
+Rstudio has been often very slow for me, and I generally feel like can not stretch around and work in RStudio IDE.
+
+In Atom, Hydrogen works, but really only works with very basic line by line testing.
+
+Using VSCode with RMD files seems much quicker, and there is room to breath.
+
+1. Install R following R installation instructions.
+2.
+Then install extension [R](https://marketplace.visualstudio.com/items?itemName=Ikuyadeu.r).
+Microsoft stopped supporting rmd in VSCode: [R Tools for Visual Studio](https://github.com/microsoft/RTVS)
+3. properly set path (might have to call vscode from r env)
+    + *r.rterm.linux*: */home/wangfanbsg75/anaconda3/envs/r_env/bin/R*
+4. Run:
+    - ctrl + enter to activate R terminal
+    - VSCode 2019 allows for Knit Rmd: *Ctrl + Shift + K*
+    - also can run code segment: select lines and *ctrl + enter*
+
+#### VSCode and Latex
+
+1. download [Latex Workshop](https://marketplace.visualstudio.com/items?itemName=James-Yu.latex-workshop)
 
@@
 - Silently update file changes made in other editors: Settings, Preferences, MISC., File Status Auto Detection, Update Silently.
+
 ### Sublime
@@
 Sublime text is used for this situation.
+
+```{bash}
+# Sublime Linux
+wget -qO - https://download.sublimetext.com/sublimehq-pub.gpg | sudo apt-key add -
+sudo apt-get install apt-transport-https
+echo "deb https://download.sublimetext.com/ apt/stable/" | sudo tee /etc/apt/sources.list.d/sublime-text.list
+sudo apt-get update
+sudo apt-get install sublime-text
+# launch from terminal
+subl
+```
 
@@
     + Windows: install okular from windows app store
+    + Okular configure shortcuts: setting, configure shortcuts
+    + Okular if menu bar lost: *Ctrl + m*
+    + Okular comment pane: *F6*
+    + Okular close left pane: *F7*
+    + Okular full scrren: *Ctrl + Shift + F*
+        * unlike acrobat, pdf allows for multiple scrrens
+    + Okular 3 pages per row view:
+        * view, overview
+    + Automatic Update when PDF updated elsewhere
+        * this is one of the key reasons to use okular, when I knit a Rmd file to PDF, the currently open Okular PDF file automatically updates and does not give file is open error like Acrobat.
+    + Background color:
+        * can easily change background color to non-white.
 - PDF Adobe Acrobat

### 2020-01-03 nontex/install/windows/fn_installations.tex
VSCode with R and Linux Setup

@@
-% Options for packages loaded elsewhere
-\PassOptionsToPackage{unicode}{hyperref}
-\PassOptionsToPackage{hyphens}{url}
-\PassOptionsToPackage{dvipsnames,svgnames*,x11names*}{xcolor}
-%
-\documentclass[
-]{article}
+\documentclass[]{article}
 \usepackage{lmodern}
@@
 \usepackage{ifxetex,ifluatex}
+\usepackage{fixltx2e} % provides \textsubscript
 \ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
@@
   \usepackage[utf8]{inputenc}
-  \usepackage{textcomp} % provide euro and other symbols
-\else % if luatex or xetex
-  \usepackage{unicode-math}
-  \defaultfontfeatures{Scale=MatchLowercase}
-  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
+\else % if luatex or xelatex
+  \ifxetex
+    \usepackage{mathspec}
+  \else
+    \usepackage{fontspec}
   \fi
-% Use upquote if available, for straight quotes in verbatim environments
+  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
+\fi
+% use upquote if available, for straight quotes in verbatim environments
 \IfFileExists{upquote.sty}{\usepackage{upquote}}{}
-\IfFileExists{microtype.sty}{% use microtype if available
-  \usepackage[]{microtype}
+% use microtype if available
+\IfFileExists{microtype.sty}{%
+\usepackage{microtype}
 \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
 }{}
-\makeatletter
-\@ifundefined{KOMAClassName}{% if non-KOMA class
-  \IfFileExists{parskip.sty}{%
-    \usepackage{parskip}
-  }{% else
-    \setlength{\parindent}{0pt}
-    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
-}{% if KOMA class
-  \KOMAoptions{parskip=half}}
-\makeatother
-\usepackage{xcolor}
-\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
-\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
-\hypersetup{
-  pdftitle={New Windows Computer Data-Science Set-up: Python (anaconda, pycharm), R (r-studio) and other Programs Installations},
+\usepackage[margin=1in]{geometry}
+\usepackage{hyperref}
+\PassOptionsToPackage{usenames,dvipsnames}{color} % color is loaded by hyperref
+\hypersetup{unicode=true,
+            pdftitle={New Computer Data-Science Set-up: Python (anaconda, pycharm), R (r-studio) and other Programs Installations},
             colorlinks=true,
             linkcolor=Maroon,
-  filecolor=Maroon,
             citecolor=Blue,
             urlcolor=blue,
-  pdfcreator={LaTeX via pandoc}}
-\urlstyle{same} % disable monospaced font for URLs
-\usepackage[margin=1in]{geometry}
+            breaklinks=true}
+\urlstyle{same}  % don't use monospace font for urls
 \usepackage{color}
@@
 \setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
-% Set default figure placement to htbp
-\makeatletter
-\def\fps@figure{htbp}
-\makeatother
+\IfFileExists{parskip.sty}{%
+\usepackage{parskip}
+}{% else
+\setlength{\parindent}{0pt}
+\setlength{\parskip}{6pt plus 2pt minus 1pt}
+}
 \setlength{\emergencystretch}{3em}  % prevent overfull lines
@@
 \setcounter{secnumdepth}{5}
+% Redefines (sub)paragraphs to behave more like sections
+\ifx\paragraph\undefined\else
+\let\oldparagraph\paragraph
+\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
+\fi
+\ifx\subparagraph\undefined\else
+\let\oldsubparagraph\subparagraph
+\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
+\fi
 
-\title{New Windows Computer Data-Science Set-up: Python (anaconda, pycharm), R
+%%% Use protect on footnotes to avoid problems with footnotes in titles
+\let\rmarkdownfootnote\footnote%
+\def\footnote{\protect\rmarkdownfootnote}
+
+%%% Change title format to be more compact
+\usepackage{titling}
+
+% Create subtitle command for use in maketitle
+\providecommand{\subtitle}[1]{
+  \posttitle{
+    \begin{center}\large#1\end{center}
+    }
+}
+
+\setlength{\droptitle}{-2em}
+
+  \title{New Computer Data-Science Set-up: Python (anaconda, pycharm), R
 (r-studio) and other Programs Installations}
+    \pretitle{\vspace{\droptitle}\centering\huge}
+  \posttitle{\par}
     \author{}
-\date{\vspace{-2.5em}}
+    \preauthor{}\postauthor{}
+    \date{}
+    \predate{}\postdate{}
 
@@
 Repository}.
+
+\hypertarget{objective}{%
+\section{Objective}\label{objective}}
+
+For the following types of programming tasks, install relevant programs,
+that are cross platform compatible. Test at the end that example
+programs work.
+
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi}.}
+\tightlist
+\item
+  Python
+
+  \begin{itemize}
+  \tightlist
+  \item
+    Anaconda Dist
+  \item
+    Pycharm
+  \item
+    atom hydrogen
+  \end{itemize}
+\item
+  R
+
+  \begin{itemize}
+  \tightlist
+  \item
+    R
+  \item
+    Rstudio
+  \item
+    atom hydrogen
+  \end{itemize}
+\item
+  Matlab
+
+  \begin{itemize}
+  \tightlist
+  \item
+    Matlab
+  \end{itemize}
+\item
+  Latex and PDF
+
+  \begin{itemize}
+  \tightlist
+  \item
+    atom latex
+  \item
+    texstudio
+  \item
+    texlive
+  \item
+    okular pdf
+  \end{itemize}
+\end{enumerate}
+
+Test at the end:
+
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi}.}
+\tightlist
+\item
+  Do sample \emph{py} files work?
+
+  \begin{itemize}
+  \tightlist
+  \item
+    work from command line?
+  \item
+    work from atom (hydrogen)
+  \end{itemize}
+\item
+  Do sample \emph{rmd} files work?
+
+  \begin{itemize}
+  \tightlist
+  \item
+    work from r-studio
+  \item
+    work from atom (hydrogen), r file
+  \end{itemize}
+\item
+  Do tex templates compile?
+
+  \begin{itemize}
+  \tightlist
+  \item
+    tikz files
+  \item
+    template files with bib
+  \end{itemize}
+\end{enumerate}
+
+\emph{note}: Github people seem to have slowed down updating Atom since
+microsoft acquisition
 
@@
 
+To install conda in Debian, follow
+\href{https://fanwangecon.github.io/Tex4Econ/nontex/install/linux/fn_ubuntu.html}{these
+instructions}.
+
 See Anaconda Installation Directory, in anaconda prompt:
@@
 \begin{Highlighting}[]
+\CommentTok{# To remove conda Fully}
+\FunctionTok{rm}\NormalTok{ -rf ~/anaconda3}
+
 \ExtensionTok{where}\NormalTok{ anaconda}
@@
 \CommentTok{###############################}
-\CommentTok{# C:/ProgramData/Anaconda3/Scripts}
-\CommentTok{# C:/ProgramData/Anaconda3}
+\CommentTok{# C:\textbackslash{}ProgramData\textbackslash{}Anaconda3\textbackslash{}Scripts}
+\CommentTok{# C:\textbackslash{}ProgramData\textbackslash{}Anaconda3}
 \end{Highlighting}
@@
 \begin{Highlighting}[]
-\CommentTok{# # if there are bugs}
+\CommentTok{# if there are bugs}
 \CommentTok{# conda clean --packages}
 \CommentTok{# use conda-forge as main channel, more updated packages}
+\ExtensionTok{conda}\NormalTok{ config --get channels}
 \ExtensionTok{conda}\NormalTok{ config --add channels conda-forge}
+\ExtensionTok{conda}\NormalTok{ config --get channels}
+\CommentTok{# remove conda-forge from channels (do so for main env install)}
+\ExtensionTok{conda}\NormalTok{ config --remove channels conda-forge}
 \CommentTok{# normal update}
 \ExtensionTok{conda}\NormalTok{ update --all}
+
+\CommentTok{# install additional packages}
+\ExtensionTok{conda}\NormalTok{ install -y statsmodels datashape seaborn}
+\ExtensionTok{conda}\NormalTok{ install -c conda-forge -y interpolation awscli}
+\ExtensionTok{conda}\NormalTok{ install -c anaconda -y boto3}
 \end{Highlighting}
@@
 
+Fist test python under command line:
+
 \begin{Shaded}
@@
 \CommentTok{# windows}
-\NormalTok{python }\StringTok{"C:/Users/fan/PyFan/ProjectSupport/Testing/Numpy/Functions.py"}
-\NormalTok{python }\StringTok{"C:/Users/fan/PyFan/ProjectSupport/graph/subplot.py"}
+\ExtensionTok{python} \StringTok{"C:/Users/fan/PyFan/ProjectSupport/Testing/Numpy/Functions.py"}
+\ExtensionTok{python} \StringTok{"C:/Users/fan/PyFan/ProjectSupport/graph/subplot.py"}
 \CommentTok{# linux}
-\NormalTok{python }\OperatorTok{~}\ErrorTok{/}\NormalTok{PyFan}\OperatorTok{/}\NormalTok{ProjectSupport}\OperatorTok{/}\NormalTok{Testing}\OperatorTok{/}\NormalTok{Numpy}\OperatorTok{/}\NormalTok{Functions.py}
-\NormalTok{python }\OperatorTok{~}\ErrorTok{/}\NormalTok{PyFan}\OperatorTok{/}\NormalTok{ProjectSupport}\OperatorTok{/}\NormalTok{graph}\OperatorTok{/}\NormalTok{subplot.py}
+\ExtensionTok{python}\NormalTok{ ~/PyFan/ProjectSupport/Testing/Numpy/Functions.py}
+\ExtensionTok{python}\NormalTok{ ~/PyFan/ProjectSupport/graph/subplot.py}
 \end{Highlighting}
@@
 
-\hypertarget{additional-packages}{%
-\subsection{Additional Packages}\label{additional-packages}}
+\hypertarget{jupyter-and-atom-hydrogen}{%
+\subsection{Jupyter and Atom Hydrogen}\label{jupyter-and-atom-hydrogen}}
+
+For both Jupyter as well as Atom, always open from command prompt, open
+from \emph{Anaconda Prompt} with admin rights.
+
+First, open up \emph{Jupyter Notebook}, does the python kernel work? If
+does not, uninstall and re-install Anaconda.
 
@@
 \begin{Highlighting}[]
-\NormalTok{conda install statsmodels datashape seaborn}
-\CommentTok{# conda install statsmodels}
-\CommentTok{# conda install datashape}
-\CommentTok{# conda install seaborn}
+\CommentTok{# start jupyter lab, from prompt}
+\ExtensionTok{jupyter}\NormalTok{ lab}
+\end{Highlighting}
+\end{Shaded}
 
-\NormalTok{conda install }\OperatorTok{-}\NormalTok{c conda}\OperatorTok{-}\NormalTok{forge interpolation awscli}
-\CommentTok{# conda install -c conda-forge interpolation}
-\CommentTok{# conda install -c conda-forge awscli}
+Now test python within atom:
 
-\NormalTok{conda install }\OperatorTok{-}\NormalTok{c anaconda boto3}
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi}.}
+\tightlist
+\item
+  install hydrogen in atom. Follow
+  \href{http://nteract.io/atom}{instructions}.
 
-\NormalTok{conda install }\OperatorTok{-}\NormalTok{c r r}\OperatorTok{-}\NormalTok{irkernel}
+  \begin{itemize}
+  \tightlist
+  \item
+    terminal in windows or linux after installation: \emph{apm install
+    hydrogen}
+  \item
+    apm is the atom package manager.
+  \end{itemize}
+\item
+  Pull/Sync with Git and open mulitple projects in atom, follow
+  \href{https://fanwangecon.github.io/Tex4Econ/nontex/install/git/fs_git_setup.html}{guide
+  here}.
+\item
+  go to the programs above and try to run.
+\end{enumerate}
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\CommentTok{# Once atom is installed, can use apm to install packages}
+\FunctionTok{apm}\NormalTok{ install hydrogen}
+\FunctionTok{apm}\NormalTok{ install project-manager}
+\FunctionTok{apm}\NormalTok{ install sublime-style-column-selection}
+\FunctionTok{apm}\NormalTok{ install minimap}
+
+\CommentTok{# vim distraction free editing}
+\FunctionTok{apm}\NormalTok{ install vim-mode-plus}
+\FunctionTok{apm}\NormalTok{ install zen}
+
+\CommentTok{# Inside Conda open up atom}
+\ExtensionTok{atom}
+
+\CommentTok{# open multiple projects from atom at the same time, after repos synced}
+\ExtensionTok{atom}\NormalTok{ ~/fanwangecon.github.io ~/Pyfan ~/Teaching ~/Tex4Econ ~/R4Econ ~/M4Econ ~/Py4Econ}
+\CommentTok{# open up any py from from within, try 1+1, does it work?}
+\CommentTok{# also use script, try ctrl + shift + b, run whole file (not hydrogen)}
 \end{Highlighting}
@@
 \hypertarget{fully-uninstall-r}{%
-\subsection{Fully uninstall r}\label{fully-uninstall-r}}
+\subsection{Fully Uninstall r}\label{fully-uninstall-r}}
 
-open up RStudio, and see where paths are. also open up R from command
+Open up RStudio, and see where paths are. also open up R from command
 prompt, see where paths are.
@@
 
+For Linux:
+
+\begin{itemize}
+\tightlist
+\item
+  if used apt-get to install, R installed under main user drive,
+  deactivate conda, and check which conda
+\end{itemize}
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\CommentTok{# Exit Conda}
+\ExtensionTok{conda}\NormalTok{ deactivate}
+\CommentTok{# where is R installed outside of Conda}
+\FunctionTok{which}\NormalTok{ R}
+\CommentTok{# /usr/bin/R}
+\CommentTok{# To remove all}
+\FunctionTok{sudo}\NormalTok{ apt-get remove r-base}
+\FunctionTok{sudo}\NormalTok{ apt-get remove r-base-core}
+
+\CommentTok{# Inside Conda base}
+\ExtensionTok{conda}\NormalTok{ activate}
+\CommentTok{# Conda r_env}
+\ExtensionTok{conda}\NormalTok{ activate r_env}
+\CommentTok{# Where is it installed?}
+\FunctionTok{which}\NormalTok{ R}
+\CommentTok{# /home/wangfanbsg75/anaconda3/bin/R}
+\ExtensionTok{conda}\NormalTok{ uninstall r-base}
+\end{Highlighting}
+\end{Shaded}
+
 \hypertarget{install-r-outside-of-conda}{%
@@
   \href{https://cloud.r-project.org/}{download R}
+
+  \begin{itemize}
+  \tightlist
+  \item
+    for debian:
+    \href{https://cran.r-project.org/bin/linux/debian/}{Johannes Ranke}
+  \end{itemize}
 \item
@@
 not up to date, this could be the case with default R versions for some
-linux installations.
+linux installations. For Debian for example, need to update the
+\emph{source.list} to include sources that have more recent versions of
+R.
+
+Additionally, need to install \emph{libcurl4-openssl-dev} and
+\emph{libssl-dev} from command prompt first inside Debian.
 
@@
 \begin{Highlighting}[]
-\CommentTok{# Install R-tools}
+\CommentTok{# If inside Debian, due to some tidymodel install issues, do this`}
+\ExtensionTok{conda}\NormalTok{ install -c r r}
+\ExtensionTok{conda}\NormalTok{ install -c r r-essentials}
+\ExtensionTok{conda}\NormalTok{ install -c r r-igraph}
+\ExtensionTok{conda}\NormalTok{ install -c conda-forge igraph}
+
+\CommentTok{# Go to get latesdebian latest r sources.list}
+\FunctionTok{cat}\NormalTok{ /etc/apt/sources.list}
+\CommentTok{# Install this First (should already be installed)}
+\FunctionTok{sudo}\NormalTok{ apt install dirmngr}
+
+\CommentTok{# Debian R is maintained by Johannes Ranke, copied from https://cran.r-project.org/bin/linux/debian/:}
+\ExtensionTok{apt-key}\NormalTok{ adv --keyserver keys.gnupg.net --recv-key }\StringTok{'E19F5F87128899B192B1A2C2AD5F960A256A04AF'}
+\CommentTok{# Add to source.list, for debian stretch (9)}
+\CommentTok{# sudo su added for security issue as super-user}
+\FunctionTok{sudo}\NormalTok{ su -c }\StringTok{"sudo echo 'deb http://cloud.r-project.org/bin/linux/debian stretch-cran35/' >> /etc/apt/sources.list"}
+\CommentTok{# if added wrong lines, delete 3rd line}
+\FunctionTok{sudo}\NormalTok{ sed }\StringTok{'3d'}\NormalTok{ /etc/apt/sources.list}
+
+\CommentTok{# Update and Install R, should say updated from cloud.r}
+\FunctionTok{sudo}\NormalTok{ apt-get update}
+\FunctionTok{sudo}\NormalTok{ apt-get install r-base r-base-dev}
+
+\CommentTok{# Also install these, otherwise r-packages do not install}
+\CommentTok{# libxml2 seems need for tidymodels}
+\FunctionTok{sudo}\NormalTok{ apt-get install libcurl4-openssl-dev}
+\FunctionTok{sudo}\NormalTok{ apt-get install libssl-dev}
+\FunctionTok{sudo}\NormalTok{ apt-get install libxml2-dev}
+\end{Highlighting}
+\end{Shaded}
+
+Which R?
+
+\begin{itemize}
+\tightlist
+\item
+  \emph{export RSTUDIO\_WHICH\_R=/usr/bin/R}
+\item
+  \emph{export RSTUDIO\_WHICH\_R=/home/wangfanbsg75/anaconda3/bin/R}
+\end{itemize}
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\CommentTok{# Can enter R from Command Prompt Conda ENV, much faster than from r-studio}
+\CommentTok{# Install R-tools, RTOOLS is for WINDOWS}
 \KeywordTok{install.packages}\NormalTok{(}\StringTok{"installr"}\NormalTok{)}
@@
 \KeywordTok{install.Rtools}\NormalTok{()}
-\CommentTok{# c:\textbackslash{}Rtools\textbackslash{}bin;}
-\CommentTok{# c:\textbackslash{}Rtools\textbackslash{}mingw_32\textbackslash{}bin;}
-\CommentTok{# c:\textbackslash{}Rtools\textbackslash{}mingw_64\textbackslash{}bin;}
+\CommentTok{# c:/Rtools/bin;}
+\CommentTok{# c:/Rtools/mingw_32/bin;}
+\CommentTok{# c:/Rtools/mingw_64/bin;}
 
 \CommentTok{# main packagevps}
-\KeywordTok{install.packages}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\StringTok{"tidyr"}\NormalTok{, }\StringTok{"tidyverse"}\NormalTok{, }\StringTok{"tidymodels"}\NormalTok{))}
+\CommentTok{# tidymodel installation on linux difficult}
+\KeywordTok{install.packages}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\StringTok{"tidyverse"}\NormalTok{, }\StringTok{"tidymodels"}\NormalTok{, }\StringTok{"tidyr"}\NormalTok{))}
 \CommentTok{# development packages}
-\KeywordTok{install.packages}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\StringTok{"devtools"}\NormalTok{, }\StringTok{"irkernel"}\NormalTok{, }\StringTok{"pkgdown"}\NormalTok{, }\StringTok{"roxygen2"}\NormalTok{))}
+\KeywordTok{install.packages}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\StringTok{"devtools"}\NormalTok{, }\StringTok{"IRkernel"}\NormalTok{, }\StringTok{"pkgdown"}\NormalTok{, }\StringTok{"roxygen2"}\NormalTok{, }\StringTok{"kableExtra"}\NormalTok{))}
 \CommentTok{# other packages}
-\KeywordTok{install.packages}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\StringTok{"AER"}\NormalTok{, }\StringTok{"minpack.lm"}\NormalTok{, }\StringTok{"knitr"}\NormalTok{, }\StringTok{"kableExtra"}\NormalTok{, }\StringTok{"matlab"}\NormalTok{))}
+\KeywordTok{install.packages}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\StringTok{"AER"}\NormalTok{, }\StringTok{"minpack.lm"}\NormalTok{, }\StringTok{"knitr"}\NormalTok{, }\StringTok{"matlab"}\NormalTok{))}
 
-\CommentTok{# Install my package}
+\CommentTok{# Install my package, need to prepare package to work for ubuntu}
+\CommentTok{# if install does not work, load locally}
 \NormalTok{devtools}\OperatorTok{::}\KeywordTok{install_github}\NormalTok{(}\StringTok{"fanwangecon/R4Econ"}\NormalTok{)}
+
+\CommentTok{# Kernel}
+\KeywordTok{install.packages}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\StringTok{'repr'}\NormalTok{, }\StringTok{'IRdisplay'}\NormalTok{, }\StringTok{'evaluate'}\NormalTok{, }\StringTok{'crayon'}\NormalTok{, }\StringTok{'pbdZMQ'}\NormalTok{, }\StringTok{'devtools'}\NormalTok{, }\StringTok{'uuid'}\NormalTok{, }\StringTok{'digest'}\NormalTok{))}
+\NormalTok{IRkernel}\OperatorTok{::}\KeywordTok{installspec}\NormalTok{()}
 \end{Highlighting}
@@
 \begin{Highlighting}[]
-\CommentTok{# Set up Channel}
-\ExtensionTok{conda}\NormalTok{ config --add channels conda-forge}
+\CommentTok{# outside of conda, install some depencies}
+\FunctionTok{sudo}\NormalTok{ apt-get install libcurl4-openssl-dev}
+\FunctionTok{sudo}\NormalTok{ apt-get install libssl-dev}
+\FunctionTok{sudo}\NormalTok{ apt-get install libxml2-dev}
+
 \CommentTok{# install key r packages within a r-environment}
 \ExtensionTok{conda}\NormalTok{ env remove -n r_env}
-\ExtensionTok{conda}\NormalTok{ create -n r_env r-essentials r-base r-tidyr r-tidyverse r-devtools r-irkernel r-pkgdown r-roxygen2}
+\CommentTok{# start empty environment}
+\ExtensionTok{conda}\NormalTok{ create -n r_env}
+\CommentTok{# activate env and check, nothing yet}
+\ExtensionTok{conda}\NormalTok{ activate r_env}
+\ExtensionTok{conda}\NormalTok{ list}
+
+\CommentTok{# check channel and add env specific channel}
+\ExtensionTok{conda}\NormalTok{ config --get channels}
+\CommentTok{# to get latest r, use conda-forge, which has more recent Rs}
+\CommentTok{# conda config --env --add channels conda-forge}
+\CommentTok{# channels for base}
+\ExtensionTok{conda}\NormalTok{ config --get channels}
+\CommentTok{# channels for cur env}
+\ExtensionTok{conda}\NormalTok{ config --get channels --env}
+
+\CommentTok{# install files}
+\ExtensionTok{conda}\NormalTok{ install -n r_env -c r r r-essentials r-tidyverse r-tidymodels -y}
+
+\CommentTok{# trouble with igraph installation, install here from conda}
+\CommentTok{# conda install -n r_env r-essentials r-base r-tidyr r-tidyverse r-devtools r-irkernel r-pkgdown r-roxygen2}
+\ExtensionTok{conda}\NormalTok{ install -n r_env -c r r-igraph}
+\ExtensionTok{conda}\NormalTok{ install -n r_env -c conda-forge igraph}
+\ExtensionTok{conda}\NormalTok{ install -n r_env -c r r-rstantools r-rstan r-rstanarm -y}
+
 \CommentTok{# see all installed environments}
@@
 
-This did not work in windows, \emph{tidymodels} failed to install.
-Perhaps because of directory issues. \emph{tidymodels} required
-\emph{rstanarm}, and \emph{rstanarm} failed to install.
+\emph{tidymodel} has installation issues sometimes.
+
+In \emph{r\_env}, type in \emph{R}, and then install from inside
+terminal's R:
 
@@
 \begin{Highlighting}[]
-\CommentTok{### One line}
-\ExtensionTok{conda}\NormalTok{ install -c conda-forge r-aer r-minpack.lm r-knitr r-kableExtra r-matlab}
-\CommentTok{# conda install -c conda-forge r-rstanarm}
+\CommentTok{# enter into env}
+\ExtensionTok{conda}\NormalTok{ activate r_env}
+\CommentTok{# enter R or type in rstudio}
+\CommentTok{# sicne R is only install inside r_env, has to enter rstudio from r_env}
+\ExtensionTok{R}
+\ExtensionTok{rstudio}
 
-\CommentTok{#######################################}
-\CommentTok{### Estimation}
-\CommentTok{#######################################}
-\CommentTok{# Estimation Tools}
-\CommentTok{# tidymodels does not work fron conda install}
-\CommentTok{# Linear Regression Package}
-\CommentTok{# https://anaconda.org/conda-forge/r-aer}
-\CommentTok{# Nonlinear Regression Package}
-\CommentTok{# https://anaconda.org/conda-forge/r-minpack.lm}
-\ExtensionTok{conda}\NormalTok{ install -c conda-forge r-aer r-minpack.lm}
-\CommentTok{# enter r and use devtools}
-\CommentTok{# install.packages("tidymodels")}
+\CommentTok{# main packagevps}
+\CommentTok{# tidymodel installation on linux difficult}
+\ExtensionTok{install.packages}\NormalTok{(c(}\StringTok{"rstantools"}\NormalTok{, }\StringTok{"rstan"}\NormalTok{, }\StringTok{"rstanarm"}\NormalTok{))}
+\ExtensionTok{install.packages}\NormalTok{(c(}\StringTok{"tidyr"}\NormalTok{, }\StringTok{"tidyverse"}\NormalTok{, }\StringTok{"tidymodels"}\NormalTok{))}
 
-\CommentTok{#######################################}
-\CommentTok{### Visualiation}
-\CommentTok{#######################################}
-\ExtensionTok{conda}\NormalTok{ install -c conda-forge r-knitr r-kableExtra}
+\CommentTok{# tidymodels}
+\CommentTok{# development packages}
+\ExtensionTok{install.packages}\NormalTok{(c(}\StringTok{"devtools"}\NormalTok{, }\StringTok{"IRkernel"}\NormalTok{, }\StringTok{"pkgdown"}\NormalTok{, }\StringTok{"roxygen2"}\NormalTok{, }\StringTok{"kableExtra"}\NormalTok{))}
+\CommentTok{# other packages}
+\ExtensionTok{install.packages}\NormalTok{(c(}\StringTok{"AER"}\NormalTok{, }\StringTok{"minpack.lm"}\NormalTok{, }\StringTok{"knitr"}\NormalTok{, }\StringTok{"matlab"}\NormalTok{))}
 
-\CommentTok{#######################################}
-\CommentTok{### Utilities}
-\CommentTok{#######################################}
-\CommentTok{# Allowing for Invoking Matlab Files from Inside R}
-\ExtensionTok{conda}\NormalTok{ install -c conda-forge r-matlab}
+\CommentTok{# Install my package, need to prepare package to work for ubuntu}
+\CommentTok{# if install does not work, load locally}
+\ExtensionTok{devtools}\NormalTok{::install_github(}\StringTok{"fanwangecon/R4Econ"}\NormalTok{)}
+
+\CommentTok{# Kernel}
+\ExtensionTok{install.packages}\NormalTok{(c(}\StringTok{'repr'}\NormalTok{, }\StringTok{'IRdisplay'}\NormalTok{, }\StringTok{'evaluate'}\NormalTok{, }\StringTok{'crayon'}\NormalTok{, }\StringTok{'pbdZMQ'}\NormalTok{, }\StringTok{'devtools'}\NormalTok{, }\StringTok{'uuid'}\NormalTok{, }\StringTok{'digest'}\NormalTok{))}
+\FunctionTok{IRkernel::installspec()}
 \end{Highlighting}
@@
 \FunctionTok{wget} \StringTok{"https://download1.rstudio.org/desktop/bionic/amd64/rstudio-1.2.5033-amd64.deb"}
+\OperatorTok{<}\NormalTok{!}\ExtensionTok{--}\NormalTok{ for debian --}\OperatorTok{>}
 \FunctionTok{sudo}\NormalTok{ apt install ./rstudio-1.2.5033-amd64.deb}
-\OperatorTok{<}\NormalTok{!}\ExtensionTok{--}\NormalTok{ for debian --}\OperatorTok{>}
 \FunctionTok{wget} \StringTok{"https://download1.rstudio.org/desktop/debian9/x86_64/rstudio-1.2.5033-amd64.deb"}
@@
 
+\CommentTok{# for r-kernel to work in Atom}
+\KeywordTok{install.packages}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\StringTok{'repr'}\NormalTok{, }\StringTok{'IRdisplay'}\NormalTok{, }\StringTok{'evaluate'}\NormalTok{, }\StringTok{'crayon'}\NormalTok{, }\StringTok{'pbdZMQ'}\NormalTok{, }\StringTok{'devtools'}\NormalTok{, }\StringTok{'uuid'}\NormalTok{, }\StringTok{'digest'}\NormalTok{))}
+\NormalTok{devtools}\OperatorTok{::}\KeywordTok{install_github}\NormalTok{(}\StringTok{'IRkernel/IRkernel'}\NormalTok{)}
+\NormalTok{IRkernel}\OperatorTok{::}\KeywordTok{installspec}\NormalTok{()}
+
 \CommentTok{# Install my package}
@@
 
-\CommentTok{# C:\textbackslash{}Users\textbackslash{}fan\textbackslash{}R4Econ\textbackslash{}summarize\textbackslash{}dist\textbackslash{}fst_hist_onevar.Rmd}
-\CommentTok{# C:\textbackslash{}Users\textbackslash{}fan\textbackslash{}R4Econ\textbackslash{}support\textbackslash{}tibble\textbackslash{}fs_tib_basics.Rmd}
-\CommentTok{# C:\textbackslash{}Users\textbackslash{}fan\textbackslash{}R4Econ\textbackslash{}optimization\textbackslash{}cesloglin\textbackslash{}fst_ces_plan_linlog.Rmd}
+\CommentTok{# C:/Users/fan/R4Econ/summarize/dist/fst_hist_onevar.Rmd}
+\CommentTok{# C:/Users/fan/R4Econ/support/tibble/fs_tib_basics.Rmd}
+\CommentTok{# C:/Users/fan/R4Econ/optimization/cesloglin/fst_ces_plan_linlog.Rmd}
 \end{Highlighting}
@@
 \item
-  editor (gui): Atom, texStudio, etc
+  editor (gui): Atom, Sublime text, texStudio, etc
 \end{enumerate}
@@
 
-\hypertarget{compile-in-atom}{%
-\subsection{Compile in Atom}\label{compile-in-atom}}
+\hypertarget{compile-in-atom-and-texstudio}{%
+\subsection{Compile in Atom and
+Texstudio}\label{compile-in-atom-and-texstudio}}
 
-Install the \href{https://github.com/thomasjo/atom-latex}{latex} package
-on atom.
+Install the following two packages in atom:
+
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi}.}
+\tightlist
+\item
+  \href{https://github.com/thomasjo/atom-latex}{latex} package on atom.
+\item
+  \href{https://atom.io/packages/language-latex}{language-latex} package
+  on atom
+\end{enumerate}
+
+In Atom Latex setting, note that on different platforms, paths to
+texlive are different:
+
+\begin{itemize}
+\tightlist
+\item
+  Path:
+
+  \begin{itemize}
+  \tightlist
+  \item
+    Windows: \emph{C:/texlive/2019/bin/win32}
+  \item
+    Chromebook Linux: \emph{/usr/bin/latex}
+  \end{itemize}
+\item
+  Which PDF viewer to use:
+
+  \begin{itemize}
+  \tightlist
+  \item
+    download Okular and use \href{https://okular.kde.org/}{Okular}
+  \end{itemize}
+\end{itemize}
 
@@
 \CommentTok{# set TeX path}
-\CommentTok{# C:\textbackslash{}texlive\textbackslash{}2019\textbackslash{}bin\textbackslash{}win32}
+\CommentTok{# C:/texlive/2019/bin/win32}
+
+\CommentTok{# Latex, after installation}
+\CommentTok{# see where texlive appears under root folder directories}
+\FunctionTok{sudo}\NormalTok{ find / -name }\StringTok{"texlive"}
+\CommentTok{# see latex version, if texlive is used}
+\ExtensionTok{latex}\NormalTok{ -v}
+\CommentTok{# see main exe directory}
+\FunctionTok{which}\NormalTok{ latex}
+\CommentTok{# /usr/bin/latex}
 \end{Highlighting}
 \end{Shaded}
+
+Go to Tex4Econ and compile various template files and other types of
+files there to see if tex is working.
+
+Compile the same files in texstudio.
 
@@
 
-\hypertarget{development-programs}{%
-\subsection{Development Programs}\label{development-programs}}
+\hypertarget{package-managers}{%
+\subsection{Package Managers}\label{package-managers}}
 
@@
 \item
-  \href{https://www.jetbrains.com/pycharm/}{pycharm}
+  \href{https://github.com/lukesampson/scoop/wiki/Quick-Start}{scoop}
 \end{itemize}
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\CommentTok{# in powershell}
+\CommentTok{# enter cmd}
+\CommentTok{# type powershell in cmd to enter powershell from cmd}
+\ExtensionTok{powershell}
+\CommentTok{# permission}
+\ExtensionTok{set-executionpolicy}\NormalTok{ remotesigned -scope currentuser}
+\CommentTok{# install}
+\ExtensionTok{iwr}\NormalTok{ -useb get.scoop.sh }\KeywordTok{|} \ExtensionTok{iex}
+\end{Highlighting}
+\end{Shaded}
+
+\hypertarget{editors}{%
+\subsection{Editors}\label{editors}}
+
+In addition to Atom, which is pretty slow, and harder to run on lower
+spec computers.
+
+\hypertarget{vscode}{%
+\subsubsection{VSCode}\label{vscode}}
+
+VSCode is much more light-weight than Atom, does not have hydrogen.
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\CommentTok{# Debian Install}
+\ExtensionTok{curl}\NormalTok{ https://packages.microsoft.com/keys/microsoft.asc }\KeywordTok{|} \ExtensionTok{gpg}\NormalTok{ --dearmor }\OperatorTok{>}\NormalTok{ microsoft.gpg}
+\FunctionTok{sudo}\NormalTok{ install -o root -g root -m 644 microsoft.gpg /usr/share/keyrings/microsoft-archive-keyring.gpg}
+\FunctionTok{sudo}\NormalTok{ sh -c }\StringTok{'echo "deb [arch=amd64 signed-by=/usr/share/keyrings/microsoft-archive-keyring.gpg] https://packages.microsoft.com/repos/vscode stable main" > /etc/apt/sources.list.d/vscode.list'}
+\FunctionTok{sudo}\NormalTok{ apt-get install apt-transport-https}
+\FunctionTok{sudo}\NormalTok{ apt-get update}
+\FunctionTok{sudo}\NormalTok{ apt-get install code }\CommentTok{# or code-insiders}
+
+\CommentTok{# Change Font (https://www.reddit.com/r/Crostini/comments/cesxr0/vscode_ui_and_fonts_too_small_heres_how_to_fix_it/)}
+\CommentTok{# modify: /usr/share/applications/code.desktop}
+\ExtensionTok{nvim}\NormalTok{ /usr/share/applications/code.desktop}
+\CommentTok{#replace this line: Exec=/usr/share/code/code --unity-launch %F}
+\VariableTok{Exec=}\NormalTok{sommelier }\ExtensionTok{-X}\NormalTok{ --scale=0.8 --dpi=160 /usr/share/code/code }\StringTok{"--unity-launch %F"}
+\CommentTok{#replace this line: Exec=/usr/share/code/code --new-window %F}
+\VariableTok{Exec=}\NormalTok{sommelier }\ExtensionTok{-X}\NormalTok{ --scale=0.8 --dpi=160 /usr/share/code/code }\StringTok{"--new-window %F"}
+
+\CommentTok{# Open File}
+\CommentTok{# low density mode to see cleary}
+\ExtensionTok{code}
+\end{Highlighting}
+\end{Shaded}
+
+Extensions to Download for VSCode:
+
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi}.}
+\setcounter{enumi}{1}
+\tightlist
+\item
+  \href{https://marketplace.visualstudio.com/items?itemName=ms-python.python}{Microsoft
+  Python Extension}
+\end{enumerate}
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\ExtensionTok{ext}\NormalTok{ install ms-python.python}
+\end{Highlighting}
+\end{Shaded}
+
+\hypertarget{vscode-shortcuts}{%
+\paragraph{VSCode Shortcuts}\label{vscode-shortcuts}}
+
+\begin{itemize}
+\tightlist
+\item
+  Open up Settings: \emph{Ctrl + ,}
+\item
+  Preview Markdown in VSCode: \emph{Ctrl + Shift + V}
+\item
+  Open up left pane: \emph{Ctrl + B}
+\item
+  Wrap Text: \emph{alt + Z}, switch between wrap or not to save screen
+  space for example.
+\end{itemize}
+
+\hypertarget{vscode-benefits}{%
+\paragraph{VSCode Benefits}\label{vscode-benefits}}
+
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi}.}
+\tightlist
+\item
+  open a file, if have workspace where the file is in, automatically
+  expand tree and show where file is on left pane.
+\end{enumerate}
+
+\hypertarget{vscode-and-r}{%
+\paragraph{VSCode and R}\label{vscode-and-r}}
+
+VSCode works pretty well it seems with Rmd files. Rmd files are useful
+to work through algorithm, examples in preparation for writing usable
+functions. Rstudio has been often very slow for me, and I generally feel
+like can not stretch around and work in RStudio IDE.
+
+In Atom, Hydrogen works, but really only works with very basic line by
+line testing.
+
+Using VSCode with RMD files seems much quicker, and there is room to
+breath.
+
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi}.}
+\tightlist
+\item
+  Install R following R installation instructions.
+\item
+  Then install extension
+  \href{https://marketplace.visualstudio.com/items?itemName=Ikuyadeu.r}{R}.
+  Microsoft stopped supporting rmd in VSCode:
+  \href{https://github.com/microsoft/RTVS}{R Tools for Visual Studio}
+\item
+  properly set path (might have to call vscode from r env)
+
+  \begin{itemize}
+  \tightlist
+  \item
+    \emph{r.rterm.linux}:
+    \emph{/home/wangfanbsg75/anaconda3/envs/r\_env/bin/R}
+  \end{itemize}
+\item
+  Run:
+
+  \begin{itemize}
+  \tightlist
+  \item
+    ctrl + enter to activate R terminal
+  \item
+    VSCode 2019 allows for Knit Rmd: \emph{Ctrl + Shift + K}
+  \item
+    also can run code segment: select lines and \emph{ctrl + enter}
+  \end{itemize}
+\end{enumerate}
+
+\hypertarget{vscode-and-latex}{%
+\paragraph{VSCode and Latex}\label{vscode-and-latex}}
+
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi}.}
+\tightlist
+\item
+  download
+  \href{https://marketplace.visualstudio.com/items?itemName=James-Yu.latex-workshop}{Latex
+  Workshop}
+\end{enumerate}
+
+\hypertarget{notepad}{%
+\subsubsection{Notepad++}\label{notepad}}
+
+\href{https://notepad-plus-plus.org/downloads/v7.8.2/}{Notepad++}. Many
+old projects have xml folder structures for Notepad++.
+
+\begin{itemize}
+\tightlist
+\item
+  Silently update file changes made in other editors: Settings,
+  Preferences, MISC., File Status Auto Detection, Update Silently.
+\end{itemize}
+
+\hypertarget{sublime}{%
+\subsubsection{Sublime}\label{sublime}}
+
+\href{https://www.sublimetext.com/3}{Sublime}
+
+there are some issues with atom. When a file is edited inside Vim, when
+changes are saved, a
+\href{https://github.com/atom/atom/issues/17186}{temp file is created in
+atom}. Sublime would, however, still show the file with the changes.
+This makes dual screen editing very difficult. Sublime text is used for
+this situation.
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\CommentTok{# Sublime Linux}
+\FunctionTok{wget}\NormalTok{ -qO - https://download.sublimetext.com/sublimehq-pub.gpg }\KeywordTok{|} \FunctionTok{sudo}\NormalTok{ apt-key add -}
+\FunctionTok{sudo}\NormalTok{ apt-get install apt-transport-https}
+\BuiltInTok{echo} \StringTok{"deb https://download.sublimetext.com/ apt/stable/"} \KeywordTok{|} \FunctionTok{sudo}\NormalTok{ tee /etc/apt/sources.list.d/sublime-text.list}
+\FunctionTok{sudo}\NormalTok{ apt-get update}
+\FunctionTok{sudo}\NormalTok{ apt-get install sublime-text}
+\CommentTok{# launch from terminal}
+\ExtensionTok{subl}
+\end{Highlighting}
+\end{Shaded}
+
+\emph{Sublime Setup}:
+
+\begin{itemize}
+\tightlist
+\item
+  \href{https://weibeld.net/r/rmd_sublime_package.html}{r and rmd setup}
+\end{itemize}
+
+\hypertarget{pycharm}{%
+\subsubsection{PyCharm}\label{pycharm}}
+
+\href{https://www.}{pycharm}jetbrains.com/pycharm/)
 
@@
 
+\textbf{PDF}
+
 \begin{itemize}
@@
 \item
-  Adobe Acrobat
+  PDF Okular
+
+  \begin{itemize}
+  \tightlist
+  \item
+    Linux: \emph{sudo apt-get install okular}
+  \item
+    Windows: install okular from windows app store
+  \item
+    Okular if menu bar lost: \emph{Ctrl + m}
+  \end{itemize}
+\item
+  PDF Adobe Acrobat
 
@@
 
+\textbf{VPN}
+
+\begin{itemize}
+\tightlist
+\item
+  \href{https://protonvpn.com/}{Proton VPN}: unlimited usage free
+  version available.
+\item
+  Express VPN
+\end{itemize}
+
 \hypertarget{utilities}{%
@@
   7-zip
+\item
+  evernote
+\item
+  keepass
 \end{itemize}

### 2020-01-03 nontex/install/windows/fn_installations.Rmd
installation clean up, sumatra color pdf as VSCode latex pdf

@@
 ---
-title: "New Computer Data-Science Set-up: Python (anaconda, pycharm), R (r-studio) and other Programs Installations"
+title: |
+  | New Computer Fan Data-Science Set-up
+  | Python (Anaconda), R (Rstudio), Matlab and Latex (Texlive)
+  | Atom, VScode, Pycharm
 output:
@@
 
-For the following types of programming tasks, install relevant programs, that are cross platform compatible. Test at the end that example programs work.
+Install various compilers and IDE:
 
-1. Python
-    + Anaconda Dist
-    + Pycharm
-    + atom hydrogen
-2. R
-    + R
-    + Rstudio
-    + atom hydrogen
+1. Python (Anaconda, Pycharm + VSCode + Atom)
+2. R (VSCode + Atom)
 3. Matlab
-    + Matlab
-4. Latex and PDF
-    + atom latex
-    + texstudio
-    + texlive
-    + okular pdf
+4. Latex and PDF (texlive, Okular, VSCode + Atom + Texstudio)
 
@@
 1. Do sample *py* files work?
-    + work from command line?
-    + work from atom (hydrogen)
+    + work from command line
+    + work from atom (hydrogen), Pycharm, VSCode
 2. Do sample *rmd* files work?
     + work from r-studio
-    + work from atom (hydrogen), r file
+    + work from atom (hydrogen), VSCode
 3. Do tex templates compile?
-    + tikz files
-    + template files with bib
+    + tikz files, template files with bib
+    + work from texstudio, VSCode live compile, Atom
 
-*note*: Github people seem to have slowed down updating Atom since microsoft acquisition
+Installation Plan outline:
 
-# Conda
+1. Conda install (python)
+2. Install Atom along with Hydrogen and other packages.
+
+# Python and Anaconda Installation
 
@@
 
-Search for Anaconda Prompt, right click, choose run as administrator.
-
-Check software versions.
+- Search for Anaconda Prompt, right click, choose run as administrator.
+- Check software versions.
 
@@
 
-Download and install for all users.
+[Download Anaconda Python 3](https://www.anaconda.com/distribution/) and install for all users.
 Afterwards, Anaconda does not automatically get added to Windows Path.
 Need to use Anaconda Prompt to access programs.
-To access Anaconda packages from windows prompt, from git bash, from R, etc, need to Add Anaconda to Windows Path
+To access Anaconda packages from windows prompt, from git bash, from R, etc, need to Add Anaconda to Windows Path.
 
-To install conda in Debian, follow [these instructions](https://fanwangecon.github.io/Tex4Econ/nontex/install/linux/fn_ubuntu.html).
+To install conda in Linux/Debian, follow [these instructions](https://fanwangecon.github.io/Tex4Econ/nontex/install/linux/fn_ubuntu.html). Overall, installations are very similar.
 
-See Anaconda Installation Directory, in anaconda prompt:
+In command/anaconda prompt:
 
@@
 To Add Anaconda to Path, In Windows
-1. search for: Environment Variables
+1. Search for: Environment Variables
 2. Edit Environment Variables
@@
 Open up Anaconda Navigator, it will update navigator automatically. If there are errors, might have to clean first.
+
+There are different channels/repositories from which packages could be installed: *conda*, *conda-forge*, for example.
+Can change where to look for packages first.
+Many packages are in multiple channels.
+Conda-forge often have mroe recent packages.
 
@@
 
-## Conda Test Python
+## Python Command Line Test
 
@@
 
-## Jupyter and Atom Hydrogen
-
-For both Jupyter as well as Atom, always open from command prompt, open from *Anaconda Prompt* with admin rights.
-
-First, open up *Jupyter Notebook*, does the python kernel work? If does not, uninstall and re-install Anaconda.
-
-```{bash}
-# start jupyter lab, from prompt
-jupyter lab
-```
-
-Now test python within atom:
-
-1. install hydrogen in atom. Follow [instructions](http://nteract.io/atom).
-    - terminal in windows or linux after installation: *apm install hydrogen*
-    - apm is the atom package manager.
-2. Pull/Sync with Git and open mulitple projects in atom, follow [guide here](https://fanwangecon.github.io/Tex4Econ/nontex/install/git/fs_git_setup.html).
-3. go to the programs above and try to run.
-
-```{bash}
-# Once atom is installed, can use apm to install packages
-apm install hydrogen
-apm install project-manager
-apm install sublime-style-column-selection
-apm install minimap
-
-# vim distraction free editing
-apm install vim-mode-plus
-apm install zen
-
-# Inside Conda open up atom
-atom
-
-# open multiple projects from atom at the same time, after repos synced
-atom ~/fanwangecon.github.io ~/Pyfan ~/Teaching ~/Tex4Econ ~/R4Econ ~/M4Econ ~/Py4Econ
-# open up any py from from within, try 1+1, does it work?
-# also use script, try ctrl + shift + b, run whole file (not hydrogen)
-```
-
 # R Installation
 
-Try to install R from within Conda. The procedure here is the same for windows as well as linux machines.
+R could be installed from Anaconda or directly on windows outside of the Anaconda directories.
+When installing from within Anaconda, could create R environment that are isolated from the rest of the computer.
+The R environment could be updated and deleted without disturbing dependencies in conda main or the rest of the computer.
+
+The computer could have multiple R installations.
+Several in different conda R environment, and also several under windows/linux primary main user R directories.
+Type *which R/where R* to see if you open up R from command line at the moment, which directory's R will be used.
+Inside Conda R environment, it will be a different R if there is a different R version there.
 
@@
 
-Open up RStudio, and see where paths are.
-also open up R from command prompt, see where paths are.
+If R was installed in R enviornments, just delete the environment.
+Otherwise, use system's uninstaller.
+Before that, from terminal/command-prompt, type *R*, and *.libPaths()* to find paths.
+Do so inside conda main, outside of conda main, inside different environments, find all paths.
+After uninstaller finishes, check in the libPath folders to see if there are still stuff there, delete all, delete the folders.
 
@@
 .libPath()
+# C:/Users/fan/Documents/R/win-library/3.6
+# C:/Program Files/R/R-3.6.1/library
 ```
 
-Open up install and uninstall programs, find R and Rstudio, and uninstall them. Then delete all files found path paths shown by *.libPath()*, looking at these:
-    - *C:/Users/fan/Documents/R/win-library/3.6*
-    - *C:/Program Files/R/R-3.6.1/library*
-
-For Linux:
-
-- if used apt-get to install, R installed under main user drive, deactivate conda, and check which conda
+For Linux and for unsintalling inside conda:
 
@@
 
+Need to install R.
+Then need to install also an editor/IDE for R.
+Rstudio is the dominant R IDE.
+VSCode and Atom also works well, especially VSCode as editors.
+Dramatically better experience for writing scripts outside of Rstudio which feels unwieldy and slow especially compared to VSCode.
+
+Overall plan:
+
 1. [download R](https://cloud.r-project.org/)
-    + for debian: [Johannes Ranke](https://cran.r-project.org/bin/linux/debian/)
+    + for debian: [Johannes Ranke](https://cran.r-project.org/bin/linux/debian/).
+For Linux/Debian installation, crucial to update the *source.list* to include sources that have more recent versions of R.
+If not, will get very old R versions that is not compatible with many packages.
+    + add R to path for Windows. In Windows Path, add for example: *C:/Program Files/R/R-3.6.2/bin/x64/* and *C:/Rtools/bin*
 2. [download R-studio](https://rstudio.com/products/rstudio/download/)
 3. Open R-studio and auto-detect R
-4. Install packages
+4. Install additional packages (from commandline)
+    + various R data-science packages have dependencies, and additional not-R programs might need to be installed.
+Install them as needed, for example:  *libcurl4-openssl-dev* and *libssl-dev* from command prompt first inside Debian.
 
-note that installation will not work if the machine's version of R is not up to date, this could be the case with default R versions for some linux installations.
-For Debian for example, need to update the *source.list* to include sources that have more recent versions of R.
+### Linux R Install
 
-Additionally, need to install *libcurl4-openssl-dev* and *libssl-dev* from command prompt first inside Debian.
+For linux/Debian, to Install latest R:
 
 ```{bash}
-# If inside Debian, due to some tidymodel install issues, do this`
-conda install -c r r
-conda install -c r r-essentials
-conda install -c r r-igraph
-conda install -c conda-forge igraph
-
 # Go to get latesdebian latest r sources.list
@@
 
-Which R?
+### Install Packages for R
 
-- *export RSTUDIO_WHICH_R=/usr/bin/R*
-- *export RSTUDIO_WHICH_R=/home/wangfanbsg75/anaconda3/bin/R*
+From command prompt, enter R by typeing *R*, and install packages:
 
@@
 
-## Set up R-Environment in Conda
-
-Conda environments are language agnostic.
-pip is a package manager for Python.
-venv is an environment manager for Python.
-conda is both a package and environment manager and is language agnostic.
-Inside Anaconda Prompt:
+## Install R (inside Conda)
 
@@
 Prioritize conda-forge to get the latest packages.
-after adding *conda-forge* to channels, that will be prioritized, so when creating a new environment, conda will install first from conda-forge if package exists there.
+After adding *conda-forge* to channels, that will be prioritized, so when creating a new environment, conda will install first from conda-forge if package exists there.
 Try the *r_env* generation line with and without first adding *conda-forge* to channel, and see that the packages installed will have different versions, reflecting versions in the default channel and in the *conda-forge* channels.
+
+### Set up Conda R environment
+
+Create a Conda Environment called *r_env*, and update its channels.
+
+- **Location**: Installed environments are shown appear in the *envs* folder of *C:/ProgramData/Anaconda3/envs/*.
+Can be easily deleted without disrupting the main base installation for conda.
+This is very important.
+During installation, could easily run into problems, and need to re-install.
+Much better to only re-install a folder.
+Note that when R is installed in *envs*, it will not show up under add or remove programs for uninstallation from there, has to be uninstalled, deleted directly here.
+- **Use only in Env**: Note that if we installed r inside r_env, if we type *r* under the base environment, we can not enter r.
+We can only enter r within r_env.
+With PATH properly set-up, this happens under Conda Prompt, Windows Prompt, etc.
+- **Multiple Pythons**: With the above installation for R, one benefit is that if R requires a different version of Python than what the base environment uses, the r_env could have a different python version.
+So type *python* in the base environment as well as inside the *r_env*.
+This also means potentially there could be duplicated installations I think.
+Look at the python versions under *conda list* in the base and in the r-environment.
+- **File Size**: Note that this creates a large installation folder, *C:/ProgramData/Anaconda3/envs/r_env/*, without additional packages, is 1.3 GB in size
 
@@
 
-# install files
-conda install -n r_env -c r r r-essentials r-tidyverse r-tidymodels -y
-
-# trouble with igraph installation, install here from conda
-# conda install -n r_env r-essentials r-base r-tidyr r-tidyverse r-devtools r-irkernel r-pkgdown r-roxygen2
-conda install -n r_env -c r r-igraph
-conda install -n r_env -c conda-forge igraph
-conda install -n r_env -c r r-rstantools r-rstan r-rstanarm -y
-
 # see all installed environments
@@
 
-- **Location**: Installed environments are shown appear in the *envs* folder of *C:/ProgramData/Anaconda3/envs/*.
-Can be easily deleted without disrupting the main base installation for conda.
-This is very important.
-During installation, could easily run into problems, and need to re-install.
-Much better to only re-install a folder.
-Note that when R is installed in *envs*, it will not show up under add or remove programs for uninstallation from there, has to be uninstalled, deleted directly here.
-- **Use only in Env**: Note that if we installed r inside r_env, if we type *r* under the base environment, we can not enter r.
-We can only enter r within r_env.
-With PATH properly set-up, this happens under Conda Prompt, Windows Prompt, etc.
-- **Multiple Pythons**: With the above installation for R, one benefit is that if R requires a different version of Python than what the base environment uses, the r_env could have a different python version.
-So type *python* in the base environment as well as inside the *r_env*.
-This also means potentially there could be duplicated installations I think.
-Look at the python versions under *conda list* in the base and in the r-environment.
-- **File Size**: Note that this creates a large installation folder, *C:/ProgramData/Anaconda3/envs/r_env/*, without additional packages, is 1.3 GB in size
+### Install R and Some Packages in Conda
 
-## Install Additional Packages inside the R-environment
+Either inside a R specific environment, or outside of it, now do additional installations for R and also R packages.
 
-These are packages that I use, these should be installed inside the environment. Or they could be installed later from inside r-studio. Installing inside r-studio is a lot better.
+During installation, the R programs might require downgrading other programs in the Conda environment that Python for example also uses.
+That is why potentially it is safer to install in R environment.
+However, when installing in R enviornment, certain packages could have issues if installer does not realize it is in an environment with special folder structure, so installation could fail.
 
+```{bash}
+# install files
+conda install -n r_env -c r r r-essentials r-tidyverse r-tidymodels -y
+
+# trouble with igraph installation, install here from conda
+# conda install -n r_env r-essentials r-base r-tidyr r-tidyverse r-devtools r-irkernel r-pkgdown r-roxygen2
+conda install -n r_env -c r r-igraph
+conda install -n r_env -c conda-forge igraph
+conda install -n r_env -c r r-rstantools r-rstan r-rstanarm -y
+```
+
+## Install Additional Packages inside the R
+
+These are packages that I use, these should be installed inside the environment.
+Or they could be installed later from inside r-studio.
+Installing inside r-studio is a lot better.
 *tidymodel* has installation issues sometimes.
 
-In *r_env*, type in *R*, and then install from inside terminal's R:
+In *r_env*, type in *R*, and then install from inside terminal's R. For conda env, devtools will be installed and will install packages inside *envs/r_env/Lib/R*.
 
-```{bash}
+```{r}
 # enter into env
-conda activate r_env
+# conda activate r_env
 # enter R or type in rstudio
 # sicne R is only install inside r_env, has to enter rstudio from r_env
-R
-rstudio
+# R
+# rstudio
 
@@
 IRkernel::installspec()
-```
-
-Install additional packages from inside R. The devtools install will install packages inside *envs/r_env/Lib/R*.
-
-```{r}
-#######################################
-### Own Package
-#######################################
-devtools::install_github("fanwangecon/R4Econ")
-# install_dev("cli")
 ```
@@
 
-## Install Packages from R-Studio
+Is RSTUDIO pointing to the R installation you want? Note you can open Rstudio from differen conda env command line, that will use different R installations. Or also set:
 
-Install addition files inside Rstudio.
-Easier to debug potentially.
-Install rtools as described [here](https://thecoatlessprofessor.com/programming/cpp/installing-rtools-for-compiled-code-via-rcpp/): [rtools download](https://cran.r-project.org/bin/windows/Rtools/).
-Alternatively:
+- *export RSTUDIO_WHICH_R=/usr/bin/R*
+- *export RSTUDIO_WHICH_R=/home/wangfanbsg75/anaconda3/bin/R*
 
-```{r}
-install.packages("installr")
-library("installr")
-# Note that this will generate several pop-up windows
-install.Rtools()
-# choose to only install 64 bit toolchain
-# this installs g++ which is needed for rstanarm
-# Add these below to windows path
-# c:/Rtools/bin;
-# c:/Rtools/mingw_64/bin;
-
-if (!require(devtools)) {
-  install.packages("devtools")
-  library(devtools)
-}
-library(devtools)
-install_github("stan-dev/rstanarm", args = "--preclean")
-
-setwd('C:/ProgramData/Anaconda3/envs/r_env/Lib/R/library')
-
-install.packages("stan-dev/rstanarm", dependencies=TRUE, INSTALL_opts = c('--no-lock'))
-
-# other packages
-install.packages(c("tidymodels", "AER", "minpack.lm", "knitr", "kableExtra", "matlab"))
-
-# for r-kernel to work in Atom
-install.packages(c('repr', 'IRdisplay', 'evaluate', 'crayon', 'pbdZMQ', 'devtools', 'uuid', 'digest'))
-devtools::install_github('IRkernel/IRkernel')
-IRkernel::installspec()
-
-# Install my package
-devtools::install_github("fanwangecon/R4Econ")
-```
-
-### Test Files
+## R Tests
 
@@
 
-# Install Latex
+# Install Latex and PDF
 
@@
 
-## Compile in Atom and Texstudio
+Test file compilations in TexStudio.
+
+## SumatraPDF
+
+For windows, install [SumatraPDF](https://www.sumatrapdfreader.org/download-free-pdf-viewer.html). Can easily modify colors.
+
+**Settings**
+
+[Kindle Sepia](https://medium.com/greatnote/kindle-sepia-color-code-1fed14b1a5ef) modifications:
+
+- Background color:
+    + Kindle Sepia: *fbf0d9*
+    + Kindle Sepia Light: *fff8e6*
+- Text color:
+    + Kindle Sepia: *5f4b32*
+    + Kindle Sepia Darker: *503f2a*
+    + Kindle Sepia Darkerer: *1e170f*
+
+```
+FixedPageUI [
+	TextColor = #1e170f
+	BackgroundColor = #fff8e6
+	SelectionColor = #f5fc0c
+	WindowMargin = 2 4 2 4
+	PageSpacing = 4 4
+]
+```
+
+## Okular PDF
+
+Linux: *sudo apt-get install okular*
+Windows: install okular from windows app store
+
+### Okular Shortcuts and Features
+
+**Settings**:
+
+- Background color:
+    + background behind pdf: configure okular, general, use custom backgroun color, Gainsboro gray: *DCDCDC*, kindle sepia: *FBF0D9*
+    + pdf background itself: configure okular, accessbility, change color, change paper color, Light Kindle Sepia: *fff8e6*
+
+**Features**:
+
+- Okular 3 pages per row view: view, overview
+- Automatic Update when PDF updated elsewhere: this is one of the key reasons to use okular, when I knit a Rmd file to PDF, the currently open Okular PDF file automatically updates and does not give file is open error like Acrobat.
+- Background color:
+    + background behind pdf: configure okular, general, use custom backgroun color, Gainsboro gray: *DCDCDC*, kindle sepia: *FBF0D9*
+    + pdf background itself: configure okular, accessbility, change color, change paper color, Light Kindle Sepia: *fff8e6*
+
+**Shortcuts**:
+
++ Okular configure shortcuts: setting, configure shortcuts
++ Okular if menu bar lost: *Ctrl + m*
++ Okular comment pane: *F6*
++ Okular close left pane: *F7*
++ Okular full scrren: *Ctrl + Shift + F*
+    * unlike acrobat, pdf allows for multiple scrrens
+
+## Adobe PDF
+
+PDF Adobe Acrobat Installation
+  + go to adobe website, log in using fwang26@uh.edu
+  + go to my account, choose view and download my apps, choose acrobat & PDF, download Acrobat DC
+  + UH account can only be activated on two accounts at once, so need to kick other computers out temporarily potentially
+
+# Install Various Editors
+
+Atom, VSCode, Notepad++, Sublime, etc.
+These are essential editors that allows for pleasant programming and writing experiences.
+See here for [fan](http://fanwangecon.github.io/) instructions on [vim](https://fanwangecon.github.io/Tex4Econ/nontex/install/linux/fn_vim.html) installations.
+
+All settings here JSON files here:
+
+- windows: *C:/Users/fan/AppData/Roaming/Code/User*, can be modified here directly
+
+## VSCode Installation
+
+VSCode is much more light-weight than Atom, much faster.
+On Windows, download [here](https://code.visualstudio.com/download).
+VScode settings easy to change for various extensions.
+Very very good Latex Editor, probably the best I have used.
+
+For Linux:
+
+```{bash}
+# Debian Install
+curl https://packages.microsoft.com/keys/microsoft.asc | gpg --dearmor > microsoft.gpg
+sudo install -o root -g root -m 644 microsoft.gpg /usr/share/keyrings/microsoft-archive-keyring.gpg
+sudo sh -c 'echo "deb [arch=amd64 signed-by=/usr/share/keyrings/microsoft-archive-keyring.gpg] https://packages.microsoft.com/repos/vscode stable main" > /etc/apt/sources.list.d/vscode.list'
+sudo apt-get install apt-transport-https
+sudo apt-get update
+sudo apt-get install code # or code-insiders
+
+# Change Font (https://wwFw.reddit.com/r/Crostini/comments/cesxr0/vscode_ui_and_fonts_too_small_heres_how_to_fix_it/)
+# modify: /usr/share/applications/code.desktop
+nvim /usr/share/applications/code.desktop
+#replace this line: Exec=/usr/share/code/code --unity-launch %F
+Exec=sommelier -X --scale=0.8 --dpi=160 /usr/share/code/code "--unity-launch %F"
+#replace this line: Exec=/usr/share/code/code --new-window %F
+Exec=sommelier -X --scale=0.8 --dpi=160 /usr/share/code/code "--new-window %F"
+
+# Open File
+# low density mode to see cleary
+code
+```
+
+### VSCode Extensions
+
+Press *Ctrl + P*, paste the *ext install* commands below to install extensions. Extensions are in: *%USERPROFILE%\.vscode\extensions* for windows. Can change code for extension there.
+
+```{bash}
+# [Microsoft Python Extension](https://marketplace.visualstudio.com/items?itemName=ms-python.python)
+ext install ms-python.python
+# [Latex Workshop](https://marketplace.visualstudio.com/items?itemName=James-Yu.latex-workshop)
+ext install latex-workshop
+# [R](https://marketplace.visualstudio.com/items?itemName=Ikuyadeu.r)
+ext install ikuyadeu.r
+```
+
+### VSCode Shortcuts and Features
+
+**Features**:
+
+1. open a file, if have workspace where the file is in, automatically expand tree and show where file is on left pane.
+
+**Shortcuts** :
+
+- Zen model: *Ctrl + k, z*, this means press control k, then press z
+- Open up Settings: *Ctrl + ,*
+- Preview Markdown in VSCode: *Ctrl + Shift + V*
+- Open up left pane: *Ctrl + B*
+- Wrap Text: *alt + Z*, switch between wrap or not to save screen space for example.
+
+### VSCode and R
+
+VSCode works pretty well it seems with Rmd files.
+Rmd files are useful to work through algorithm, examples in preparation for writing usable functions.
+Rstudio has been often very slow for me, and I generally feel like can not stretch around and work in RStudio IDE.
+
+In Atom, Hydrogen works, but really only works with very basic line by line testing.
+
+Using VSCode with RMD files seems much quicker, and there is room to breath.
+
+1. Install R following R installation instructions.
+2.
+Then install extension [R](https://marketplace.visualstudio.com/items?itemName=Ikuyadeu.r).
+Microsoft stopped supporting rmd in VSCode: [R Tools for Visual Studio](https://github.com/microsoft/RTVS)
+3. properly set path (might have to call vscode from r env)
+    + *r.rterm.linux*: */home/wangfanbsg75/anaconda3/envs/r_env/bin/R*
+    + *r.rterm.windows*: *C:/Program Files/R/R-3.6.2/bin/x64/R.exe*
+        * note *R.exe* at the end
+4. Run:
+    - ctrl + enter to activate R terminal
+    - VSCode 2019 allows for Knit Rmd: *Ctrl + Shift + K*
+    - also can run code segment: select lines and *ctrl + enter*
+
+### VSCode and Latex
+
+Download [Latex Workshop](https://marketplace.visualstudio.com/items?itemName=James-Yu.latex-workshop).
+
+**Settings**
+
+change background border pdf color (not pdf but border): *ctrl + shift + x*, LatexWorkshop, Settings, Configure Extension Settings, Search for background, change color name.
+or enter: *latex-workshop.view.pdf.backgroundColor*.
+use gainsboro gray: *#DCDCDC*, or lightgray *#D3D3D3*.
+
+To take advantage of Okular (where background color can be none-white for example). Go to settings, and:
+1. Change: *latex-workshop.view.pdf.viewer* to external
+2. Change: *latex-workshop.view.pdf.external.viewer.command* to *C:/Program Files/SumatraPDF/SumatraPDF.exe*
+ open up *C:/Users/fan/AppData/Roaming/Code/User/settings.json*, and copy these in:
+
+```{JSON}
+"latex-workshop.view.pdf.external.synctex.command": "C:/Program Files/SumatraPDF/SumatraPDF.exe",
+"latex-workshop.view.pdf.external.synctex.args": [
+  "-forward-search",
+  "%TEX%",
+  "%LINE%",
+  "-reuse-instance",
+  "-inverse-search",
+  "code \"C:\\Users\\fan\\AppData\\Local\\Programs\\Microsoft VS Code\\resources\\app\\out\\cli.js\" -r -g \"%f:%l\"",
+  "%PDF%",
+]
+```
+
+**Features**:
+
+1. upon savings, rebuid file and update pdf (similar to overleaf)
+2. hover offers equation preview
+
+**Shortcuts**:
+
+1. preview: *ctrl + alt + v*
+2. synctex location: *ctrl + alt + j*
+
+### VSCode settings.json
+
+The settings.json file, *%APPDATA%/Code/User/settings.json*:
+
+```
+{
+  "r.rterm.windows": "C:/Program Files/R/R-3.6.2/bin/x64/R.exe",
+  "window.zoomLevel": 0,
+  "latex-workshop.view.pdf.viewer": "external",
+  "latex-workshop.view.pdf.external.synctex.command": "C:/Program Files/SumatraPDF/SumatraPDF.exe",
+  "latex-workshop.view.pdf.external.synctex.args": [
+		"-forward-search",
+		"%TEX%",
+		"%LINE%",
+		"-reuse-instance",
+		"-inverse-search",
+		"code \"C:\\Users\\fan\\AppData\\Local\\Programs\\Microsoft VS Code\\resources\\app\\out\\cli.js\" -r -g \"%f:%l\"",
+		"%PDF%",
+	],
+	"latex-workshop.view.pdf.external.viewer.command": "C:/Program Files/SumatraPDF/SumatraPDF.exe"
+}
+```
+## Atom Installation
+
+Atom is slow but has clean look and nice git/github integration.
+
+### Atom Extensions
+
+Terminal in windows or linux after installation: *apm install hydrogen*. apm is the atom package manager:
+
+```{bash}
+# Once atom is installed, can use apm to install packages
+apm install hydrogen
+apm install project-manager
+apm install sublime-style-column-selection
+apm install minimap
+
+# vim distraction free editing
+apm install vim-mode-plus
+apm install zen
+
+# Inside Conda open up atom
+atom
+
+```
+
+### Atom Shortcuts and Features
+
+**Features**:
+
+```{bash}
+# open multiple projects from atom at the same time, after repos synced
+atom ~/fanwangecon.github.io ~/Pyfan ~/Teaching ~/Tex4Econ ~/R4Econ ~/M4Econ ~/Py4Econ
+# open up any py from from within, try 1+1, does it work?
+# also use script, try ctrl + shift + b, run whole file (not hydrogen)
+```
+
+**Shortcuts** :
+
+- Git Pane: *Ctrl + 9*, *Ctrl + 8*
+
+### Atom and Python
+
+Having installed Anaconda, now install Atom and Hydrogen to Test with Python. For both Jupyter as well as Atom, always open from command prompt, open from *Anaconda Prompt* with admin rights.
+
+Open up *Jupyter Notebook*, does the python kernel work? If does not, uninstall and re-install Anaconda.
+
+```{bash}
+# start jupyter lab, from prompt
+jupyter lab
+```
+
+Try *1+1*.
+
+### Atom and Latex
 
@@
 
-Go to Tex4Econ and compile various template files and other types of files there to see if tex is working.
-
-Compile the same files in texstudio.
-
-# Other Programs to Install
-
-## Package Managers
-
-- [scoop](https://github.com/lukesampson/scoop/wiki/Quick-Start)
-
-```{bash}
-# in powershell
-# enter cmd
-# type powershell in cmd to enter powershell from cmd
-powershell
-# permission
-set-executionpolicy remotesigned -scope currentuser
-# install
-iwr -useb get.scoop.sh | iex
-```
-
-## Editors
-
-In addition to Atom, which is pretty slow, and harder to run on lower spec computers.
-
-### VSCode
-
-VSCode is much more light-weight than Atom, does not have hydrogen.
-
-```{bash}
-# Debian Install
-curl https://packages.microsoft.com/keys/microsoft.asc | gpg --dearmor > microsoft.gpg
-sudo install -o root -g root -m 644 microsoft.gpg /usr/share/keyrings/microsoft-archive-keyring.gpg
-sudo sh -c 'echo "deb [arch=amd64 signed-by=/usr/share/keyrings/microsoft-archive-keyring.gpg] https://packages.microsoft.com/repos/vscode stable main" > /etc/apt/sources.list.d/vscode.list'
-sudo apt-get install apt-transport-https
-sudo apt-get update
-sudo apt-get install code # or code-insiders
-
-# Change Font (https://www.reddit.com/r/Crostini/comments/cesxr0/vscode_ui_and_fonts_too_small_heres_how_to_fix_it/)
-# modify: /usr/share/applications/code.desktop
-nvim /usr/share/applications/code.desktop
-#replace this line: Exec=/usr/share/code/code --unity-launch %F
-Exec=sommelier -X --scale=0.8 --dpi=160 /usr/share/code/code "--unity-launch %F"
-#replace this line: Exec=/usr/share/code/code --new-window %F
-Exec=sommelier -X --scale=0.8 --dpi=160 /usr/share/code/code "--new-window %F"
-
-# Open File
-# low density mode to see cleary
-code
-```
-
-Extensions to Download for VSCode:
-
-2. [Microsoft Python Extension](https://marketplace.visualstudio.com/items?itemName=ms-python.python)
-
-```{bash}
-ext install ms-python.python
-ext install latex-workshop
-```
-
-#### VSCode Shortcuts
-
-- Open up Settings: *Ctrl + ,*
-- Preview Markdown in VSCode: *Ctrl + Shift + V*
-- Open up left pane: *Ctrl + B*
-- Wrap Text: *alt + Z*, switch between wrap or not to save screen space for example.
-
-#### VSCode Benefits
-
-1. open a file, if have workspace where the file is in, automatically expand tree and show where file is on left pane.
-
-#### VSCode and R
-
-VSCode works pretty well it seems with Rmd files.
-Rmd files are useful to work through algorithm, examples in preparation for writing usable functions.
-Rstudio has been often very slow for me, and I generally feel like can not stretch around and work in RStudio IDE.
-
-In Atom, Hydrogen works, but really only works with very basic line by line testing.
-
-Using VSCode with RMD files seems much quicker, and there is room to breath.
-
-1. Install R following R installation instructions.
-2.
-Then install extension [R](https://marketplace.visualstudio.com/items?itemName=Ikuyadeu.r).
-Microsoft stopped supporting rmd in VSCode: [R Tools for Visual Studio](https://github.com/microsoft/RTVS)
-3. properly set path (might have to call vscode from r env)
-    + *r.rterm.linux*: */home/wangfanbsg75/anaconda3/envs/r_env/bin/R*
-4. Run:
-    - ctrl + enter to activate R terminal
-    - VSCode 2019 allows for Knit Rmd: *Ctrl + Shift + K*
-    - also can run code segment: select lines and *ctrl + enter*
-
-#### VSCode and Latex
-
-1. download [Latex Workshop](https://marketplace.visualstudio.com/items?itemName=James-Yu.latex-workshop)
+## Other Editors
 
@@
 
-## Key Programs
+# Other Programs to Install
 
-**PDF**
+## Package Managers
 
-- PDF Okular
-    + Linux: *sudo apt-get install okular*
-    + Windows: install okular from windows app store
-    + Okular configure shortcuts: setting, configure shortcuts
-    + Okular if menu bar lost: *Ctrl + m*
-    + Okular comment pane: *F6*
-    + Okular close left pane: *F7*
-    + Okular full scrren: *Ctrl + Shift + F*
-        * unlike acrobat, pdf allows for multiple scrrens
-    + Okular 3 pages per row view:
-        * view, overview
-    + Automatic Update when PDF updated elsewhere
-        * this is one of the key reasons to use okular, when I knit a Rmd file to PDF, the currently open Okular PDF file automatically updates and does not give file is open error like Acrobat.
-    + Background color:
-        * can easily change background color to non-white.
-- PDF Adobe Acrobat
-    + go to adobe website, log in using fwang26@uh.edu
-    + go to my account, choose view and download my apps, choose acrobat & PDF, download Acrobat DC
-    + UH account can only be activated on two accounts at once, so need to kick other computers out temporarily potentially
+To install packages in windows more easily:
 
-**VPN**
+- [scoop](https://github.com/lukesampson/scoop/wiki/Quick-Start)
 
-- [Proton VPN](https://protonvpn.com/): unlimited usage free version available.
-- Express VPN
+```{bash}
+# in powershell
+# enter cmd
+# type powershell in cmd to enter powershell from cmd
+powershell
+# permission
+set-executionpolicy remotesigned -scope currentuser
+# install
+iwr -useb get.scoop.sh | iex
+```
 
@@
 - evernote
+
+## Security
+
 - keepass
+- [Proton VPN](https://protonvpn.com/): unlimited usage free version available.
+- Express VPN

### 2020-01-03 nontex/install/windows/fn_installations.tex
installation clean up, sumatra color pdf as VSCode latex pdf

@@
+\PassOptionsToPackage{unicode=true}{hyperref} % options for packages loaded elsewhere
+\PassOptionsToPackage{hyphens}{url}
+\PassOptionsToPackage{dvipsnames,svgnames*,x11names*}{xcolor}
+%
 \documentclass[]{article}
@@
   \usepackage[utf8]{inputenc}
+  \usepackage{textcomp} % provides euro and other symbols
 \else % if luatex or xelatex
-  \ifxetex
-    \usepackage{mathspec}
-  \else
-    \usepackage{fontspec}
-  \fi
+  \usepackage{unicode-math}
   \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
@@
 \IfFileExists{microtype.sty}{%
-\usepackage{microtype}
+\usepackage[]{microtype}
 \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
 }{}
-\usepackage[margin=1in]{geometry}
+\IfFileExists{parskip.sty}{%
+\usepackage{parskip}
+}{% else
+\setlength{\parindent}{0pt}
+\setlength{\parskip}{6pt plus 2pt minus 1pt}
+}
+\usepackage{xcolor}
 \usepackage{hyperref}
-\PassOptionsToPackage{usenames,dvipsnames}{color} % color is loaded by hyperref
-\hypersetup{unicode=true,
-            pdftitle={New Computer Data-Science Set-up: Python (anaconda, pycharm), R (r-studio) and other Programs Installations},
+\hypersetup{
             colorlinks=true,
             linkcolor=Maroon,
+            filecolor=Maroon,
             citecolor=Blue,
@@
 \urlstyle{same}  % don't use monospace font for urls
+\usepackage[margin=1in]{geometry}
 \usepackage{color}
@@
 \setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
-\IfFileExists{parskip.sty}{%
-\usepackage{parskip}
-}{% else
-\setlength{\parindent}{0pt}
-\setlength{\parskip}{6pt plus 2pt minus 1pt}
-}
 \setlength{\emergencystretch}{3em}  % prevent overfull lines
@@
 
-%%% Use protect on footnotes to avoid problems with footnotes in titles
-\let\rmarkdownfootnote\footnote%
-\def\footnote{\protect\rmarkdownfootnote}
-
-%%% Change title format to be more compact
-\usepackage{titling}
-
-% Create subtitle command for use in maketitle
-\providecommand{\subtitle}[1]{
-  \posttitle{
-    \begin{center}\large#1\end{center}
-    }
-}
-
-\setlength{\droptitle}{-2em}
-
-  \title{New Computer Data-Science Set-up: Python (anaconda, pycharm), R
-(r-studio) and other Programs Installations}
-    \pretitle{\vspace{\droptitle}\centering\huge}
-  \posttitle{\par}
+% set default figure placement to htbp
+\makeatletter
+\def\fps@figure{htbp}
+\makeatother
+
+\title{New Computer Fan Data-Science Set-up\\
+Python (Anaconda), R (Rstudio), Matlab and Latex (Texlive)\\
+Atom, VScode, Pycharm}
 \author{}
-    \preauthor{}\postauthor{}
-    \date{}
-    \predate{}\postdate{}
+\date{\vspace{-2.5em}}
 
@@
 
-For the following types of programming tasks, install relevant programs,
-that are cross platform compatible. Test at the end that example
-programs work.
+Install various compilers and IDE:
 
@@
 \item
-  Python
-
-  \begin{itemize}
-  \tightlist
-  \item
-    Anaconda Dist
-  \item
-    Pycharm
-  \item
-    atom hydrogen
-  \end{itemize}
-\item
-  R
-
-  \begin{itemize}
-  \tightlist
-  \item
-    R
-  \item
-    Rstudio
-  \item
-    atom hydrogen
-  \end{itemize}
+  Python (Anaconda, Pycharm + VSCode + Atom)
+\item
+  R (VSCode + Atom)
 \item
   Matlab
-
-  \begin{itemize}
-  \tightlist
-  \item
-    Matlab
-  \end{itemize}
-\item
-  Latex and PDF
-
-  \begin{itemize}
-  \tightlist
-  \item
-    atom latex
-  \item
-    texstudio
-  \item
-    texlive
-  \item
-    okular pdf
-  \end{itemize}
+\item
+  Latex and PDF (texlive, Okular, VSCode + Atom + Texstudio)
 \end{enumerate}
@@
   \item
-    work from command line?
-  \item
-    work from atom (hydrogen)
+    work from command line
+  \item
+    work from atom (hydrogen), Pycharm, VSCode
   \end{itemize}
@@
   \item
-    work from atom (hydrogen), r file
+    work from atom (hydrogen), VSCode
   \end{itemize}
@@
   \item
-    tikz files
-  \item
-    template files with bib
+    tikz files, template files with bib
+  \item
+    work from texstudio, VSCode live compile, Atom
   \end{itemize}
@@
 
-\emph{note}: Github people seem to have slowed down updating Atom since
-microsoft acquisition
-
-\hypertarget{conda}{%
-\section{Conda}\label{conda}}
+Installation Plan outline:
+
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi}.}
+\tightlist
+\item
+  Conda install (python)
+\item
+  Install Atom along with Hydrogen and other packages.
+\end{enumerate}
+
+\hypertarget{python-and-anaconda-installation}{%
+\section{Python and Anaconda
+Installation}\label{python-and-anaconda-installation}}
 
@@
 
+\begin{itemize}
+\tightlist
+\item
   Search for Anaconda Prompt, right click, choose run as administrator.
-
+\item
   Check software versions.
+\end{itemize}
 
@@
 
-Download and install for all users. Afterwards, Anaconda does not
+\href{https://www.anaconda.com/distribution/}{Download Anaconda Python
+3} and install for all users. Afterwards, Anaconda does not
 automatically get added to Windows Path. Need to use Anaconda Prompt to
 access programs. To access Anaconda packages from windows prompt, from
-git bash, from R, etc, need to Add Anaconda to Windows Path
-
-To install conda in Debian, follow
+git bash, from R, etc, need to Add Anaconda to Windows Path.
+
+To install conda in Linux/Debian, follow
 \href{https://fanwangecon.github.io/Tex4Econ/nontex/install/linux/fn_ubuntu.html}{these
-instructions}.
-
-See Anaconda Installation Directory, in anaconda prompt:
+instructions}. Overall, installations are very similar.
+
+In command/anaconda prompt:
 
@@
 
-To Add Anaconda to Path, In Windows 1. search for: Environment Variables
+To Add Anaconda to Path, In Windows 1. Search for: Environment Variables
 2. Edit Environment Variables 3. Add new to Path (lower half): -
@@
 there are errors, might have to clean first.
+
+There are different channels/repositories from which packages could be
+installed: \emph{conda}, \emph{conda-forge}, for example. Can change
+where to look for packages first. Many packages are in multiple
+channels. Conda-forge often have mroe recent packages.
 
@@
 
-\hypertarget{conda-test-python}{%
-\subsection{Conda Test Python}\label{conda-test-python}}
+\hypertarget{python-command-line-test}{%
+\subsection{Python Command Line Test}\label{python-command-line-test}}
 
@@
 
-\hypertarget{jupyter-and-atom-hydrogen}{%
-\subsection{Jupyter and Atom Hydrogen}\label{jupyter-and-atom-hydrogen}}
-
-For both Jupyter as well as Atom, always open from command prompt, open
-from \emph{Anaconda Prompt} with admin rights.
-
-First, open up \emph{Jupyter Notebook}, does the python kernel work? If
-does not, uninstall and re-install Anaconda.
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\CommentTok{# start jupyter lab, from prompt}
-\ExtensionTok{jupyter}\NormalTok{ lab}
-\end{Highlighting}
-\end{Shaded}
-
-Now test python within atom:
-
-\begin{enumerate}
-\def\labelenumi{\arabic{enumi}.}
-\tightlist
-\item
-  install hydrogen in atom. Follow
-  \href{http://nteract.io/atom}{instructions}.
-
-  \begin{itemize}
-  \tightlist
-  \item
-    terminal in windows or linux after installation: \emph{apm install
-    hydrogen}
-  \item
-    apm is the atom package manager.
-  \end{itemize}
-\item
-  Pull/Sync with Git and open mulitple projects in atom, follow
-  \href{https://fanwangecon.github.io/Tex4Econ/nontex/install/git/fs_git_setup.html}{guide
-  here}.
-\item
-  go to the programs above and try to run.
-\end{enumerate}
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\CommentTok{# Once atom is installed, can use apm to install packages}
-\FunctionTok{apm}\NormalTok{ install hydrogen}
-\FunctionTok{apm}\NormalTok{ install project-manager}
-\FunctionTok{apm}\NormalTok{ install sublime-style-column-selection}
-\FunctionTok{apm}\NormalTok{ install minimap}
-
-\CommentTok{# vim distraction free editing}
-\FunctionTok{apm}\NormalTok{ install vim-mode-plus}
-\FunctionTok{apm}\NormalTok{ install zen}
-
-\CommentTok{# Inside Conda open up atom}
-\ExtensionTok{atom}
-
-\CommentTok{# open multiple projects from atom at the same time, after repos synced}
-\ExtensionTok{atom}\NormalTok{ ~/fanwangecon.github.io ~/Pyfan ~/Teaching ~/Tex4Econ ~/R4Econ ~/M4Econ ~/Py4Econ}
-\CommentTok{# open up any py from from within, try 1+1, does it work?}
-\CommentTok{# also use script, try ctrl + shift + b, run whole file (not hydrogen)}
-\end{Highlighting}
-\end{Shaded}
-
 \hypertarget{r-installation}{%
@@
 
-Try to install R from within Conda. The procedure here is the same for
-windows as well as linux machines.
+R could be installed from Anaconda or directly on windows outside of the
+Anaconda directories. When installing from within Anaconda, could create
+R environment that are isolated from the rest of the computer. The R
+environment could be updated and deleted without disturbing dependencies
+in conda main or the rest of the computer.
+
+The computer could have multiple R installations. Several in different
+conda R environment, and also several under windows/linux primary main
+user R directories. Type \emph{which R/where R} to see if you open up R
+from command line at the moment, which directory's R will be used.
+Inside Conda R environment, it will be a different R if there is a
+different R version there.
 
@@
 
-Open up RStudio, and see where paths are. also open up R from command
-prompt, see where paths are.
+If R was installed in R enviornments, just delete the environment.
+Otherwise, use system's uninstaller. Before that, from
+terminal/command-prompt, type \emph{R}, and \emph{.libPaths()} to find
+paths. Do so inside conda main, outside of conda main, inside different
+environments, find all paths. After uninstaller finishes, check in the
+libPath folders to see if there are still stuff there, delete all,
+delete the folders.
 
@@
 \KeywordTok{.libPath}\NormalTok{()}
-\end{Highlighting}
-\end{Shaded}
-
-Open up install and uninstall programs, find R and Rstudio, and
-uninstall them. Then delete all files found path paths shown by
-\emph{.libPath()}, looking at these: -
-\emph{C:/Users/fan/Documents/R/win-library/3.6} - \emph{C:/Program
-Files/R/R-3.6.1/library}
-
-For Linux:
-
-\begin{itemize}
-\tightlist
-\item
-  if used apt-get to install, R installed under main user drive,
-  deactivate conda, and check which conda
-\end{itemize}
+\CommentTok{# C:/Users/fan/Documents/R/win-library/3.6}
+\CommentTok{# C:/Program Files/R/R-3.6.1/library}
+\end{Highlighting}
+\end{Shaded}
+
+For Linux and for unsintalling inside conda:
 
@@
 
+Need to install R. Then need to install also an editor/IDE for R.
+Rstudio is the dominant R IDE. VSCode and Atom also works well,
+especially VSCode as editors. Dramatically better experience for writing
+scripts outside of Rstudio which feels unwieldy and slow especially
+compared to VSCode.
+
+Overall plan:
+
 \begin{enumerate}
@@
     for debian:
-    \href{https://cran.r-project.org/bin/linux/debian/}{Johannes Ranke}
+    \href{https://cran.r-project.org/bin/linux/debian/}{Johannes Ranke}.
+    For Linux/Debian installation, crucial to update the
+    \emph{source.list} to include sources that have more recent versions
+    of R. If not, will get very old R versions that is not compatible
+    with many packages.
+  \item
+    add R to path for Windows. In Windows Path, add for example:
+    \emph{C:/Program Files/R/R-3.6.2/bin/x64/} and \emph{C:/Rtools/bin}
   \end{itemize}
@@
 \item
-  Install packages
+  Install additional packages (from commandline)
+
+  \begin{itemize}
+  \tightlist
+  \item
+    various R data-science packages have dependencies, and additional
+    not-R programs might need to be installed. Install them as needed,
+    for example: \emph{libcurl4-openssl-dev} and \emph{libssl-dev} from
+    command prompt first inside Debian.
+  \end{itemize}
 \end{enumerate}
 
-note that installation will not work if the machine's version of R is
-not up to date, this could be the case with default R versions for some
-linux installations. For Debian for example, need to update the
-\emph{source.list} to include sources that have more recent versions of
-R.
-
-Additionally, need to install \emph{libcurl4-openssl-dev} and
-\emph{libssl-dev} from command prompt first inside Debian.
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\CommentTok{# If inside Debian, due to some tidymodel install issues, do this`}
-\ExtensionTok{conda}\NormalTok{ install -c r r}
-\ExtensionTok{conda}\NormalTok{ install -c r r-essentials}
-\ExtensionTok{conda}\NormalTok{ install -c r r-igraph}
-\ExtensionTok{conda}\NormalTok{ install -c conda-forge igraph}
-
+\hypertarget{linux-r-install}{%
+\subsubsection{Linux R Install}\label{linux-r-install}}
+
+For linux/Debian, to Install latest R:
+
+\begin{Shaded}
+\begin{Highlighting}[]
 \CommentTok{# Go to get latesdebian latest r sources.list}
@@
 
-Which R?
-
-\begin{itemize}
-\tightlist
-\item
-  \emph{export RSTUDIO\_WHICH\_R=/usr/bin/R}
-\item
-  \emph{export RSTUDIO\_WHICH\_R=/home/wangfanbsg75/anaconda3/bin/R}
-\end{itemize}
+\hypertarget{install-packages-for-r}{%
+\subsubsection{Install Packages for R}\label{install-packages-for-r}}
+
+From command prompt, enter R by typeing \emph{R}, and install packages:
 
@@
 
-\hypertarget{set-up-r-environment-in-conda}{%
-\subsection{Set up R-Environment in
-Conda}\label{set-up-r-environment-in-conda}}
-
-Conda environments are language agnostic. pip is a package manager for
-Python. venv is an environment manager for Python. conda is both a
-package and environment manager and is language agnostic. Inside
-Anaconda Prompt:
+\hypertarget{install-r-inside-conda}{%
+\subsection{Install R (inside Conda)}\label{install-r-inside-conda}}
 
@@
 (official distribution) and also the more frequently updated conda-forge
-channel. Prioritize conda-forge to get the latest packages. after adding
+channel. Prioritize conda-forge to get the latest packages. After adding
 \emph{conda-forge} to channels, that will be prioritized, so when
@@
 the default channel and in the \emph{conda-forge} channels.
+
+\hypertarget{set-up-conda-r-environment}{%
+\subsubsection{Set up Conda R
+environment}\label{set-up-conda-r-environment}}
+
+Create a Conda Environment called \emph{r\_env}, and update its
+channels.
+
+\begin{itemize}
+\tightlist
+\item
+  \textbf{Location}: Installed environments are shown appear in the
+  \emph{envs} folder of \emph{C:/ProgramData/Anaconda3/envs/}. Can be
+  easily deleted without disrupting the main base installation for
+  conda. This is very important. During installation, could easily run
+  into problems, and need to re-install. Much better to only re-install
+  a folder. Note that when R is installed in \emph{envs}, it will not
+  show up under add or remove programs for uninstallation from there,
+  has to be uninstalled, deleted directly here.
+\item
+  \textbf{Use only in Env}: Note that if we installed r inside r\_env,
+  if we type \emph{r} under the base environment, we can not enter r. We
+  can only enter r within r\_env. With PATH properly set-up, this
+  happens under Conda Prompt, Windows Prompt, etc.
+\item
+  \textbf{Multiple Pythons}: With the above installation for R, one
+  benefit is that if R requires a different version of Python than what
+  the base environment uses, the r\_env could have a different python
+  version. So type \emph{python} in the base environment as well as
+  inside the \emph{r\_env}. This also means potentially there could be
+  duplicated installations I think. Look at the python versions under
+  \emph{conda list} in the base and in the r-environment.
+\item
+  \textbf{File Size}: Note that this creates a large installation
+  folder, \emph{C:/ProgramData/Anaconda3/envs/r\_env/}, without
+  additional packages, is 1.3 GB in size
+\end{itemize}
 
@@
 
-\CommentTok{# install files}
-\ExtensionTok{conda}\NormalTok{ install -n r_env -c r r r-essentials r-tidyverse r-tidymodels -y}
-
-\CommentTok{# trouble with igraph installation, install here from conda}
-\CommentTok{# conda install -n r_env r-essentials r-base r-tidyr r-tidyverse r-devtools r-irkernel r-pkgdown r-roxygen2}
-\ExtensionTok{conda}\NormalTok{ install -n r_env -c r r-igraph}
-\ExtensionTok{conda}\NormalTok{ install -n r_env -c conda-forge igraph}
-\ExtensionTok{conda}\NormalTok{ install -n r_env -c r r-rstantools r-rstan r-rstanarm -y}
-
 \CommentTok{# see all installed environments}
@@
 
-\begin{itemize}
-\tightlist
-\item
-  \textbf{Location}: Installed environments are shown appear in the
-  \emph{envs} folder of \emph{C:/ProgramData/Anaconda3/envs/}. Can be
-  easily deleted without disrupting the main base installation for
-  conda. This is very important. During installation, could easily run
-  into problems, and need to re-install. Much better to only re-install
-  a folder. Note that when R is installed in \emph{envs}, it will not
-  show up under add or remove programs for uninstallation from there,
-  has to be uninstalled, deleted directly here.
-\item
-  \textbf{Use only in Env}: Note that if we installed r inside r\_env,
-  if we type \emph{r} under the base environment, we can not enter r. We
-  can only enter r within r\_env. With PATH properly set-up, this
-  happens under Conda Prompt, Windows Prompt, etc.
-\item
-  \textbf{Multiple Pythons}: With the above installation for R, one
-  benefit is that if R requires a different version of Python than what
-  the base environment uses, the r\_env could have a different python
-  version. So type \emph{python} in the base environment as well as
-  inside the \emph{r\_env}. This also means potentially there could be
-  duplicated installations I think. Look at the python versions under
-  \emph{conda list} in the base and in the r-environment.
-\item
-  \textbf{File Size}: Note that this creates a large installation
-  folder, \emph{C:/ProgramData/Anaconda3/envs/r\_env/}, without
-  additional packages, is 1.3 GB in size
-\end{itemize}
-
-\hypertarget{install-additional-packages-inside-the-r-environment}{%
+\hypertarget{install-r-and-some-packages-in-conda}{%
+\subsubsection{Install R and Some Packages in
+Conda}\label{install-r-and-some-packages-in-conda}}
+
+Either inside a R specific environment, or outside of it, now do
+additional installations for R and also R packages.
+
+During installation, the R programs might require downgrading other
+programs in the Conda environment that Python for example also uses.
+That is why potentially it is safer to install in R environment.
+However, when installing in R enviornment, certain packages could have
+issues if installer does not realize it is in an environment with
+special folder structure, so installation could fail.
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\CommentTok{# install files}
+\ExtensionTok{conda}\NormalTok{ install -n r_env -c r r r-essentials r-tidyverse r-tidymodels -y}
+
+\CommentTok{# trouble with igraph installation, install here from conda}
+\CommentTok{# conda install -n r_env r-essentials r-base r-tidyr r-tidyverse r-devtools r-irkernel r-pkgdown r-roxygen2}
+\ExtensionTok{conda}\NormalTok{ install -n r_env -c r r-igraph}
+\ExtensionTok{conda}\NormalTok{ install -n r_env -c conda-forge igraph}
+\ExtensionTok{conda}\NormalTok{ install -n r_env -c r r-rstantools r-rstan r-rstanarm -y}
+\end{Highlighting}
+\end{Shaded}
+
+\hypertarget{install-additional-packages-inside-the-r}{%
 \subsection{Install Additional Packages inside the
-R-environment}\label{install-additional-packages-inside-the-r-environment}}
+R}\label{install-additional-packages-inside-the-r}}
 
@@
 environment. Or they could be installed later from inside r-studio.
-Installing inside r-studio is a lot better.
-
-\emph{tidymodel} has installation issues sometimes.
+Installing inside r-studio is a lot better. \emph{tidymodel} has
+installation issues sometimes.
 
 In \emph{r\_env}, type in \emph{R}, and then install from inside
-terminal's R:
+terminal's R. For conda env, devtools will be installed and will install
+packages inside \emph{envs/r\_env/Lib/R}.
 
@@
 \CommentTok{# enter into env}
-\ExtensionTok{conda}\NormalTok{ activate r_env}
+\CommentTok{# conda activate r_env}
 \CommentTok{# enter R or type in rstudio}
 \CommentTok{# sicne R is only install inside r_env, has to enter rstudio from r_env}
-\ExtensionTok{R}
-\ExtensionTok{rstudio}
+\CommentTok{# R}
+\CommentTok{# rstudio}
 
@@
 \CommentTok{# tidymodel installation on linux difficult}
-\ExtensionTok{install.packages}\NormalTok{(c(}\StringTok{"rstantools"}\NormalTok{, }\StringTok{"rstan"}\NormalTok{, }\StringTok{"rstanarm"}\NormalTok{))}
-\ExtensionTok{install.packages}\NormalTok{(c(}\StringTok{"tidyr"}\NormalTok{, }\StringTok{"tidyverse"}\NormalTok{, }\StringTok{"tidymodels"}\NormalTok{))}
+\KeywordTok{install.packages}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\StringTok{"rstantools"}\NormalTok{, }\StringTok{"rstan"}\NormalTok{, }\StringTok{"rstanarm"}\NormalTok{))}
+\KeywordTok{install.packages}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\StringTok{"tidyr"}\NormalTok{, }\StringTok{"tidyverse"}\NormalTok{, }\StringTok{"tidymodels"}\NormalTok{))}
 
@@
 \CommentTok{# development packages}
-\ExtensionTok{install.packages}\NormalTok{(c(}\StringTok{"devtools"}\NormalTok{, }\StringTok{"IRkernel"}\NormalTok{, }\StringTok{"pkgdown"}\NormalTok{, }\StringTok{"roxygen2"}\NormalTok{, }\StringTok{"kableExtra"}\NormalTok{))}
+\KeywordTok{install.packages}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\StringTok{"devtools"}\NormalTok{, }\StringTok{"IRkernel"}\NormalTok{, }\StringTok{"pkgdown"}\NormalTok{, }\StringTok{"roxygen2"}\NormalTok{, }\StringTok{"kableExtra"}\NormalTok{))}
 \CommentTok{# other packages}
-\ExtensionTok{install.packages}\NormalTok{(c(}\StringTok{"AER"}\NormalTok{, }\StringTok{"minpack.lm"}\NormalTok{, }\StringTok{"knitr"}\NormalTok{, }\StringTok{"matlab"}\NormalTok{))}
+\KeywordTok{install.packages}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\StringTok{"AER"}\NormalTok{, }\StringTok{"minpack.lm"}\NormalTok{, }\StringTok{"knitr"}\NormalTok{, }\StringTok{"matlab"}\NormalTok{))}
 
@@
 \CommentTok{# if install does not work, load locally}
-\ExtensionTok{devtools}\NormalTok{::install_github(}\StringTok{"fanwangecon/R4Econ"}\NormalTok{)}
+\NormalTok{devtools}\OperatorTok{::}\KeywordTok{install_github}\NormalTok{(}\StringTok{"fanwangecon/R4Econ"}\NormalTok{)}
 
 \CommentTok{# Kernel}
-\ExtensionTok{install.packages}\NormalTok{(c(}\StringTok{'repr'}\NormalTok{, }\StringTok{'IRdisplay'}\NormalTok{, }\StringTok{'evaluate'}\NormalTok{, }\StringTok{'crayon'}\NormalTok{, }\StringTok{'pbdZMQ'}\NormalTok{, }\StringTok{'devtools'}\NormalTok{, }\StringTok{'uuid'}\NormalTok{, }\StringTok{'digest'}\NormalTok{))}
-\FunctionTok{IRkernel::installspec()}
-\end{Highlighting}
-\end{Shaded}
-
-Install additional packages from inside R. The devtools install will
-install packages inside \emph{envs/r\_env/Lib/R}.
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\CommentTok{#######################################}
-\CommentTok{### Own Package}
-\CommentTok{#######################################}
-\NormalTok{devtools}\OperatorTok{::}\KeywordTok{install_github}\NormalTok{(}\StringTok{"fanwangecon/R4Econ"}\NormalTok{)}
-\CommentTok{# install_dev("cli")}
+\KeywordTok{install.packages}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\StringTok{'repr'}\NormalTok{, }\StringTok{'IRdisplay'}\NormalTok{, }\StringTok{'evaluate'}\NormalTok{, }\StringTok{'crayon'}\NormalTok{, }\StringTok{'pbdZMQ'}\NormalTok{, }\StringTok{'devtools'}\NormalTok{, }\StringTok{'uuid'}\NormalTok{, }\StringTok{'digest'}\NormalTok{))}
+\NormalTok{IRkernel}\OperatorTok{::}\KeywordTok{installspec}\NormalTok{()}
 \end{Highlighting}
@@
 
-\hypertarget{install-packages-from-r-studio}{%
-\subsection{Install Packages from
-R-Studio}\label{install-packages-from-r-studio}}
-
-Install addition files inside Rstudio. Easier to debug potentially.
-Install rtools as described
-\href{https://thecoatlessprofessor.com/programming/cpp/installing-rtools-for-compiled-code-via-rcpp/}{here}:
-\href{https://cran.r-project.org/bin/windows/Rtools/}{rtools download}.
-Alternatively:
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\KeywordTok{install.packages}\NormalTok{(}\StringTok{"installr"}\NormalTok{)}
-\KeywordTok{library}\NormalTok{(}\StringTok{"installr"}\NormalTok{)}
-\CommentTok{# Note that this will generate several pop-up windows}
-\KeywordTok{install.Rtools}\NormalTok{()}
-\CommentTok{# choose to only install 64 bit toolchain}
-\CommentTok{# this installs g++ which is needed for rstanarm}
-\CommentTok{# Add these below to windows path}
-\CommentTok{# c:/Rtools/bin;}
-\CommentTok{# c:/Rtools/mingw_64/bin;}
-
-\ControlFlowTok{if}\NormalTok{ (}\OperatorTok{!}\KeywordTok{require}\NormalTok{(devtools)) \{}
-  \KeywordTok{install.packages}\NormalTok{(}\StringTok{"devtools"}\NormalTok{)}
-  \KeywordTok{library}\NormalTok{(devtools)}
-\NormalTok{\}}
-\KeywordTok{library}\NormalTok{(devtools)}
-\KeywordTok{install_github}\NormalTok{(}\StringTok{"stan-dev/rstanarm"}\NormalTok{, }\DataTypeTok{args =} \StringTok{"--preclean"}\NormalTok{)}
-
-\KeywordTok{setwd}\NormalTok{(}\StringTok{'C:/ProgramData/Anaconda3/envs/r_env/Lib/R/library'}\NormalTok{)}
-
-\KeywordTok{install.packages}\NormalTok{(}\StringTok{"stan-dev/rstanarm"}\NormalTok{, }\DataTypeTok{dependencies=}\OtherTok{TRUE}\NormalTok{, }\DataTypeTok{INSTALL_opts =} \KeywordTok{c}\NormalTok{(}\StringTok{'--no-lock'}\NormalTok{))}
-
-\CommentTok{# other packages}
-\KeywordTok{install.packages}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\StringTok{"tidymodels"}\NormalTok{, }\StringTok{"AER"}\NormalTok{, }\StringTok{"minpack.lm"}\NormalTok{, }\StringTok{"knitr"}\NormalTok{, }\StringTok{"kableExtra"}\NormalTok{, }\StringTok{"matlab"}\NormalTok{))}
-
-\CommentTok{# for r-kernel to work in Atom}
-\KeywordTok{install.packages}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\StringTok{'repr'}\NormalTok{, }\StringTok{'IRdisplay'}\NormalTok{, }\StringTok{'evaluate'}\NormalTok{, }\StringTok{'crayon'}\NormalTok{, }\StringTok{'pbdZMQ'}\NormalTok{, }\StringTok{'devtools'}\NormalTok{, }\StringTok{'uuid'}\NormalTok{, }\StringTok{'digest'}\NormalTok{))}
-\NormalTok{devtools}\OperatorTok{::}\KeywordTok{install_github}\NormalTok{(}\StringTok{'IRkernel/IRkernel'}\NormalTok{)}
-\NormalTok{IRkernel}\OperatorTok{::}\KeywordTok{installspec}\NormalTok{()}
-
-\CommentTok{# Install my package}
-\NormalTok{devtools}\OperatorTok{::}\KeywordTok{install_github}\NormalTok{(}\StringTok{"fanwangecon/R4Econ"}\NormalTok{)}
-\end{Highlighting}
-\end{Shaded}
-
-\hypertarget{test-files}{%
-\subsubsection{Test Files}\label{test-files}}
+Is RSTUDIO pointing to the R installation you want? Note you can open
+Rstudio from differen conda env command line, that will use different R
+installations. Or also set:
+
+\begin{itemize}
+\tightlist
+\item
+  \emph{export RSTUDIO\_WHICH\_R=/usr/bin/R}
+\item
+  \emph{export RSTUDIO\_WHICH\_R=/home/wangfanbsg75/anaconda3/bin/R}
+\end{itemize}
+
+\hypertarget{r-tests}{%
+\subsection{R Tests}\label{r-tests}}
 
@@
 
-\hypertarget{install-latex}{%
-\section{Install Latex}\label{install-latex}}
+\hypertarget{install-latex-and-pdf}{%
+\section{Install Latex and PDF}\label{install-latex-and-pdf}}
 
@@
 
-\hypertarget{compile-in-atom-and-texstudio}{%
-\subsection{Compile in Atom and
-Texstudio}\label{compile-in-atom-and-texstudio}}
+Test file compilations in TexStudio.
+
+\hypertarget{okular-pdf}{%
+\subsection{Okular PDF}\label{okular-pdf}}
+
+Linux: \emph{sudo apt-get install okular} Windows: install okular from
+windows app store
+
+\hypertarget{okular-shortcuts-and-features}{%
+\subsubsection{Okular Shortcuts and
+Features}\label{okular-shortcuts-and-features}}
+
+\textbf{Features}:
+
+\begin{itemize}
+\tightlist
+\item
+  Okular 3 pages per row view:
+
+  \begin{itemize}
+  \tightlist
+  \item
+    view, overview
+  \end{itemize}
+\item
+  Automatic Update when PDF updated elsewhere
+
+  \begin{itemize}
+  \tightlist
+  \item
+    this is one of the key reasons to use okular, when I knit a Rmd file
+    to PDF, the currently open Okular PDF file automatically updates and
+    does not give file is open error like Acrobat.
+  \end{itemize}
+\item
+  Background color:
+
+  \begin{itemize}
+  \tightlist
+  \item
+    can easily change background color to non-white.
+  \end{itemize}
+\end{itemize}
+
+\textbf{Shortcuts}:
+
+\begin{itemize}
+\tightlist
+\item
+  Okular configure shortcuts: setting, configure shortcuts
+\item
+  Okular if menu bar lost: \emph{Ctrl + m}
+\item
+  Okular comment pane: \emph{F6}
+\item
+  Okular close left pane: \emph{F7}
+\item
+  Okular full scrren: \emph{Ctrl + Shift + F}
+
+  \begin{itemize}
+  \tightlist
+  \item
+    unlike acrobat, pdf allows for multiple scrrens
+  \end{itemize}
+\end{itemize}
+
+\hypertarget{adobe-pdf}{%
+\subsection{Adobe PDF}\label{adobe-pdf}}
+
+PDF Adobe Acrobat Installation + go to adobe website, log in using
+\href{mailto:fwang26@uh.edu}{\nolinkurl{fwang26@uh.edu}} + go to my
+account, choose view and download my apps, choose acrobat \& PDF,
+download Acrobat DC + UH account can only be activated on two accounts
+at once, so need to kick other computers out temporarily potentially
+
+\hypertarget{install-various-editors}{%
+\section{Install Various Editors}\label{install-various-editors}}
+
+Atom, VSCode, Notepad++, Sublime, etc. These are essential editors that
+allows for pleasant programming and writing experiences. See here for
+\href{http://fanwangecon.github.io/}{fan} instructions on
+\href{https://fanwangecon.github.io/Tex4Econ/nontex/install/linux/fn_vim.html}{vim}
+installations.
+
+\hypertarget{vscode-installation}{%
+\subsection{VSCode Installation}\label{vscode-installation}}
+
+VSCode is much more light-weight than Atom, much faster. On Windows,
+download \href{https://code.visualstudio.com/download}{here}.
+
+For Linux:
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\CommentTok{# Debian Install}
+\ExtensionTok{curl}\NormalTok{ https://packages.microsoft.com/keys/microsoft.asc }\KeywordTok{|} \ExtensionTok{gpg}\NormalTok{ --dearmor }\OperatorTok{>}\NormalTok{ microsoft.gpg}
+\FunctionTok{sudo}\NormalTok{ install -o root -g root -m 644 microsoft.gpg /usr/share/keyrings/microsoft-archive-keyring.gpg}
+\FunctionTok{sudo}\NormalTok{ sh -c }\StringTok{'echo "deb [arch=amd64 signed-by=/usr/share/keyrings/microsoft-archive-keyring.gpg] https://packages.microsoft.com/repos/vscode stable main" > /etc/apt/sources.list.d/vscode.list'}
+\FunctionTok{sudo}\NormalTok{ apt-get install apt-transport-https}
+\FunctionTok{sudo}\NormalTok{ apt-get update}
+\FunctionTok{sudo}\NormalTok{ apt-get install code }\CommentTok{# or code-insiders}
+
+\CommentTok{# Change Font (https://wwFw.reddit.com/r/Crostini/comments/cesxr0/vscode_ui_and_fonts_too_small_heres_how_to_fix_it/)}
+\CommentTok{# modify: /usr/share/applications/code.desktop}
+\ExtensionTok{nvim}\NormalTok{ /usr/share/applications/code.desktop}
+\CommentTok{#replace this line: Exec=/usr/share/code/code --unity-launch %F}
+\VariableTok{Exec=}\NormalTok{sommelier }\ExtensionTok{-X}\NormalTok{ --scale=0.8 --dpi=160 /usr/share/code/code }\StringTok{"--unity-launch %F"}
+\CommentTok{#replace this line: Exec=/usr/share/code/code --new-window %F}
+\VariableTok{Exec=}\NormalTok{sommelier }\ExtensionTok{-X}\NormalTok{ --scale=0.8 --dpi=160 /usr/share/code/code }\StringTok{"--new-window %F"}
+
+\CommentTok{# Open File}
+\CommentTok{# low density mode to see cleary}
+\ExtensionTok{code}
+\end{Highlighting}
+\end{Shaded}
+
+\hypertarget{vscode-extensions}{%
+\subsubsection{VSCode Extensions}\label{vscode-extensions}}
+
+Press \emph{Ctrl + P}, paste the \emph{ext install} commands below to
+install extensions:
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\CommentTok{# [Microsoft Python Extension](https://marketplace.visualstudio.com/items?itemName=ms-python.python)}
+\ExtensionTok{ext}\NormalTok{ install ms-python.python}
+\CommentTok{# [Latex Workshop](https://marketplace.visualstudio.com/items?itemName=James-Yu.latex-workshop)}
+\ExtensionTok{ext}\NormalTok{ install latex-workshop}
+\CommentTok{# [R](https://marketplace.visualstudio.com/items?itemName=Ikuyadeu.r)}
+\ExtensionTok{ext}\NormalTok{ install ikuyadeu.r}
+\end{Highlighting}
+\end{Shaded}
+
+\hypertarget{vscode-shortcuts-and-features}{%
+\subsubsection{VSCode Shortcuts and
+Features}\label{vscode-shortcuts-and-features}}
+
+\textbf{Features}:
+
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi}.}
+\tightlist
+\item
+  open a file, if have workspace where the file is in, automatically
+  expand tree and show where file is on left pane.
+\end{enumerate}
+
+\textbf{Shortcuts} :
+
+\begin{itemize}
+\tightlist
+\item
+  Zen model: \emph{Ctrl + k, z}, this means press control k, then press
+  z
+\item
+  Open up Settings: \emph{Ctrl + ,}
+\item
+  Preview Markdown in VSCode: \emph{Ctrl + Shift + V}
+\item
+  Open up left pane: \emph{Ctrl + B}
+\item
+  Wrap Text: \emph{alt + Z}, switch between wrap or not to save screen
+  space for example.
+\end{itemize}
+
+\hypertarget{vscode-and-r}{%
+\subsubsection{VSCode and R}\label{vscode-and-r}}
+
+VSCode works pretty well it seems with Rmd files. Rmd files are useful
+to work through algorithm, examples in preparation for writing usable
+functions. Rstudio has been often very slow for me, and I generally feel
+like can not stretch around and work in RStudio IDE.
+
+In Atom, Hydrogen works, but really only works with very basic line by
+line testing.
+
+Using VSCode with RMD files seems much quicker, and there is room to
+breath.
+
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi}.}
+\tightlist
+\item
+  Install R following R installation instructions.
+\item
+  Then install extension
+  \href{https://marketplace.visualstudio.com/items?itemName=Ikuyadeu.r}{R}.
+  Microsoft stopped supporting rmd in VSCode:
+  \href{https://github.com/microsoft/RTVS}{R Tools for Visual Studio}
+\item
+  properly set path (might have to call vscode from r env)
+
+  \begin{itemize}
+  \tightlist
+  \item
+    \emph{r.rterm.linux}:
+    \emph{/home/wangfanbsg75/anaconda3/envs/r\_env/bin/R}
+  \item
+    \emph{r.rterm.windows}: \emph{C:/Program
+    Files/R/R-3.6.2/bin/x64/R.exe}
+
+    \begin{itemize}
+    \tightlist
+    \item
+      note \emph{R.exe} at the end
+    \end{itemize}
+  \end{itemize}
+\item
+  Run:
+
+  \begin{itemize}
+  \tightlist
+  \item
+    ctrl + enter to activate R terminal
+  \item
+    VSCode 2019 allows for Knit Rmd: \emph{Ctrl + Shift + K}
+  \item
+    also can run code segment: select lines and \emph{ctrl + enter}
+  \end{itemize}
+\end{enumerate}
+
+\hypertarget{vscode-and-latex}{%
+\paragraph{VSCode and Latex}\label{vscode-and-latex}}
+
+Download
+\href{https://marketplace.visualstudio.com/items?itemName=James-Yu.latex-workshop}{Latex
+Workshop}.
+
+\hypertarget{atom-installation}{%
+\subsection{Atom Installation}\label{atom-installation}}
+
+Atom is slow but has clean look and nice git/github integration.
+
+\hypertarget{atom-extensions}{%
+\subsubsection{Atom Extensions}\label{atom-extensions}}
+
+Terminal in windows or linux after installation: \emph{apm install
+hydrogen}. apm is the atom package manager:
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\CommentTok{# Once atom is installed, can use apm to install packages}
+\FunctionTok{apm}\NormalTok{ install hydrogen}
+\FunctionTok{apm}\NormalTok{ install project-manager}
+\FunctionTok{apm}\NormalTok{ install sublime-style-column-selection}
+\FunctionTok{apm}\NormalTok{ install minimap}
+
+\CommentTok{# vim distraction free editing}
+\FunctionTok{apm}\NormalTok{ install vim-mode-plus}
+\FunctionTok{apm}\NormalTok{ install zen}
+
+\CommentTok{# Inside Conda open up atom}
+\ExtensionTok{atom}
+\end{Highlighting}
+\end{Shaded}
+
+\hypertarget{atom-shortcuts-and-features}{%
+\subsubsection{Atom Shortcuts and
+Features}\label{atom-shortcuts-and-features}}
+
+\textbf{Features}:
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\CommentTok{# open multiple projects from atom at the same time, after repos synced}
+\ExtensionTok{atom}\NormalTok{ ~/fanwangecon.github.io ~/Pyfan ~/Teaching ~/Tex4Econ ~/R4Econ ~/M4Econ ~/Py4Econ}
+\CommentTok{# open up any py from from within, try 1+1, does it work?}
+\CommentTok{# also use script, try ctrl + shift + b, run whole file (not hydrogen)}
+\end{Highlighting}
+\end{Shaded}
+
+\textbf{Shortcuts} :
+
+\begin{itemize}
+\tightlist
+\item
+  Git Pane: \emph{Ctrl + 9}, \emph{Ctrl + 8}
+\end{itemize}
+
+\hypertarget{atom-and-python}{%
+\subsubsection{Atom and Python}\label{atom-and-python}}
+
+Having installed Anaconda, now install Atom and Hydrogen to Test with
+Python. For both Jupyter as well as Atom, always open from command
+prompt, open from \emph{Anaconda Prompt} with admin rights.
+
+Open up \emph{Jupyter Notebook}, does the python kernel work? If does
+not, uninstall and re-install Anaconda.
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\CommentTok{# start jupyter lab, from prompt}
+\ExtensionTok{jupyter}\NormalTok{ lab}
+\end{Highlighting}
+\end{Shaded}
+
+Try \emph{1+1}.
+
+\hypertarget{atom-and-latex}{%
+\subsubsection{Atom and Latex}\label{atom-and-latex}}
 
@@
 
-Go to Tex4Econ and compile various template files and other types of
-files there to see if tex is working.
-
-Compile the same files in texstudio.
+\hypertarget{other-editors}{%
+\subsection{Other Editors}\label{other-editors}}
+
+\hypertarget{notepad}{%
+\subsubsection{Notepad++}\label{notepad}}
+
+\href{https://notepad-plus-plus.org/downloads/v7.8.2/}{Notepad++}. Many
+old projects have xml folder structures for Notepad++.
+
+\begin{itemize}
+\tightlist
+\item
+  Silently update file changes made in other editors: Settings,
+  Preferences, MISC., File Status Auto Detection, Update Silently.
+\end{itemize}
+
+\hypertarget{sublime}{%
+\subsubsection{Sublime}\label{sublime}}
+
+\href{https://www.sublimetext.com/3}{Sublime}
+
+there are some issues with atom. When a file is edited inside Vim, when
+changes are saved, a
+\href{https://github.com/atom/atom/issues/17186}{temp file is created in
+atom}. Sublime would, however, still show the file with the changes.
+This makes dual screen editing very difficult. Sublime text is used for
+this situation.
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\CommentTok{# Sublime Linux}
+\FunctionTok{wget}\NormalTok{ -qO - https://download.sublimetext.com/sublimehq-pub.gpg }\KeywordTok{|} \FunctionTok{sudo}\NormalTok{ apt-key add -}
+\FunctionTok{sudo}\NormalTok{ apt-get install apt-transport-https}
+\BuiltInTok{echo} \StringTok{"deb https://download.sublimetext.com/ apt/stable/"} \KeywordTok{|} \FunctionTok{sudo}\NormalTok{ tee /etc/apt/sources.list.d/sublime-text.list}
+\FunctionTok{sudo}\NormalTok{ apt-get update}
+\FunctionTok{sudo}\NormalTok{ apt-get install sublime-text}
+\CommentTok{# launch from terminal}
+\ExtensionTok{subl}
+\end{Highlighting}
+\end{Shaded}
+
+\emph{Sublime Setup}:
+
+\begin{itemize}
+\tightlist
+\item
+  \href{https://weibeld.net/r/rmd_sublime_package.html}{r and rmd setup}
+\end{itemize}
+
+\hypertarget{pycharm}{%
+\subsubsection{PyCharm}\label{pycharm}}
+
+\href{https://www.}{pycharm}jetbrains.com/pycharm/)
 
@@
 \subsection{Package Managers}\label{package-managers}}
+
+To install packages in windows more easily:
 
@@
 
-\hypertarget{editors}{%
-\subsection{Editors}\label{editors}}
-
-In addition to Atom, which is pretty slow, and harder to run on lower
-spec computers.
-
-\hypertarget{vscode}{%
-\subsubsection{VSCode}\label{vscode}}
-
-VSCode is much more light-weight than Atom, does not have hydrogen.
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\CommentTok{# Debian Install}
-\ExtensionTok{curl}\NormalTok{ https://packages.microsoft.com/keys/microsoft.asc }\KeywordTok{|} \ExtensionTok{gpg}\NormalTok{ --dearmor }\OperatorTok{>}\NormalTok{ microsoft.gpg}
-\FunctionTok{sudo}\NormalTok{ install -o root -g root -m 644 microsoft.gpg /usr/share/keyrings/microsoft-archive-keyring.gpg}
-\FunctionTok{sudo}\NormalTok{ sh -c }\StringTok{'echo "deb [arch=amd64 signed-by=/usr/share/keyrings/microsoft-archive-keyring.gpg] https://packages.microsoft.com/repos/vscode stable main" > /etc/apt/sources.list.d/vscode.list'}
-\FunctionTok{sudo}\NormalTok{ apt-get install apt-transport-https}
-\FunctionTok{sudo}\NormalTok{ apt-get update}
-\FunctionTok{sudo}\NormalTok{ apt-get install code }\CommentTok{# or code-insiders}
-
-\CommentTok{# Change Font (https://www.reddit.com/r/Crostini/comments/cesxr0/vscode_ui_and_fonts_too_small_heres_how_to_fix_it/)}
-\CommentTok{# modify: /usr/share/applications/code.desktop}
-\ExtensionTok{nvim}\NormalTok{ /usr/share/applications/code.desktop}
-\CommentTok{#replace this line: Exec=/usr/share/code/code --unity-launch %F}
-\VariableTok{Exec=}\NormalTok{sommelier }\ExtensionTok{-X}\NormalTok{ --scale=0.8 --dpi=160 /usr/share/code/code }\StringTok{"--unity-launch %F"}
-\CommentTok{#replace this line: Exec=/usr/share/code/code --new-window %F}
-\VariableTok{Exec=}\NormalTok{sommelier }\ExtensionTok{-X}\NormalTok{ --scale=0.8 --dpi=160 /usr/share/code/code }\StringTok{"--new-window %F"}
-
-\CommentTok{# Open File}
-\CommentTok{# low density mode to see cleary}
-\ExtensionTok{code}
-\end{Highlighting}
-\end{Shaded}
-
-Extensions to Download for VSCode:
-
-\begin{enumerate}
-\def\labelenumi{\arabic{enumi}.}
-\setcounter{enumi}{1}
-\tightlist
-\item
-  \href{https://marketplace.visualstudio.com/items?itemName=ms-python.python}{Microsoft
-  Python Extension}
-\end{enumerate}
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\ExtensionTok{ext}\NormalTok{ install ms-python.python}
-\end{Highlighting}
-\end{Shaded}
-
-\hypertarget{vscode-shortcuts}{%
-\paragraph{VSCode Shortcuts}\label{vscode-shortcuts}}
-
-\begin{itemize}
-\tightlist
-\item
-  Open up Settings: \emph{Ctrl + ,}
-\item
-  Preview Markdown in VSCode: \emph{Ctrl + Shift + V}
-\item
-  Open up left pane: \emph{Ctrl + B}
-\item
-  Wrap Text: \emph{alt + Z}, switch between wrap or not to save screen
-  space for example.
-\end{itemize}
-
-\hypertarget{vscode-benefits}{%
-\paragraph{VSCode Benefits}\label{vscode-benefits}}
-
-\begin{enumerate}
-\def\labelenumi{\arabic{enumi}.}
-\tightlist
-\item
-  open a file, if have workspace where the file is in, automatically
-  expand tree and show where file is on left pane.
-\end{enumerate}
-
-\hypertarget{vscode-and-r}{%
-\paragraph{VSCode and R}\label{vscode-and-r}}
-
-VSCode works pretty well it seems with Rmd files. Rmd files are useful
-to work through algorithm, examples in preparation for writing usable
-functions. Rstudio has been often very slow for me, and I generally feel
-like can not stretch around and work in RStudio IDE.
-
-In Atom, Hydrogen works, but really only works with very basic line by
-line testing.
-
-Using VSCode with RMD files seems much quicker, and there is room to
-breath.
-
-\begin{enumerate}
-\def\labelenumi{\arabic{enumi}.}
-\tightlist
-\item
-  Install R following R installation instructions.
-\item
-  Then install extension
-  \href{https://marketplace.visualstudio.com/items?itemName=Ikuyadeu.r}{R}.
-  Microsoft stopped supporting rmd in VSCode:
-  \href{https://github.com/microsoft/RTVS}{R Tools for Visual Studio}
-\item
-  properly set path (might have to call vscode from r env)
-
-  \begin{itemize}
-  \tightlist
-  \item
-    \emph{r.rterm.linux}:
-    \emph{/home/wangfanbsg75/anaconda3/envs/r\_env/bin/R}
-  \end{itemize}
-\item
-  Run:
-
-  \begin{itemize}
-  \tightlist
-  \item
-    ctrl + enter to activate R terminal
-  \item
-    VSCode 2019 allows for Knit Rmd: \emph{Ctrl + Shift + K}
-  \item
-    also can run code segment: select lines and \emph{ctrl + enter}
-  \end{itemize}
-\end{enumerate}
-
-\hypertarget{vscode-and-latex}{%
-\paragraph{VSCode and Latex}\label{vscode-and-latex}}
-
-\begin{enumerate}
-\def\labelenumi{\arabic{enumi}.}
-\tightlist
-\item
-  download
-  \href{https://marketplace.visualstudio.com/items?itemName=James-Yu.latex-workshop}{Latex
-  Workshop}
-\end{enumerate}
-
-\hypertarget{notepad}{%
-\subsubsection{Notepad++}\label{notepad}}
-
-\href{https://notepad-plus-plus.org/downloads/v7.8.2/}{Notepad++}. Many
-old projects have xml folder structures for Notepad++.
-
-\begin{itemize}
-\tightlist
-\item
-  Silently update file changes made in other editors: Settings,
-  Preferences, MISC., File Status Auto Detection, Update Silently.
-\end{itemize}
-
-\hypertarget{sublime}{%
-\subsubsection{Sublime}\label{sublime}}
-
-\href{https://www.sublimetext.com/3}{Sublime}
-
-there are some issues with atom. When a file is edited inside Vim, when
-changes are saved, a
-\href{https://github.com/atom/atom/issues/17186}{temp file is created in
-atom}. Sublime would, however, still show the file with the changes.
-This makes dual screen editing very difficult. Sublime text is used for
-this situation.
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\CommentTok{# Sublime Linux}
-\FunctionTok{wget}\NormalTok{ -qO - https://download.sublimetext.com/sublimehq-pub.gpg }\KeywordTok{|} \FunctionTok{sudo}\NormalTok{ apt-key add -}
-\FunctionTok{sudo}\NormalTok{ apt-get install apt-transport-https}
-\BuiltInTok{echo} \StringTok{"deb https://download.sublimetext.com/ apt/stable/"} \KeywordTok{|} \FunctionTok{sudo}\NormalTok{ tee /etc/apt/sources.list.d/sublime-text.list}
-\FunctionTok{sudo}\NormalTok{ apt-get update}
-\FunctionTok{sudo}\NormalTok{ apt-get install sublime-text}
-\CommentTok{# launch from terminal}
-\ExtensionTok{subl}
-\end{Highlighting}
-\end{Shaded}
-
-\emph{Sublime Setup}:
-
-\begin{itemize}
-\tightlist
-\item
-  \href{https://weibeld.net/r/rmd_sublime_package.html}{r and rmd setup}
-\end{itemize}
-
-\hypertarget{pycharm}{%
-\subsubsection{PyCharm}\label{pycharm}}
-
-\href{https://www.}{pycharm}jetbrains.com/pycharm/)
-
-\hypertarget{key-programs}{%
-\subsection{Key Programs}\label{key-programs}}
-
-\textbf{PDF}
-
-\begin{itemize}
-\tightlist
-\item
-  PDF Okular
-
-  \begin{itemize}
-  \tightlist
-  \item
-    Linux: \emph{sudo apt-get install okular}
-  \item
-    Windows: install okular from windows app store
-  \item
-    Okular if menu bar lost: \emph{Ctrl + m}
-  \end{itemize}
-\item
-  PDF Adobe Acrobat
-
-  \begin{itemize}
-  \tightlist
-  \item
-    go to adobe website, log in using
-    \href{mailto:fwang26@uh.edu}{\nolinkurl{fwang26@uh.edu}}
-  \item
-    go to my account, choose view and download my apps, choose acrobat
-    \& PDF, download Acrobat DC
-  \item
-    UH account can only be activated on two accounts at once, so need to
-    kick other computers out temporarily potentially
-  \end{itemize}
-\end{itemize}
-
-\textbf{VPN}
-
-\begin{itemize}
-\tightlist
+\hypertarget{utilities}{%
+\subsection{Utilities}\label{utilities}}
+
+\begin{itemize}
+\tightlist
+\item
+  7-zip
+\item
+  evernote
+\end{itemize}
+
+\hypertarget{security}{%
+\subsection{Security}\label{security}}
+
+\begin{itemize}
+\tightlist
+\item
+  keepass
 \item
@@
 
-\hypertarget{utilities}{%
-\subsection{Utilities}\label{utilities}}
-
-\begin{itemize}
-\tightlist
-\item
-  7-zip
-\item
-  evernote
-\item
-  keepass
-\end{itemize}
-
 \end{document}

### 2020-01-03 nontex/install/git/fs_git_setup.tex
set up compile minor update

--- 2019-12-23 nontex/install/windows/fn_installations.tex
@@
-% Options for packages loaded elsewhere
-\PassOptionsToPackage{unicode}{hyperref}
+\PassOptionsToPackage{unicode=true}{hyperref} % options for packages loaded elsewhere
 \PassOptionsToPackage{hyphens}{url}
@@
 %
-\documentclass[
-]{article}
+\documentclass[]{article}
 \usepackage{lmodern}
@@
   \usepackage[utf8]{inputenc}
-  \usepackage{textcomp} % provide euro and other symbols
-\else % if luatex or xetex
+  \usepackage{textcomp} % provides euro and other symbols
+\else % if luatex or xelatex
   \usepackage{unicode-math}
-  \defaultfontfeatures{Scale=MatchLowercase}
-  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
+  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
 \fi
-% Use upquote if available, for straight quotes in verbatim environments
+% use upquote if available, for straight quotes in verbatim environments
 \IfFileExists{upquote.sty}{\usepackage{upquote}}{}
-\IfFileExists{microtype.sty}{% use microtype if available
+% use microtype if available
+\IfFileExists{microtype.sty}{%
 \usepackage[]{microtype}
@@
 }{}
-\makeatletter
-\@ifundefined{KOMAClassName}{% if non-KOMA class
 \IfFileExists{parskip.sty}{%
@@
 \setlength{\parindent}{0pt}
-    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
-}{% if KOMA class
-  \KOMAoptions{parskip=half}}
-\makeatother
+\setlength{\parskip}{6pt plus 2pt minus 1pt}
+}
 \usepackage{xcolor}
-\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
-\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
+\usepackage{hyperref}
 \hypersetup{
-  pdftitle={New Windows Computer Data-Science Set-up: Python (anaconda, pycharm), R (r-studio) and other Programs Installations},
+            pdftitle={Git and Github Example and Tutorial, Sync with Multiple Repositories, Store Password},
             colorlinks=true,
             linkcolor=Maroon,
-  filecolor=Maroon,
             citecolor=Blue,
             urlcolor=blue,
-  pdfcreator={LaTeX via pandoc}}
-\urlstyle{same} % disable monospaced font for URLs
+            breaklinks=true}
+\urlstyle{same}  % don't use monospace font for urls
 \usepackage[margin=1in]{geometry}
@@
 \setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
-% Set default figure placement to htbp
-\makeatletter
-\def\fps@figure{htbp}
-\makeatother
 \setlength{\emergencystretch}{3em}  % prevent overfull lines
@@
 \setcounter{secnumdepth}{5}
+% Redefines (sub)paragraphs to behave more like sections
+\ifx\paragraph\undefined\else
+\let\oldparagraph\paragraph
+\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
+\fi
+\ifx\subparagraph\undefined\else
+\let\oldsubparagraph\subparagraph
+\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
+\fi
 
-\title{New Windows Computer Data-Science Set-up: Python (anaconda, pycharm), R
-(r-studio) and other Programs Installations}
+% set default figure placement to htbp
+\makeatletter
+\def\fps@figure{htbp}
+\makeatother
+
+\title{Git and Github Example and Tutorial, Sync with Multiple Repositories,
+Store Password}
 \author{}
@@
 
-\hypertarget{conda}{%
-\section{Conda}\label{conda}}
-
-Use conda across platforms, so that locally on windows and ubuntu and
-remotely on aws, can have the same software setup environment.
-
-Search for Anaconda Prompt, right click, choose run as administrator.
-
-Check software versions.
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\ExtensionTok{conda}\NormalTok{ list anaconda}
-\ExtensionTok{python}\NormalTok{ -V}
-\end{Highlighting}
-\end{Shaded}
-
-\hypertarget{first-time-conda-install}{%
-\subsection{First Time Conda Install}\label{first-time-conda-install}}
-
-Download and install for all users. Afterwards, Anaconda does not
-automatically get added to Windows Path. Need to use Anaconda Prompt to
-access programs. To access Anaconda packages from windows prompt, from
-git bash, from R, etc, need to Add Anaconda to Windows Path
-
-See Anaconda Installation Directory, in anaconda prompt:
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\ExtensionTok{where}\NormalTok{ anaconda}
-\CommentTok{# C:/ProgramData/Anaconda3/Scripts/anaconda.exe}
-\ExtensionTok{where}\NormalTok{ python}
-\CommentTok{# C:/ProgramData/Anaconda3/python.exe}
-\ExtensionTok{where}\NormalTok{ jupyter}
-\CommentTok{# C:/ProgramData/Anaconda3/Scripts/jupyter.exe}
-\ExtensionTok{where}\NormalTok{ jupyter-kernelspec}
-\CommentTok{# if R installed already}
-\ExtensionTok{where}\NormalTok{ r}
-
-\CommentTok{###############################}
-\CommentTok{# Add these to Windows PATH:}
-\CommentTok{###############################}
-\CommentTok{# C:/ProgramData/Anaconda3/Scripts}
-\CommentTok{# C:/ProgramData/Anaconda3}
-\end{Highlighting}
-\end{Shaded}
-
-To Add Anaconda to Path, In Windows 1. search for: Environment Variables
-2. Edit Environment Variables 3. Add new to Path (lower half): -
-C:/ProgramData/Anaconda3/Scripts/ - C:/ProgramData/Anaconda3/ 4. Now
-open up regular windows command Prompt, Type in: - conda --version -
-also Close and Open up Git Bash: conda --version
-
-\hypertarget{conda-update}{%
-\subsection{Conda Update}\label{conda-update}}
-
-Open up Anaconda Navigator, it will update navigator automatically. If
-there are errors, might have to clean first.
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\CommentTok{# # if there are bugs}
-\CommentTok{# conda clean --packages}
-\CommentTok{# use conda-forge as main channel, more updated packages}
-\ExtensionTok{conda}\NormalTok{ config --add channels conda-forge}
-\CommentTok{# normal update}
-\ExtensionTok{conda}\NormalTok{ update --all}
-\end{Highlighting}
-\end{Shaded}
-
-\hypertarget{conda-test-python}{%
-\subsection{Conda Test Python}\label{conda-test-python}}
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\CommentTok{# windows}
-\NormalTok{python }\StringTok{"C:/Users/fan/PyFan/ProjectSupport/Testing/Numpy/Functions.py"}
-\NormalTok{python }\StringTok{"C:/Users/fan/PyFan/ProjectSupport/graph/subplot.py"}
-\CommentTok{# linux}
-\NormalTok{python }\OperatorTok{~}\ErrorTok{/}\NormalTok{PyFan}\OperatorTok{/}\NormalTok{ProjectSupport}\OperatorTok{/}\NormalTok{Testing}\OperatorTok{/}\NormalTok{Numpy}\OperatorTok{/}\NormalTok{Functions.py}
-\NormalTok{python }\OperatorTok{~}\ErrorTok{/}\NormalTok{PyFan}\OperatorTok{/}\NormalTok{ProjectSupport}\OperatorTok{/}\NormalTok{graph}\OperatorTok{/}\NormalTok{subplot.py}
-\end{Highlighting}
-\end{Shaded}
-
-\hypertarget{additional-packages}{%
-\subsection{Additional Packages}\label{additional-packages}}
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\NormalTok{conda install statsmodels datashape seaborn}
-\CommentTok{# conda install statsmodels}
-\CommentTok{# conda install datashape}
-\CommentTok{# conda install seaborn}
-
-\NormalTok{conda install }\OperatorTok{-}\NormalTok{c conda}\OperatorTok{-}\NormalTok{forge interpolation awscli}
-\CommentTok{# conda install -c conda-forge interpolation}
-\CommentTok{# conda install -c conda-forge awscli}
-
-\NormalTok{conda install }\OperatorTok{-}\NormalTok{c anaconda boto3}
-
-\NormalTok{conda install }\OperatorTok{-}\NormalTok{c r r}\OperatorTok{-}\NormalTok{irkernel}
-\end{Highlighting}
-\end{Shaded}
-
-\hypertarget{r-installation}{%
-\section{R Installation}\label{r-installation}}
-
-Try to install R from within Conda. The procedure here is the same for
-windows as well as linux machines.
-
-\hypertarget{fully-uninstall-r}{%
-\subsection{Fully uninstall r}\label{fully-uninstall-r}}
-
-open up RStudio, and see where paths are. also open up R from command
-prompt, see where paths are.
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\KeywordTok{.libPath}\NormalTok{()}
-\end{Highlighting}
-\end{Shaded}
-
-Open up install and uninstall programs, find R and Rstudio, and
-uninstall them. Then delete all files found path paths shown by
-\emph{.libPath()}, looking at these: -
-\emph{C:/Users/fan/Documents/R/win-library/3.6} - \emph{C:/Program
-Files/R/R-3.6.1/library}
-
-\hypertarget{install-r-outside-of-conda}{%
-\subsection{Install R (outside of
-Conda)}\label{install-r-outside-of-conda}}
+\hypertarget{download-programs}{%
+\section{Download Programs}\label{download-programs}}
 
@@
 \item
-  \href{https://cloud.r-project.org/}{download R}
+  Install \href{https://git-scm.com/download/win}{git for windows}:
+  after install, try ``cd \textasciitilde{}/PyFan''
 \item
-  \href{https://rstudio.com/products/rstudio/download/}{download
-  R-studio}
+  Install \href{https://atom.io/}{atom}
 \item
-  Open R-studio and auto-detect R
-\item
-  Install packages
+  Might need to install \href{https://www.putty.org/}{putty} possibly
 \end{enumerate}
 
-note that installation will not work if the machine's version of R is
-not up to date, this could be the case with default R versions for some
-linux installations.
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\CommentTok{# Install R-tools}
-\KeywordTok{install.packages}\NormalTok{(}\StringTok{"installr"}\NormalTok{)}
-\KeywordTok{library}\NormalTok{(}\StringTok{"installr"}\NormalTok{)}
-\KeywordTok{install.Rtools}\NormalTok{()}
-\CommentTok{# c:\textbackslash{}Rtools\textbackslash{}bin;}
-\CommentTok{# c:\textbackslash{}Rtools\textbackslash{}mingw_32\textbackslash{}bin;}
-\CommentTok{# c:\textbackslash{}Rtools\textbackslash{}mingw_64\textbackslash{}bin;}
-
-\CommentTok{# main packagevps}
-\KeywordTok{install.packages}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\StringTok{"tidyr"}\NormalTok{, }\StringTok{"tidyverse"}\NormalTok{, }\StringTok{"tidymodels"}\NormalTok{))}
-\CommentTok{# development packages}
-\KeywordTok{install.packages}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\StringTok{"devtools"}\NormalTok{, }\StringTok{"irkernel"}\NormalTok{, }\StringTok{"pkgdown"}\NormalTok{, }\StringTok{"roxygen2"}\NormalTok{))}
-\CommentTok{# other packages}
-\KeywordTok{install.packages}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\StringTok{"AER"}\NormalTok{, }\StringTok{"minpack.lm"}\NormalTok{, }\StringTok{"knitr"}\NormalTok{, }\StringTok{"kableExtra"}\NormalTok{, }\StringTok{"matlab"}\NormalTok{))}
-
-\CommentTok{# Install my package}
-\NormalTok{devtools}\OperatorTok{::}\KeywordTok{install_github}\NormalTok{(}\StringTok{"fanwangecon/R4Econ"}\NormalTok{)}
-\end{Highlighting}
-\end{Shaded}
-
-\hypertarget{set-up-r-environment-in-conda}{%
-\subsection{Set up R-Environment in
-Conda}\label{set-up-r-environment-in-conda}}
-
-Conda environments are language agnostic. pip is a package manager for
-Python. venv is an environment manager for Python. conda is both a
-package and environment manager and is language agnostic. Inside
-Anaconda Prompt:
-
-Key packages are generally available in conda's default channel
-(official distribution) and also the more frequently updated conda-forge
-channel. Prioritize conda-forge to get the latest packages. after adding
-\emph{conda-forge} to channels, that will be prioritized, so when
-creating a new environment, conda will install first from conda-forge if
-package exists there. Try the \emph{r\_env} generation line with and
-without first adding \emph{conda-forge} to channel, and see that the
-packages installed will have different versions, reflecting versions in
-the default channel and in the \emph{conda-forge} channels.
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\CommentTok{# Set up Channel}
-\ExtensionTok{conda}\NormalTok{ config --add channels conda-forge}
-\CommentTok{# install key r packages within a r-environment}
-\ExtensionTok{conda}\NormalTok{ env remove -n r_env}
-\ExtensionTok{conda}\NormalTok{ create -n r_env r-essentials r-base r-tidyr r-tidyverse r-devtools r-irkernel r-pkgdown r-roxygen2}
-\CommentTok{# see all installed environments}
-\ExtensionTok{conda}\NormalTok{ env list}
-\CommentTok{# activate an environment to use it, if in base, r does not exist, isolated in r_env}
-\ExtensionTok{conda}\NormalTok{ activate r_env}
-\CommentTok{# see packages in environment}
-\ExtensionTok{conda}\NormalTok{ list}
-\CommentTok{# to quit}
-\ExtensionTok{conda}\NormalTok{ deactivate}
-\end{Highlighting}
-\end{Shaded}
-
-\begin{itemize}
-\tightlist
-\item
-  \textbf{Location}: Installed environments are shown appear in the
-  \emph{envs} folder of \emph{C:/ProgramData/Anaconda3/envs/}. Can be
-  easily deleted without disrupting the main base installation for
-  conda. This is very important. During installation, could easily run
-  into problems, and need to re-install. Much better to only re-install
-  a folder. Note that when R is installed in \emph{envs}, it will not
-  show up under add or remove programs for uninstallation from there,
-  has to be uninstalled, deleted directly here.
-\item
-  \textbf{Use only in Env}: Note that if we installed r inside r\_env,
-  if we type \emph{r} under the base environment, we can not enter r. We
-  can only enter r within r\_env. With PATH properly set-up, this
-  happens under Conda Prompt, Windows Prompt, etc.
-\item
-  \textbf{Multiple Pythons}: With the above installation for R, one
-  benefit is that if R requires a different version of Python than what
-  the base environment uses, the r\_env could have a different python
-  version. So type \emph{python} in the base environment as well as
-  inside the \emph{r\_env}. This also means potentially there could be
-  duplicated installations I think. Look at the python versions under
-  \emph{conda list} in the base and in the r-environment.
-\item
-  \textbf{File Size}: Note that this creates a large installation
-  folder, \emph{C:/ProgramData/Anaconda3/envs/r\_env/}, without
-  additional packages, is 1.3 GB in size
-\end{itemize}
-
-\hypertarget{install-additional-packages-inside-the-r-environment}{%
-\subsection{Install Additional Packages inside the
-R-environment}\label{install-additional-packages-inside-the-r-environment}}
-
-These are packages that I use, these should be installed inside the
-environment. Or they could be installed later from inside r-studio.
-Installing inside r-studio is a lot better.
-
-This did not work in windows, \emph{tidymodels} failed to install.
-Perhaps because of directory issues. \emph{tidymodels} required
-\emph{rstanarm}, and \emph{rstanarm} failed to install.
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\CommentTok{### One line}
-\ExtensionTok{conda}\NormalTok{ install -c conda-forge r-aer r-minpack.lm r-knitr r-kableExtra r-matlab}
-\CommentTok{# conda install -c conda-forge r-rstanarm}
-
-\CommentTok{#######################################}
-\CommentTok{### Estimation}
-\CommentTok{#######################################}
-\CommentTok{# Estimation Tools}
-\CommentTok{# tidymodels does not work fron conda install}
-\CommentTok{# Linear Regression Package}
-\CommentTok{# https://anaconda.org/conda-forge/r-aer}
-\CommentTok{# Nonlinear Regression Package}
-\CommentTok{# https://anaconda.org/conda-forge/r-minpack.lm}
-\ExtensionTok{conda}\NormalTok{ install -c conda-forge r-aer r-minpack.lm}
-\CommentTok{# enter r and use devtools}
-\CommentTok{# install.packages("tidymodels")}
-
-\CommentTok{#######################################}
-\CommentTok{### Visualiation}
-\CommentTok{#######################################}
-\ExtensionTok{conda}\NormalTok{ install -c conda-forge r-knitr r-kableExtra}
-
-\CommentTok{#######################################}
-\CommentTok{### Utilities}
-\CommentTok{#######################################}
-\CommentTok{# Allowing for Invoking Matlab Files from Inside R}
-\ExtensionTok{conda}\NormalTok{ install -c conda-forge r-matlab}
-\end{Highlighting}
-\end{Shaded}
-
-Install additional packages from inside R. The devtools install will
-install packages inside \emph{envs/r\_env/Lib/R}.
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\CommentTok{#######################################}
-\CommentTok{### Own Package}
-\CommentTok{#######################################}
-\NormalTok{devtools}\OperatorTok{::}\KeywordTok{install_github}\NormalTok{(}\StringTok{"fanwangecon/R4Econ"}\NormalTok{)}
-\CommentTok{# install_dev("cli")}
-\end{Highlighting}
-\end{Shaded}
-
-\hypertarget{r-studio-set-up-download-from-rstudio}{%
-\subsection{R-Studio Set-up Download from
-Rstudio}\label{r-studio-set-up-download-from-rstudio}}
+\hypertarget{git-and-github-security-set-up}{%
+\section{git and Github Security
+Set-up}\label{git-and-github-security-set-up}}
 
@@
 \item
-  Download R-studio, and install, as normal (not from conda, directly
-  from rstudio website latest windows version)
+  open up git bash
 \item
-  Open up anaconda prompt, enter \emph{r\_env} environment:
-  \emph{activate r\_env}
-\item
-  cd into rstudio exe file folder: cd ``C:/Program Files/RStudio/bin''
-\item
-  start r-studio from inside \emph{r\_env}: rstudio.exe
-\item
-  inside r-studio, check: \emph{.libPaths()}
+  generate rsa
 
@@
   \item
-    ``C:/ProgramData/Anaconda3/envs/r\_env/Lib/R/library''
+    \emph{ssh-keygen -t rsa -C
+    ``\href{mailto:wangfanbsg75@live.com}{\nolinkurl{wangfanbsg75@live.com}}''}
+  \item
+    when prompted, do not enter ``file in which save the key'', when
+    prompted for passphrase, enter ``WHATEVERPASSWORDIS''
+  \end{itemize}
+\item
+  copy key
+
+  \begin{itemize}
+  \tightlist
+  \item
+    WINDOWS: \emph{clip \textless{} \textasciitilde{}/.ssh/id\_rsa.pub}
+  \item
+    LINUX: \emph{cat \textasciitilde{}/.ssh/id\_rsa.pub}
+  \end{itemize}
+\item
+  log on to github ssh section, generate new ssh rsa key
+
+  \begin{itemize}
+  \tightlist
+  \item
+    SSH and GPG keys, choose New SSH key, paste in clipped text.
   \end{itemize}
@@
 \begin{Highlighting}[]
-\ExtensionTok{activate}\NormalTok{ r_env}
-\BuiltInTok{cd} \StringTok{"C:/Program Files/RStudio/bin"}
-\ExtensionTok{rstudio.exe}
-
-\BuiltInTok{cd} \StringTok{"C:/ProgramData/Anaconda3/envs/r_env/Lib/R/library"}
-\StringTok{"C:/Program Files/RStudio/bin/rstudio.exe"}
+\CommentTok{# inside git bash}
+\FunctionTok{ssh-keygen}\NormalTok{ -t rsa -C }\StringTok{"wangfanbsg75@live.com"}
+\CommentTok{# this copies the text in the .pub file generated}
+\ExtensionTok{clip} \OperatorTok{<}\NormalTok{ ~/.ssh/id_rsa.pub}
 \end{Highlighting}
@@
 
-For linux, note that rstudio offers Ubuntu as well as Debian versions
-that can be installed with wget:
+\hypertarget{start-and-sync-key-repositories}{%
+\section{Start and Sync Key
+Repositories}\label{start-and-sync-key-repositories}}
 
-\begin{Shaded}
-\begin{Highlighting}[]
-\OperatorTok{<}\NormalTok{!}\ExtensionTok{--}\NormalTok{ for ubuntu --}\OperatorTok{>}
-\FunctionTok{wget} \StringTok{"https://download1.rstudio.org/desktop/bionic/amd64/rstudio-1.2.5033-amd64.deb"}
-\FunctionTok{sudo}\NormalTok{ apt install ./rstudio-1.2.5033-amd64.deb}
-\OperatorTok{<}\NormalTok{!}\ExtensionTok{--}\NormalTok{ for debian --}\OperatorTok{>}
-\FunctionTok{wget} \StringTok{"https://download1.rstudio.org/desktop/debian9/x86_64/rstudio-1.2.5033-amd64.deb"}
-\FunctionTok{sudo}\NormalTok{ apt install ./rstudio-1.2.5033-amd64.deb}
-\ExtensionTok{conda}\NormalTok{ install -c r rstudio}
-\BuiltInTok{cd} \StringTok{"C:/Program Files/RStudio/bin"}
-\ExtensionTok{rstudio.exe}
-
-\BuiltInTok{cd} \StringTok{"C:/ProgramData/Anaconda3/envs/r_env/Lib/R/library"}
-\StringTok{"C:/Program Files/RStudio/bin/rstudio.exe"}
-\end{Highlighting}
-\end{Shaded}
-
-\hypertarget{install-packages-from-r-studio}{%
-\subsection{Install Packages from
-R-Studio}\label{install-packages-from-r-studio}}
-
-Install addition files inside Rstudio. Easier to debug potentially.
-Install rtools as described
-\href{https://thecoatlessprofessor.com/programming/cpp/installing-rtools-for-compiled-code-via-rcpp/}{here}:
-\href{https://cran.r-project.org/bin/windows/Rtools/}{rtools download}.
-Alternatively:
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\KeywordTok{install.packages}\NormalTok{(}\StringTok{"installr"}\NormalTok{)}
-\KeywordTok{library}\NormalTok{(}\StringTok{"installr"}\NormalTok{)}
-\CommentTok{# Note that this will generate several pop-up windows}
-\KeywordTok{install.Rtools}\NormalTok{()}
-\CommentTok{# choose to only install 64 bit toolchain}
-\CommentTok{# this installs g++ which is needed for rstanarm}
-\CommentTok{# Add these below to windows path}
-\CommentTok{# c:/Rtools/bin;}
-\CommentTok{# c:/Rtools/mingw_64/bin;}
-
-\ControlFlowTok{if}\NormalTok{ (}\OperatorTok{!}\KeywordTok{require}\NormalTok{(devtools)) \{}
-  \KeywordTok{install.packages}\NormalTok{(}\StringTok{"devtools"}\NormalTok{)}
-  \KeywordTok{library}\NormalTok{(devtools)}
-\NormalTok{\}}
-\KeywordTok{library}\NormalTok{(devtools)}
-\KeywordTok{install_github}\NormalTok{(}\StringTok{"stan-dev/rstanarm"}\NormalTok{, }\DataTypeTok{args =} \StringTok{"--preclean"}\NormalTok{)}
-
-\KeywordTok{setwd}\NormalTok{(}\StringTok{'C:/ProgramData/Anaconda3/envs/r_env/Lib/R/library'}\NormalTok{)}
-
-\KeywordTok{install.packages}\NormalTok{(}\StringTok{"stan-dev/rstanarm"}\NormalTok{, }\DataTypeTok{dependencies=}\OtherTok{TRUE}\NormalTok{, }\DataTypeTok{INSTALL_opts =} \KeywordTok{c}\NormalTok{(}\StringTok{'--no-lock'}\NormalTok{))}
-
-\CommentTok{# other packages}
-\KeywordTok{install.packages}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\StringTok{"tidymodels"}\NormalTok{, }\StringTok{"AER"}\NormalTok{, }\StringTok{"minpack.lm"}\NormalTok{, }\StringTok{"knitr"}\NormalTok{, }\StringTok{"kableExtra"}\NormalTok{, }\StringTok{"matlab"}\NormalTok{))}
-
-\CommentTok{# Install my package}
-\NormalTok{devtools}\OperatorTok{::}\KeywordTok{install_github}\NormalTok{(}\StringTok{"fanwangecon/R4Econ"}\NormalTok{)}
-\end{Highlighting}
-\end{Shaded}
-
-\hypertarget{test-files}{%
-\subsubsection{Test Files}\label{test-files}}
-
-Test the following file to see if we can execute a R file. Do it inside
-\emph{r\_env} and inside a \emph{r} session.
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\CommentTok{# A simple file with summary statistics using tidyverse}
-\KeywordTok{source}\NormalTok{(}\StringTok{'C:/Users/fan/R4Econ/summarize/dist/fst_hist_onevar.R'}\NormalTok{)}
-\CommentTok{# Another simple file with summary statistics using tidyverse}
-\KeywordTok{source}\NormalTok{(}\StringTok{'C:/Users/fan/R4Econ/support/tibble/fs_tib_basics.R'}\NormalTok{)}
-\CommentTok{# A file involving estimation}
-\KeywordTok{source}\NormalTok{(}\StringTok{'C:/Users/fan/R4Econ/optimization/cesloglin/fst_ces_plan_linlog.R'}\NormalTok{)}
-
-\CommentTok{# C:\textbackslash{}Users\textbackslash{}fan\textbackslash{}R4Econ\textbackslash{}summarize\textbackslash{}dist\textbackslash{}fst_hist_onevar.Rmd}
-\CommentTok{# C:\textbackslash{}Users\textbackslash{}fan\textbackslash{}R4Econ\textbackslash{}support\textbackslash{}tibble\textbackslash{}fs_tib_basics.Rmd}
-\CommentTok{# C:\textbackslash{}Users\textbackslash{}fan\textbackslash{}R4Econ\textbackslash{}optimization\textbackslash{}cesloglin\textbackslash{}fst_ces_plan_linlog.Rmd}
-\end{Highlighting}
-\end{Shaded}
-
-\hypertarget{install-latex}{%
-\section{Install Latex}\label{install-latex}}
-
-Use a combination of overleaf and local compile. The goal is to have the
-same installation set-up for windows as well as linux. And hopefully,
-locally compilable file also can be compiled on overleaf (only use
-packages also available on overleaf).
-
-There are several pieces of things to install:
+Inside git bash (open as \emph{administrator}), Sync Several Key
+Repositories that should be synced on all computers:
 
@@
 \item
-  latex compiler: pdflatex, etc
+  fanwangecon.github.io: Github root repo
 \item
-  tex distributions: MikTex, texlive
-
-  \begin{itemize}
-  \tightlist
+  PyFan: Private Repo with Python Support Files
 \item
-    these folders, once various packages are installed, could be very
-    large, many GB
-  \end{itemize}
+  \href{https://github.com/FanWangEcon/Tex4Econ}{Tex4Econ}: Latex,
+  installation, and various other support files, public repo.
 \item
-  latex packages from distributions
+  \href{https://github.com/FanWangEcon/R4Econ}{R4Econ}: Public repo, R
+  package, R research programs
 \item
-  editor (gui): Atom, texStudio, etc
+  \href{https://github.com/FanWangEcon/M4Econ}{M4Econ}: Public repo,
+  Matlab package, Matlab examples and research files
+\item
+  \href{https://github.com/FanWangEcon/Py4Econ}{Py4Econ}: Public repo,
+  Python package, Python research programs
+\item
+  Teaching: Private teaching repository
 \end{enumerate}
 
-\hypertarget{uninstall}{%
-\subsection{Uninstall}\label{uninstall}}
+Other repositories can be synced when needed on an ad-hoc basis. The
+repositories above are essential repositories.
 
-\begin{itemize}
-\tightlist
-\item
-  uninstall \emph{MiKTeX}: delete from programs, then delete remaining
-  folder in Program Files.
-\item
-  uninstall \emph{texlive}: go to \emph{c:/texlive}, delete the folder
-\end{itemize}
+\hypertarget{repo-folders-and-global-config}{%
+\subsection{Repo Folders and Global
+config}\label{repo-folders-and-global-config}}
 
-\hypertarget{install}{%
-\subsection{Install}\label{install}}
-
-\emph{Install on Windows}
-
-\begin{itemize}
-\tightlist
-\item
-  \href{https://www.texstudio.org/}{Install Texstudio}
-\item
-  \href{https://www.tug.org/texlive/acquire-netinstall.html}{Install
-  texlive}
-\end{itemize}
-
-\emph{Install on Ubuntu}
-
-install texlive and texstudio ubuntu/debian.
+Remember git bash or bash should be in windows opened as
+\emph{administrator}.
 
@@
 \begin{Highlighting}[]
-\FunctionTok{sudo}\NormalTok{ apt-get update}
-\FunctionTok{sudo}\NormalTok{ apt-get install texlive-full}
-\FunctionTok{sudo}\NormalTok{ apt-get install texstudio}
+\CommentTok{# cd to root folder}
+\BuiltInTok{cd}\NormalTok{ ~}
+\CommentTok{# generate all needed key repositories}
+\FunctionTok{mkdir}\NormalTok{ fanwangecon.github.io PyFan Tex4Econ R4Econ M4Econ Py4Econ Teaching}
+
+\CommentTok{# Set global config settings, in ~/.gitconfig}
+\FunctionTok{git}\NormalTok{ config --global user.name }\StringTok{"Fan Wang"}
+\FunctionTok{git}\NormalTok{ config --global user.email wangfanbsg75@live.com}
 \end{Highlighting}
@@
 
-\hypertarget{compile-in-atom}{%
-\subsection{Compile in Atom}\label{compile-in-atom}}
-
-Install the \href{https://github.com/thomasjo/atom-latex}{latex} package
-on atom.
+\hypertarget{initalize-and-add-remote-repo-for-each}{%
+\subsection{Initalize and add remote repo for
+each:}\label{initalize-and-add-remote-repo-for-each}}
 
@@
 \begin{Highlighting}[]
-\CommentTok{# set TeX path}
-\CommentTok{# C:\textbackslash{}texlive\textbackslash{}2019\textbackslash{}bin\textbackslash{}win32}
+\CommentTok{# Initialize Repositories}
+\BuiltInTok{cd}\NormalTok{ ~/fanwangecon.github.io}
+\FunctionTok{git}\NormalTok{ init}
+\FunctionTok{git}\NormalTok{ remote add github git@github.com:fanwangecon/fanwangecon.github.io.git}
+\BuiltInTok{cd}\NormalTok{ ~/PyFan}
+\FunctionTok{git}\NormalTok{ init}
+\FunctionTok{git}\NormalTok{ remote add github git@github.com:fanwangecon/PyFan}
+\BuiltInTok{cd}\NormalTok{ ~/Tex4Econ}
+\FunctionTok{git}\NormalTok{ init}
+\FunctionTok{git}\NormalTok{ remote add github git@github.com:fanwangecon/Tex4Econ}
+\BuiltInTok{cd}\NormalTok{ ~/R4Econ}
+\FunctionTok{git}\NormalTok{ init}
+\FunctionTok{git}\NormalTok{ remote add github git@github.com:fanwangecon/R4Econ}
+\BuiltInTok{cd}\NormalTok{ ~/M4Econ}
+\FunctionTok{git}\NormalTok{ init}
+\FunctionTok{git}\NormalTok{ remote add github git@github.com:fanwangecon/M4Econ}
+\BuiltInTok{cd}\NormalTok{ ~/Py4Econ}
+\FunctionTok{git}\NormalTok{ init}
+\FunctionTok{git}\NormalTok{ remote add github git@github.com:fanwangecon/Py4Econ}
+\BuiltInTok{cd}\NormalTok{ ~/Teaching}
+\FunctionTok{git}\NormalTok{ init}
+\FunctionTok{git}\NormalTok{ remote add github git@github.com:fanwangecon/Teaching}
 \end{Highlighting}
@@
 
-\hypertarget{other-programs-to-install}{%
-\section{Other Programs to Install}\label{other-programs-to-install}}
+\hypertarget{sync-repo-in-ssh-secure-session}{%
+\subsection{Sync Repo in SSH Secure
+Session}\label{sync-repo-in-ssh-secure-session}}
 
-\hypertarget{development-programs}{%
-\subsection{Development Programs}\label{development-programs}}
+Pull latested from multiple repositories. Just Paste the following
+lines.
 
-\begin{itemize}
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi}.}
 \tightlist
 \item
-  \href{https://www.jetbrains.com/pycharm/}{pycharm}
-\end{itemize}
+  start ssh-agent secure session
+\item
+  pull from multiple Repositories upon start of working session.
+\item
+  commit changes as work on one computer
+\item
+  upon leaving a computer with commited changes, push all
+\item
+  create bash file to make it easier to repeat steps
+\end{enumerate}
 
-\hypertarget{key-programs}{%
-\subsection{Key Programs}\label{key-programs}}
+Start and end ssh session:
 
-\begin{itemize}
-\tightlist
-\item
-  Adobe Acrobat
+\begin{Shaded}
+\begin{Highlighting}[]
+\CommentTok{# To avoid having to enter password each time, start background authentication agent.}
+\BuiltInTok{eval} \StringTok{"}\VariableTok{$(}\FunctionTok{ssh-agent}\VariableTok{)}\StringTok{"}
+\FunctionTok{ssh-add}\NormalTok{ ~/.ssh/id_rsa}
 
-  \begin{itemize}
-  \tightlist
-  \item
-    go to adobe website, log in using
-    \href{mailto:fwang26@uh.edu}{\nolinkurl{fwang26@uh.edu}}
-  \item
-    go to my account, choose view and download my apps, choose acrobat
-    \& PDF, download Acrobat DC
-  \item
-    UH account can only be activated on two accounts at once, so need to
-    kick other computers out temporarily potentially
-  \end{itemize}
-\end{itemize}
+\CommentTok{# to stop the ssh session}
+\BuiltInTok{kill} \VariableTok{$SSH_AGENT_PID}
+\end{Highlighting}
+\end{Shaded}
 
-\hypertarget{utilities}{%
-\subsection{Utilities}\label{utilities}}
+Pull from repos:
 
-\begin{itemize}
-\tightlist
-\item
-  7-zip
-\end{itemize}
+\begin{Shaded}
+\begin{Highlighting}[]
+\CommentTok{# Pull from Repositories, do these one by one first}
+\BuiltInTok{cd}\NormalTok{ ~/fanwangecon.github.io}
+\FunctionTok{git}\NormalTok{ pull github master}
+\BuiltInTok{cd}\NormalTok{ ~/PyFan}
+\FunctionTok{git}\NormalTok{ pull github master}
+\BuiltInTok{cd}\NormalTok{ ~/Tex4Econ}
+\FunctionTok{git}\NormalTok{ pull github master}
+\BuiltInTok{cd}\NormalTok{ ~/R4Econ}
+\FunctionTok{git}\NormalTok{ pull github master}
+\BuiltInTok{cd}\NormalTok{ ~/M4Econ}
+\FunctionTok{git}\NormalTok{ pull github master}
+\BuiltInTok{cd}\NormalTok{ ~/Py4Econ}
+\FunctionTok{git}\NormalTok{ pull github master}
+\BuiltInTok{cd}\NormalTok{ ~/Teaching}
+\FunctionTok{git}\NormalTok{ pull github master}
+\end{Highlighting}
+\end{Shaded}
+
+Push from repos committed changes
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\CommentTok{# Push to Repositories, do these one by one first}
+\BuiltInTok{cd}\NormalTok{ ~/fanwangecon.github.io}
+\FunctionTok{git}\NormalTok{ push -u github master}
+\BuiltInTok{cd}\NormalTok{ ~/PyFan}
+\FunctionTok{git}\NormalTok{ push -u github master}
+\BuiltInTok{cd}\NormalTok{ ~/Tex4Econ}
+\FunctionTok{git}\NormalTok{ push -u github master}
+\BuiltInTok{cd}\NormalTok{ ~/R4Econ}
+\FunctionTok{git}\NormalTok{ push -u github master}
+\BuiltInTok{cd}\NormalTok{ ~/M4Econ}
+\FunctionTok{git}\NormalTok{ push -u github master}
+\BuiltInTok{cd}\NormalTok{ ~/Py4Econ}
+\FunctionTok{git}\NormalTok{ push -u github master}
+\BuiltInTok{cd}\NormalTok{ ~/Teaching}
+\FunctionTok{git}\NormalTok{ push -u github master}
+\end{Highlighting}
+\end{Shaded}
+
+to create bash file to store these (from git bash in windows):
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\CommentTok{# store bash file in ~\textbackslash{}PyFan\textbackslash{}bin}
+\FunctionTok{mkdir}\NormalTok{ ~/PyFan/bin}
+\BuiltInTok{cd}\NormalTok{ ~/PyFan/bin}
+
+\CommentTok{# create bash file}
+\ExtensionTok{vim}\NormalTok{ pull_repos}
+\ExtensionTok{vim}\NormalTok{ push_repos}
+
+\CommentTok{# paste the text below over, comfirm bash loc with: which bash}
+\CommentTok{#!/usr/bin/bash}
+\BuiltInTok{echo}\NormalTok{ start fan github pull}
+\CommentTok{# Security}
+\BuiltInTok{eval} \StringTok{"}\VariableTok{$(}\FunctionTok{ssh-agent}\VariableTok{)}\StringTok{"}
+\FunctionTok{ssh-add}\NormalTok{ ~/.ssh/id_rsa}
+\CommentTok{# Pull from Persistent Repos}
+\BuiltInTok{cd}\NormalTok{ ~/fanwangecon.github.io}
+\FunctionTok{git}\NormalTok{ pull github master}
+\CommentTok{# Stop Secured SSH}
+\BuiltInTok{kill} \VariableTok{$SSH_AGENT_PID}
+
+\CommentTok{# change permission to make file an executable}
+\FunctionTok{chmod}\NormalTok{ u+x ~/PyFan/bin/pull_repos}
+\FunctionTok{chmod}\NormalTok{ u+x ~/PyFan/bin/push_repos}
+\CommentTok{# execute script}
+\FunctionTok{bash}\NormalTok{ ~/PyFan/bin/pull_repos}
+\end{Highlighting}
+\end{Shaded}
 

### 2020-01-03 nontex/install/linux/fn_ubuntu.tex
set up compile minor update

@@
 \setlength{\parindent}{0pt}
-    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
-}{% if KOMA class
-  \KOMAoptions{parskip=half}}
-\makeatother
+\setlength{\parskip}{6pt plus 2pt minus 1pt}
+}
 \usepackage{xcolor}
-\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
-\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
+\usepackage{hyperref}
 \hypersetup{
@@
             linkcolor=Maroon,
-  filecolor=Maroon,
             citecolor=Blue,
             urlcolor=blue,
-  pdfcreator={LaTeX via pandoc}}
-\urlstyle{same} % disable monospaced font for URLs
+            breaklinks=true}
+\urlstyle{same}  % don't use monospace font for urls
 \usepackage[margin=1in]{geometry}
@@
 \setcounter{secnumdepth}{5}
+% Redefines (sub)paragraphs to behave more like sections
+\ifx\paragraph\undefined\else
+\let\oldparagraph\paragraph
+\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
+\fi
+\ifx\subparagraph\undefined\else
+\let\oldsubparagraph\subparagraph
+\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
+\fi
+
+% set default figure placement to htbp
+\makeatletter
+\def\fps@figure{htbp}
+\makeatother
 
@@
 \FunctionTok{sudo}\NormalTok{ apt-get install atom}
+\CommentTok{# install various atom packages that are necessary}
+\FunctionTok{apm}\NormalTok{ install vim-mode-plus}
 \end{Highlighting}
@@
 \item
-  source \textasciitilde/.bashrc
+  source \textasciitilde{}/.bashrc
 \end{enumerate}
@@
 \begin{Highlighting}[]
+\CommentTok{# To remove conda Fully}
+\FunctionTok{rm}\NormalTok{ -rf ~/anaconda3}
+
 \CommentTok{# could be saved in current folder: pwd}
@@
 \BuiltInTok{source}\NormalTok{ ~/.bashrc}
+
 \CommentTok{# show all installed packages under current envir}
@@
 \CommentTok{# use conda-forge as main channel and update all}
-\ExtensionTok{conda}\NormalTok{ config --add channels conda-forge}
+\ExtensionTok{/*}\NormalTok{ conda config --add channels conda-forge */}
 \ExtensionTok{conda}\NormalTok{ update --all}
+\end{Highlighting}
+\end{Shaded}
+
+Additional statistics and related models to install:
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\NormalTok{conda install }\OperatorTok{-}\NormalTok{y statsmodels datashape seaborn}
+\CommentTok{# conda install statsmodels}
+\CommentTok{# conda install datashape}
+\CommentTok{# conda install seaborn}
+
+\NormalTok{conda install }\OperatorTok{-}\NormalTok{c conda}\OperatorTok{-}\NormalTok{forge }\OperatorTok{-}\NormalTok{y interpolation awscli}
+\CommentTok{# conda install -c conda-forge interpolation}
+\CommentTok{# conda install -c conda-forge awscli}
+
+\NormalTok{conda install }\OperatorTok{-}\NormalTok{c anaconda }\OperatorTok{-}\NormalTok{y boto3}
+
+\CommentTok{# conda install -c r r-irkernel}
 \end{Highlighting}
@@
 \begin{Highlighting}[]
-\ExtensionTok{apt-get}\NormalTok{ update}
-\ExtensionTok{apt-get}\NormalTok{ install r-base r-base-dev}
+\CommentTok{# Debian R is maintained by Johannes Ranke, copied from https://cran.r-project.org/bin/linux/debian/:}
+\ExtensionTok{apt-key}\NormalTok{ adv --keyserver keys.gnupg.net --recv-key }\StringTok{'E19F5F87128899B192B1A2C2AD5F960A256A04AF'}
+\CommentTok{# Add to source.list, for debian stretch (9)}
+\CommentTok{# sudo su added for security issue as super-user}
+\FunctionTok{sudo}\NormalTok{ su -c }\StringTok{"sudo echo 'deb http://cloud.r-project.org/bin/linux/debian stretch-cran35/' >> /etc/apt/sources.list"}
+\CommentTok{# if added wrong lines, delete 3rd line}
+\FunctionTok{sudo}\NormalTok{ sed }\StringTok{'3d'}\NormalTok{ /etc/apt/sources.list}
+
+\CommentTok{# Update and Install R, should say updated from cloud.r}
+\FunctionTok{sudo}\NormalTok{ apt-get update}
+\FunctionTok{sudo}\NormalTok{ apt-get install r-base r-base-dev}
 \end{Highlighting}
@@
 
+\hypertarget{install-other-programs-and-packages}{%
+\section{Install Other Programs and
+Packages}\label{install-other-programs-and-packages}}
+
+Other key programs and packages to install.
+
+\begin{itemize}
+\tightlist
+\item
+  vim: faster editor, on lower resource machines, atom is slow and
+  typing could feel laggy.
+\item
+  htop: for resource monitoring
+\end{itemize}
+
+\begin{verbatim}
+sudo apt-get install vim
+sudo apt-get install sublime-text
+sudo apt-get install htop
+\end{verbatim}
+
 \end{document}

### 2020-01-03 nontex/install/linux/fn_vim.tex
set up compile minor update

\PassOptionsToPackage{unicode=true}{hyperref} % options for packages loaded elsewhere
\PassOptionsToPackage{hyphens}{url}
\PassOptionsToPackage{dvipsnames,svgnames*,x11names*}{xcolor}
%
\documentclass[]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provides euro and other symbols
\else % if luatex or xelatex
  \usepackage{unicode-math}
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage[]{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\usepackage{xcolor}
\usepackage{hyperref}
\hypersetup{
            pdftitle={Example and Tutorial for Vim Editor (Linux)},
            colorlinks=true,
            linkcolor=Maroon,
            citecolor=Blue,
            urlcolor=blue,
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage[margin=1in]{geometry}
\usepackage{color}
\usepackage{fancyvrb}
\newcommand{\VerbBar}{|}
\newcommand{\VERB}{\Verb[commandchars=\\\{\}]}
\DefineVerbatimEnvironment{Highlighting}{Verbatim}{commandchars=\\\{\}}
% Add ',fontsize=\small' for more characters per line
\usepackage{framed}
\definecolor{shadecolor}{RGB}{248,248,248}
\newenvironment{Shaded}{\begin{snugshade}}{\end{snugshade}}
\newcommand{\AlertTok}[1]{\textcolor[rgb]{0.94,0.16,0.16}{#1}}
\newcommand{\AnnotationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\AttributeTok}[1]{\textcolor[rgb]{0.77,0.63,0.00}{#1}}
\newcommand{\BaseNTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\BuiltInTok}[1]{#1}
\newcommand{\CharTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\CommentTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
\newcommand{\CommentVarTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\ConstantTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\ControlFlowTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
\newcommand{\DataTypeTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{#1}}
\newcommand{\DecValTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\DocumentationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\ErrorTok}[1]{\textcolor[rgb]{0.64,0.00,0.00}{\textbf{#1}}}
\newcommand{\ExtensionTok}[1]{#1}
\newcommand{\FloatTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\FunctionTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\ImportTok}[1]{#1}
\newcommand{\InformationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\KeywordTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
\newcommand{\NormalTok}[1]{#1}
\newcommand{\OperatorTok}[1]{\textcolor[rgb]{0.81,0.36,0.00}{\textbf{#1}}}
\newcommand{\OtherTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{#1}}
\newcommand{\PreprocessorTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
\newcommand{\RegionMarkerTok}[1]{#1}
\newcommand{\SpecialCharTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\SpecialStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\StringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\VariableTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\VerbatimStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\WarningTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{5}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

% set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother

\title{Example and Tutorial for Vim Editor (Linux)}
\author{}
\date{\vspace{-2.5em}}

\begin{document}
\maketitle

Go back to \href{http://fanwangecon.github.io/}{fan}'s
\href{http://fanwangecon.github.io/Tex4Econ/}{Tex4Econ and Miscellaneous
Repository}.

\hypertarget{vim-installations}{%
\section{Vim Installations}\label{vim-installations}}

Vim ships with Debian. Also install neo-vim:

\begin{Shaded}
\begin{Highlighting}[]
\ExtensionTok{vim}
\FunctionTok{sudo}\NormalTok{ apt-get install neovim}
\end{Highlighting}
\end{Shaded}

Just installing onedark, neovim seems to work better than vim. Vim has
delete lag, and extra white space rows at the bottom of the screen that
could take up very large screen segment. Neovim with onedark does not
have this issue, could be due to some basic setting differences.

\hypertarget{install-vim-plug-plug-ins-manager-for-vim}{%
\subsection{Install Vim-Plug Plug-ins manager for
Vim}\label{install-vim-plug-plug-ins-manager-for-vim}}

Follow the
\href{https://github.com/junegunn/vim-plug/wiki/tutorial}{instructions
here} for installations. Several steps:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  generate \textasciitilde{}/.vim and \textasciitilde{}/.vimrc folders
\item
  curl plug.vim to \textasciitilde{}/.vim/autoload
\item
  update \textasciitilde{}/.vimrc file with instructions regarding which
  files to install.
\item
  open vim, type: \emph{:PlugInstall} or \emph{:PlugUpdate}, should
  start seeing updating packages.
\item
  type: \emph{:scriptnames} to see loaded plugins
\item
  just comment out or delete plug lines for packages no longer needed.
\item
  how to install a particular package? See
  \href{https://vimawesome.com/plugin/onedark-vim}{vimawesome}
\end{enumerate}

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{# curl plug.vim}
\ExtensionTok{curl}\NormalTok{ -fLo ~/.vim/autoload/plug.vim --create-dirs \textbackslash{}}
\NormalTok{    https://raw.githubusercontent.com/junegunn/vim-plug/master/plug.vim}

\CommentTok{# create vimrc file}
\BuiltInTok{cd} \VariableTok{$HOME}
\ExtensionTok{vim}\NormalTok{ .vimrc}

\CommentTok{# paste into file the text below.}
\end{Highlighting}
\end{Shaded}

Example .vimrc file with only one package one dark atom visual for vim:

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{if} \ExtensionTok{empty}\NormalTok{(glob(}\StringTok{'~/.vim/autoload/plug.vim'}\NormalTok{))}
        \ExtensionTok{silent}\NormalTok{ !curl -fLo ~/.vim/autoload/plug.vim --create-dirs}
                \ExtensionTok{\textbackslash{} https}\NormalTok{://raw.githubusercontent.com/junegunn/vim-plug/master/plug.vim}
        \ExtensionTok{autocmd}\NormalTok{ VimEnter * PlugInstall --sync }\KeywordTok{|} \BuiltInTok{source} \VariableTok{$MYVIMRC}
\ExtensionTok{endif}

\StringTok{" Plugins will be downloaded under the specified directory.}
\StringTok{call plug#begin('~/.vim/plugged')}

\StringTok{"} \ExtensionTok{Declare}\NormalTok{ the list of plugins.}
\ExtensionTok{Plug} \StringTok{'joshdick/onedark.vim'}

\StringTok{" List ends here. Plugins become visible to Vim after this call.}
\StringTok{call plug#end()}

\StringTok{"""""""""""""""""""""""""""""""""""""""""""""""""}
\StringTok{" Settings}
\StringTok{"""""""""""""""""""""""""""""""""""""""""""""""""}
\ExtensionTok{syntax}\NormalTok{ on}
\ExtensionTok{colorscheme}\NormalTok{ onedark}
\end{Highlighting}
\end{Shaded}

\hypertarget{install-vim-plug-plug-ins-manager-for-neovim}{%
\subsection{Install Vim-Plug Plug-ins manager for
Neovim}\label{install-vim-plug-plug-ins-manager-for-neovim}}

Follow the
\href{https://github.com/junegunn/vim-plug/wiki/tutorial}{instructions
here} for installations. Very similar steps as above for Vim:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  curl \emph{plug.vim} to \emph{.local/share/nvim}. Directory different
  than vim
\item
  create nvim folder under .config, vimrc contents should be in this
  file: \emph{\textasciitilde{}/.config/nvim/init.vim}
\item
  enter nvim and \emph{:PlugInstall}
\end{enumerate}

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{# Neovim (~/.local/share/nvim/site/autoload)}
\ExtensionTok{curl}\NormalTok{ -fLo ~/.local/share/nvim/site/autoload/plug.vim --create-dirs \textbackslash{}}
\NormalTok{    https://raw.githubusercontent.com/junegunn/vim-plug/master/plug.vim}

\CommentTok{# create vimrc file}
\FunctionTok{mkdir}\NormalTok{ ~/.config/nvim}
\ExtensionTok{nvim}\NormalTok{ ~/.config/nvim/init.vim}

\CommentTok{# paste into file the text below.}
\end{Highlighting}
\end{Shaded}

Vimrc file with atom styling:

\begin{verbatim}
" Plugins will be downloaded under the specified directory.
call plug#begin('~/.local/share/nvim/site/plugged')

" Declare the list of plugins.
Plug 'vim-airline/vim-airline'

" Visual Settings
Plug 'junegunn/goyo.vim'
Plug 'junegunn/limelight.vim'

" Color theme plugins
Plug 'joshdick/onedark.vim'

" List ends here. Plugins become visible to Vim after this call.
call plug#end()

"""""""""""""""""""""""""""""""""""""""""""""""""
" Color Settings
"""""""""""""""""""""""""""""""""""""""""""""""""
syntax on

colorscheme onedark

"""""""""""""""""""""""""""""""""""""""""""""""""
" Visual Settings
"""""""""""""""""""""""""""""""""""""""""""""""""
" For Goyo
let g:goyo_width=85

" For LimeLight
" Color name (:help cterm-colors) or ANSI code
let g:limelight_conceal_ctermfg = 'gray'
let g:limelight_conceal_ctermfg = 240
" Color name (:help gui-colors) or RGB color
let g:limelight_conceal_guifg = 'DarkGray'
let g:limelight_conceal_guifg = '#777777'
" highlight line
let g:limelight_bop = '^.*$'
" let g:limelight_eop = '\n'
let g:limelight_paragraph_span = 0

"""""""""""""""""""""""""""""""""""""""""""""""""
" UI Settings
"""""""""""""""""""""""""""""""""""""""""""""""""
" Keep cursor in the middle of the page, useful for editing text
set so=999
" Turn limelight on by default
" autocmd VimEnter * Limelight
" Turn Goyo on by default
autocmd VimEnter * Goyo
" autocmd VimEnter * AirlineToggle
" In Goyo, if airline is turned on, do nto show scratch area
" autocmd! User GoyoEnter nested set eventignore=FocusGained
" autocmd! User GoyoLeave nested set eventignore=
\end{verbatim}

\hypertarget{install-neovim-in-windows}{%
\subsection{Install Neovim in Windows}\label{install-neovim-in-windows}}

Install and access neovim all from windows powershell. Type in
\emph{powershell} in regular command prompt for example.

\hypertarget{install-neovim-and-vim-plug-in-windows}{%
\subsubsection{Install Neovim and Vim-Plug in
Windows}\label{install-neovim-and-vim-plug-in-windows}}

\begin{verbatim}
# install scoop and use scoop
scoop install neovim

# follow vim-plug instructions
md ~\AppData\Local\nvim\autoload
$uri = 'https://raw.githubusercontent.com/junegunn/vim-plug/master/plug.vim'
(New-Object Net.WebClient).DownloadFile(
  $uri,
  $ExecutionContext.SessionState.Path.GetUnresolvedProviderPathFromPSPath(
    "~\AppData\Local\nvim\autoload\plug.vim"
  )
)
\end{verbatim}

\hypertarget{set-up-init.vim-file-in-windows}{%
\subsubsection{Set up init.vim File in
Windows}\label{set-up-init.vim-file-in-windows}}

Inside powershell, create init.vim file:

\begin{verbatim}
cd ~\AppData\Local\nvim\
nvim init.vim
\end{verbatim}

paste these in \emph{:set paste}:

\begin{verbatim}
" Plugins will be downloaded under the specified directory.
call plug#begin('~/AppData/Local/nvim/site/plugged')

" Declare the list of plugins.
Plug 'vim-airline/vim-airline'

" Markdown
Plug 'godlygeek/tabular'
Plug 'plasticboy/vim-markdown'

" Visual Settings
Plug 'junegunn/goyo.vim'
Plug 'junegunn/limelight.vim'
Plug 'reedes/vim-pencil'

" Color theme plugins
Plug 'joshdick/onedark.vim'
Plug 'morhetz/gruvbox'
Plug 'junegunn/seoul256.vim'
Plug 'jaredgorski/spacecamp'
Plug 'lifepillar/vim-solarized8'
Plug 'reedes/vim-colors-pencil'

" List ends here. Plugins become visible to Vim after this call.
call plug#end()

"""""""""""""""""""""""""""""""""""""""""""""""""
" Color Settings
"""""""""""""""""""""""""""""""""""""""""""""""""
syntax on

" onedark:
colorscheme onedark

" seoul256:
" seoul256 (dark), 236 is darkest
" let g:seoul256_background = 236
" colorscheme seoul256

" spacecamp:
" colorscheme spacecamp

" vim-solarized8:
" set background=dark
" colorscheme solarized8

" vim-colors-pencil:
" let g:pencil_higher_contrast_ui = 0
" colorscheme pencil
" set background=dark

"""""""""""""""""""""""""""""""""""""""""""""""""
" Visual Settings
"""""""""""""""""""""""""""""""""""""""""""""""""
" For Goyo
let g:goyo_width=85

" For LimeLight
" Color name (:help cterm-colors) or ANSI code
let g:limelight_conceal_ctermfg = 'gray'
let g:limelight_conceal_ctermfg = 240
" Color name (:help gui-colors) or RGB color
let g:limelight_conceal_guifg = 'DarkGray'
let g:limelight_conceal_guifg = '#777777'
" if Limelight should highlight line rather than paragraph
let g:limelight_bop = '^.*$'
" let g:limelight_eop = '\n'
let g:limelight_paragraph_span = 0

"""""""""""""""""""""""""""""""""""""""""""""""""
" UI Settings
"""""""""""""""""""""""""""""""""""""""""""""""""
" Keep cursor in the middle of the page, useful for editing text
set so=999
" Turn limelight on by default
" autocmd VimEnter * Limelight
" Turn Goyo on by default
autocmd VimEnter * Goyo

"""""""""""""""""""""""""""""""""""""""""""""""""
" Markdown **, * etc settings
"""""""""""""""""""""""""""""""""""""""""""""""""
" set concealcursor=n
" set conceallevel=3
" hi Asterisks NONE
" hi AsteriskBold  cterm=bold gui=bold
" syn match Asterisks contained "**" conceal
" syn match AsteriskBold "\\\@<!\*\*[^"*|]\+\*\*" contains=Asterisks
" autocmd VimEnter * highlight Normal ctermbg=black
" ctermfg=grey

"""""""""""""""""""""""""""""""""""""""""""""""""
" Other Settings
"""""""""""""""""""""""""""""""""""""""""""""""""
set paste               " to enable pasting in windows
\end{verbatim}

\begin{verbatim}
nvim "C:/Users/d674a/Tex4Econ/_other/equation/multilines.tex"
\end{verbatim}

\hypertarget{full-screen-vim-window-in-windows}{%
\subsubsection{Full Screen Vim Window in
Windows}\label{full-screen-vim-window-in-windows}}

It is nice to have full screen, no distraction work experience. To set
command prompt to full screen (to get rid of scrolling bar on the right
in full screen), use windows command prompt which allows for full
screen, right click on window top border, choose property, then choose
layout, then set height and width of window size and buffer size to be
the same. This will allow for full screen experience.

\hypertarget{vim-basics}{%
\section{Vim Basics}\label{vim-basics}}

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{# to open vim}
\ExtensionTok{vim}\NormalTok{ -v}
\CommentTok{# to exit vim}
\NormalTok{:}\ExtensionTok{q}\NormalTok{!}
\CommentTok{# open up file from google drive}
\ExtensionTok{vim} \StringTok{"/mnt/chromeos/GoogleDrive/MyDrive/Reading Papers/Reading/Referee/pa_2019_oct_journal/jor_12345_comments.Rmd"}
\CommentTok{# start editing, type i to enter insert mode}
\ExtensionTok{i}
\CommentTok{# when editing is done, to exit and save, write and quit}
\CommentTok{# esc first}
\NormalTok{:}\ExtensionTok{wq}
\end{Highlighting}
\end{Shaded}

\hypertarget{vim-cursor-movements}{%
\section{Vim Cursor Movements}\label{vim-cursor-movements}}

Move cursor to the beginning of a line? This should not be done in edit
mode, esc, use movement commands, then back to insert mode. There are
six most basic movements, \emph{wbjk()0\$}:

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{# forward one word}
\FunctionTok{w}
\CommentTok{# back one word to begin}
\ExtensionTok{b}
\CommentTok{# back to word to end}
\ExtensionTok{e}

\CommentTok{# forward one line, achieved by also pressing downward arrow}
\ExtensionTok{j}
\CommentTok{# backward one line, achieved by pressing upward arrow}
\ExtensionTok{k}
\CommentTok{# left arrow}
\ExtensionTok{h}
\CommentTok{# right arrow}
\ExtensionTok{l}

\CommentTok{# Jump forward one Sentence}
\NormalTok{)}
\CommentTok{# Jump backward one Sentence}
\KeywordTok{(}

\CommentTok{# Forward one page and back one page}
\CommentTok{# ctrl+f, ctrl+b}

\CommentTok{# Begin of line}
\ExtensionTok{0}
\CommentTok{# End of Line}
\NormalTok{$}

\CommentTok{# Begin of File}
\ExtensionTok{gg}
\CommentTok{# End of File}
\ExtensionTok{G}
\end{Highlighting}
\end{Shaded}

In combination, the basic commands can be used in combination

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{# move to the beginning of the next line}
\ExtensionTok{j0}
\CommentTok{# move to the end of the next line}
\ExtensionTok{j}\NormalTok{$}
\end{Highlighting}
\end{Shaded}

\hypertarget{very-convinent-functions}{%
\section{Very Convinent Functions}\label{very-convinent-functions}}

Some functionalities take much more efforts to complete in many other
editors, but are very easy in vim:

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{# combine lines: bunch of lines, with carriage break, one block of text, reflow/join}
\CommentTok{# 1. select block}
\ExtensionTok{Vjjjj}
\CommentTok{# 2. reflow/join}
\ExtensionTok{J}
\end{Highlighting}
\end{Shaded}

\hypertarget{vim-go-to-spot-in-text-quickly}{%
\subsection{Vim go to Spot in Text
Quickly}\label{vim-go-to-spot-in-text-quickly}}

\begin{verbatim}
# ESC
# Search for word
/abc
# esc
# next occurance of word
n
# last occurance
N
# first occurance overall
ggn
# last occurance overall
G
# clear search highlighting
:noh
\end{verbatim}

back to previous point

\begin{verbatim}
~.
\end{verbatim}

\hypertarget{combo-operations}{%
\subsection{Combo Operations}\label{combo-operations}}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Delete:

  \begin{itemize}
  \tightlist
  \item
    delete current word and go into insert mode: \emph{ciw}
  \item
    Delete current word: \emph{dw}
  \item
    Delete from cursor until end of sentence: \emph{dis}
  \item
    Delete from cursor to end of line: \emph{d\$} or \emph{D}
  \item
    Delete until end of paragraph: \emph{dip}
  \item
    Delete all text in file: \emph{ggdG}
  \end{itemize}
\end{enumerate}

\hypertarget{vim-statistics}{%
\subsection{Vim Statistics}\label{vim-statistics}}

\begin{itemize}
\tightlist
\item
  word count: \emph{g, ctrl+g}
\end{itemize}

\hypertarget{vim-errors}{%
\section{Vim Errors}\label{vim-errors}}

Vim seems frozen (hard for vim to freeze, it is not really frozen). This
is likely due to pressing \emph{ctrl + s}, then need to press \emph{ctrl
+ q}.

vim error: ``E297: Write error in swap file''

\begin{verbatim}
# Trying to save
:w
# E297 can not save, override changes elswhere, and force save what is on screen.
:e!
\end{verbatim}

\hypertarget{vim-set-up-others}{%
\section{Vim Set-Up Others}\label{vim-set-up-others}}

\hypertarget{chromebook}{%
\subsection{Chromebook}\label{chromebook}}

pressing esc key is an issue, too far away. On chromebook, remap the
search key which is in the spot of the caps lock key to esc. and remap
the esc key to search key.

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  search for keyboard under settings
\item
  launcher to escape, and escape to launcher
\end{enumerate}

\end{document}

### 2020-01-03 nontex/install/windows/fn_installations.Rmd
set up compile minor update

@@
 
-Press *Ctrl + P*, paste the *ext install* commands below to install extensions. Extensions are in: *%USERPROFILE%\.vscode\extensions* for windows. Can change code for extension there.
+Press *Ctrl + P*, paste the *ext install* commands below to install extensions. Extensions are in: *%USERPROFILE%/.vscode/extensions* for windows. Can change code for extension there.
 
@@
 
-```{JSON}
+```
 "latex-workshop.view.pdf.external.synctex.command": "C:/Program Files/SumatraPDF/SumatraPDF.exe",

### 2020-01-03 nontex/install/windows/fn_installations.tex
set up compile minor update

@@
             linkcolor=Maroon,
-            filecolor=Maroon,
             citecolor=Blue,
@@
 
+\hypertarget{sumatrapdf}{%
+\subsection{SumatraPDF}\label{sumatrapdf}}
+
+For windows, install
+\href{https://www.sumatrapdfreader.org/download-free-pdf-viewer.html}{SumatraPDF}.
+Can easily modify colors.
+
+\textbf{Settings}
+
+\href{https://medium.com/greatnote/kindle-sepia-color-code-1fed14b1a5ef}{Kindle
+Sepia} modifications:
+
+\begin{itemize}
+\tightlist
+\item
+  Background color:
+
+  \begin{itemize}
+  \tightlist
+  \item
+    Kindle Sepia: \emph{fbf0d9}
+  \item
+    Kindle Sepia Light: \emph{fff8e6}
+  \end{itemize}
+\item
+  Text color:
+
+  \begin{itemize}
+  \tightlist
+  \item
+    Kindle Sepia: \emph{5f4b32}
+  \item
+    Kindle Sepia Darker: \emph{503f2a}
+  \item
+    Kindle Sepia Darkerer: \emph{1e170f}
+  \end{itemize}
+\end{itemize}
+
+\begin{verbatim}
+FixedPageUI [
+    TextColor = #1e170f
+    BackgroundColor = #fff8e6
+    SelectionColor = #f5fc0c
+    WindowMargin = 2 4 2 4
+    PageSpacing = 4 4
+]
+\end{verbatim}
+
 \hypertarget{okular-pdf}{%
@@
 
+\textbf{Settings}:
+
+\begin{itemize}
+\tightlist
+\item
+  Background color:
+
+  \begin{itemize}
+  \tightlist
+  \item
+    background behind pdf: configure okular, general, use custom
+    backgroun color, Gainsboro gray: \emph{DCDCDC}, kindle sepia:
+    \emph{FBF0D9}
+  \item
+    pdf background itself: configure okular, accessbility, change color,
+    change paper color, Light Kindle Sepia: \emph{fff8e6}
+  \end{itemize}
+\end{itemize}
+
 \textbf{Features}:
@@
 \item
-  Okular 3 pages per row view:
-
-  \begin{itemize}
-  \tightlist
-  \item
-    view, overview
-  \end{itemize}
-\item
-  Automatic Update when PDF updated elsewhere
-
-  \begin{itemize}
-  \tightlist
-  \item
-    this is one of the key reasons to use okular, when I knit a Rmd file
-    to PDF, the currently open Okular PDF file automatically updates and
-    does not give file is open error like Acrobat.
-  \end{itemize}
+  Okular 3 pages per row view: view, overview
+\item
+  Automatic Update when PDF updated elsewhere: this is one of the key
+  reasons to use okular, when I knit a Rmd file to PDF, the currently
+  open Okular PDF file automatically updates and does not give file is
+  open error like Acrobat.
 \item
@@
   \item
-    can easily change background color to non-white.
+    background behind pdf: configure okular, general, use custom
+    backgroun color, Gainsboro gray: \emph{DCDCDC}, kindle sepia:
+    \emph{FBF0D9}
+  \item
+    pdf background itself: configure okular, accessbility, change color,
+    change paper color, Light Kindle Sepia: \emph{fff8e6}
   \end{itemize}
@@
 
+All settings here JSON files here:
+
+\begin{itemize}
+\tightlist
+\item
+  windows: \emph{C:/Users/fan/AppData/Roaming/Code/User}, can be
+  modified here directly
+\end{itemize}
+
 \hypertarget{vscode-installation}{%
@@
 VSCode is much more light-weight than Atom, much faster. On Windows,
-download \href{https://code.visualstudio.com/download}{here}.
+download \href{https://code.visualstudio.com/download}{here}. VScode
+settings easy to change for various extensions. Very very good Latex
+Editor, probably the best I have used.
 
@@
 Press \emph{Ctrl + P}, paste the \emph{ext install} commands below to
-install extensions:
+install extensions. Extensions are in:
+\emph{\%USERPROFILE\%/.vscode/extensions} for windows. Can change code
+for extension there.
 
@@
 \hypertarget{vscode-and-latex}{%
-\paragraph{VSCode and Latex}\label{vscode-and-latex}}
+\subsubsection{VSCode and Latex}\label{vscode-and-latex}}
 
@@
 Workshop}.
+
+\textbf{Settings}
+
+change background border pdf color (not pdf but border): \emph{ctrl +
+shift + x}, LatexWorkshop, Settings, Configure Extension Settings,
+Search for background, change color name. or enter:
+\emph{latex-workshop.view.pdf.backgroundColor}. use gainsboro gray:
+\emph{\#DCDCDC}, or lightgray \emph{\#D3D3D3}.
+
+To take advantage of Okular (where background color can be none-white
+for example). Go to settings, and: 1. Change:
+\emph{latex-workshop.view.pdf.viewer} to external 2. Change:
+\emph{latex-workshop.view.pdf.external.viewer.command} to
+\emph{C:/Program Files/SumatraPDF/SumatraPDF.exe} open up
+\emph{C:/Users/fan/AppData/Roaming/Code/User/settings.json}, and copy
+these in:
+
+\begin{verbatim}
+"latex-workshop.view.pdf.external.synctex.command": "C:/Program Files/SumatraPDF/SumatraPDF.exe",
+"latex-workshop.view.pdf.external.synctex.args": [
+  "-forward-search",
+  "%TEX%",
+  "%LINE%",
+  "-reuse-instance",
+  "-inverse-search",
+  "code \"C:\\Users\\fan\\AppData\\Local\\Programs\\Microsoft VS Code\\resources\\app\\out\\cli.js\" -r -g \"%f:%l\"",
+  "%PDF%",
+]
+\end{verbatim}
+
+\textbf{Features}:
+
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi}.}
+\tightlist
+\item
+  upon savings, rebuid file and update pdf (similar to overleaf)
+\item
+  hover offers equation preview
+\end{enumerate}
+
+\textbf{Shortcuts}:
+
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi}.}
+\tightlist
+\item
+  preview: \emph{ctrl + alt + v}
+\item
+  synctex location: \emph{ctrl + alt + j}
+\end{enumerate}
+
+\hypertarget{vscode-settings.json}{%
+\subsubsection{VSCode settings.json}\label{vscode-settings.json}}
+
+The settings.json file, \emph{\%APPDATA\%/Code/User/settings.json}:
+
+\begin{verbatim}
+{
+  "r.rterm.windows": "C:/Program Files/R/R-3.6.2/bin/x64/R.exe",
+  "window.zoomLevel": 0,
+  "latex-workshop.view.pdf.viewer": "external",
+  "latex-workshop.view.pdf.external.synctex.command": "C:/Program Files/SumatraPDF/SumatraPDF.exe",
+  "latex-workshop.view.pdf.external.synctex.args": [
+        "-forward-search",
+        "%TEX%",
+        "%LINE%",
+        "-reuse-instance",
+        "-inverse-search",
+        "code \"C:\\Users\\fan\\AppData\\Local\\Programs\\Microsoft VS Code\\resources\\app\\out\\cli.js\" -r -g \"%f:%l\"",
+        "%PDF%",
+    ],
+    "latex-workshop.view.pdf.external.viewer.command": "C:/Program Files/SumatraPDF/SumatraPDF.exe"
+}
+\end{verbatim}
 

### 2020-01-05 nontex/install/git/fs_git_setup.Rmd
installation file updates, RMD Template

@@
 ---
-title: "Git and Github Example and Tutorial, Sync with Multiple Repositories, Store Password"
+title: |
+  | Git and Github Example and Tutorial
+  | Sync with Multiple Repositories, Store Password etc.
 output:
-  pdf_document:
-    df_print: paged
+  html_document:
     number_sections: true
@@
     number_sections: true
-  html_document:
+  pdf_document:
+    df_print: paged
     number_sections: true

### 2020-01-05 nontex/install/linux/fn_ubuntu.Rmd
tikz tree, vim set up, other setup updates
installation file updates, RMD Template

@@
 output:
-  pdf_document:
-    df_print: paged
+  html_document:
     number_sections: true
@@
 sudo apt-get install vim
+sudo apt-get install sublime-text
 sudo apt-get install htop

### 2020-01-05 nontex/install/windows/fn_installations.Rmd
installation file updates, RMD Template

@@
 
+R-studio theme, [VSCode theme](https://github.com/anthonynorth/rscodeio) for Rstudio works very well:
+
+```{r}
+# admin rights
+sudo rstudio --no-sandbox
+remotes::install_github("anthonynorth/rscodeio")
+rscodeio::install_theme()
+```
+
 ## R Tests
@@
 - Open up Settings: *Ctrl + ,*
-- Preview Markdown in VSCode: *Ctrl + Shift + V*
-- Open up left pane: *Ctrl + B*
-- Wrap Text: *alt + Z*, switch between wrap or not to save screen space for example.
+- Preview Markdown in VSCode: *Ctrl + Shift + v*
+- Open up left pane: *Ctrl + b*
+- Wrap Text: *alt + z*, switch between wrap or not to save screen space for example.
+- Hide Console Pane (running code): *Ctrl + j*
 
@@
 apm install hydrogen
-apm install project-manager
+# apm install project-manager
 apm install sublime-style-column-selection
 apm install minimap
+
+# r-related
+# for me the best r-syntax highlighter I have found
+apm install r-syntax
 

### 2020-01-05 nontex/rmd/fex_rmd_template_guide.Rmd
installation file updates, RMD Template

--- 2020-01-03 nontex/install/windows/fn_installations.Rmd
@@
 title: |
-  | New Computer Fan Data-Science Set-up
-  | Python (Anaconda), R (Rstudio), Matlab and Latex (Texlive)
-  | Atom, VScode, Pycharm
+  | Template Example Generation  
+  | Example to do ABC
 output:
@@
 
-1. Python (Anaconda, Pycharm + VSCode + Atom)
-2. R (VSCode + Atom)
-3. Matlab
-4. Latex and PDF (texlive, Okular, VSCode + Atom + Texstudio)
+1. Objective One
+2. Objectie Two
 
-Test at the end:
-
-1. Do sample *py* files work?
-    + work from command line
-    + work from atom (hydrogen), Pycharm, VSCode
-2. Do sample *rmd* files work?
-    + work from r-studio
-    + work from atom (hydrogen), VSCode
-3. Do tex templates compile?
-    + tikz files, template files with bib
-    + work from texstudio, VSCode live compile, Atom
-
-Installation Plan outline:
-
-1. Conda install (python)
-2. Install Atom along with Hydrogen and other packages.
-
-# Python and Anaconda Installation
+# Part One
 
@@
 ```
-
-## First Time Conda Install
-
-[Download Anaconda Python 3](https://www.anaconda.com/distribution/) and install for all users.
-Afterwards, Anaconda does not automatically get added to Windows Path.
-Need to use Anaconda Prompt to access programs.
-To access Anaconda packages from windows prompt, from git bash, from R, etc, need to Add Anaconda to Windows Path.
-
-To install conda in Linux/Debian, follow [these instructions](https://fanwangecon.github.io/Tex4Econ/nontex/install/linux/fn_ubuntu.html). Overall, installations are very similar.
-
-In command/anaconda prompt:
-
-```{bash}
-# To remove conda Fully
-rm -rf ~/anaconda3
-
-where anaconda
-# C:/ProgramData/Anaconda3/Scripts/anaconda.exe
-where python
-# C:/ProgramData/Anaconda3/python.exe
-where jupyter
-# C:/ProgramData/Anaconda3/Scripts/jupyter.exe
-where jupyter-kernelspec
-# if R installed already
-where r
-
-###############################
-# Add these to Windows PATH:
-###############################
-# C:\ProgramData\Anaconda3\Scripts
-# C:\ProgramData\Anaconda3
-```
-
-To Add Anaconda to Path, In Windows
-1. Search for: Environment Variables
-2. Edit Environment Variables
-3. Add new to Path (lower half):
-    - C:/ProgramData/Anaconda3/Scripts/
-    - C:/ProgramData/Anaconda3/
-4. Now open up regular windows command Prompt, Type in:
-    - conda --version
-    - also Close and Open up Git Bash: conda --version
-
-## Conda Update
-
-Open up Anaconda Navigator, it will update navigator automatically. If there are errors, might have to clean first.
-
-There are different channels/repositories from which packages could be installed: *conda*, *conda-forge*, for example.
-Can change where to look for packages first.
-Many packages are in multiple channels.
-Conda-forge often have mroe recent packages.
-
-```{bash}
-# if there are bugs
-# conda clean --packages
-# use conda-forge as main channel, more updated packages
-conda config --get channels
-conda config --add channels conda-forge
-conda config --get channels
-# remove conda-forge from channels (do so for main env install)
-conda config --remove channels conda-forge
-# normal update
-conda update --all
-
-# install additional packages
-conda install -y statsmodels datashape seaborn
-conda install -c conda-forge -y interpolation awscli
-conda install -c anaconda -y boto3
-```
-
-## Python Command Line Test
-
-Fist test python under command line:
-
-```{bash}
-# windows
-python "C:/Users/fan/PyFan/ProjectSupport/Testing/Numpy/Functions.py"
-python "C:/Users/fan/PyFan/ProjectSupport/graph/subplot.py"
-# linux
-python ~/PyFan/ProjectSupport/Testing/Numpy/Functions.py
-python ~/PyFan/ProjectSupport/graph/subplot.py
-```
-
-# R Installation
-
-R could be installed from Anaconda or directly on windows outside of the Anaconda directories.
-When installing from within Anaconda, could create R environment that are isolated from the rest of the computer.
-The R environment could be updated and deleted without disturbing dependencies in conda main or the rest of the computer.
-
-The computer could have multiple R installations.
-Several in different conda R environment, and also several under windows/linux primary main user R directories.
-Type *which R/where R* to see if you open up R from command line at the moment, which directory's R will be used.
-Inside Conda R environment, it will be a different R if there is a different R version there.
-
-## Fully Uninstall r
-
-If R was installed in R enviornments, just delete the environment.
-Otherwise, use system's uninstaller.
-Before that, from terminal/command-prompt, type *R*, and *.libPaths()* to find paths.
-Do so inside conda main, outside of conda main, inside different environments, find all paths.
-After uninstaller finishes, check in the libPath folders to see if there are still stuff there, delete all, delete the folders.
-
-```{R}
-.libPath()
-# C:/Users/fan/Documents/R/win-library/3.6
-# C:/Program Files/R/R-3.6.1/library
-```
-
-For Linux and for unsintalling inside conda:
-
-```{bash}
-# Exit Conda
-conda deactivate
-# where is R installed outside of Conda
-which R
-# /usr/bin/R
-# To remove all
-sudo apt-get remove r-base
-sudo apt-get remove r-base-core
-
-# Inside Conda base
-conda activate
-# Conda r_env
-conda activate r_env
-# Where is it installed?
-which R
-# /home/wangfanbsg75/anaconda3/bin/R
-conda uninstall r-base
-```
-
-## Install R (outside of Conda)
-
-Need to install R.
-Then need to install also an editor/IDE for R.
-Rstudio is the dominant R IDE.
-VSCode and Atom also works well, especially VSCode as editors.
-Dramatically better experience for writing scripts outside of Rstudio which feels unwieldy and slow especially compared to VSCode.
-
-Overall plan:
-
-1. [download R](https://cloud.r-project.org/)
-    + for debian: [Johannes Ranke](https://cran.r-project.org/bin/linux/debian/).
-For Linux/Debian installation, crucial to update the *source.list* to include sources that have more recent versions of R.
-If not, will get very old R versions that is not compatible with many packages.
-    + add R to path for Windows. In Windows Path, add for example: *C:/Program Files/R/R-3.6.2/bin/x64/* and *C:/Rtools/bin*
-2. [download R-studio](https://rstudio.com/products/rstudio/download/)
-3. Open R-studio and auto-detect R
-4. Install additional packages (from commandline)
-    + various R data-science packages have dependencies, and additional not-R programs might need to be installed.
-Install them as needed, for example:  *libcurl4-openssl-dev* and *libssl-dev* from command prompt first inside Debian.
-
-### Linux R Install
-
-For linux/Debian, to Install latest R:
-
-```{bash}
-# Go to get latesdebian latest r sources.list
-cat /etc/apt/sources.list
-# Install this First (should already be installed)
-sudo apt install dirmngr
-
-# Debian R is maintained by Johannes Ranke, copied from https://cran.r-project.org/bin/linux/debian/:
-apt-key adv --keyserver keys.gnupg.net --recv-key 'E19F5F87128899B192B1A2C2AD5F960A256A04AF'
-# Add to source.list, for debian stretch (9)
-# sudo su added for security issue as super-user
-sudo su -c "sudo echo 'deb http://cloud.r-project.org/bin/linux/debian stretch-cran35/' >> /etc/apt/sources.list"
-# if added wrong lines, delete 3rd line
-sudo sed '3d' /etc/apt/sources.list
-
-# Update and Install R, should say updated from cloud.r
-sudo apt-get update
-sudo apt-get install r-base r-base-dev
-
-# Also install these, otherwise r-packages do not install
-# libxml2 seems need for tidymodels
-sudo apt-get install libcurl4-openssl-dev
-sudo apt-get install libssl-dev
-sudo apt-get install libxml2-dev
-```
-
-### Install Packages for R
-
-From command prompt, enter R by typeing *R*, and install packages:
-
-```{r}
-# Can enter R from Command Prompt Conda ENV, much faster than from r-studio
-# Install R-tools, RTOOLS is for WINDOWS
-install.packages("installr")
-library("installr")
-install.Rtools()
-# c:/Rtools/bin;
-# c:/Rtools/mingw_32/bin;
-# c:/Rtools/mingw_64/bin;
-
-# main packagevps
-# tidymodel installation on linux difficult
-install.packages(c("tidyverse", "tidymodels", "tidyr"))
-# development packages
-install.packages(c("devtools", "IRkernel", "pkgdown", "roxygen2", "kableExtra"))
-# other packages
-install.packages(c("AER", "minpack.lm", "knitr", "matlab"))
-
-# Install my package, need to prepare package to work for ubuntu
-# if install does not work, load locally
-devtools::install_github("fanwangecon/R4Econ")
-
-# Kernel
-install.packages(c('repr', 'IRdisplay', 'evaluate', 'crayon', 'pbdZMQ', 'devtools', 'uuid', 'digest'))
-IRkernel::installspec()
-```
-
-## Install R (inside Conda)
-
-Key packages are generally available in conda's default channel (official distribution) and also the more frequently updated conda-forge channel.
-Prioritize conda-forge to get the latest packages.
-After adding *conda-forge* to channels, that will be prioritized, so when creating a new environment, conda will install first from conda-forge if package exists there.
-Try the *r_env* generation line with and without first adding *conda-forge* to channel, and see that the packages installed will have different versions, reflecting versions in the default channel and in the *conda-forge* channels.
-
-### Set up Conda R environment
-
-Create a Conda Environment called *r_env*, and update its channels.
-
-- **Location**: Installed environments are shown appear in the *envs* folder of *C:/ProgramData/Anaconda3/envs/*.
-Can be easily deleted without disrupting the main base installation for conda.
-This is very important.
-During installation, could easily run into problems, and need to re-install.
-Much better to only re-install a folder.
-Note that when R is installed in *envs*, it will not show up under add or remove programs for uninstallation from there, has to be uninstalled, deleted directly here.
-- **Use only in Env**: Note that if we installed r inside r_env, if we type *r* under the base environment, we can not enter r.
-We can only enter r within r_env.
-With PATH properly set-up, this happens under Conda Prompt, Windows Prompt, etc.
-- **Multiple Pythons**: With the above installation for R, one benefit is that if R requires a different version of Python than what the base environment uses, the r_env could have a different python version.
-So type *python* in the base environment as well as inside the *r_env*.
-This also means potentially there could be duplicated installations I think.
-Look at the python versions under *conda list* in the base and in the r-environment.
-- **File Size**: Note that this creates a large installation folder, *C:/ProgramData/Anaconda3/envs/r_env/*, without additional packages, is 1.3 GB in size
-
-```{bash}
-# outside of conda, install some depencies
-sudo apt-get install libcurl4-openssl-dev
-sudo apt-get install libssl-dev
-sudo apt-get install libxml2-dev
-
-# install key r packages within a r-environment
-conda env remove -n r_env
-# start empty environment
-conda create -n r_env
-# activate env and check, nothing yet
-conda activate r_env
-conda list
-
-# check channel and add env specific channel
-conda config --get channels
-# to get latest r, use conda-forge, which has more recent Rs
-# conda config --env --add channels conda-forge
-# channels for base
-conda config --get channels
-# channels for cur env
-conda config --get channels --env
-
-# see all installed environments
-conda env list
-# activate an environment to use it, if in base, r does not exist, isolated in r_env
-conda activate r_env
-# see packages in environment
-conda list
-# to quit
-conda deactivate
-```
-
-### Install R and Some Packages in Conda
-
-Either inside a R specific environment, or outside of it, now do additional installations for R and also R packages.
-
-During installation, the R programs might require downgrading other programs in the Conda environment that Python for example also uses.
-That is why potentially it is safer to install in R environment.
-However, when installing in R enviornment, certain packages could have issues if installer does not realize it is in an environment with special folder structure, so installation could fail.
-
-```{bash}
-# install files
-conda install -n r_env -c r r r-essentials r-tidyverse r-tidymodels -y
-
-# trouble with igraph installation, install here from conda
-# conda install -n r_env r-essentials r-base r-tidyr r-tidyverse r-devtools r-irkernel r-pkgdown r-roxygen2
-conda install -n r_env -c r r-igraph
-conda install -n r_env -c conda-forge igraph
-conda install -n r_env -c r r-rstantools r-rstan r-rstanarm -y
-```
-
-## Install Additional Packages inside the R
-
-These are packages that I use, these should be installed inside the environment.
-Or they could be installed later from inside r-studio.
-Installing inside r-studio is a lot better.
-*tidymodel* has installation issues sometimes.
-
-In *r_env*, type in *R*, and then install from inside terminal's R. For conda env, devtools will be installed and will install packages inside *envs/r_env/Lib/R*.
-
-```{r}
-# enter into env
-# conda activate r_env
-# enter R or type in rstudio
-# sicne R is only install inside r_env, has to enter rstudio from r_env
-# R
-# rstudio
-
-# main packagevps
-# tidymodel installation on linux difficult
-install.packages(c("rstantools", "rstan", "rstanarm"))
-install.packages(c("tidyr", "tidyverse", "tidymodels"))
-
-# tidymodels
-# development packages
-install.packages(c("devtools", "IRkernel", "pkgdown", "roxygen2", "kableExtra"))
-# other packages
-install.packages(c("AER", "minpack.lm", "knitr", "matlab"))
-
-# Install my package, need to prepare package to work for ubuntu
-# if install does not work, load locally
-devtools::install_github("fanwangecon/R4Econ")
-
-# Kernel
-install.packages(c('repr', 'IRdisplay', 'evaluate', 'crayon', 'pbdZMQ', 'devtools', 'uuid', 'digest'))
-IRkernel::installspec()
-```
-
-## R-Studio Set-up Download from Rstudio
-
-1. Download R-studio, and install, as normal (not from conda, directly from rstudio website latest windows version)
-2. Open up anaconda prompt, enter *r_env* environment: *activate r_env*
-3. cd into rstudio exe file folder: cd "C:/Program Files/RStudio/bin"
-4. start r-studio from inside *r_env*: rstudio.exe
-5. inside r-studio, check: *.libPaths()*
-    - "C:/ProgramData/Anaconda3/envs/r_env/Lib/R/library"
-
-```{bash}
-activate r_env
-cd "C:/Program Files/RStudio/bin"
-rstudio.exe
-
-cd "C:/ProgramData/Anaconda3/envs/r_env/Lib/R/library"
-"C:/Program Files/RStudio/bin/rstudio.exe"
-```
-
-For linux, note that rstudio offers Ubuntu as well as Debian versions that can be installed with wget:
-
-```{bash}
-<!-- for ubuntu -->
-wget "https://download1.rstudio.org/desktop/bionic/amd64/rstudio-1.2.5033-amd64.deb"
-<!-- for debian -->
-sudo apt install ./rstudio-1.2.5033-amd64.deb
-wget "https://download1.rstudio.org/desktop/debian9/x86_64/rstudio-1.2.5033-amd64.deb"
-sudo apt install ./rstudio-1.2.5033-amd64.deb
-conda install -c r rstudio
-cd "C:/Program Files/RStudio/bin"
-rstudio.exe
-
-cd "C:/ProgramData/Anaconda3/envs/r_env/Lib/R/library"
-"C:/Program Files/RStudio/bin/rstudio.exe"
-```
-
-Is RSTUDIO pointing to the R installation you want? Note you can open Rstudio from differen conda env command line, that will use different R installations. Or also set:
-
-- *export RSTUDIO_WHICH_R=/usr/bin/R*
-- *export RSTUDIO_WHICH_R=/home/wangfanbsg75/anaconda3/bin/R*
-
-## R Tests
-
-Test the following file to see if we can execute a R file. Do it inside *r_env* and inside a *r* session.
-
-```{r}
-# A simple file with summary statistics using tidyverse
-source('C:/Users/fan/R4Econ/summarize/dist/fst_hist_onevar.R')
-# Another simple file with summary statistics using tidyverse
-source('C:/Users/fan/R4Econ/support/tibble/fs_tib_basics.R')
-# A file involving estimation
-source('C:/Users/fan/R4Econ/optimization/cesloglin/fst_ces_plan_linlog.R')
-
-# C:/Users/fan/R4Econ/summarize/dist/fst_hist_onevar.Rmd
-# C:/Users/fan/R4Econ/support/tibble/fs_tib_basics.Rmd
-# C:/Users/fan/R4Econ/optimization/cesloglin/fst_ces_plan_linlog.Rmd
-```
-
-# Install Latex and PDF
-
-Use a combination of overleaf and local compile.
-The goal is to have the same installation set-up for windows as well as linux.
-And hopefully, locally compilable file also can be compiled on overleaf (only use packages also available on overleaf).
-
-There are several pieces of things to install:
-
-1. latex compiler: pdflatex, etc
-2. tex distributions: MikTex, texlive
-    + these folders, once various packages are installed, could be very large, many GB
-3. latex packages from distributions
-3. editor (gui): Atom, Sublime text, texStudio, etc
-
-## Uninstall
-
-- uninstall *MiKTeX*: delete from programs, then delete remaining folder in Program Files.
-- uninstall *texlive*: go to *c:/texlive*, delete the folder
-
-## Install
-
-*Install on Windows*
-
-- [Install Texstudio](https://www.texstudio.org/)
-- [Install texlive](https://www.tug.org/texlive/acquire-netinstall.html)
-
-*Install on Ubuntu*
-
-install texlive and texstudio ubuntu/debian.
-
-```{bash}
-sudo apt-get update
-sudo apt-get install texlive-full
-sudo apt-get install texstudio
-```
-
-Test file compilations in TexStudio.
-
-## SumatraPDF
-
-For windows, install [SumatraPDF](https://www.sumatrapdfreader.org/download-free-pdf-viewer.html). Can easily modify colors.
-
-**Settings**
-
-[Kindle Sepia](https://medium.com/greatnote/kindle-sepia-color-code-1fed14b1a5ef) modifications:
-
-- Background color:
-    + Kindle Sepia: *fbf0d9*
-    + Kindle Sepia Light: *fff8e6*
-- Text color:
-    + Kindle Sepia: *5f4b32*
-    + Kindle Sepia Darker: *503f2a*
-    + Kindle Sepia Darkerer: *1e170f*
-
-```
-FixedPageUI [
-	TextColor = #1e170f
-	BackgroundColor = #fff8e6
-	SelectionColor = #f5fc0c
-	WindowMargin = 2 4 2 4
-	PageSpacing = 4 4
-]
-```
-
-## Okular PDF
-
-Linux: *sudo apt-get install okular*
-Windows: install okular from windows app store
-
-### Okular Shortcuts and Features
-
-**Settings**:
-
-- Background color:
-    + background behind pdf: configure okular, general, use custom backgroun color, Gainsboro gray: *DCDCDC*, kindle sepia: *FBF0D9*
-    + pdf background itself: configure okular, accessbility, change color, change paper color, Light Kindle Sepia: *fff8e6*
-
-**Features**:
-
-- Okular 3 pages per row view: view, overview
-- Automatic Update when PDF updated elsewhere: this is one of the key reasons to use okular, when I knit a Rmd file to PDF, the currently open Okular PDF file automatically updates and does not give file is open error like Acrobat.
-- Background color:
-    + background behind pdf: configure okular, general, use custom backgroun color, Gainsboro gray: *DCDCDC*, kindle sepia: *FBF0D9*
-    + pdf background itself: configure okular, accessbility, change color, change paper color, Light Kindle Sepia: *fff8e6*
-
-**Shortcuts**:
-
-+ Okular configure shortcuts: setting, configure shortcuts
-+ Okular if menu bar lost: *Ctrl + m*
-+ Okular comment pane: *F6*
-+ Okular close left pane: *F7*
-+ Okular full scrren: *Ctrl + Shift + F*
-    * unlike acrobat, pdf allows for multiple scrrens
-
-## Adobe PDF
-
-PDF Adobe Acrobat Installation
-  + go to adobe website, log in using fwang26@uh.edu
-  + go to my account, choose view and download my apps, choose acrobat & PDF, download Acrobat DC
-  + UH account can only be activated on two accounts at once, so need to kick other computers out temporarily potentially
-
-# Install Various Editors
-
-Atom, VSCode, Notepad++, Sublime, etc.
-These are essential editors that allows for pleasant programming and writing experiences.
-See here for [fan](http://fanwangecon.github.io/) instructions on [vim](https://fanwangecon.github.io/Tex4Econ/nontex/install/linux/fn_vim.html) installations.
-
-All settings here JSON files here:
-
-- windows: *C:/Users/fan/AppData/Roaming/Code/User*, can be modified here directly
-
-## VSCode Installation
-
-VSCode is much more light-weight than Atom, much faster.
-On Windows, download [here](https://code.visualstudio.com/download).
-VScode settings easy to change for various extensions.
-Very very good Latex Editor, probably the best I have used.
-
-For Linux:
-
-```{bash}
-# Debian Install
-curl https://packages.microsoft.com/keys/microsoft.asc | gpg --dearmor > microsoft.gpg
-sudo install -o root -g root -m 644 microsoft.gpg /usr/share/keyrings/microsoft-archive-keyring.gpg
-sudo sh -c 'echo "deb [arch=amd64 signed-by=/usr/share/keyrings/microsoft-archive-keyring.gpg] https://packages.microsoft.com/repos/vscode stable main" > /etc/apt/sources.list.d/vscode.list'
-sudo apt-get install apt-transport-https
-sudo apt-get update
-sudo apt-get install code # or code-insiders
-
-# Change Font (https://wwFw.reddit.com/r/Crostini/comments/cesxr0/vscode_ui_and_fonts_too_small_heres_how_to_fix_it/)
-# modify: /usr/share/applications/code.desktop
-nvim /usr/share/applications/code.desktop
-#replace this line: Exec=/usr/share/code/code --unity-launch %F
-Exec=sommelier -X --scale=0.8 --dpi=160 /usr/share/code/code "--unity-launch %F"
-#replace this line: Exec=/usr/share/code/code --new-window %F
-Exec=sommelier -X --scale=0.8 --dpi=160 /usr/share/code/code "--new-window %F"
-
-# Open File
-# low density mode to see cleary
-code
-```
-
-### VSCode Extensions
-
-Press *Ctrl + P*, paste the *ext install* commands below to install extensions. Extensions are in: *%USERPROFILE%/.vscode/extensions* for windows. Can change code for extension there.
-
-```{bash}
-# [Microsoft Python Extension](https://marketplace.visualstudio.com/items?itemName=ms-python.python)
-ext install ms-python.python
-# [Latex Workshop](https://marketplace.visualstudio.com/items?itemName=James-Yu.latex-workshop)
-ext install latex-workshop
-# [R](https://marketplace.visualstudio.com/items?itemName=Ikuyadeu.r)
-ext install ikuyadeu.r
-```
-
-### VSCode Shortcuts and Features
-
-**Features**:
-
-1. open a file, if have workspace where the file is in, automatically expand tree and show where file is on left pane.
-
-**Shortcuts** :
-
-- Zen model: *Ctrl + k, z*, this means press control k, then press z
-- Open up Settings: *Ctrl + ,*
-- Preview Markdown in VSCode: *Ctrl + Shift + V*
-- Open up left pane: *Ctrl + B*
-- Wrap Text: *alt + Z*, switch between wrap or not to save screen space for example.
-
-### VSCode and R
-
-VSCode works pretty well it seems with Rmd files.
-Rmd files are useful to work through algorithm, examples in preparation for writing usable functions.
-Rstudio has been often very slow for me, and I generally feel like can not stretch around and work in RStudio IDE.
-
-In Atom, Hydrogen works, but really only works with very basic line by line testing.
-
-Using VSCode with RMD files seems much quicker, and there is room to breath.
-
-1. Install R following R installation instructions.
-2.
-Then install extension [R](https://marketplace.visualstudio.com/items?itemName=Ikuyadeu.r).
-Microsoft stopped supporting rmd in VSCode: [R Tools for Visual Studio](https://github.com/microsoft/RTVS)
-3. properly set path (might have to call vscode from r env)
-    + *r.rterm.linux*: */home/wangfanbsg75/anaconda3/envs/r_env/bin/R*
-    + *r.rterm.windows*: *C:/Program Files/R/R-3.6.2/bin/x64/R.exe*
-        * note *R.exe* at the end
-4. Run:
-    - ctrl + enter to activate R terminal
-    - VSCode 2019 allows for Knit Rmd: *Ctrl + Shift + K*
-    - also can run code segment: select lines and *ctrl + enter*
-
-### VSCode and Latex
-
-Download [Latex Workshop](https://marketplace.visualstudio.com/items?itemName=James-Yu.latex-workshop).
-
-**Settings**
-
-change background border pdf color (not pdf but border): *ctrl + shift + x*, LatexWorkshop, Settings, Configure Extension Settings, Search for background, change color name.
-or enter: *latex-workshop.view.pdf.backgroundColor*.
-use gainsboro gray: *#DCDCDC*, or lightgray *#D3D3D3*.
-
-To take advantage of Okular (where background color can be none-white for example). Go to settings, and:
-1. Change: *latex-workshop.view.pdf.viewer* to external
-2. Change: *latex-workshop.view.pdf.external.viewer.command* to *C:/Program Files/SumatraPDF/SumatraPDF.exe*
- open up *C:/Users/fan/AppData/Roaming/Code/User/settings.json*, and copy these in:
-
-```
-"latex-workshop.view.pdf.external.synctex.command": "C:/Program Files/SumatraPDF/SumatraPDF.exe",
-"latex-workshop.view.pdf.external.synctex.args": [
-  "-forward-search",
-  "%TEX%",
-  "%LINE%",
-  "-reuse-instance",
-  "-inverse-search",
-  "code \"C:\\Users\\fan\\AppData\\Local\\Programs\\Microsoft VS Code\\resources\\app\\out\\cli.js\" -r -g \"%f:%l\"",
-  "%PDF%",
-]
-```
-
-**Features**:
-
-1. upon savings, rebuid file and update pdf (similar to overleaf)
-2. hover offers equation preview
-
-**Shortcuts**:
-
-1. preview: *ctrl + alt + v*
-2. synctex location: *ctrl + alt + j*
-
-### VSCode settings.json
-
-The settings.json file, *%APPDATA%/Code/User/settings.json*:
-
-```
-{
-  "r.rterm.windows": "C:/Program Files/R/R-3.6.2/bin/x64/R.exe",
-  "window.zoomLevel": 0,
-  "latex-workshop.view.pdf.viewer": "external",
-  "latex-workshop.view.pdf.external.synctex.command": "C:/Program Files/SumatraPDF/SumatraPDF.exe",
-  "latex-workshop.view.pdf.external.synctex.args": [
-		"-forward-search",
-		"%TEX%",
-		"%LINE%",
-		"-reuse-instance",
-		"-inverse-search",
-		"code \"C:\\Users\\fan\\AppData\\Local\\Programs\\Microsoft VS Code\\resources\\app\\out\\cli.js\" -r -g \"%f:%l\"",
-		"%PDF%",
-	],
-	"latex-workshop.view.pdf.external.viewer.command": "C:/Program Files/SumatraPDF/SumatraPDF.exe"
-}
-```
-## Atom Installation
-
-Atom is slow but has clean look and nice git/github integration.
-
-### Atom Extensions
-
-Terminal in windows or linux after installation: *apm install hydrogen*. apm is the atom package manager:
-
-```{bash}
-# Once atom is installed, can use apm to install packages
-apm install hydrogen
-apm install project-manager
-apm install sublime-style-column-selection
-apm install minimap
-
-# vim distraction free editing
-apm install vim-mode-plus
-apm install zen
-
-# Inside Conda open up atom
-atom
-
-```
-
-### Atom Shortcuts and Features
-
-**Features**:
-
-```{bash}
-# open multiple projects from atom at the same time, after repos synced
-atom ~/fanwangecon.github.io ~/Pyfan ~/Teaching ~/Tex4Econ ~/R4Econ ~/M4Econ ~/Py4Econ
-# open up any py from from within, try 1+1, does it work?
-# also use script, try ctrl + shift + b, run whole file (not hydrogen)
-```
-
-**Shortcuts** :
-
-- Git Pane: *Ctrl + 9*, *Ctrl + 8*
-
-### Atom and Python
-
-Having installed Anaconda, now install Atom and Hydrogen to Test with Python. For both Jupyter as well as Atom, always open from command prompt, open from *Anaconda Prompt* with admin rights.
-
-Open up *Jupyter Notebook*, does the python kernel work? If does not, uninstall and re-install Anaconda.
-
-```{bash}
-# start jupyter lab, from prompt
-jupyter lab
-```
-
-Try *1+1*.
-
-### Atom and Latex
-
-Install the following two packages in atom:
-
-1. [latex](https://github.com/thomasjo/atom-latex) package on atom.
-2. [language-latex](https://atom.io/packages/language-latex) package on atom
-
-In Atom Latex setting, note that on different platforms, paths to texlive are different:
-
-- Path:
-    + Windows: *C:/texlive/2019/bin/win32*
-    + Chromebook Linux: */usr/bin/latex*
-- Which PDF viewer to use:
-    + download Okular and use [Okular](https://okular.kde.org/)
-
-```{bash}
-# set TeX path
-# C:/texlive/2019/bin/win32
-
-# Latex, after installation
-# see where texlive appears under root folder directories
-sudo find / -name "texlive"
-# see latex version, if texlive is used
-latex -v
-# see main exe directory
-which latex
-# /usr/bin/latex
-```
-
-## Other Editors
-
-### Notepad++
-
-[Notepad++](https://notepad-plus-plus.org/downloads/v7.8.2/). Many old projects have xml folder structures for Notepad++.
-
-- Silently update file changes made in other editors: Settings, Preferences, MISC., File Status Auto Detection, Update Silently.
-
-### Sublime
-
-[Sublime](https://www.sublimetext.com/3)
-
-there are some issues with atom.
-When a file is edited inside Vim, when changes are saved, a [temp file is created in atom](https://github.com/atom/atom/issues/17186).
-Sublime would, however, still show the file with the changes.
-This makes dual screen editing very difficult.
-Sublime text is used for this situation.
-
-```{bash}
-# Sublime Linux
-wget -qO - https://download.sublimetext.com/sublimehq-pub.gpg | sudo apt-key add -
-sudo apt-get install apt-transport-https
-echo "deb https://download.sublimetext.com/ apt/stable/" | sudo tee /etc/apt/sources.list.d/sublime-text.list
-sudo apt-get update
-sudo apt-get install sublime-text
-# launch from terminal
-subl
-```
-
-*Sublime Setup*:
-
-- [r and rmd setup](https://weibeld.net/r/rmd_sublime_package.html)
-
-### PyCharm
-
-[pycharm](https://www.)jetbrains.com/pycharm/)
-
-# Other Programs to Install
-
-## Package Managers
-
-To install packages in windows more easily:
-
-- [scoop](https://github.com/lukesampson/scoop/wiki/Quick-Start)
-
-```{bash}
-# in powershell
-# enter cmd
-# type powershell in cmd to enter powershell from cmd
-powershell
-# permission
-set-executionpolicy remotesigned -scope currentuser
-# install
-iwr -useb get.scoop.sh | iex
-```
-
-## Utilities
-
-- 7-zip
-- evernote
-
-## Security
-
-- keepass
-- [Proton VPN](https://protonvpn.com/): unlimited usage free version available.
-- Express VPN

### 2020-01-05 nontex/install/linux/fn_vim.Rmd
r project template folder to reuse

@@
 
-1. Delete:
+1. Delete
     - delete current word and go into insert mode: *ciw*
@@
     - Delete all text in file: *ggdG*
+2. Copying: replace *d* by *y* for all oeprations.
+    - Copy current word: *dw*
+    - Copy from cursor to end of line (need to set this): *y$* or *Y*
+    - Copy until end of paragraph: *yip*
+3. Insert to edit:
+    - Insert after last character of document: *GA*
+    - Insert at the end of line: *A*
+    - Insert after cursor, *a*, insert before curosr *i*
 

### 2020-01-06 nontex/install/windows/fn_installations.Rmd
several additional apms

@@
 ```
+
 ## Atom Installation
@@
 # apm install project-manager
-apm install sublime-style-column-selection
-apm install minimap
 
@@
 
+# Selection and Overview
+apm install sublime-style-column-selection
+apm install minimap
+apm install highlight-selected
+
 # vim distraction free editing
@@
 apm install zen
+
+# support
+apm install date
 
@@
 # /usr/bin/latex
+```
+
+### Atom settings file
+
+The settings.json file, *%APPDATA%/Code/User/settings.json*:
+
+```
+{
+  "r.rterm.windows": "C:/Program Files/R/R-3.6.2/bin/x64/R.exe",
+  "window.zoomLevel": 0,
+  "latex-workshop.view.pdf.viewer": "external",
+  "latex-workshop.view.pdf.external.synctex.command": "C:/Program Files/SumatraPDF/SumatraPDF.exe",
+  "latex-workshop.view.pdf.external.synctex.args": [
+		"-forward-search",
+		"%TEX%",
+		"%LINE%",
+		"-reuse-instance",
+		"-inverse-search",
+		"code \"C:\\Users\\fan\\AppData\\Local\\Programs\\Microsoft VS Code\\resources\\app\\out\\cli.js\" -r -g \"%f:%l\"",
+		"%PDF%",
+	],
+	"latex-workshop.view.pdf.external.viewer.command": "C:/Program Files/SumatraPDF/SumatraPDF.exe"
+}
 ```

### 2020-01-07 nontex/install/linux/fn_vim.Rmd
installation atom keymap, yiw and viwp

--- 2020-01-05 nontex/install/linux/fn_vim.Rmd
@@
 " autocmd! User GoyoLeave nested set eventignore=
+""""""""""""""""""""""""""""""""""""""""""""""""""
+" Remap Keys
+"""""""""""""""""""""""""""""""""""""""""""""""""
+" esc in insert mode
+" inoremap jj <esc>
 ```
@@
 set paste               " to enable pasting in windows
+set nofoldenable        " avoid folding by default
+
+"""""""""""""""""""""""""""""""""""""""""""""""""
+" Remap Keys
+"""""""""""""""""""""""""""""""""""""""""""""""""
+" esc in insert mode
+" inoremap jj <esc>
 ```
@@
 
-1. Delete:
+**Delete**:
+
 - delete current word and go into insert mode: *ciw*
@@
 - Delete all text in file: *ggdG*
+
+**Copying**: replace *d* by *y* for all oeprations.
+
+- Copy current word: *dw*
+- Copy from cursor to end of line (need to set this): *y$* or *Y*
+- Copy until end of paragraph: *yip*
+
+**Insert to edit**:
+
+- Insert after last character of document: *GA*
+- Insert at the end of line: *A*
+- Insert after cursor, *a*, insert before curosr *i*
+
+**Copy and Replace**:
+
+- copy current word: *yiw*, then move to the next word to replace: *viwp*
 

### 2020-01-07 nontex/install/windows/fn_installations.Rmd
installation atom keymap, yiw and viwp
R4Econ package to REconTools Package

@@
 # if install does not work, load locally
-devtools::install_github("fanwangecon/R4Econ")
+devtools::install_github("fanwangecon/REconTools")
 
@@
 
+**Shortcuts**
+
+- compile: *ctrl + alt + b*
+- sync: *ctrl + alt + j*
+- live save
+
 **Settings**
@@
 apm install r-syntax
+
+# latex-related
+apm install language-latex
+apm install latex
 
@@
 
-The settings.json file, *%APPDATA%/Code/User/settings.json*:
+Atom keymap.cson file:
 
 ```
-{
-  "r.rterm.windows": "C:/Program Files/R/R-3.6.2/bin/x64/R.exe",
-  "window.zoomLevel": 0,
-  "latex-workshop.view.pdf.viewer": "external",
-  "latex-workshop.view.pdf.external.synctex.command": "C:/Program Files/SumatraPDF/SumatraPDF.exe",
-  "latex-workshop.view.pdf.external.synctex.args": [
-		"-forward-search",
-		"%TEX%",
-		"%LINE%",
-		"-reuse-instance",
-		"-inverse-search",
-		"code \"C:\\Users\\fan\\AppData\\Local\\Programs\\Microsoft VS Code\\resources\\app\\out\\cli.js\" -r -g \"%f:%l\"",
-		"%PDF%",
-	],
-	"latex-workshop.view.pdf.external.viewer.command": "C:/Program Files/SumatraPDF/SumatraPDF.exe"
-}
+# https://github.com/t9md/atom-vim-mode-plus/issues/130
+'atom-text-editor.vim-mode-plus.insert-mode':
+  'j j': 'vim-mode-plus:activate-normal-mode'
 ```

### 2020-01-09 _other/tikz/tree/fs_tikz_gametree.tex
apm ex-mode :q :w, game tree continued

@@
 
-\subsection{Nodes Only}
+\subsection{Develop Tree Outline}
 
-When developing trees, to simply the problem, first just draw nodes and branches, no text, no benidng, no coloring.
+\subsubsection{Nodes Only}
+
+Draw nodes and branches, no text, no bending, no coloring.
 
@@
         child
-        child
         }
@@
 child;
+\end{tikzpicture}
+\end{center}
+
+\subsubsection{First Two Nodes with Continuous Curved Bend Right}
+
+Add Continuous bending curves.
+
+\def\famm{5mm}
+\begin{center}
+\begin{tikzpicture}[scale=1.5,font=\footnotesize]W
+\tikzstyle{level 1}=[level distance=\famm,sibling distance=\famm]
+\tikzstyle{level 2}=[level distance=\famm,sibling distance=\famm]
+\tikzstyle{level 3}=[level distance=\famm,sibling distance=\famm]
+% B Level 1 point
+\node(0)[solid node,label=left:{$P1$}]{}
+[grow=right]
+child{ 
+    [black] node(11)[]{}
+}
+child{
+    [grow=right]
+    child{
+        [black] node(21)[]{}
+    }
+    child{
+        [grow=right]
+        child
+        child
+        child
+        child
+    }
+    child{
+        [black] node(23)[]{}
+    }
+}
+child{
+    [black] node(13)[]{}
+};
+% information set
+\draw[dashed, bend right]
+    (11) to (13);
+\draw[dashed, bend right]
+    (21) to (23);
+\end{tikzpicture}
+\end{center}
+
+\subsubsection{Extend Middle node Rightward}
+
+Continuous bending exceed middle node, now offset middle node.
+
+\def\famm{5mm}
+\begin{center}
+\begin{tikzpicture}[scale=1.5,font=\footnotesize]W
+\tikzstyle{level 1}=[level distance=\famm,sibling distance=\famm]
+\tikzstyle{level 2}=[level distance=\famm,sibling distance=\famm]
+\tikzstyle{level 3}=[level distance=\famm,sibling distance=\famm]
+% B Level 1 point
+\node(0)[solid node,label=left:{$P1$}]{}
+[grow=right]
+child{ 
+    [black] node(11)[]{}
+}
+child{
+    [grow=right]
+    [white] node(12)[solid node, xshift=7.5, yshift=0]{}
+    child{
+        [black] node(21)[]{}
+    }
+    child{
+        [grow=right]
+        [white] node(22)[solid node, xshift=7.5, yshift=0]{}
+        child {
+            [black] node(31)[]{}
+        }
+        child{
+            [black] node(32)[]{}
+        }
+        child{
+            [black] node(33)[]{}   
+        }
+        child{
+            [black] node(34)[]{}
+        }
+    }
+    child{
+        [black] node(23)[]{}
+    }
+}
+child{
+    [black] node(13)[]{}
+};
+% information set
+\draw[dashed, bend right]
+    (11) to (13);
+\draw[dashed, bend right]
+    (21) to (23);
+\draw[dotted, line width=0.35mm]
+    (0) to (12);
+\draw[dotted, line width=0.35mm]
+    (12) to (22);
 \end{tikzpicture}

### 2020-01-09 nontex/install/linux/fn_vim.Rmd
apm ex-mode :q :w, game tree continued

@@
 
+" Rmd Syntax Highlighting, Nvim-R renders
+Plug 'jalvesaq/Nvim-R' 
+Plug 'vim-pandoc/vim-rmarkdown'
+Plug 'vim-pandoc/vim-pandoc-syntax'
+
 " Visual Settings
@@
 " esc in insert mode
-" inoremap jj <esc>
+inoremap jj <Esc>
 ```

### 2020-01-09 nontex/install/windows/fn_installations.Rmd
apm ex-mode :q :w, game tree continued

@@
 
-```{R}
+```{r}
 .libPath()
@@
 apm install vim-mode-plus
+apm install ex-mode
 apm install zen

### 2020-01-10 nontex/install/linux/fn_vim.Rmd
vim delete and insert, D

@@
 
+**Delete and Insert**:
+
+- delete from now till end of sentence and insert mode: *C*
+- delete whole sentence you are on and insert: *cc*
+- delete until end of sentence and insert mode: *cis*
+- delete current word and go into insert mode: *cw*
+
 **Delete**:
 
-- delete current word and go into insert mode: *ciw*
 - Delete current word: *dw*
@@
 - Copy until end of paragraph: *yip*
+- Copy all text on page: *ggVGY*
 

### 2020-01-11 nontex/install/windows/fn_installations.Rmd
atom cson, vscode zen mode no minimap

@@
 
+- see all shortcuts: *Ctrl + k, ctrl + s*
 - Zen model: *Ctrl + k, z*, this means press control k, then press z
+    + note that z mode can be adjusted by shiftin the bar on the left
 - Open up Settings: *Ctrl + ,*
@@
 - Hide Console Pane (running code): *Ctrl + j*
+
+*personal bindings*
+
+- toggle minimap: *Ctrl + k, ctrl + z*
 
@@
 ```
+'atom-text-editor':
+  'ctrl-shift-j': 'pretty-json:prettify'
+  'alt-z':'date:date'
+  'alt-x':'date:time'
+  'alt-c':'date:datetime'
+'body':
+  'ctrl-tab': 'pane:show-next-item'
+  'ctrl-shift-tab': 'pane:show-previous-item'
+'.editor':
+  'ctrl-alt-z': 'atom-beautify:beautify-editor'
+  'ctrl-shift-r': 'hydrogen:restart-kernel'
+'atom-text-editor:not([mini])':
+  'ctrl-*': 'highlight-selected:select-all'
+'atom-text-editor, webview.markdown-preview-plus':
+  'ctrl-shift-X': 'markdown-preview-plus:toggle-render-latex'
+
 # https://github.com/t9md/atom-vim-mode-plus/issues/130

### 2020-01-12 nontex/install/git/fs_git_setup.Rmd
repo pull bash update, sublime to path

@@
 
-to create bash file to store these (from git bash in windows):
+to create bash file to store these (from git bash in windows), generate a pull_repos and push_repos file.
 
@@
 vim push_repos
+```
 
+What *pull_repos* could look like, *push_repos* will look similar:
+
+```{bash}
 # paste the text below over, comfirm bash loc with: which bash
@@
 echo start fan github pull
-# Security
+
+# Security, will prompt for password once.
 eval "$(ssh-agent)"
 ssh-add ~/.ssh/id_rsa
+
 # Pull from Persistent Repos
@@
 git pull github master
+cd ~/PyFan
+git pull github master
+cd ~/Teaching
+git pull github master
+
 # Stop Secured SSH
@@
 
+# Open Atom with the Projects
+atom ~/fanwangecon.github.io ~/PyFan ~/Teaching
+```
+
+Possibly do this:
+
+```{bash}
 # change permission to make file an executable

### 2020-01-12 nontex/install/linux/fn_vim.Rmd
repo pull bash update, sublime to path

@@
 
-- Copy current word: *dw*
+- Copy current word: *yiw*; or *yw* which yanks word from current letter to end
 - Copy from cursor to end of line (need to set this): *y$* or *Y*

### 2020-01-12 nontex/install/windows/fn_installations.Rmd
repo pull bash update, sublime to path

@@
 # install additional packages
+# linux utilites
+conda install -y m2-base 
+# stats and graphs
 conda install -y statsmodels datashape seaborn
+# various
 conda install -c conda-forge -y interpolation awscli
+# aws communicate
 conda install -c anaconda -y boto3
@@
 
+Put sublime path in windows path for example:
+
+```
+C:\Program Files\Sublime Text 3\
+```
+
 - [r and rmd setup](https://weibeld.net/r/rmd_sublime_package.html)

### 2020-01-12 nontex/install/git/fs_git_setup.Rmd
git setup single repo pull and push

@@
 output:
-  html_document:
+  pdf_document:
+    df_print: paged
     number_sections: true
@@
     number_sections: true
-  pdf_document:
-    df_print: paged
+  html_document:
     number_sections: true
@@
 ```
+
+## Quick Pull and Push Single Repo and Delete
+
+Suppose temporarily need to work on a repo, but don't want it to take up too much space. Create two bash files with these single repo info
+
+1. initialize
+2. secure and pull
+3. push 
+4. delete
+
+Steps 1 and 2, note do not leave space when defining bash variables around the equality symbol:
+
+```{bash}
+#!/usr/bin/bash
+STRREPO='EconStatClass'
+echo pull single repository
+echo going to pull from $STRREPO
+
+# generate all needed key repositories
+cd ~
+mkdir $STRREPO
+
+# Set global config settings, in ~/.gitconfig
+git config --global user.name "Fan Wang"
+git config --global user.email wangfanbsg75@live.com
+
+# Initialize
+cd ~
+cd $STRREPO
+git init
+git remote add github git@github.com:fanwangecon/$STRREPO
+
+# Secure
+eval "$(ssh-agent)"
+ssh-add ~/.ssh/id_rsa
+
+# Pull
+cd ~
+cd $STRREPO
+git pull github master
+
+# Open Repository in Atom
+atom ~/$STRREPO
+```
+
+Steps 3 and 4:
+
+```{bash}
+# push
+cd ~
+cd $STR_REPO
+git push -u github master
+
+# remove fully
+cd ~
+cd $STR_REPO
+git rm -r $STR_REPO
+```
+
+bash scripts
+
+```{bash}
+# change permission to make file an executable
+chmod u+x ~/PyFan/bin/pull_one
+chmod u+x ~/PyFan/bin/push_one
+# execute script
+bash ~/PyFan/bin/pull_one
+```

### 2020-01-15 nontex/install/windows/fn_installations.Rmd
install latex atom clean options

@@
 
+**Latex Package Option**
+
+*clean* pattern
+
+```{bash}
+**/*.run.xml, **/*.aux, **/*.aux.bak, **/*.bbl, **/*.bcf, **/*.blg, **/*.dvi, **/*.fdb_latexmk, **/*.fls, **/*.idx, **/*.idx.bak, **/*.ilg, **/*.ind, **/*.lof, **/*.log, **/*.lol, **/*.lot, **/*.nav, **/*.out, **/*.ps, **/*.snm, **/*.synctex.gz, **/*.toc, /**/_minted-{jobname}, /{output_dir}/sage-plots-for-{jobname}.tex, /missfont.log, /texput.log, /texput.aux
+```
+
 ### Atom settings file

### 2020-01-18 nontex/install/windows/fn_installations.Rmd
install split-diff
revealjs markdown test

@@
 
+# Present
+install.packages("revealjs")
 # Kernel
@@
 	],
-	"latex-workshop.view.pdf.external.viewer.command": "C:/Program Files/SumatraPDF/SumatraPDF.exe"
+	"latex-workshop.view.pdf.external.viewer.command": "C:/Program Files/SumatraPDF/SumatraPDF.exe",
+  "editor.minimap.enabled": false,
+  "latex-workshop.latex.clean.fileTypes": [
+    "*.aux",
+    "*.bbl",
+    "*.blg",
+    "*.idx",
+    "*.ind",
+    "*.lof",
+    "*.lot",
+    "*.out",
+    "*.toc",
+    "*.acn",
+    "*.acr",
+    "*.alg",
+    "*.glg",
+    "*.glo",
+    "*.gls",
+    "*.fls",
+    "*.log",
+    "*.fdb_latexmk",
+    "*.snm",
+    "*.synctex(busy)",
+    "*.synctex.gz(busy)",
+    "*.nav",
+    "*.xml",
+    "*.gz",
+    "*.bcf"
+  ]  
 }
@@
 apm install highlight-selected
+apm install split-diff
 

### 2020-01-18 nontex/revealjs/_guide/fs_revealjs_basics.Rmd
revealjs markdown test

---
title: |
  | Basics of Reveal.js
  | for Mathmatical Presentations
output:
  pdf_document:
    df_print: paged
    number_sections: true
  html_notebook:
    number_sections: true
  word_document:
    number_sections: true
  html_document:
    number_sections: true
urlcolor: blue
always_allow_html: yes
---

Go back to [fan](http://fanwangecon.github.io/)'s [Tex4Econ and Miscellaneous Repository](http://fanwangecon.github.io/Tex4Econ/).

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval = FALSE)
```

# Equations and Reveal.js

## Page Fragments

- long html multiple files
- html fragments separate files
- rmd bookdown revealjs

### 2020-01-22 nontex/revealjs/_guide/fs_revealjs_basics.Rmd
mathjax basic

@@
 
+In *serif_fan.css* To change main body font, change font-size below.
+
+```
+.reveal p {
+  margin: 20px 0;
+  font-size: 1em;
+  line-height: 1.3; }
+```
+
+To change MathJax font size, add to end of *serif_fan.css*:
+
+[MathJax, how to change text size?](https://stackoverflow.com/questions/48136559/mathjax-how-to-change-text-size)
+[How to change font for MathJax](https://stackoverflow.com/questions/41474096/how-to-change-font-for-mathjax)
+
+```
+.math span {
+  font-size: 12px;
+}
+```
+
 # Equations and Reveal.js

### 2020-01-27 _support/spacing/reduce/reduce.tex
Equation gap control specific group

--- 2019-09-12 _support/spacing/reduce.tex
@@
 \usepackage{mathptmx}
-
 \usepackage{amsfonts}
@@
 \titlespacing\subsubsection{0pt}{2pt}{0pt}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%% Reduce Spacing for Math Equations
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\makeatletter
-\g@addto@macro\normalsize{%
-  \setlength\abovedisplayskip{1pt}
-  \setlength\belowdisplayskip{1pt}
-  \setlength\abovedisplayshortskip{1pt}
-  \setlength\belowdisplayshortskip{1pt}
-}
 
@@
 
+\subsection{Code to Change Equation Spacing in One Spot}
+\begin{lstlisting}
+  {
+  \abovedisplayskip=25pt
+  \belowdisplayskip=25pt
+  \abovedisplayshortskip=5pt
+  \belowdisplayshortskip=5pt
+  let's skip a lot on top
+  \begin{align*}
+    \begin{gathered}
+          1+1=2\\
+          2+2=4
+  \end{gathered}
+  \end{align*}  
+  let's skip not skip a lot at the bottom
+  }
+\end{lstlisting}
+{
+  \abovedisplayskip=125pt
+  \belowdisplayskip=125pt
+  \abovedisplayshortskip=5pt
+  \belowdisplayshortskip=5pt
+  let's skip a lot on top
+  \[
+  1+1=2
+  \]
+  let's skip not skip a lot at the bottom
+}
+
+\subsection{Change Equation Spacing Different Equations}
+
+Some types of equations one spacing, others another.
+
+\begin{lstlisting}
+\newcommand{\assumptionskip}{
+\abovedisplayskip=6pt
+\belowdisplayskip=6pt
+\abovedisplayshortskip=6pt
+\belowdisplayshortskip=6pt
+}
+\newcommand{\theoremskip}{
+\abovedisplayskip=12.0pt plus 3.0pt minus 7.0pt
+\belowdisplayskip=12.0pt plus 3.0pt minus 7.0pt
+\abovedisplayshortskip=0.0pt plus 3.0pt
+\belowdisplayshortskip=6.5pt plus 3.5pt minus 3.0pt
+}
+{
+\assumptionskip
+\begin{assumption}
+\label{as:2a}
+Let $A$ be an $i$ specific function with input $b$, specifically:
+\begin{align*}
+	\begin{gathered}
+        1+1=2\\
+        2+2=4\\
+\end{gathered}
+\end{align*}
+where the effects of binary input $B$ on $C$ is additively separable from $Z$.
+\end{assumption}
+}
+
+\end{lstlisting}
+
+see: \href{https://www.overleaf.com/learn/latex/%5Cabovedisplayskip%20and%20related%20commands}{abovedisplayskip and related commands}
+
 \section{Margins}

### 2020-01-27 nontex/windows/tricks/fs_windows_tricks.Rmd
Equation gap control specific group

---
title: |
  | Windows Tricks
  | Shortcuts
output:
  pdf_document:
    df_print: paged
    number_sections: true
  html_notebook:
    number_sections: true
  word_document:
    number_sections: true
  html_document:
    number_sections: true
urlcolor: blue
always_allow_html: yes
---

Go back to [fan](http://fanwangecon.github.io/)'s [Tex4Econ and Miscellaneous Repository](http://fanwangecon.github.io/Tex4Econ/).

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval = FALSE)
```

# Windows Shortcuts

[Microsoft Keyboard shortcuts](https://www.microsoft.com/accessories/en-us/support/hardware-tips-and-tricks)

## Launch Programs Pinned to Task Bar

Can pin 1 through 0 programs to windows task bar, and access quickly via **win + 1** for the first pinned program for example.

But how to access the 11th pinned program?

**Info**:

- [5 Ways To Quickly Launch Programs On Windows](https://www.howtogeek.com/124109/5-ways-to-quickly-launch-programs-on-windows/)
- [Hey, Scripting Guy! How Can I Add a Windows PowerShell Shortcut to the Quick Launch Toolbar?](https://devblogs.microsoft.com/scripting/hey-scripting-guy-how-can-i-add-a-windows-powershell-shortcut-to-the-quick-launch-toolbar/)
- [Define shortcut key for shortcut in PowerShell](https://stackoverflow.com/questions/32126697/define-shortcut-key-for-shortcut-in-powershell)
- [get target path of shortcuts](https://social.technet.microsoft.com/Forums/en-US/fddb6ec0-cc48-43f0-929e-bf25d07fbf48/get-target-path-of-shortcuts?forum=winserverpowershell)

### 2020-02-04 nontex/revealjsrmd/test_img.Rmd
revealjs slides rmd with many images and to pdf with decktape

---
title: "Test Include Several Images in Revealjs and Generate PDF"
author: Fan Wang (fanwangecon.github.io)
date: February 4th, 2020
output:
  revealjs::revealjs_presentation:
    theme: sky
    highlight: pygments
    center: false
    transition: none
    css: fan_present.css
    mathjax: local
    self_contained: false
params:
    imgwidth: 25px
---

# Rmd RevealJS and Decktape
<!--
decktape convert to PDF
cd "C:/Users/fan/Tex4Econ/nontex/revealjsrmd/"
decktape automatic test_img.html test_img.pdf
-->

To produce very low cost, easy to compile, easy to produce presentations, use these:

1. [revealjs](https://revealjs.com/#/)
2. [revealjs_presentation](https://github.com/rstudio/revealjs)
3. [decktape](https://github.com/astefanutti/decktape)

Use the revealjs r package to write revealjs documents in r markdown and knit to html. Then use decktape to conver html to pdf.

## revealjs and r

See the [rmd file](http://fanwangecon.github.io/Tex4Econ/nontex/revealjsrmd/test_img.Rmd) that generated this presentation.

## revealjs and r

<!-- cd "C:/Users/fan/Tex4Econ/nontex/revealjsrmd/" -->

Once the HTML file is created, we can use decktape to convert it to pdf:

- install decktape: install [nodejs](https://nodejs.org/en/), npm install -g decktape
- to save results as image slides individually:
    * *decktape reveal --screenshots test_img.html test_img.pdf*
- to save results as a single pdf
    * *decktape reveal --size='2048x1536' test_img.html test_img.pdf*
    * [gap issue with large size workaround](https://github.com/astefanutti/decktape/issues/151)

# Image Group One

## Image One JPG

- small jpg profile photo
- Equation: $1+2=3$

![](images/profile_tiny.jpg)

## Two JPGs Together

- Two Images Together Same Page
- Equation: $1+2=3$

![](images/profile_tiny.jpg){width=100px}
![](images/github_logo.jpg){width=100px}

# Image Group Two

## pDF and SVG

- svg and then pdf

![](images/github_logo.svg){width=100px}
![Alt](images/github_logo.pdf){width=100px}

### 2020-02-05 nontex/install/git/fs_git_setup.Rmd
git setup incorporate conditional in bash

@@
 
-## Initalize and add remote repo for each:
+## Initialize and add remote repo for each:
 
@@
 
-Pull latested from multiple repositories. Just Paste the following lines.
+Pull latest from multiple repositories. Just Paste the following lines.
 
@@
 3. commit changes as work on one computer
-4. upon leaving a computer with commited changes, push all
+4. upon leaving a computer with committed changes, push all
 5. create bash file to make it easier to repeat steps
@@
 git pull github master
+
+# Conditional Pull, pull if some conditional satisfied
+# For example, if a computer has some folder, pull to that.
+if [ -d "D:/Dropbox (UH-ECON)/Project_Nguyen_Townsend_Wang_ThaiFinChoice/draft" ]
+then
+  echo "On Office Precision Desktop, Pull also for NTW Dropbox from Git Repo"
+  cd "D:/Dropbox (UH-ECON)/Project_Nguyen_Townsend_Wang_ThaiFinChoice/draft"
+  git pull github master
+else
+  echo "Not on office Precision, do not pull from NTW git repo to NTW Dropbox"
+fi
 

### 2020-02-06 nontex/revealjsrmd/test_tex.Rmd
revealjs newcommand tex math

---
title: "rmd revealjs Latex test"
author: Fan Wang 
date: Feb 5, 2020
output:
  revealjs::revealjs_presentation:
    theme: sky
    highlight: pygments
    center: true
    transition: none
    css: fan_present.css
    mathjax: local
    self_contained: false
---

# Overview

See more from [Fan](fanwangecon.github.io)'s [Tex4Econ](fanwangecon.github.io/Tex4Econ)

We will test out writing equations in RMD + revealjs

# Defining NEWCOMMAND

\newcommand{\vara}{\mathrm{Var}}
\newcommand{\varb}{\mathrm{\alpha + \beta}}
\newcommand{\varc}{
  \frac{a + b}{c + d} \times \exp\left( x \right) = y
}

<section style="font-size:60%;">

- This is from *\\vara+2*: $\vara+2$ 
- This is from *\\varb+2*: $\varb+2$ 
- This is from *\\varc+2*: $\varc+2$

</section>

```{tex echo=TRUE, eval=FALSE}
\newcommand{\vara}{\mathrm{Var}}
\newcommand{\varb}{\mathrm{\alpha + \beta}}
\newcommand{\varc}{
  \frac{a + b}{c + d} \times \exp\left( x \right) = y
}
```

# Equations

## Inline Equation

<div style="color:darkred;margin:20px;margin-top:50px;" >
Here is some text that is in red, 
<b>in between the b symbols mean put this text in bold</b> 
but this text is not bold
</div>

<p style="margin:10px;font-size:50%;">
<i>This is smaller italisized text</i>, font size 50 percent.
</p>

- Regular sized Equation: $1+2=3$
- Smaller Equation: <span style="font-size:50%;"> $1+2=3$ </span>

## Display Equation

<div style="font-size:40%;" >
$$
\begin{equation}
\label{eq:targetcost}
Z\left(\tau,\delta\right) =
\sum\limits_{
	\substack{
	\mathrm{cohort} \\ \in{\left\{70,72,74,76\right\}}}
	}
\left\{\delta\cdot
\int_{\epsilon}
\int_{Y_{min}}^{F_{Y}^{-1}\left(\tau\right)}
\int_{X}
N\Big(
\substack{
	Y,X,\epsilon; \\
	\delta, \Gamma_{\mathrm{cohort}}
}
\Big)f\left(X|Y\right)f\left(Y\right)f\left(\epsilon\right)\mathrm{d}X\mathrm{d}Y\mathrm{d}\epsilon\right\}
\end{equation}
$$
</div>

# Equations New Command

\newcommand{\target}{
\begin{equation}
Z\left(\tau,\delta\right) =
\sum\limits_{
	\substack{
	\mathrm{cohort} \\ \in{\left\{70,72,74,76\right\}}}
	}
\left\{\delta\cdot
\int_{\epsilon}
\int_{Y_{min}}^{F_{Y}^{-1}\left(\tau\right)}
\int_{X}
N\Big(
\substack{
	Y,X,\epsilon; \\
	\delta, \Gamma_{\mathrm{cohort}}
}
\Big)f\left(X|Y\right)f\left(Y\right)f\left(\epsilon\right)\mathrm{d}X\mathrm{d}Y\mathrm{d}\epsilon\right\}
\end{equation}
}

Equation defined as new command with different zoom:

<span style="font-size:10%;"> $$\target$$ </span>
<span style="font-size:20%;"> $$\target$$ </span>
<span style="font-size:30%;"> $$\target$$ </span>
<span style="font-size:40%;"> $$\target$$ </span>
<span style="font-size:50%;"> $$\target$$ </span>

### 2020-02-07 nontex/revealjsrmd/test_tex.Rmd
rmd math and tex

@@
 # Overview
+
+<!--
+decktape convert to PDF
+cd "C:/Users/fan/Tex4Econ/nontex/revealjsrmd/"
+decktape automatic test_tex.html test_tex.pdf
+-->
 
@@
 
-# Equations New Command
+# Equations Space Saving
+
+The paper latex file already contains various newcommands pre-defined, want to share those latex files with RMD.
+
+## New Command Define First
+
+Define long newcommand in RMD and show equation multiple times.
 
@@
 <span style="font-size:50%;"> $$\target$$ </span>
+
+## INclude Equations and Symbols Defined Elsewhere
+
+```{r echo=TRUE, eval=FALSE}
+{r child = 'test_tex_define.tex'}
+```
+
+```{r child = 'test_tex_define.tex'}
+```
+
+<span style="font-size:40%;"> $$\exa$$ </span>
+<span style="font-size:40%;"> $$\exb$$ </span>
+<span style="font-size:40%;"> $$\exc$$ </span>

### 2020-02-18 _other/tikz/tree/fs_tikz_gametree.tex
game tree theta phi

@@
 \usepackage{subcaption}
+\usepackage{relsize} % make some math large
+\usepackage{bm} % make some math bold
 
@@
     % Y-shift to move level 3 child node lower
-    [purple] node(2)[solid node, xshift=30, yshift=-50, label=right:{hello}]{}
+    [red]  % this is the style of the line middle line
+        node(2)[solid node, xshift=30, yshift=-50, label=right:{hello}]{} % this is the style of the middle point that would have matched up the middle line        
     % D.1 Left level 3 (from middle level 2)
@@
     edge from parent
+        % draw none here prevents the middle line extending rom P1 to hello to be drawn
+        [draw=none]
         %note that you need to adjust the yshift if you change the level distance
@@
     child{
-        [black] node(21)[]{}
+        [blue] node(21)[]{}
     }
@@
     child{
-        [black] node(23)[]{}
+        [red] node(23)[]{}
     }
@@
 child{
-    [black] node(13)[]{}
+    [red] node(13)[]{}
 };
@@
 \begin{center}
-\begin{tikzpicture}[scale=1.5,font=\footnotesize]W
+\begin{tikzpicture}[scale=1.5,font=\footnotesize]
 \tikzstyle{level 1}=[level distance=\famm,sibling distance=\famm]
@@
 
+\subsection{Spanning Multi--Tree with Text as a part of Timeline}
+
+Two spanning continuous choices, with text on boundary, clear descriptions. inside of what choices are made. Then inset this as a part of a longer timeline.
+
+\subsubsection{Two Nodes and Text Along Edges}
+
+Draw nodes and branches, no text, no bending, no coloring.
+
+\def\famm{13mm}
+\begin{center}
+\begin{tikzpicture}[scale=1.5,font=\footnotesize]
+\tikzstyle{level 1}=[level distance=\famm,sibling distance=\famm]
+\tikzstyle{level 2}=[level distance=\famm,sibling distance=\famm]
+% B Level 1 point
+\node(0)[solid node, % solid node gives fist (left to right) black dot
+         label=left:{
+            $\textcolor{black}{\mathlarger{\mathlarger{\mathlarger{\bm{\phi}}}}}$
+             }]{}
+[grow=right]
+child{ 
+    [black] node(11)[]{}
+    edge from parent
+            node[sloped, below, black]{$\phi=0$}
+}
+child{
+    [grow=right]
+    % The starting node for theta
+    node(12)[solid node, xshift=16, yshift=0, % solid node gives second (left to right) black dot
+                     label=left:{
+                        $\textcolor{black}{\mathlarger{\mathlarger{\mathlarger{\bm{\theta}}}}}$
+                     }]{}
+    % Draw the theta branches
+        child{
+            [red] node(21)[]{}
+            edge from parent
+                node[sloped, below, black]{$\theta=0$}
+        }
+        child{
+            [white] node(22)[xshift=16, yshift=0]{}        
+            edge from parent
+                [draw=none] % prevents a line to be drawn from phi to phi
+                node[above, black, xshift=7]{$k' = \theta \cdot \Lambda$}
+                node[below, black, xshift=10]{$b' = \Lambda - k'$}    
+        }
+        child{
+            [black] node(23)[]{}
+            edge from parent
+                node[sloped, above, black]{$\theta=1$}
+        }
+    edge from parent
+        [draw=none] % prevents a line to be drawn from phi to phi
+        % node[above, black, yshift=-55]{$c = \phi \cdot \Gamma$}
+        % node[below, black, yshift=-55]{$\Lambda = \left(1-\phi\right) \cdot \Gamma$}
+        node[above, black, xshift=4]{$c = \phi \cdot \Gamma$}
+        node[below, black, xshift=4]{$\Lambda = \Gamma - c$}
+        }
+child{
+    [red] node(13)[]{}
+    edge from parent
+            node[sloped, above, black]{$\phi=1$}
+};
+% information set
+\draw[dashed, bend right]
+    (11) to (13);
+\draw[dashed, bend right]
+    (21) to (23);
+\end{tikzpicture}
+\end{center}
+
+% child{
+%     % C.1.a Node line color
+%     [red]
+%     % C.1.b Node dot
+%     node(1)[solid node, label=below:{red dot}]{}
+%     % C.1.c now go to edge
+%     edge from parent
+%         % C.1.c Node along edge
+%         node[sloped, above, black, text width=3cm]{Minimum Choice showing up along this red line}
+%     }
+
 % \begin{istgame}[font=\scriptsize]

### 2020-02-23 _other/tikz/tree/fs_tikz_gametree.tex
more tree changes

@@
 
+\subsubsection{State Node and Choice Nodes}
+
+States Nodes, Realizations, and then Continuous and Discrete Choice Nodes
+\def\famm{5mm}
+\def\fammlong{20mm}
+\begin{center}
+\begin{tikzpicture}[scale=1.5,font=\footnotesize]
+\tikzstyle{level 1}=[level distance=\fammlong,sibling distance=\famm]
+\tikzstyle{level 2}=[level distance=\fammlong,sibling distance=\famm]
+\tikzstyle{level 3}=[level distance=\famm,sibling distance=\famm]
+\tikzstyle{level 4}=[level distance=\famm,sibling distance=\famm]
+\tikzstyle{level 5}=[level distance=\famm,sibling distance=\famm]
+
+% B Level 1 point
+\node(0)[solid node, red, label=left:{
+    $k,b$ chosen
+    }]{}
+[grow=right]
+child{
+    [grow=right]
+    node(1)[solid node, blue, label=left:{
+        $\Gamma$ realized 
+        }]{}
+    edge from parent
+        [draw=none]
+    child{
+        [grow=right]
+        node(2)[solid node, black, label=left:{$P1$}]{}
+        edge from parent
+            [draw=none]
+        child{
+            [black] node(11)[]{}
+        }
+        child{
+            [grow=right]
+            [white] node(12)[solid node, xshift=7.5, yshift=0]{}
+            child{
+                [black] node(21)[]{}
+            }
+            child{
+                [grow=right]
+                [white] node(22)[solid node, xshift=7.5, yshift=0]{}
+                child {
+                    [black] node(31)[]{}
+                }
+                child{
+                    [black] node(32)[]{}
+                }
+                child{
+                    [black] node(33)[]{}
+                }
+                child{
+                    [black] node(34)[]{}
+                }
+            }
+            child{
+                [black] node(23)[]{}
+            }
+        }
+        child{
+            [black] node(13)[]{}
+        }
+    }
+};
+% information set
+\draw[dashed, bend right]
+    (11) to (13);
+\draw[dashed, bend right]
+    (21) to (23);
+\draw[dotted, line width=0.35mm]
+    (2) to (12);
+\draw[dotted, line width=0.35mm]
+    (12) to (22);
+\end{tikzpicture}
+\end{center}
+
 \subsection{Spanning Multi--Tree with Text as a part of Timeline}

### 2020-02-23 nontex/install/windows/fn_installations.Rmd
dcase larger fraction in case mode mathtools
more tree changes

@@
 - sync: *ctrl + alt + j*
+- terminate pdflatex compile hang: *ctrl + shift + p; kill latex compiler process*
 - live save
@@
 
+- [sublime markdown Monokai Extended](https://github.com/jonschlinkert/sublime-monokai-extended), [sublime markdown extended](https://github.com/jonschlinkert/sublime-markdown-extended)
+
 ### PyCharm

### 2020-04-09 _other/pandoc/fansample.tex
Tex etc updates
pandoc typo

@@
 \usepackage{hyperref}
+\hypersetup{
+    colorlinks=true,
+    linkcolor=blue,
+    filecolor=magenta,
+    urlcolor=cyan,
+}
 
@@
 % Titling and Author
-\title{Sandbox Testing Latex}
+\title{Latex Example, Pandoc Conversion}
 \author{Fan Wang (University of Houston)}
@@
 \begin{enumerate}
-	\item \textit{run this for word to tex}: pandoc --bibliography=fansample.bib -o fansample.docx fansample.tex
+	\item \textit{run this for tex to word with bib}: pandoc --bibliography=fansample.bib -o fansample.docx fansample.tex
 \end{enumerate}

### 2020-04-20 nontex/git/g_basics/git_basics.Rmd
python poetry installation guides

---
title: "Basic Git Commands"
output:
  pdf_document: default
  word_document: default
  html_document: default
  html_notebook: default
urlcolor: blue
always_allow_html: yes
---

### Basic Git Commands

#### Check File Status

Check if a particular file has had local changes that have not been commited yet.

Use the [*git status*](https://git-scm.com/docs/git-status) command, with short *-s* option:

- *modified*: the *grepl(' M ')* check will be true
- *new*: the *grepl('?? ')* check will be true
- *existing no change*: the *(st_git_status == "")* check will be true

```{r}
spg_modified <- 
  paste0('git status -s',
         'C:/Users/fan/R4Econ/amto/array/fs_ary_mesh.Rmd')
spg_anewfile <- 
  paste0('git status -s',
         'C:/Users/fan/R4Econ/math/differentiation/fs_differentiate_lhopital.Rmd')
spg_nochange <- 
  paste0('git status -s',
         'C:/Users/fan/R4Econ/math/func_ineq/fs_atkinson_ces.Rmd')

st_git_status <- toString(system(spg_modified, intern=TRUE))
grepl(' M ', st_git_status, fixed=TRUE)
grepl('?? ', st_git_status, fixed=TRUE)
(st_git_status == "")

st_git_status <- toString(system(spg_anewfile, intern=TRUE))
grepl(' M ', st_git_status, fixed=TRUE)
grepl('?? ', st_git_status, fixed=TRUE)
(st_git_status == "")

st_git_status <- toString(system(spg_nochange, intern=TRUE))
grepl(' M ', st_git_status, fixed=TRUE)
grepl('?? ', st_git_status, fixed=TRUE)
(st_git_status == "")
```

### 2020-04-20 nontex/install/windows/fn_installations.Rmd
python poetry installation guides

@@
 
+# Python Testing and Installation with Poetry and Docs
+
+Locally test specially functions in [poetry](https://python-poetry.org/docs/#installation) environment. Push to github and Pypi, and then install via pip for system wide use.
+
+## Poetry
+
+1. If a module requires another dependency: *poetry add numpy*, if adding numpy. This will install in the virtual env *numpy*.
+2.
+Type in *poetry env info*, and copy path: *C:/Users/fan/AppData/Local/pypoetry/Cache/virtualenvs/py4econ-6xnVtByB-py3.7*, to pycharm, so that can test module in pycharm using the poetry generated isolated packaging testing env.
+    + in Pycharm: Settings (ctrl+alt+s) > Project > Python interpreter > click on the cog, "Add" > Right menu, "Virtual Environement" > Existing environement > Three dots > paste the path and point it to the python.exe in Scripts
+3. When finished, *build* and *publish*
+
+```{bash}
+rm -rf dist/ build/
+poetry install
+poetry build 
+poetry publish
+# provide pypi username and password
+```
+
+## Local Install
+
+```{bash}
+pip install --no-index --find-links="C:/Users/fan/Py4Econ/dist/fantools-0.0.0.900.tar.gz" fantools --ignore-installed
+```
+
+## Pypi Install
+
+Open up conda prompt, pip install from base. Will install dependencies of package that are in the poetry env but not otherwise in python installation main path.
+
+```{bash}
+pip install git+https://github.com/fanwangecon/Py4Econ.git#egg=fantools
+
+pip install fantools --ignore-installed
+pip show fantools
+```
+
+```{python}
+import fantools as fantools
+
+```
+
+## sphinx and readthedocs
+
+readthedocs is logged in via github account. Automatically recognizes github repositories, and can import repositories to generate documentation that it can.
+
+1. install sphinx
+
+```{bash}
+pip install sphinx
+cd ~/Py4Econ
+mkdir docs
+sphinx-quickstart
+make html
+```
+
+### autodoc
+
+[Documenting Python Packages with Sphinx and ReadTheDocs](https://brendanhasz.github.io/2019/01/05/sphinx.html)
+
+The Napoleon extension for Sphinx allows for NumPy/Google style docstrings instead of using the hard-to-read reStructuredText in your docstrings
+
+> The autodoc extension for sphinx can automatically generate API reference doc pages from the docstrings in your python code.
+Python docstrings are string literals which occur immediately after function or class definitions.
+They’re treated as comments, and it’s customary to document a function or class in its docstring.
+The autodoc extension allows you to include reStructuredText in your docstrings, and will build an API reference automatically for your module from the docstrings, while allowing for further customization.
+
+To enable the autodoc extension, in your conf.py file, add the string 'sphinx.ext.autodoc' to the extensions list (this should have already been done if you answered yes to enabling the autodoc extension during sphinx-quickstart).
+
+```{python}
+# If extensions (or modules to document with autodoc) are in another directory,
+# add these directories to sys.path here. If the directory is relative to the
+# documentation root, use os.path.abspath to make it absolute, like shown here.
+#
+# import os
+# import sys
+# sys.path.insert(0, os.path.abspath('.'))
+```
+
+After enabling autodoc, in the documentation’s .rst files, you can use the automodule directive:
+
+.. automodule:: package_name.module
+   :members:
+
+.. autosummary::
+   :toctree: _autosummary
+
+   fantools.utility
+   fantools.utility.inout
+   fantools.utility.inout.bookdownparse
+   fantools.utility.inout.rmdparse
+   fantools.utility.timer
+
+### rst
+
+= for page titles,
+- for sections,
+^ for subsections, and
+" for subsubsections.
+
+Bulleted lists use asterisks, numbered lists use numbers, and nesting is done with indentation, like Markdown (though nested lists need to be surrounded by blank lines):
+
+* Bulleted
+* list
+
+  * nested
+  * list
+
+* con't
+
+1. Numbered
+2. list
+
+``Code sample``
+
+For hyperlinks, use:
+
+`Link text <http://www.link-address.com>`_
+
+Commented lines begin with two periods and a space (like a directive w/o the double colons):
+
+.. I'm a comment!
+And multiline comments are also like directives w/o the colons:
+
+..
+   I am
+   a multiline
+
+   comment
+
+## Python, Poetry, Docs, Git
+
+Start from without a package. Create two packages: pyecon, pyfan
+
+1. generate poetry repos first, before adding in .git with pull_repos
+2.
+
+```{bash}
+cd ~
+poetry new pyfan
+
+cd ~
+poetry new pyecon
+
+base ~/base/bin/pull_repos
+
+cd ~/pyfan
+cd "C:/Users/fan/pyfan"
+mkdir docs
+<!-- change release number conf.py and .toml -->
+<!-- sphinx-quickstart -->
+make html
+poetry build 
+poetry publish
+
+cd ~/pyecon
+cd "C:/Users/fan/pyecon"
+mkdir docs
+poetry build 
+poetry publish
+sphinx-quickstart
+make html
+
+poetry env info
+<!-- get virtual env info  -->
+```
+
+install git locally so can use outside of env
+
+pip install git+https://github.com/fanwangecon/pyfan.git#egg=pyfan
+pip show pyfan
+
+> Name: pyfan
+> Version: 0.1.2
+> Summary:
+> Home-page: None
+> Author: Fan Wang
+> Author-email: wangfanbsg75@live.com
+> License: None
+> Location: c:\programdata\anaconda3\lib\site-packages
+> Requires:
+> Required-by:
+
+```{python}
+import pyfan.util.rmd.rmdparse as ft_rmdparse
+ft_rmdparse.fs_rmd_yml_parse()
+
+import pyfan.util.rmd.bookdownparse as ft_bookdownparse
+sfc_prj = 'R4Econ'
+sph_prj = 'C:/Users/fan/R4Econ/'
+spn_prj_bookdown_yml = '_bookdown.yml'
+spn_prj_readme_toc = 'README_toc_three.md'
+
+ft_bookdownparse.fs_yml2readme(sfc_prj=sfc_prj, sph_prj=sph_prj,
+                          spn_prj_bookdown_yml=spn_prj_bookdown_yml,
+                          spn_prj_readme_toc=spn_prj_readme_toc)
+```
+
 # Python and Anaconda Installation
@@
 
+## Install Packages
+
+Note that some packages are dependencies for fantools and fanecon packages, they would be installed jointly with those packages.
+
+```{bash}
+pip install --user --upgrade setuptools wheel
+pip install sphinx
+pip install fantools --ignore-installed
+```
+
 ## Python Command Line Test
@@
 ### Install Packages for R
+
+What are the packages I need in R:
+
+**Use Multiple Languages**:
+
+- [reticulate](https://github.com/rstudio/reticulate)
+
+**Visualization, Packaging Etc**:
+
+- [bookdown](https://bookdown.org/)
+- [formatR](https://cran.r-project.org/web/packages/formatR/index.html): to tidy up rmd chunks
 
@@
 
+#### Sublime and Outline (Markdown)
+
+To get the markdown outline of the current document if it is markdown press *Ctrl + R*, shows tabbed nested outline view.
+
+#### Sublime Search and Replace
+
+Append to end of all lines with starting string some suffix.
+We have many lines that start with *print('abc')*, but the printed statements differ in length.
+Within the document, want to change all print statements to message statements, and have: *message(print('abc'))*:
+
+1. cursor select *print(*
+2. *alt + F3*, this selects all occurances
+3. *ctrl + end*, moves cursor to end of each line, any other single cursor point speicifc left right end start operation should work
+4. append new text suffix
+5. *ctrl + home*, move cursor to the start of all print lines, and append prefix as needed.
+
 ### PyCharm

### 2020-04-28 _support/docu/hierarchy/flatten.Rmd
over and unber bar, bold or not. bm mand accents package.

---
title: "Tex Flatten Subdirectory files to Root"
titleshort: "Tex Flatten Subdirectory files to Root"
description: |
  Working directory has multiple subfolders, folders, and refer to input files, flatten all into one level without subfolders.
  Extract subdirectory files to main directory and edit main file links.
core:
  - package: tex
    code: |
      tex
date: 2020-04-27
date_start: 2020-04-27
output:
  pdf_document:
    pandoc_args: '../../_output_kniti_pdf.yaml'
    includes:
      in_header: '../../preamble.tex'
  html_document:
    pandoc_args: '../../_output_kniti_html.yaml'
    includes:
      in_header: "../../hdga.html"
always_allow_html: true
urlcolor: blue
---

### Flatten Latex File

```{r global_options, include = FALSE}
try(source("../../.Rprofile"))
```

`r text_shared_preamble_one`
`r text_shared_preamble_two`
`r text_shared_preamble_thr`

- latex automatically extract \input to put in same file
- [Replace \input{fileX} by the content of fileX automatically](https://tex.stackexchange.com/questions/21838/replace-inputfilex-by-the-content-of-filex-automatically/21840)

Can use Pandoc, but pandoc conversion leads to all incorrect labels, confusing references.

```{bash}
cd "C:\Users\fan\Documents\Dropbox (UH-ECON)\Project Emily Minority Survey\Drafts_RR\ChinaSchoolClosure"
pandoc -s draft_edcc_submit_rr.tex -o draft_edcc_submit_rr_flat.tex
```

use latexpand

```{bash}
conda activate wk_perl
cd "C:\Users\fan\Documents\Dropbox (UH-ECON)\Project Emily Minority Survey\Drafts_RR\OverleafChinaSchoolClosure"
perl "C:\Users\fan\.conda\envs\wk_perl\latexpand\latexpand" draft_main.tex > draft_main_flat.tex
```

### 2020-04-28 nontex/install/linux/fn_ubuntu.Rmd
over and unber bar, bold or not. bm mand accents package.

@@
 # generate repo directory and sync
-mkdir ~/PyFan
-# mkdir fanwangecon.github.io PyFan Tex4Econ R4Econ M4Econ Py4Econ Teaching
-cd ~/PyFan
+mkdir ~/base
+# mkdir fanwangecon.github.io base Tex4Econ R4Econ M4Econ Py4Econ Teaching
+cd ~/base
 git init
@@
 git config --global user.email wangfanbsg75@live.com
-git remote add github git@github.com:FanWangEcon/PyFan.git
+git remote add github git@github.com:FanWangEcon/base.git
 git pull github master
@@
 # could be saved in download folder: ~/Downloads
-wget https://repo.anaconda.com/archive/Anaconda3-2019.10-Linux-x86_64.sh
+wget https://repo.anaconda.com/archive/Anaconda3-2020.02-Linux-x86_64.sh
 # install file
-bash "Anaconda3-2019.10-Linux-x86_64.sh"
+bash "Anaconda3-2020.02-Linux-x86_64.sh"
 # refresh
@@
 ```{r}
-conda install -y statsmodels datashape seaborn
+# Install poetry 
+curl -sSL https://raw.githubusercontent.com/python-poetry/poetry/master/get-poetry.py | python
+# Install pyecon pyfan
+pip install pyfan
+
+# conda install -y statsmodels datashape seaborn
 # conda install statsmodels
@@
 
-conda install -c conda-forge -y interpolation awscli
+# conda install -c conda-forge -y interpolation awscli
 # conda install -c conda-forge interpolation
@@
 
-conda install -c anaconda -y boto3
-
+# conda install -c anaconda -y boto3
 # conda install -c r r-irkernel

### 2020-04-28 nontex/install/windows/fn_installations.Rmd
over and unber bar, bold or not. bm mand accents package.

@@
 
-1. Python (Anaconda, Pycharm + VSCode + Atom)
+1. Python (Anaconda, Pycharm + VSCode + Atom, Poetry)
 2. R (VSCode + Atom)
@@
 
-Locally test specially functions in [poetry](https://python-poetry.org/docs/#installation) environment. Push to github and Pypi, and then install via pip for system wide use.
+When to use Python:
+
+1. Main use Python for Dynamic programing type tasks
+2. All immediate data tasks should be done in R, including things like generating data structures. Also graph generation in R.
+3. Certain basic tabulation summary statistics etc things done in Stata
+
+Two types of python usage cases:
+
+1. Small chunks of python code in RMD for tutorial/class files, combine files in book format as bookdown.
+2.
+Python installable packages and modules created with poetry, push to github as pypi: Locally test specially functions in [poetry](https://python-poetry.org/docs/#installation) environment.
+Push to github and Pypi, and then install via pip for system wide use.
+
+Installations:
+
+1. Python package development in poetry virtual environment, install with needed dependencies.
+	- This means, during python package development, do not install the packages needed directly in conda, but add as dependency in Poetry
+2. General environment with pip installed packages and conda installed path discoverable pathon packages for rmd chunks.
 
@@
 
-1. If a module requires another dependency: *poetry add numpy*, if adding numpy. This will install in the virtual env *numpy*.
-2.
-Type in *poetry env info*, and copy path: *C:/Users/fan/AppData/Local/pypoetry/Cache/virtualenvs/py4econ-6xnVtByB-py3.7*, to pycharm, so that can test module in pycharm using the poetry generated isolated packaging testing env.
-    + in Pycharm: Settings (ctrl+alt+s) > Project > Python interpreter > click on the cog, "Add" > Right menu, "Virtual Environement" > Existing environement > Three dots > paste the path and point it to the python.exe in Scripts
-3. When finished, *build* and *publish*
-
-```{bash}
+Install Python via Anaconda first following other instructions. Possibly cleanly uninstall and reinstall. Use Poetry to build python packages and modules.
+
+For development machines, install [Poetry](https://github.com/python-poetry/poetry) and nstall [sphinx](https://www.sphinx-doc.org/en/master/).
+
+```{bash}
+# poetry
+curl -sSL https://raw.githubusercontent.com/python-poetry/poetry/master/get-poetry.py | python
+# sphinx
+pip install sphinx
+```
+
+Initialize a Poetry-style Python Package and add Sphinx style docs. This creates the folder *~/pyfan* and initialize it with various:
+
+```{bash}
+# creates ~/pyfan as poetry packaging
+cd ~
+poetry new pyfan
+
+# sphinix quickstart
+cd ~/pyfan
+mkdir docs
+sphinx-quickstart
+make html
+
+# build empty package
 rm -rf dist/ build/
@@
 poetry publish
-# provide pypi username and password
-```
-
-## Local Install
-
-```{bash}
-pip install --no-index --find-links="C:/Users/fan/Py4Econ/dist/fantools-0.0.0.900.tar.gz" fantools --ignore-installed
-```
-
-## Pypi Install
+
+# What is the virtual Env id
+poetry env info
+```
+
+### Installating Poetry Created Packages
+
+Normally install/test/use inside conda virtual env or poetry virtual env.
+Poetry would install with *poetry add* and *poetry install*.
+After seeing some package of interest on github etc, see if the package is on pypi.
+pip install from pypi if possible.
+
+Local Install
+
+```{bash}
+pip install --no-index --find-links="C:/Users/fan/Py4Econ/dist/pyfan-0.0.0.900.tar.gz" pyfan --ignore-installed
+```
+
+Pypi Install
 
@@
 ```{bash}
-pip install git+https://github.com/fanwangecon/Py4Econ.git#egg=fantools
-
-pip install fantools --ignore-installed
-pip show fantools
-```
-
-```{python}
-import fantools as fantools
-
+pip install git+https://github.com/fanwangecon/pyfan.git#egg=pyfan
+pip install pyfan --ignore-installed
+pip show pyfan
+```
+
+Sometimes, someone ports a package and adds certain things that I need, so need to install from git a package whose modified version is not on pypi, then use git+https
+
+#### What are egg, tar.gz, whl?
+
+poetry creates tar.gz and whl in the dist folder, what are they?
+
+- tarballs: tar.gz
+
+### Developing and testing new tools Pycharm + Poetry
+
+When tesing and developing tools, do so in the poetry virtual environment for the package in which testing is taking place.
+
+After a package has been created and poetry built and poetry publish:
+
+1.
+Type in *poetry env info*, and copy for example path: *C:/Users/fan/AppData/Local/pypoetry/Cache/virtualenvs/py4econ-6xnVtByB-py3.7*, to pycharm, so that can test module in pycharm using the poetry generated isolated packaging testing env.
+2. In Pycharm: Settings (ctrl+alt+s), Project, Python interpreter.
+3. Click on the cog button, "Add" > Right menu, "Virtual Environement" > Existing environement > Three dots > paste the path and point it to the python.exe in Scripts
+
+```{bash}
+poetry env info
+```
+
+When a particular tool is needed to build this new module inside package, add the tool via poetry add as a dependency.
+If a module requires another dependency: *poetry add numpy*, if adding numpy.
+This will install in the virtual env *numpy*.
+When packages are added, they are automatically installed.
+When the the *pyfan* package repo is downloaded somewhere, the dependencies might not be installed yet, and *poetry install* would install them.
+
+```{bash}
+poetry add numpy
+```
+
+#### Development for pyfan
+
+pyfan is the general python tools package for various projects, not economics related directly.
+
+Poetry added dependencies are in */pyfan/pyproject.toml*, Poetry add:
+
+```{bash}
+cd "C:/Users/fan/pyfan"
+cd ~/pyfan
+poetry env info
+```
+
+All installations:
+
+```{bash}
+poetry remove python-frontmatter pyyaml
+poetry add python-frontmatter pyyaml
+```
+
+Poetry modules added over time:
+
+```{bash}
+# 2020-04
+poetry add pyyaml
+poetry add python-frontmatter
+```
+
+After modules are added and new programs developed
+
+```{bash}
+cd ~/pyfan
+cd "C:/Users/fan/pyfan"
+poetry install
+make html
+rm -rf dist/ build/
+poetry build
+poetry publish
+```
+
+On some local computer install pyfan:
+
+```{bash}
+pip show pyfan
+# conda activate pyfan
+pip install pyfan
+```
+
+##### Uninstall
+
+uninstall packages in the overall environment
+```{bash}
+# list all installed packages
+pip list
+pip show pyyaml
+pip show python-frontmatter
+pip show pyfan
+# unstall packages
+pip uninstall pyyaml
+pip uninstall python-frontmatter
 ```
@@
 
-## First Time Conda Install
+## Anaconda Install
+
+### First Time Conda Install
 
@@
 ###############################
+# C:\ProgramData\Anaconda3
 # C:\ProgramData\Anaconda3\Scripts
-# C:\ProgramData\Anaconda3
+# C:\ProgramData\Anaconda3\Scripts\bin
 ```
@@
 3. Add new to Path (lower half):
+    - C:/ProgramData/Anaconda3/
     - C:/ProgramData/Anaconda3/Scripts/
-    - C:/ProgramData/Anaconda3/
+    - C:/ProgramData/Anaconda3/Scripts/bin        
 4. Now open up regular windows command Prompt, Type in:
@@
 
-## Conda Update
+### Conda Update, Install, Channels
 
@@
 conda update --all
-
-# install additional packages
-# linux utilites
-conda install -y m2-base 
-# stats and graphs
-conda install -y statsmodels datashape seaborn
-# various
-conda install -c conda-forge -y interpolation awscli
-# aws communicate
-conda install -c anaconda -y boto3
-```
-
-## Install Packages
-
-Note that some packages are dependencies for fantools and fanecon packages, they would be installed jointly with those packages.
+```
+
+### Conda Environments
+
+For testing installed packages.
+Note that for development, using poetry for testing package dependencies for package development, and associate pycharm for projects with poetry virtual environments.
+The idea is that there might be dependency problems etc for packages depending on where/when they were made, might not work in the overall conda environment where pyfan and pyecon, my main tools are installed.
+Some specific task might only need one particular package.
+And when working on these, use a conda environment.
+When this works, could incorporate whatever I am working on into a pyfan, pyecon package along with other packages.
+
+```{bash}
+conda list env
+conda env remove -n test_package_name
+conda create -n test_package_name -y
+conda activate test_package_name
+conda list
+conda deactivate
+
+conda install pip
+
+# see if package exists on pip and install from pip
+pip install smop
+```
+
+#### Conda Perl Environment
+
+To run some perl tools in an isolated environment:
+
+1. [latexpand](https://tex.stackexchange.com/a/21840/109818)
+
+```{bash}
+# Set up
+conda list env
+conda env remove -n wk_perl
+conda create -n wk_perl -y
+conda activate wk_perl
+conda install -c anaconda perl
+conda list
+conda deactivate
+
+# intall packages in virtual env
+cd "C:\Users\fan\.conda\envs\wk_perl\"
+git clone https://gitlab.com/latexpand/latexpand.git
+
+# use latexpand
+conda activate wk_perl
+cd "C:\Users\fan\Documents\Dropbox (UH-ECON)\Project Emily Minority Survey\Drafts_RR\OverleafChinaSchoolClosure"
+perl "C:\Users\fan\.conda\envs\wk_perl\latexpand\latexpand" draft_edcc_submit_rr.tex > draft_edcc_submit_rr_flat.tex
+```
+
+#### Conda Jinja Environment
+
+For testing and packaging latex files. In particular, single folder latex files for final paper submissions.
+
+```{r}
+# Set up
+conda deactivate
+conda list env
+conda env remove -n wk_jinja
+conda create -n wk_jinja -y
+conda activate wk_jinja
+conda install -c anaconda jinja2
+conda install -c anaconda pyyaml
+
+# use yaml2tex
+cd "C:\Users\fan\Documents\Dropbox (UH-ECON)\repos\fanwangecon.github.io\_cv\templating\"
+python yaml2tex.py
+```
+
+## Essential Programs to Install
+
+Install Packages, note that some packages are dependencies for fantools and fanecon packages, they would be installed jointly with those packages.
 
@@
 
-## Python Command Line Test
-
-Fist test python under command line:
+Previously:
+
+```{bash}
+# install additional packages
+# linux utilites
+# conda install -y m2-base
+# stats and graphs
+# conda install -y statsmodels datashape seaborn
+# various
+# conda install -c conda-forge -y interpolation awscli
+# aws communicate
+# conda install -c anaconda -y boto3
+```
+
+## Fist test python under command line:
 
@@
 
+- [pandoc](https://pandoc.org/installing.html)
 - 7-zip

### 2020-04-29 nontex/revealjsrmd/test_img.Rmd
realjs rmd include tex preamble, clean tex comments, includechild

@@
 <!--
-decktape convert to PDF
+# decktape convert to PDF
 cd "C:/Users/fan/Tex4Econ/nontex/revealjsrmd/"

### 2020-04-29 nontex/revealjsrmd/test_tex.Rmd
realjs rmd include tex preamble, clean tex comments, includechild

@@
 decktape convert to PDF
-cd "C:/Users/fan/Tex4Econ/nontex/revealjsrmd/"
+cd "C:/Users/fan/Documents/Dropbox (UH-ECON)/repos/Tex4Econ/nontex/revealjsrmd/"
 decktape automatic test_tex.html test_tex.pdf
@@
 
-## INclude Equations and Symbols Defined Elsewhere
+## Include Equations and Symbols Defined Elsewhere
+
+Reuse tex preamble from paper, load as child, and clean comments.
 
 ```{r echo=TRUE, eval=FALSE}
-{r child = 'test_tex_define.tex'}
+# This loads the tex preamble with predefined formula, reuseable symbols etc.
+test_tex_define_out = knitr::knit_child('test_tex_define.tex')
+# Delete all comment lines, which starts with percent, and end with carriage return
+# This deletes all but the last line
+test_tex_define_out = gsub("\\%.*?\\\n", "", test_tex_define_out)
+# Delete last comment if on final line
+test_tex_define_out = gsub("\\\n%.*","", test_tex_define_out)
 ```
 
-```{r child = 'test_tex_define.tex'}
+```{r include=FALSE, eval=TRUE}
+test_tex_define_out = knitr::knit_child('test_tex_define.tex')
+test_tex_define_out = gsub("\\%.*?\\\n", "", test_tex_define_out)
+test_tex_define_out = gsub("\\\n%.*","", test_tex_define_out)
 ```
+
+`r paste(test_tex_define_out, collapse='\n')`
 

### 2020-05-15 _support/docu/fs_comment.tex
timelime improvements, bold symbol, etc. revealjs tests.

--- 2019-12-22 _other/tikz/annotate/fs_tikz_annotate.tex
@@
-\documentclass{article}
+\documentclass[12pt,english]{article}
+\usepackage[utf8]{inputenc}
 
-\usepackage{blindtext}
-\usepackage{multicol}
-\usepackage{caption}
-\usepackage{bm}
-\usepackage{tikz}
-\usepackage{pgfplots}
+% url package
 \usepackage{hyperref}
@@
 }
-\usepackage{geometry}
-\geometry{
-	a4paper,
-	noheadfoot=true,
-	left=1.0in,
-	right=1.0in,
-	top=1.0in,
-	bottom=1.0in
-}
-
-% url package
-\usepackage{hyperref}
-\usepackage{subcaption}
+% Bibliography package
+\usepackage[authordate, backend=biber]{biblatex-chicago}
+\bibliography{fansample}
 
 % Titling and Author
-\title{Latex Tikz Examples, Annotate on Graph}
+\title{Latex Preamble}
 \author{\href{https://fanwangecon.github.io/}{Fan Wang}\thanks{https://fanwangecon.github.io, repository: \href{https://fanwangecon.github.io/Tex4Econ/}{Tex4Econ}}}
@@
 
-\maketitle
-
-\section{Annotate Text in Figure}
-
-\subsection{Slope and Intercept Annotate}
-
-Draw axis below, and a line, middle of page, and annotate the slope of the intercept with arrows. Annotate with box without color.
+Comment will not appear with percent in front
 
 \begin{verbatim}
-\begin{center}
-\begin{tikzpicture}
-\draw (0,2) -- (0.25*\textwidth,2);
-\draw (0,1) -- (0.5*\textwidth,1);
-\end{tikzpicture}
-\end{center}
+% Comment
 \end{verbatim}
-\bigskip
-\begin{center}
-\begin{tikzpicture}
-\draw[->] (-1,0) -- (6,0) node[right] {$N_m$};
-\draw[->] (0,-1) -- (0,6) node[above] {$N_{m^{\prime}}$};
+% Comment
 
-% A. Clip area so that line below is only drawn inside finite box
-\clip (-3,-1) rectangle (6,6);
+yml block?
 
-% B. Draw a line with intercept and slope
-\draw[line width=0.50mm,domain=-1:6,smooth,variable=\x, blue] plot ({\x},{1+\x*1.25});
+\begin{verbatim}
+<!-- regular html comment -->
+\end{verbatim}
 
-% C. Draw Line pointing to Intercept of line
-\draw[->, line width=0.75mm] (-1.7,2.2) -- (-0.1,1.1);
-
-% D. Draw a transparent text box that wraps text
-\node[text width=3cm] at (-1.4,3.25) {\large{$\bm{\alpha_i}$ (this is the position of the \textbf{x-intercept}), wrap text.}};
-
-\end{tikzpicture}
-\end{center}
+<!-- regular html comment -->
 

### 2020-05-15 nontex/install/windows/fn_installations.Rmd
timelime improvements, bold symbol, etc. revealjs tests.

@@
 # use yaml2tex
+cd "C:\Users\fan\Documents\Dropbox (UH-ECON)\repos\fanwangecon.github.io\_cv\templating\"
+python yaml2tex.py
+```
+
+#### Conda revealjs nodejs Environment
+
+revealjs, decktape to pdf conversions
+
+```{r}
+# Set up
+conda deactivate
+conda list env
+conda env remove -n wk_nodejs
+conda create -n wk_nodejs -y
+conda activate wk_nodejs
+
+conda install -c conda-forge nodejs -y
+# ended up downloading installer for windows nodejs and installing out of conda
+# was having lots of bugs
+npm i -g --production windows-build-tools
+npm install -g --force decktape
+# use yaml2tex
+
 cd "C:\Users\fan\Documents\Dropbox (UH-ECON)\repos\fanwangecon.github.io\_cv\templating\"
@@
 
-## Other Editors
-
-### Notepad++
-
-[Notepad++](https://notepad-plus-plus.org/downloads/v7.8.2/). Many old projects have xml folder structures for Notepad++.
-
-- Silently update file changes made in other editors: Settings, Preferences, MISC., File Status Auto Detection, Update Silently.
-
-### Sublime
+## Sublime
 
@@
 
-#### Sublime and Outline (Markdown)
+### Sublime and Outline (Markdown)
 
@@
 
-#### Sublime Search and Replace
+### Sublime Search and Replace
 
@@
 
-### PyCharm
+## PyCharm
 
 [pycharm](https://www.)jetbrains.com/pycharm/)
+
+### PyCharm Short Cuts
+
+- Auto-Indent: *CTRL + SHIFT + ALT + L*
+
+## Other Editors
+
+### Notepad++
+
+[Notepad++](https://notepad-plus-plus.org/downloads/v7.8.2/). Many old projects have xml folder structures for Notepad++.
+
+- Silently update file changes made in other editors: Settings, Preferences, MISC., File Status Auto Detection, Update Silently.
 
@@
 - [pandoc](https://pandoc.org/installing.html)
+- [nodejs](https://nodejs.org/en/) (revealjs pdf conversion)
 - 7-zip

### 2020-05-15 nontex/revealjsrmd/math_tests/fragments/preamble_main.tex
timelime improvements, bold symbol, etc. revealjs tests.

\input{../fragments/preamble_one.tex}
\input{../fragments/preamble_two.tex}

% Special String Shorthands
\input{../fragments/shorthand/short_text_syms.tex}
\input{../fragments/shorthand/short_math.tex}
\input{../fragments/shorthand/short_math_param.tex}
\input{../fragments/shorthand/short_math_var.tex}
\input{../fragments/shorthand/short_math_slopeintercept.tex}
\input{../fragments/shorthand/short_math_esti_space.tex}
\input{../fragments/shorthand/short_math_ces_prod.tex}

\input{../fragments/shorthand/short_math_ntw.tex}
\input{../fragments/shorthand/short_support.tex}

### 2020-05-15 nontex/revealjsrmd/math_tests/fragments/shorthand/short_support.tex
timelime improvements, bold symbol, etc. revealjs tests.

% Various supporting strings
% \newcommand{\papertitle}{Optimal Targeting Queues}
% \newcommand{\papertitle}{From Efficiency to Equity: the Optimal Allocation of Discrete and Continuous Resources Among Heterogeneous Individuals}
\newcommand{\papertitle}{The Optimal Allocation of Resources Among Heterogeneous Individuals}
% \newcommand{\papertitle}{The Allocative Implications of Empirical Estimates}
\newcommand{\paperauthor}{\href{https://fanwangecon.github.io}{Fan Wang}}
\newcommand{\urlpaper}{https://fanwangecon.github.io/assets/FanWang_OptimalTargetingQueue.pdf}
\newcommand{\urlrepo}{https://fanwangecon.github.io/PrjOptiAlloc/}
\newcommand{\thankszpart}[1]{This is a file that contains all #1\xspace from the paper ``\papertitle''. The paper's supporting website is \href{\urlrepo}{https://fanwangecon.github.io/PrjOptiAlloc/}. The full paper pdf can be found \href{https://fanwangecon.github.io/assets/FanWang_OptimalTargetingQueues.pdf}{here}}
\newcommand{\thanksmain}{Department of Economics, University of Houston (email: fwang26@uh.edu). The latest paper pdf can be found \href{https://fanwangecon.github.io/assets/FanWang_OptimalTargetingQueue.pdf}{here}. The paper's supporting website is \href{\urlrepo}{https://fanwangecon.github.io/PrjOptiAlloc/}.}

### 2020-05-15 nontex/revealjsrmd/math_tests/revealjs/present_test.Rmd
timelime improvements, bold symbol, etc. revealjs tests.

---
title: "Test RevealJS Loading Many Latex Files with Many Newcommands"
author: Fan Wang (fanwangecon.github.io)
date: May 4, 2020
output:
  revealjs::revealjs_presentation:
    theme: sky
    highlight: pygments
    center: false
    transition: none
    css: fan_present.css
    mathjax: local
    self_contained: false
    includes:
      in_header:
params:
    imgwidth: 25px
---

# Loading Many Latex Files with Many Newcommands

Need to avoid retyping latex newcommands which have many formated equations with parameters, symbols, and words that are concontrolled centrally.

# Loading Files from Another Directory

Usually the latex preamble files are stored somewhere else to work with the main paper draft tex file.

## Load Tex from the same folder

```{r echo=TRUE, eval=FALSE}
test_tex_define_out = knitr::knit_child('tex_preamble.tex')
test_tex_define_out = gsub("\\%.*?\\\n", "", test_tex_define_out)
test_tex_define_out = gsub("\\\n%.*","", test_tex_define_out)
```

```{r include=FALSE, eval=TRUE}
test_tex_define_out = knitr::knit_child('tex_preamble.tex')
test_tex_define_out = gsub("\\%.*?\\\n", "", test_tex_define_out)
test_tex_define_out = gsub("\\\n%.*","", test_tex_define_out)
```
`r paste(test_tex_define_out, collapse='\n')`

<span style="font-size:40%;"> $$\exa$$ </span>
<span style="font-size:40%;"> $$\exb$$ </span>
<span style="font-size:40%;"> $$\exc$$ </span>

## Load Tex from the parallel folder

```{r echo=TRUE, eval=FALSE}
test_tex_define_out = knitr::knit_child('../fragments/tex_preamble.tex')
test_tex_define_out = gsub("\\%.*?\\\n", "", test_tex_define_out)
test_tex_define_out = gsub("\\\n%.*","", test_tex_define_out)
```

```{r include=FALSE, eval=TRUE}
test_tex_define_out = knitr::knit_child('../fragments/tex_preamble.tex')
test_tex_define_out = gsub("\\%.*?\\\n", "", test_tex_define_out)
test_tex_define_out = gsub("\\\n%.*","", test_tex_define_out)
```
`r paste(test_tex_define_out, collapse='\n')`

<span style="font-size:40%;"> $$\exd$$ </span>
<span style="font-size:40%;"> $$\exe$$ </span>
<span style="font-size:40%;"> $$\exf$$ </span>

## Load Tex from the parallel folder subfolder

```{r echo=TRUE, eval=FALSE}
test_tex_define_out = knitr::knit_child('../fragments/shorthand/tex_preamble.tex')
test_tex_define_out = gsub("\\%.*?\\\n", "", test_tex_define_out)
test_tex_define_out = gsub("\\\n%.*","", test_tex_define_out)
```

```{r include=FALSE, eval=TRUE}
test_tex_define_out = knitr::knit_child('../fragments/shorthand/tex_preamble.tex')
test_tex_define_out = gsub("\\%.*?\\\n", "", test_tex_define_out)
test_tex_define_out = gsub("\\\n%.*","", test_tex_define_out)
```
`r paste(test_tex_define_out, collapse='\n')`

<span style="font-size:40%;"> $$\exg$$ </span>
<span style="font-size:40%;"> $$\exh$$ </span>
<span style="font-size:40%;"> $$\exi$$ </span>

# Loading Multiple Latex Files Together with single input

Find all files with certain suffix in a folder, and then load them all in as child:

```{r echo=TRUE, eval=FALSE}
spt_root <- 'C:/Users/fan/Documents/Dropbox (UH-ECON)/repos/Tex4Econ/'
spt_texfolder <- 'nontex/revealjsrmd/math_tests/fragments/shorthand'
ls_path_group_use <- paste0(spt_root, spt_texfolder)
ls_sfls <- list.files(path=ls_path_group_use, recursive=T, pattern="short.*.tex", full.names=T)

test_tex_define_all <- ''
for (spt_file in ls_sfls) {
  test_tex_define_out = knitr::knit_child(spt_file)
  test_tex_define_out = gsub("\\%.*?\\\n", "", test_tex_define_out)
  test_tex_define_out = gsub("\\\n%.*","", test_tex_define_out)
  test_tex_define_all <- paste0(test_tex_define_all, test_tex_define_out)
}
```

```{r include=FALSE, eval=TRUE}
spt_root <- 'C:/Users/fan/Documents/Dropbox (UH-ECON)/repos/Tex4Econ/'
spt_texfolder <- 'nontex/revealjsrmd/math_tests/fragments/shorthand'
ls_path_group_use <- paste0(spt_root, spt_texfolder)
ls_sfls <- list.files(path=ls_path_group_use, recursive=T, pattern="short.*.tex", full.names=T)

test_tex_define_all <- ''
for (spt_file in ls_sfls) {
  test_tex_define_out = knitr::knit_child(spt_file)
  test_tex_define_out = gsub("\\%.*?\\\n", "", test_tex_define_out)
  test_tex_define_out = gsub("\\\n%.*","", test_tex_define_out)
  test_tex_define_all <- paste0(test_tex_define_all, test_tex_define_out)
}
```
`r paste(test_tex_define_all, collapse='\n')`

## Equations from Tex Preamble

These are equations created for paper:

$$\optirelainterceptyfullprc{\Ic}{\Icp}$$
$$\optirelaslopeyfullreorg{\Ic}{\Icp}$$

## More Equations from Tex Preamble

These are equations created for paper:

$$\optirelainterceptyfullreorg{\Ic}{\Icp}$$

## Longer Equation

<span style="font-size:40%;">
\begin{align}
    \label{eq:disconstrainset}
    \begin{split}
    \Fconsds \equiv \Bigg\{
        \bm{\VD} =
        \left( \VD_1, \cdots, \VD_{\Nc} \right) :
        \VD_{\Ic} \in \Big\{ 0, 1, \dots, \VDhg \Big\}
        \text{, and, }
        \sum_{\Ic=1}^{\Nc} \VDc \le \VDagg \in \mathcal{N}_{+}
    \Bigg\}.\\
    \end{split}
\end{align}
</span>

There exist $\FDopti_{1}, \cdots, \FDopti_{\Nc}$ allocation mappings
\begin{align}
    \begin{split}
    \FDopti_{\Ic}\left(
      \VDagg, \Peq, \left\{\Pwgcp\right\}_{\Icp=1}^{\Nc}
                , \left\{\VAcp\right\}_{\Icp=1}^{\Nc},
                \left\{
                    \left\{\VM_{\Icp\Ik}\right\}_{\Ik = \VDlw}^{\VDhg}
                    \right\}_{\Icp=1}^{\Nc}
        \right)
    \end{split}
\end{align}

## Equations with Options 1

\eqtwoctsinvoptilub{\inon}{\intw}

## Equations with Options 2

\eqtwoctsoptilub{\inon}{\intw}

## Additional symbol testing

Using mathbf (does not work with greeks):

$mathbf\mathbf{this is bold} not bold$
$a + b \mathbf{+ a + b} + a + b$
$A + B \mathbf{+ A + B} + A + B$
$\alpha + \beta \mathbf{+ \alpha + \beta} + \alpha + \beta$

Using boldsymbol:

$boldsymbol\boldsymbol{this is boldsymbol} not boldsymbol$
$a + b \boldsymbol{+ a + b} + a + b$
$A + B \boldsymbol{+ A + B} + A + B$
$\alpha + \beta \boldsymbol{+ \alpha + \beta} + \alpha + \beta$

### 2020-05-20 nontex/install/git/fs_git_setup.Rmd
8 pane timeline text and panes fully parametrized and dynamically sized.

@@
 ```
+
+## Versioning and Tagging
+
+[Git Tagging](https://git-scm.com/book/en/v2/Git-Basics-Tagging). [Semantic Versioning](https://semver.org/):
+
+Given a version number MAJOR.MINOR.PATCH, increment the:
+
+1. MAJOR version when you make incompatible API changes,
+2. MINOR version when you add functionality in a backwards compatible manner, and
+3. PATCH version when you make backwards compatible bug fixes.
+
+Additional labels for pre-release and build metadata are available as extensions to the MAJOR.MINOR.PATCH format.
+
+By default, the **git push** command doesn’t transfer tags to remote servers.
+You will have to explicitly push tags to a shared server after you have created them.
+This process is just like sharing remote branches — you can run git push origin <tagname>.
+
+```{bash}
+git tag -l
+git tag -a v0.1.1 -m "Genereate Package after updating to R 4.0.0 Arbor Day."
+git show v0.1.1
+git push github v0.1.1
+```
+
+## Githug pages
+
+local test github pages. [Testing your GitHub Pages site locally with Jekyll](https://help.github.com/en/github/working-with-github-pages/testing-your-github-pages-site-locally-with-jekyll).
+
+For testing github pages sites. On windows, install ruby using [windows-installer](https://rubyinstaller.org/downloads/). Windows choose install option 3, install toolchain.
+
+[jekyll with bundler](https://jekyllrb.com/tutorials/using-jekyll-with-bundler/)
+
+```{bash}
+ruby -v
+gem -v 
+gcc -v
+g++ -v 
+make -v
+
+gem install jekyll bundler
+jekyll -v
+gem install bundler
+gem install minima
+gem install jekyll-feed
+
+cd ~/fanwangecon.github.io
+<!-- delete existing Gemfile Gemfile.lock possibly in directory -->
+bundle init
+bundle config set --local path 'vendor/bundle'
+bundle add jekyll
+bundle add minima
+bundle add jekyll-feed
+bundle exec jekyll new --force --skip-bundle .
+
+bundle exec jekyll serve
+http://localhost:4000
+
+https://jekyllrb.com/tutorials/using-jekyll-with-bundler/
+```

### 2020-05-20 nontex/install/windows/fn_installations.Rmd
8 pane timeline text and panes fully parametrized and dynamically sized.

@@
 
+Theme for sphinx
+```{bash}
+pip install sphinx-rtd-theme
+pip install sphinx_bootstrap_theme
+```
+
 Initialize a Poetry-style Python Package and add Sphinx style docs. This creates the folder *~/pyfan* and initialize it with various:
@@
 
+[sphinx readthedocx](https://samnicholls.net/2016/06/15/how-to-sphinx-readthedocs/)
+
 ```{bash}
@@
 poetry install
-make html
-rm -rf dist/ build/
+
+rm -rf dist/ build/ docs/
+cd docs/
+sphinx-build -b html ../ _build
+<!-- make html -->
+sphinx-build -b latexpdf ../ _build
+make latexpdf
+
 poetry build
@@
 pip install pyfan
-```
-
+pip install git+https://github.com/fanwangecon/pyfan.git#egg=pyfan
+```
+
+```{bash}
+ipython
+import pyfan.util.rmd.bookdownparse as bookdownparse
+?bookdownparse.fs_yml2readme
+```
 ##### Uninstall
@@
 
+#### Conda Jekyll Environment (Ruby)
+
+For testing github pages sites. On windows, install ruby using [windows-installer](https://rubyinstaller.org/downloads/). Windows choose install option 3, install toolchain.
+
+```{r}
+# Set up
+conda deactivate
+conda list env
+conda env remove -n wk_ruby
+conda create -n wk_ruby -y
+conda activate wk_ruby
+
+ruby -v
+gem -v 
+gcc -v
+g++ -v 
+make -v
+
+gem install jekyll bundler
+
+# use yaml2tex
+cd "C:\Users\fan\Documents\Dropbox (UH-ECON)\repos\fanwangecon.github.io\_cv\templating\"
+python yaml2tex.py
+```
+
 #### Conda revealjs nodejs Environment
@@
 ```{r}
+# Install RTools First!
+# https://cran.r-project.org/bin/windows/Rtools/
+
+# Install tidyverse
+install.packages(c("tidyverse", "tidymodels"))
+
+# Install Packaging tools
+install.packages(c("devtools", "pkgdown", "roxygen2", "bookdown", "knitr", "kableExtra", "formatR"))
+
+# Install Statistics models
+install.packages(c("AER", "minpack.lm"))
+
+# Install Tools to Work with Other Packages
+install.packages(c("reticulate"))
+
+# Personal Packages
+devtools::install_github("fanwangecon/REconTools")
+```
+```{r}
 # Can enter R from Command Prompt Conda ENV, much faster than from r-studio
 # Install R-tools, RTOOLS is for WINDOWS
-install.packages("installr")
-library("installr")
-install.Rtools()
+# install.packages("installr")
+# library("installr")
+# install.Rtools()
 # c:/Rtools/bin;
@@
 
+# Install RTools First!
+https://cran.r-project.org/bin/windows/Rtools/
+
 # main packagevps
 # tidymodel installation on linux difficult
-install.packages(c("tidyverse", "tidymodels", "tidyr"))
+# install.packages(c("tidyverse", "tidymodels", "tidyr"))
 # development packages
-install.packages(c("devtools", "IRkernel", "pkgdown", "roxygen2", "kableExtra"))
+# install.packages(c("devtools", "IRkernel", "pkgdown", "roxygen2", "kableExtra"))
 # other packages
-install.packages(c("AER", "minpack.lm", "knitr", "matlab"))
+install.packages(c("AER", "minpack.lm"))
+# install.packages(c("AER", "minpack.lm", "knitr", "matlab"))
+
+# for working with other tools
+# install.packages(c("reticulate"))
 
@@
 # Kernel
-install.packages(c('repr', 'IRdisplay', 'evaluate', 'crayon', 'pbdZMQ', 'devtools', 'uuid', 'digest'))
-IRkernel::installspec()
+# install.packages(c('repr', 'IRdisplay', 'evaluate', 'crayon', 'pbdZMQ', 'devtools', 'uuid', 'digest'))
+# IRkernel::installspec()
 ```

### 2020-06-02 nontex/install/git/fs_git_setup.Rmd
8 pane file complete

@@
 gem install jekyll-feed
+gem install jekyll-sitemap
 
@@
 bundle add minima
-bundle add jekyll-feed
-bundle exec jekyll new --force --skip-bundle .
+bundle add jekyll-sitemap
 

### 2020-06-02 nontex/install/windows/fn_installations.Rmd
8 pane file complete

@@
 ```
+
 ##### Uninstall
@@
 pip uninstall python-frontmatter
+```
+
+##### pyfan workflow and files added
+
+New python functions are added, or new Rmd files are added with python exampls.
+
+List of to dos and checks.
+
+New rmd files:
+
+1. Edit yaml to include functions used
+  + Go over each part, add to short desc
+  + In each section, add code usage
+2. Link to py functions if implemented there
+3. Run file internally
+4. Add new files to *_bookdown.yml*
+5. Run pyfan rmd compile
+6. Overall bookdown check pdf and html
+
+New py functions:
+
+1. Document with function name, parameters and returns
+2. update version number
+3. Test run the function file's main 
+4. Local sphnix text etc
+5. Poetry publish
+6. Git push 
+7. Check Docs on readthedocs
+8. Uninstall and install locally
+9. Uninstall and install in wk_pyfan envir
+
+```{bash}
+cd "C:/Users/fan/pyfan"
+poetry install
+
+rm -rf dist/ build/ docs/
+mkdir docs
+cd docs/
+sphinx-build -b html ../ _build
+
+poetry build
+poetry publish
+```
+
+```{bash}
+pip show pyfan
+<!-- pip install pyfan -->
+pip uninstall pyfan -y
+pip install pyfan
+pip install git+https://github.com/fanwangecon/pyfan.git#egg=pyfan
+
+conda activate wk_pyfan
+pip uninstall pyfan -y
+pip install pyfan
+pip install git+https://github.com/fanwangecon/pyfan.git#egg=pyfan
+conda deactivate
 ```
@@
 # Set up
+conda deactivate
 conda list env
@@
 conda activate wk_perl
-conda install -c anaconda perl
+conda install -c anaconda perl -y
 conda list
@@
 cd "C:\Users\fan\.conda\envs\wk_perl\"
+cd "C:\ProgramData\Anaconda3\envs\wk_perl\"
 git clone https://gitlab.com/latexpand/latexpand.git
@@
 conda list env
-conda env remove -n wk_nodejs
-conda create -n wk_nodejs -y
-conda activate wk_nodejs
-
-conda install -c conda-forge nodejs -y
-# ended up downloading installer for windows nodejs and installing out of conda
-# was having lots of bugs
-npm i -g --production windows-build-tools
-npm install -g --force decktape
-# use yaml2tex
-
-cd "C:\Users\fan\Documents\Dropbox (UH-ECON)\repos\fanwangecon.github.io\_cv\templating\"
-python yaml2tex.py
-```
-
+conda env remove -n wk_pyfan
+conda create -n wk_pyfan -y
+conda activate wk_pyfan
+
+# add channel
+conda config --env --add channels conda-forge
+conda config --get channels
+conda config --get channels --env
+
+# yaml
+conda install python-frontmatter -y
+conda install pyyaml -y
+
+# environment data
+conda install cdsapi -y
+conda install -c conda-forge eccodes -y
+
+# pyfan install 
+pip install pyfan
+
+```
+
+#### Conda Bookdown for pyfan
+
+To run some perl tools in an isolated environment:
+
+1. [latexpand](https://tex.stackexchange.com/a/21840/109818)
+
+```{bash}
+# Set up
+conda deactivate
+conda list env
+conda env remove -n wk_perl
+conda create -n wk_perl -y
+conda activate wk_perl
+conda install -c anaconda perl -y
+conda list
+conda deactivate
+
+# intall packages in virtual env
+cd "C:\Users\fan\.conda\envs\wk_perl\"
+cd "C:\ProgramData\Anaconda3\envs\wk_perl\"
+git clone https://gitlab.com/latexpand/latexpand.git
+
+# use latexpand
+conda activate wk_perl
+cd "C:\Users\fan\Documents\Dropbox (UH-ECON)\Project Emily Minority Survey\Drafts_RR\OverleafChinaSchoolClosure"
+perl "C:\Users\fan\.conda\envs\wk_perl\latexpand\latexpand" draft_edcc_submit_rr.tex > draft_edcc_submit_rr_flat.tex
+```
 ## Essential Programs to Install
@@
 # Install Tools to Work with Other Packages
-install.packages(c("reticulate"))
+install.packages(c("reticulate", "JuliaCall"))
 
@@
 - Open up Settings: *Ctrl + ,*
+- Open up Extensions: *Ctrl + Shift + X*
 - Preview Markdown in VSCode: *Ctrl + Shift + v*
@@
 2. synctex location: *ctrl + alt + j*
+
+### VSCode Spell Check
+
+Download [Spell Right](https://marketplace.visualstudio.com/items?itemName=ban.spellright).
 

### 2020-11-22 nontex/development/python/fn_installations.Rmd
additional installation guides

---
title: |
  | Develop Python Package with Sphinx
output:
  html_document:
    number_sections: true
    toc: yes
  html_notebook:
    number_sections: true
    toc: yes
  word_document:
    number_sections: true
  pdf_document:
    df_print: paged
    number_sections: true
    toc: yes
urlcolor: blue
always_allow_html: yes
---

Go back to [fan](http://fanwangecon.github.io/)'s [Tex4Econ and Miscellaneous Repository](http://fanwangecon.github.io/Tex4Econ/).

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval = FALSE)
```

# Develop Python Package with Sphinx

## RST

[cheatsheet](https://github.com/ralsina/rst-cheatsheet/blob/master/rst-cheatsheet.rst)

### Sections

```
Chapter 1 Title
===============
Section 1.1 Title
-----------------
Subsection 1.1.1 Title
~~~~~~~~~~~~~~~~~~~~~~
Section 1.2 Title
-----------------
Chapter 2 Title
===============
```

### Definitions

*literal block*: ?

### 2020-11-22 nontex/install/git/fs_git_setup.Rmd
additional installation guides

@@
 git tag -l
-git tag -a v0.1.1 -m "Genereate Package after updating to R 4.0.0 Arbor Day."
-git show v0.1.1
-git push github v0.1.1
+git tag -a v0.1.3 -m "Genereate Package after updating to R 4.0.0 Arbor Day."
+git tag -a v0.1.37 -m "pyfan with sphinx"
+git show v0.1.37
+git push github v0.1.37
 ```
 
-## Githug pages
+## Github pages
 
@@
 ```
+
+# Git Commands
+
+## Stop tracking a particular file
+
+```
+cd ~/PrjOptiSNW
+git filter-branch --tree-filter 'rm -f ~/PrjOptiSNW/PrjOptiSNW.mltbx' -- --all
+```

### 2020-11-22 nontex/install/windows/fn_installations.Rmd
additional installation guides

@@
 title: |
-  | New Computer Fan Data-Science Set-up
+  | Data-Science Set-up
   | Python (Anaconda), R (Rstudio), Matlab and Latex (Texlive)
-  | Atom, VScode, Pycharm
+  | VScode, Atom, Sublime Pycharm
 output:
+  html_document:
+    number_sections: true
+    toc: yes
+  html_notebook:
+    number_sections: true
+    toc: yes
+  word_document:
+    number_sections: true
   pdf_document:
@@
     number_sections: true
-  html_notebook:
-    number_sections: true
-  word_document:
-    number_sections: true
-  html_document:
-    number_sections: true
+    toc: yes
 urlcolor: blue
@@
 
-Go back to [fan](http://fanwangecon.github.io/)'s [Tex4Econ and Miscellaneous Repository](http://fanwangecon.github.io/Tex4Econ/).
+Go back to [fan](http://fanwangecon.github.io/)'s [Tex4Econ and Miscellaneous Repository](http://fanwangecon.github.io/Tex4Econ/). This file contains various excessive details on installations.
 
@@
 curl -sSL https://raw.githubusercontent.com/python-poetry/poetry/master/get-poetry.py | python
+poetry --version
 # sphinx
@@
 pip install sphinx_bootstrap_theme
+pip install nbsphinx --user
 ```
@@
 
+### Poetry Update Python Version
+
+[poetry change python version to 3.x](https://stackoverflow.com/questions/60580113/poetry-change-python-version-to-3-x)
+
+The existing poetry env needs to be deleted and re-created if need to update python version.
+
+```{bash}
+poetry env list 
+```
+
+1. Update python requirement in .toml to *python = "^3.8"*
+2. delete current env: *poetry env remove python*
+3. run: *poetry lock*
+4. run: *poetry update*, *poetry install*, etc...
+
 ### Installating Poetry Created Packages
@@
 ```{bash}
+# pyfan
 poetry remove python-frontmatter pyyaml
 poetry add python-frontmatter pyyaml
+poetry add numpy
+poetry add scipy
+poetry add cython
+
+# Compuational and Stats
+poetry add statsmodels
+poetry add numba
+poetry add sklearn
+
+# visualize
+poetry add matplotlib
+poetry add seaborn
+
+# pyecon
+poetry add pyfan
+
+# aws
+poetry add boto3
 ```
@@
 
+SEE BELOW *pyfan/pyecon workflow and files added*:
+
 ```{bash}
@@
 cd "C:/Users/fan/pyfan"
+cd "C:/Users/fan/pyecon"
 poetry install
 
-rm -rf dist/ build/ docs/
-cd docs/
+<!-- rm -rf dist/ build/ docs/
+mkdir docs -->
+cd doc/
+rm -rf _build/ auto_examples/ gen_modules/backreferences gen_modules/generators
 sphinx-build -b html ../ _build
@@
 
-On some local computer install pyfan:
+SEE BELOW *pyfan/pyecon workflow and files added*, on some local computer install pyfan:
 
@@
 
-##### pyfan workflow and files added
+##### pyfan/pyecon workflow and files added
 
@@
 ```{bash}
-cd "C:/Users/fan/pyfan"
+conda activate base
+
+<!-- to update all dependencies -->
+poetry update
+
+cd "C:/Users/fan/pyfan/"
+cd "C:/Users/fan/pyecon/"
 poetry install
 
-rm -rf dist/ build/ docs/
-mkdir docs
-cd docs/
-sphinx-build -b html ../ _build
-
+cd "C:/Users/fan/pyfan/doc/"
+cd "C:/Users/fan/pyecon/doc"
+rm -rf _build/ auto_examples/ gen_modules/backreferences gen_modules/generators
+make html
+
+<!-- Check Results in: C:\Users\fan\pyfan\doc\_build\html\index.html -->
+
+cd "C:/Users/fan/pyfan/"
+cd "C:/Users/fan/pyecon/"
 poetry build
@@
 
-```{bash}
+pip install works inside conda env. Uninstall first. Then install pyfan in conda env using pip. With user option, seems to install system-wide.
+
+Note that if some of the conda env use different python versions than base, then when base programs are updated, will not update in env.
+
+Might need to update this in all sub-directories
+
+```{bash}
+<!-- local install, this does not install in conda env -->
+cd "C:/Users/fan/pyfan/"
+cd "C:/Users/fan/pyecon/"
+python setup.py install --user
+<!-- after installing show appear under pip: pip show pyfan, with latest version ID -->
+<!-- after installing this does not appear on conda list: conda list -n base, but in python, import pyfan as pyfan works -->
+<!-- help('modules') in python to see if installed-->
+
 pip show pyfan
@@
 conda activate wk_pyfan
+conda activate wk_cgefi
+
+<!-- if pyfan already installed, but not in conda env, uninstall and installing puts it in conda env -->
 pip uninstall pyfan -y
 pip install pyfan
+<!-- --user installs it for outside of env -->
+pip install pyfan --user
+
 pip install git+https://github.com/fanwangecon/pyfan.git#egg=pyfan
@@
 make html
+```
+
+2. install sphinx packages
+
+- [phinx-gallery](https://sphinx-gallery.github.io/stable/index.html)
+
+```{bash}
+pip install sphinx-gallery
 ```
@@
 
+Conda update python version
+
+```{bash}
+conda install -c anaconda python=3.7
+conda update --all
+```
+
 Open up Anaconda Navigator, it will update navigator automatically. If there are errors, might have to clean first.
@@
 # normal update
+# to show all currently installed: conda list -n base
 conda update --all
@@
 pip install smop
+```
+#### Conda Base
+
+```{base}
+conda install -c anaconda boto3 -y
+
 ```
@@
 
-#### Conda revealjs nodejs Environment
+#### Conda wk_pyfan bookdown
 
@@
 ```{r}
+conda update -n base -c defaults conda
+
 # Set up
@@
 conda env remove -n wk_pyfan
-conda create -n wk_pyfan -y
+conda create -n wk_pyfan -y python=3.8
 conda activate wk_pyfan
@@
 # add channel
-conda config --env --add channels conda-forge
+# conda config --env --add channels conda-forge
 conda config --get channels
@@
 # yaml
-conda install python-frontmatter -y
+# conda install python-frontmatter -y
+pip install python-frontmatter
 conda install pyyaml -y
+
+# pyfan install 
+pip install pyfan
+
+# numpy etc install
+conda install -c anaconda numpy
+# https://github.com/numpy/numpy/issues/17726
+# https://github.com/numpy/numpy/wiki/FMod-Bug-on-Windows
+# pip install numpy==1.19.3
+# conda install -c anaconda cython
+
+# matplotlib install
+# conda install -c anaconda matplotlib -y
+# python -m pip install -U matplotlib
+
+# to test aws
+conda install boto3 -y
 
@@
 conda install -c conda-forge eccodes -y
-
-# pyfan install 
+conda install -c conda-forge cfgrib
+
+```
+
+#### Conda ECMWF Envir
+
+```
+
+conda deactivate
+conda list env
+conda env remove -n wk_ecmwf
+conda create -n wk_ecmwf -y
+conda activate wk_ecmwf
+
+conda install -c conda-forge cdsapi -y
+conda install -c conda-forge eccodes -y
+conda install -c conda-forge cfgrib -y
+conda install -c conda-forge xarray -y
+conda install -c conda-forge netcdf4 -y
+
+```
+
+#### Conda ECMWF Envir Python 2
+
+```
+
+conda deactivate
+conda list env
+conda env remove -n wk_ecmwf_py2
+conda create -n wk_ecmwf_py2 python=2.7 -y 
+conda activate wk_ecmwf_py2
+
+python --version
+```
+
+#### Conda CGE Environment
+
+Installing pip installed/updated python version from 3.7 to 3.8.
+
+```
+conda deactivate
+conda list env
+conda env remove -n wk_cgefi
+conda create -n wk_cgefi -y
+conda activate wk_cgefi
+
+# Install External Tools
+conda install -c anaconda pip -y
+
+# Cloud
+conda install -c anaconda boto3 -y
+
+# Python tools
+conda install -c anaconda pytest -y
+
+# Install Own Tools
 pip install pyfan
 
+# Scientific Computing
+conda install -c anaconda numpy -y
+conda install -c anaconda statsmodels -y
+conda install -c conda-forge interpolation -y
+conda install -c anaconda pandas -y
+conda install -c anaconda scikit-learn
+conda install -c anaconda cython
+
+# Graphing
+conda install -c anaconda matplotlib -y
+conda install -c anaconda pillow -y
+
+```
+
+#### Conda AWS Environment
+
+AWS environment and set-up on local computer
+
+```
+conda deactivate
+conda list env
+conda env remove -n wk_aws
+conda create -n wk_aws -y
+conda activate wk_aws
+
+install docker
 ```
@@
 
+## Numpydoc
+
+```{bash}
+Returns:
+    None
+
+```
+
 # R Installation
@@
 # Conda r_env
-conda activate r_env
+conda activate r_envr
 # Where is it installed?
@@
 
+### Update R
+
+1. On windows, install the *installr* package, and use *updateR()*
+2. At the end, will ask if want to move all old pacages to new R directory
+
+New R will have new package directory, could keep all in old, should copy all to new, and not keep old.
+
+```{r}
+# https://www.r-project.org/nosvn/pandoc/installr.html
+install.packages('installr')
+# update R from inside R (not Rstudio)
+require(installr)
+# this will open dialog boxes to take you through the steps.
+updateR() 
+# Set Rstudio to the Latest R
+```
+
 ### Install Packages for R
@@
 - [reticulate](https://github.com/rstudio/reticulate)
+    + install directly from: devtools::install_github("rstudio/reticulate")
 
@@
 
+# Install system tools
+install.packages(c("backports"))
+
 # Install tidyverse
-install.packages(c("tidyverse", "tidymodels"))
+install.packages(c("tidyverse", "tidymodels", "vroom"))
 
@@
 install.packages(c("reticulate", "JuliaCall"))
+# for reticulate errors, install directly from: devtools::install_github("rstudio/reticulate")
+
+# Paralell
+install.packages(c("parallel", "doParallel", "foreach"))
 
@@
 devtools::install_github("fanwangecon/REconTools")
+devtools::install_github("fanwangecon/PrjOptiAlloc")
 ```
@@
 
+# Matlab Installation
+
+1. go to Mathworks, download the latest file.s
+
+# Word
+
+[Change background color and text color in word](https://www.davidbosman.fr/scsaw/?p=687)
+
+Use these for my preferred background and text colors, consistent with SumatraPDF
+
+> TextColor = #1e170f, R=30, G=23, B=15
+> BackgroundColor = #fff8e6, R=255, G=248, B=230
+
 # Install Latex and PDF
@@
 # Install Various Editors
+
+Editors to Install:
+
+1. Notepad++: for sync with Sumatra and quick edit by section, and fast quick editor in general
+2.
 
@@
 - toggle minimap: *Ctrl + k, ctrl + z*
+
+### VSCode and Python
+
+#### Virtual Env Python VSCode
+
+(Using Python environments in VS Code)[https://code.visualstudio.com/docs/python/environments]
+
+1. Ctrl + Shift + P
+2. type in: Python: Select Interpreter
 
@@
 
-### Atom Shortcuts and Features
+### Atom Shortcuts, Features and Settings
 
@@
 - Git Pane: *Ctrl + 9*, *Ctrl + 8*
+- Hard Wrap Text: *Ctrl + Shift + q*
+
+**Spellcheck Scope** :
+
+- cmd+shift+p, run *Editor: Log Cursor Scope*, see notification that comes up, add the *scopes* found to the *spell-check* package scope list.
 
@@
 
+### Sublime Shortcut
+
+- *json pretty*, "alt + shift + j"
 ### Sublime and Outline (Markdown)
@@
 
+## RStudio
+
+### RStudio Short Cuts
+
+**GUI**
+
+- clear all console outputs, collapse all: *edit + clear all outputs*
+
 ## PyCharm
@@
 
+### PyCharm Settings GUI View etc
+
+Change Theme, modify by changing plug-in.
+
+Go to Settings, *Ctrl + Alt + S*, inside settings, go to theme/appearances, and chagne which theme is used. Material theme has a number of different options.
+
+- Change where Tabs are displayed top or side: Settings -> Editor -> Editor Tabs -> Tab Placement (right)
+- To change font: Settings -> Color Scheme -> Color Scheme Font ->
+
+### PyCharm Set Virtual Env
+
+1. In conda env: `where python`: `C:\ProgramData\Anaconda3\envs\wk_cgefi\python.exe`
+2. In Pycharm: Settings (ctrl+alt+s), Project, Python interpreter.
+3. Click on the cog button, "Add" > Right menu, "Virtual Environement" > Existing environement > Three dots > paste the path and point it to the python.exe in Scripts
+
 ### PyCharm Short Cuts
 
+**copy/paste**
+
+- copy current function/line reference: *Ctrl + Shift + Alt + C*
+- copy current file full path: *Ctrl + Shift + C*
+
+**run/debug/test**
+
+- Run current file: *ctrl+shift+f10*
+- Run all tests in current file: *alt+shift+f10*
+- Clear all Break-Points: *Ctrl+Shift+F8, Delete*
+- Open up evaluator during debug: *Alt + F8*
+- right click on a file and choose to run all "pytest", then should start test x of N
+
+**Coding**
+
+[code editor help](https://www.jetbrains.com/help/pycharm/using-code-editor.html)
+
+- Refractor Names: *SHIFT + F6*
 - Auto-Indent: *CTRL + SHIFT + ALT + L*
-
-## Other Editors
-
-### Notepad++
+- Upper Case All: "CTRL + SHFT + U"
+- Lower Case All: "CTRL + SHFT + L"
+- reformat auto-indent: "Ctrl + Alt + L"
+- Highlight searched: "Ctrl + Shift + F7"
+
+**GUI**
+
+Switching between panes:
+
+1. set up default: Windows - Store Current as Default, go to default with *Shift + F12*
+2. back to editor main: *CTRL + SHIFT + F12*
+
+- Hide All non-code Windows: *CTRL + SHIFT + F12*
+- Shift to last active: *F12*
+- Maximize Output/Console Pane: *CTRL + SHIFT + QUOTE*
+- Hide Output Pane: *SHIFT + ESC*
+- Show Console output max: first debug, where debug is activate, *Ctrl + Shift + '*
+
+**Settings**
+
+- Go to Settings: *Ctrl + Alt + S*, click on keymap
+
+## Notepad++
 
@@
 - Silently update file changes made in other editors: Settings, Preferences, MISC., File Status Auto Detection, Update Silently.
+
+### Installation
+
+- Install Notepad++
+- Settings + Preferences + Cloud + Google Drive/App/Notepad++ Sync Setting there. 
+- install [Npp-1-Dark](https://github.com/60ss/Npp-1-Dark)
 

### 2020-11-22 nontex/install/windows/fn_installations_R.Rmd
additional installation guides

--- 2020-05-20 nontex/install/windows/fn_installations.Rmd
@@
 title: |
-  | New Computer Fan Data-Science Set-up
-  | Python (Anaconda), R (Rstudio), Matlab and Latex (Texlive)
-  | Atom, VScode, Pycharm
+  | R Installation and Update
 output:
+  html_document:
+    number_sections: true
+    toc: yes
+  html_notebook:
+    number_sections: true
+    toc: yes
+  word_document:
+    number_sections: true
   pdf_document:
@@
 
-# Objective
+# R Installation and Set-Up
 
-Install various compilers and IDE:
-
-1. Python (Anaconda, Pycharm + VSCode + Atom, Poetry)
-2. R (VSCode + Atom)
-3. Matlab
-4. Latex and PDF (texlive, Okular, VSCode + Atom + Texstudio)
-
-Test at the end:
-
-1. Do sample *py* files work?
-    + work from command line
-    + work from atom (hydrogen), Pycharm, VSCode
-2. Do sample *rmd* files work?
-    + work from r-studio
-    + work from atom (hydrogen), VSCode
-3. Do tex templates compile?
-    + tikz files, template files with bib
-    + work from texstudio, VSCode live compile, Atom
-
-Installation Plan outline:
-
-1. Conda install (python)
-2. Install Atom along with Hydrogen and other packages.
-
-# Python Testing and Installation with Poetry and Docs
-
-When to use Python:
-
-1. Main use Python for Dynamic programing type tasks
-2. All immediate data tasks should be done in R, including things like generating data structures. Also graph generation in R.
-3. Certain basic tabulation summary statistics etc things done in Stata
-
-Two types of python usage cases:
-
-1. Small chunks of python code in RMD for tutorial/class files, combine files in book format as bookdown.
-2.
-Python installable packages and modules created with poetry, push to github as pypi: Locally test specially functions in [poetry](https://python-poetry.org/docs/#installation) environment.
-Push to github and Pypi, and then install via pip for system wide use.
-
-Installations:
-
-1. Python package development in poetry virtual environment, install with needed dependencies.
-	- This means, during python package development, do not install the packages needed directly in conda, but add as dependency in Poetry
-2. General environment with pip installed packages and conda installed path discoverable pathon packages for rmd chunks.
-
-## Poetry
-
-Install Python via Anaconda first following other instructions. Possibly cleanly uninstall and reinstall. Use Poetry to build python packages and modules.
-
-For development machines, install [Poetry](https://github.com/python-poetry/poetry) and nstall [sphinx](https://www.sphinx-doc.org/en/master/).
-
-```{bash}
-# poetry
-curl -sSL https://raw.githubusercontent.com/python-poetry/poetry/master/get-poetry.py | python
-# sphinx
-pip install sphinx
-```
-
-Theme for sphinx
-```{bash}
-pip install sphinx-rtd-theme
-pip install sphinx_bootstrap_theme
-```
-
-Initialize a Poetry-style Python Package and add Sphinx style docs. This creates the folder *~/pyfan* and initialize it with various:
-
-```{bash}
-# creates ~/pyfan as poetry packaging
-cd ~
-poetry new pyfan
-
-# sphinix quickstart
-cd ~/pyfan
-mkdir docs
-sphinx-quickstart
-make html
-
-# build empty package
-rm -rf dist/ build/
-poetry install
-poetry build
-poetry publish
-
-# What is the virtual Env id
-poetry env info
-```
-
-### Installating Poetry Created Packages
-
-Normally install/test/use inside conda virtual env or poetry virtual env.
-Poetry would install with *poetry add* and *poetry install*.
-After seeing some package of interest on github etc, see if the package is on pypi.
-pip install from pypi if possible.
-
-Local Install
-
-```{bash}
-pip install --no-index --find-links="C:/Users/fan/Py4Econ/dist/pyfan-0.0.0.900.tar.gz" pyfan --ignore-installed
-```
-
-Pypi Install
-
-Open up conda prompt, pip install from base. Will install dependencies of package that are in the poetry env but not otherwise in python installation main path.
-
-```{bash}
-pip install git+https://github.com/fanwangecon/pyfan.git#egg=pyfan
-pip install pyfan --ignore-installed
-pip show pyfan
-```
-
-Sometimes, someone ports a package and adds certain things that I need, so need to install from git a package whose modified version is not on pypi, then use git+https
-
-#### What are egg, tar.gz, whl?
-
-poetry creates tar.gz and whl in the dist folder, what are they?
-
-- tarballs: tar.gz
-
-### Developing and testing new tools Pycharm + Poetry
-
-When tesing and developing tools, do so in the poetry virtual environment for the package in which testing is taking place.
-
-After a package has been created and poetry built and poetry publish:
-
-1.
-Type in *poetry env info*, and copy for example path: *C:/Users/fan/AppData/Local/pypoetry/Cache/virtualenvs/py4econ-6xnVtByB-py3.7*, to pycharm, so that can test module in pycharm using the poetry generated isolated packaging testing env.
-2. In Pycharm: Settings (ctrl+alt+s), Project, Python interpreter.
-3. Click on the cog button, "Add" > Right menu, "Virtual Environement" > Existing environement > Three dots > paste the path and point it to the python.exe in Scripts
-
-```{bash}
-poetry env info
-```
-
-When a particular tool is needed to build this new module inside package, add the tool via poetry add as a dependency.
-If a module requires another dependency: *poetry add numpy*, if adding numpy.
-This will install in the virtual env *numpy*.
-When packages are added, they are automatically installed.
-When the the *pyfan* package repo is downloaded somewhere, the dependencies might not be installed yet, and *poetry install* would install them.
-
-```{bash}
-poetry add numpy
-```
-
-#### Development for pyfan
-
-pyfan is the general python tools package for various projects, not economics related directly.
-
-Poetry added dependencies are in */pyfan/pyproject.toml*, Poetry add:
-
-```{bash}
-cd "C:/Users/fan/pyfan"
-cd ~/pyfan
-poetry env info
-```
-
-All installations:
-
-```{bash}
-poetry remove python-frontmatter pyyaml
-poetry add python-frontmatter pyyaml
-```
-
-Poetry modules added over time:
-
-```{bash}
-# 2020-04
-poetry add pyyaml
-poetry add python-frontmatter
-```
-
-After modules are added and new programs developed
-
-[sphinx readthedocx](https://samnicholls.net/2016/06/15/how-to-sphinx-readthedocs/)
-
-```{bash}
-cd ~/pyfan
-cd "C:/Users/fan/pyfan"
-poetry install
-
-rm -rf dist/ build/ docs/
-cd docs/
-sphinx-build -b html ../ _build
-<!-- make html -->
-sphinx-build -b latexpdf ../ _build
-make latexpdf
-
-poetry build
-poetry publish
-```
-
-On some local computer install pyfan:
-
-```{bash}
-pip show pyfan
-# conda activate pyfan
-pip install pyfan
-pip install git+https://github.com/fanwangecon/pyfan.git#egg=pyfan
-```
-
-```{bash}
-ipython
-import pyfan.util.rmd.bookdownparse as bookdownparse
-?bookdownparse.fs_yml2readme
-```
-##### Uninstall
-
-uninstall packages in the overall environment
-```{bash}
-# list all installed packages
-pip list
-pip show pyyaml
-pip show python-frontmatter
-pip show pyfan
-# unstall packages
-pip uninstall pyyaml
-pip uninstall python-frontmatter
-```
-
-## sphinx and readthedocs
-
-readthedocs is logged in via github account. Automatically recognizes github repositories, and can import repositories to generate documentation that it can.
-
-1. install sphinx
-
-```{bash}
-pip install sphinx
-cd ~/Py4Econ
-mkdir docs
-sphinx-quickstart
-make html
-```
-
-### autodoc
-
-[Documenting Python Packages with Sphinx and ReadTheDocs](https://brendanhasz.github.io/2019/01/05/sphinx.html)
-
-The Napoleon extension for Sphinx allows for NumPy/Google style docstrings instead of using the hard-to-read reStructuredText in your docstrings
-
-> The autodoc extension for sphinx can automatically generate API reference doc pages from the docstrings in your python code.
-Python docstrings are string literals which occur immediately after function or class definitions.
-They’re treated as comments, and it’s customary to document a function or class in its docstring.
-The autodoc extension allows you to include reStructuredText in your docstrings, and will build an API reference automatically for your module from the docstrings, while allowing for further customization.
-
-To enable the autodoc extension, in your conf.py file, add the string 'sphinx.ext.autodoc' to the extensions list (this should have already been done if you answered yes to enabling the autodoc extension during sphinx-quickstart).
-
-```{python}
-# If extensions (or modules to document with autodoc) are in another directory,
-# add these directories to sys.path here. If the directory is relative to the
-# documentation root, use os.path.abspath to make it absolute, like shown here.
-#
-# import os
-# import sys
-# sys.path.insert(0, os.path.abspath('.'))
-```
-
-After enabling autodoc, in the documentation’s .rst files, you can use the automodule directive:
-
-.. automodule:: package_name.module
-   :members:
-
-.. autosummary::
-   :toctree: _autosummary
-
-   fantools.utility
-   fantools.utility.inout
-   fantools.utility.inout.bookdownparse
-   fantools.utility.inout.rmdparse
-   fantools.utility.timer
-
-### rst
-
-= for page titles,
-- for sections,
-^ for subsections, and
-" for subsubsections.
-
-Bulleted lists use asterisks, numbered lists use numbers, and nesting is done with indentation, like Markdown (though nested lists need to be surrounded by blank lines):
-
-* Bulleted
-* list
-
-  * nested
-  * list
-
-* con't
-
-1. Numbered
-2. list
-
-``Code sample``
-
-For hyperlinks, use:
-
-`Link text <http://www.link-address.com>`_
-
-Commented lines begin with two periods and a space (like a directive w/o the double colons):
-
-.. I'm a comment!
-And multiline comments are also like directives w/o the colons:
-
-..
-   I am
-   a multiline
-
-   comment
-
-## Python, Poetry, Docs, Git
-
-Start from without a package. Create two packages: pyecon, pyfan
-
-1. generate poetry repos first, before adding in .git with pull_repos
-2.
-
-```{bash}
-cd ~
-poetry new pyfan
-
-cd ~
-poetry new pyecon
-
-base ~/base/bin/pull_repos
-
-cd ~/pyfan
-cd "C:/Users/fan/pyfan"
-mkdir docs
-<!-- change release number conf.py and .toml -->
-<!-- sphinx-quickstart -->
-make html
-poetry build
-poetry publish
-
-cd ~/pyecon
-cd "C:/Users/fan/pyecon"
-mkdir docs
-poetry build
-poetry publish
-sphinx-quickstart
-make html
-
-poetry env info
-<!-- get virtual env info  -->
-```
-
-install git locally so can use outside of env
-
-pip install git+https://github.com/fanwangecon/pyfan.git#egg=pyfan
-pip show pyfan
-
-> Name: pyfan
-> Version: 0.1.2
-> Summary:
-> Home-page: None
-> Author: Fan Wang
-> Author-email: wangfanbsg75@live.com
-> License: None
-> Location: c:\programdata\anaconda3\lib\site-packages
-> Requires:
-> Required-by:
-
-```{python}
-import pyfan.util.rmd.rmdparse as ft_rmdparse
-ft_rmdparse.fs_rmd_yml_parse()
-
-import pyfan.util.rmd.bookdownparse as ft_bookdownparse
-sfc_prj = 'R4Econ'
-sph_prj = 'C:/Users/fan/R4Econ/'
-spn_prj_bookdown_yml = '_bookdown.yml'
-spn_prj_readme_toc = 'README_toc_three.md'
-
-ft_bookdownparse.fs_yml2readme(sfc_prj=sfc_prj, sph_prj=sph_prj,
-                          spn_prj_bookdown_yml=spn_prj_bookdown_yml,
-                          spn_prj_readme_toc=spn_prj_readme_toc)
-```
-
-# Python and Anaconda Installation
-
-Use conda across platforms, so that locally on windows and ubuntu and remotely on aws, can have the same software setup environment.
-
-- Search for Anaconda Prompt, right click, choose run as administrator.
-- Check software versions.
-
-```{bash}
-conda list anaconda
-python -V
-```
-
-## Anaconda Install
-
-### First Time Conda Install
-
-[Download Anaconda Python 3](https://www.anaconda.com/distribution/) and install for all users.
-Afterwards, Anaconda does not automatically get added to Windows Path.
-Need to use Anaconda Prompt to access programs.
-To access Anaconda packages from windows prompt, from git bash, from R, etc, need to Add Anaconda to Windows Path.
-
-To install conda in Linux/Debian, follow [these instructions](https://fanwangecon.github.io/Tex4Econ/nontex/install/linux/fn_ubuntu.html). Overall, installations are very similar.
-
-In command/anaconda prompt:
-
-```{bash}
-# To remove conda Fully
-rm -rf ~/anaconda3
-
-where anaconda
-# C:/ProgramData/Anaconda3/Scripts/anaconda.exe
-where python
-# C:/ProgramData/Anaconda3/python.exe
-where jupyter
-# C:/ProgramData/Anaconda3/Scripts/jupyter.exe
-where jupyter-kernelspec
-# if R installed already
-where r
-
-###############################
-# Add these to Windows PATH:
-###############################
-# C:\ProgramData\Anaconda3
-# C:\ProgramData\Anaconda3\Scripts
-# C:\ProgramData\Anaconda3\Scripts\bin
-```
-
-To Add Anaconda to Path, In Windows
-1. Search for: Environment Variables
-2. Edit Environment Variables
-3. Add new to Path (lower half):
-    - C:/ProgramData/Anaconda3/
-    - C:/ProgramData/Anaconda3/Scripts/
-    - C:/ProgramData/Anaconda3/Scripts/bin        
-4. Now open up regular windows command Prompt, Type in:
-    - conda --version
-    - also Close and Open up Git Bash: conda --version
-
-### Conda Update, Install, Channels
-
-Open up Anaconda Navigator, it will update navigator automatically. If there are errors, might have to clean first.
-
-There are different channels/repositories from which packages could be installed: *conda*, *conda-forge*, for example.
-Can change where to look for packages first.
-Many packages are in multiple channels.
-Conda-forge often have mroe recent packages.
-
-```{bash}
-# if there are bugs
-# conda clean --packages
-# use conda-forge as main channel, more updated packages
-conda config --get channels
-conda config --add channels conda-forge
-conda config --get channels
-# remove conda-forge from channels (do so for main env install)
-conda config --remove channels conda-forge
-# normal update
-conda update --all
-```
-
-### Conda Environments
-
-For testing installed packages.
-Note that for development, using poetry for testing package dependencies for package development, and associate pycharm for projects with poetry virtual environments.
-The idea is that there might be dependency problems etc for packages depending on where/when they were made, might not work in the overall conda environment where pyfan and pyecon, my main tools are installed.
-Some specific task might only need one particular package.
-And when working on these, use a conda environment.
-When this works, could incorporate whatever I am working on into a pyfan, pyecon package along with other packages.
-
-```{bash}
-conda list env
-conda env remove -n test_package_name
-conda create -n test_package_name -y
-conda activate test_package_name
-conda list
-conda deactivate
-
-conda install pip
-
-# see if package exists on pip and install from pip
-pip install smop
-```
-
-#### Conda Perl Environment
-
-To run some perl tools in an isolated environment:
-
-1. [latexpand](https://tex.stackexchange.com/a/21840/109818)
-
-```{bash}
-# Set up
-conda list env
-conda env remove -n wk_perl
-conda create -n wk_perl -y
-conda activate wk_perl
-conda install -c anaconda perl
-conda list
-conda deactivate
-
-# intall packages in virtual env
-cd "C:\Users\fan\.conda\envs\wk_perl\"
-git clone https://gitlab.com/latexpand/latexpand.git
-
-# use latexpand
-conda activate wk_perl
-cd "C:\Users\fan\Documents\Dropbox (UH-ECON)\Project Emily Minority Survey\Drafts_RR\OverleafChinaSchoolClosure"
-perl "C:\Users\fan\.conda\envs\wk_perl\latexpand\latexpand" draft_edcc_submit_rr.tex > draft_edcc_submit_rr_flat.tex
-```
-
-#### Conda Jinja Environment
-
-For testing and packaging latex files. In particular, single folder latex files for final paper submissions.
-
-```{r}
-# Set up
-conda deactivate
-conda list env
-conda env remove -n wk_jinja
-conda create -n wk_jinja -y
-conda activate wk_jinja
-conda install -c anaconda jinja2
-conda install -c anaconda pyyaml
-
-# use yaml2tex
-cd "C:\Users\fan\Documents\Dropbox (UH-ECON)\repos\fanwangecon.github.io\_cv\templating\"
-python yaml2tex.py
-```
-
-#### Conda Jekyll Environment (Ruby)
-
-For testing github pages sites. On windows, install ruby using [windows-installer](https://rubyinstaller.org/downloads/). Windows choose install option 3, install toolchain.
-
-```{r}
-# Set up
-conda deactivate
-conda list env
-conda env remove -n wk_ruby
-conda create -n wk_ruby -y
-conda activate wk_ruby
-
-ruby -v
-gem -v 
-gcc -v
-g++ -v 
-make -v
-
-gem install jekyll bundler
-
-# use yaml2tex
-cd "C:\Users\fan\Documents\Dropbox (UH-ECON)\repos\fanwangecon.github.io\_cv\templating\"
-python yaml2tex.py
-```
-
-#### Conda revealjs nodejs Environment
-
-revealjs, decktape to pdf conversions
-
-```{r}
-# Set up
-conda deactivate
-conda list env
-conda env remove -n wk_nodejs
-conda create -n wk_nodejs -y
-conda activate wk_nodejs
-
-conda install -c conda-forge nodejs -y
-# ended up downloading installer for windows nodejs and installing out of conda
-# was having lots of bugs
-npm i -g --production windows-build-tools
-npm install -g --force decktape
-# use yaml2tex
-
-cd "C:\Users\fan\Documents\Dropbox (UH-ECON)\repos\fanwangecon.github.io\_cv\templating\"
-python yaml2tex.py
-```
-
-## Essential Programs to Install
-
-Install Packages, note that some packages are dependencies for fantools and fanecon packages, they would be installed jointly with those packages.
-
-```{bash}
-pip install --user --upgrade setuptools wheel
-pip install sphinx
-pip install fantools --ignore-installed
-```
-
-Previously:
-
-```{bash}
-# install additional packages
-# linux utilites
-# conda install -y m2-base
-# stats and graphs
-# conda install -y statsmodels datashape seaborn
-# various
-# conda install -c conda-forge -y interpolation awscli
-# aws communicate
-# conda install -c anaconda -y boto3
-```
-
-## Fist test python under command line:
-
-```{bash}
-# windows
-python "C:/Users/fan/PyFan/ProjectSupport/Testing/Numpy/Functions.py"
-python "C:/Users/fan/PyFan/ProjectSupport/graph/subplot.py"
-# linux
-python ~/PyFan/ProjectSupport/Testing/Numpy/Functions.py
-python ~/PyFan/ProjectSupport/graph/subplot.py
-```
-
-# R Installation
-
-R could be installed from Anaconda or directly on windows outside of the Anaconda directories.
-When installing from within Anaconda, could create R environment that are isolated from the rest of the computer.
-The R environment could be updated and deleted without disturbing dependencies in conda main or the rest of the computer.
-
-The computer could have multiple R installations.
-Several in different conda R environment, and also several under windows/linux primary main user R directories.
-Type *which R/where R* to see if you open up R from command line at the moment, which directory's R will be used.
-Inside Conda R environment, it will be a different R if there is a different R version there.
+Install R and Update R
 
@@
 
-If R was installed in R enviornments, just delete the environment.
+Uninstall R, RStudio and RTools from Windows "Programs and Features" menu
+
+If R was installed in a virtual environment, delete the environment.
 Otherwise, use system's uninstaller.
@@
 ```{r}
-.libPath()
+ls_spn_paths <- .libPaths()
+print(ls_spn_paths)
 # C:/Users/fan/Documents/R/win-library/3.6
@@
 
-For Linux and for unsintalling inside conda:
-
-```{bash}
-# Exit Conda
-conda deactivate
-# where is R installed outside of Conda
-which R
-# /usr/bin/R
-# To remove all
-sudo apt-get remove r-base
-sudo apt-get remove r-base-core
-
-# Inside Conda base
-conda activate
-# Conda r_env
-conda activate r_env
-# Where is it installed?
-which R
-# /home/wangfanbsg75/anaconda3/bin/R
-conda uninstall r-base
-```
-
-## Install R (outside of Conda)
-
-Need to install R.
-Then need to install also an editor/IDE for R.
-Rstudio is the dominant R IDE.
-VSCode and Atom also works well, especially VSCode as editors.
-Dramatically better experience for writing scripts outside of Rstudio which feels unwieldy and slow especially compared to VSCode.
-
-Overall plan:
+## Install R First Time
 
@@
     + add R to path for Windows. In Windows Path, add for example: *C:/Program Files/R/R-3.6.2/bin/x64/* and *C:/Rtools/bin*
+2. [Install Rtools](https://cran.r-project.org/bin/windows/Rtools/) for building R packages.
 2. [download R-studio](https://rstudio.com/products/rstudio/download/)
 3. Open R-studio and auto-detect R
-4. Install additional packages (from commandline)
-    + various R data-science packages have dependencies, and additional not-R programs might need to be installed.
-Install them as needed, for example:  *libcurl4-openssl-dev* and *libssl-dev* from command prompt first inside Debian.
+4. Install additional packages
 
-### Linux R Install
+After installing R, change the path sequence so that packages install for all users:
 
-For linux/Debian, to Install latest R:
-
-```{bash}
-# Go to get latesdebian latest r sources.list
-cat /etc/apt/sources.list
-# Install this First (should already be installed)
-sudo apt install dirmngr
-
-# Debian R is maintained by Johannes Ranke, copied from https://cran.r-project.org/bin/linux/debian/:
-apt-key adv --keyserver keys.gnupg.net --recv-key 'E19F5F87128899B192B1A2C2AD5F960A256A04AF'
-# Add to source.list, for debian stretch (9)
-# sudo su added for security issue as super-user
-sudo su -c "sudo echo 'deb http://cloud.r-project.org/bin/linux/debian stretch-cran35/' >> /etc/apt/sources.list"
-# if added wrong lines, delete 3rd line
-sudo sed '3d' /etc/apt/sources.list
-
-# Update and Install R, should say updated from cloud.r
-sudo apt-get update
-sudo apt-get install r-base r-base-dev
-
-# Also install these, otherwise r-packages do not install
-# libxml2 seems need for tidymodels
-sudo apt-get install libcurl4-openssl-dev
-sudo apt-get install libssl-dev
-sudo apt-get install libxml2-dev
+```{r}
+ls_spn_paths <- .libPaths()
+print(ls_spn_paths)
+ls_spn_paths <- c(ls_spn_paths[2], ls_spn_paths[1])
+.libPaths(ls_spn_paths)
+ls_spn_paths <- .libPaths()
+print(ls_spn_paths)
 ```
-
-### Install Packages for R
-
-What are the packages I need in R:
-
-**Use Multiple Languages**:
-
-- [reticulate](https://github.com/rstudio/reticulate)
-
-**Visualization, Packaging Etc**:
-
-- [bookdown](https://bookdown.org/)
-- [formatR](https://cran.r-project.org/web/packages/formatR/index.html): to tidy up rmd chunks
-
-From command prompt, enter R by typeing *R*, and install packages:
 
@@
 
+# Install system tools
+install.packages(c("backports"))
+
 # Install tidyverse
-install.packages(c("tidyverse", "tidymodels"))
+install.packages(c("tidyverse", "tidymodels", "vroom"))
 
 # Install Packaging tools
-install.packages(c("devtools", "pkgdown", "roxygen2", "bookdown", "knitr", "kableExtra", "formatR"))
+install.packages(c("devtools", "pkgdown", "roxygen2", "bookdown", "knitr", "kableExtra", "formatR", "revealjs"))
 
@@
 install.packages(c("AER", "minpack.lm"))
+install.packages(c("quantreg"))
 
 # Install Tools to Work with Other Packages
-install.packages(c("reticulate"))
+install.packages(c("reticulate", "JuliaCall"))
+# for reticulate errors, install directly from: devtools::install_github("rstudio/reticulate")
+
+# Paralell
+install.packages(c("parallel", "doParallel", "foreach"))
+
+# for sublime r-ide
+# install.packages("languageserver")
 
@@
 devtools::install_github("fanwangecon/REconTools")
-```
-```{r}
-# Can enter R from Command Prompt Conda ENV, much faster than from r-studio
-# Install R-tools, RTOOLS is for WINDOWS
-# install.packages("installr")
-# library("installr")
-# install.Rtools()
-# c:/Rtools/bin;
-# c:/Rtools/mingw_32/bin;
-# c:/Rtools/mingw_64/bin;
+devtools::install_github("fanwangecon/PrjOptiAlloc")
 
-# Install RTools First!
-https://cran.r-project.org/bin/windows/Rtools/
-
-# main packagevps
-# tidymodel installation on linux difficult
-# install.packages(c("tidyverse", "tidymodels", "tidyr"))
-# development packages
-# install.packages(c("devtools", "IRkernel", "pkgdown", "roxygen2", "kableExtra"))
-# other packages
-install.packages(c("AER", "minpack.lm"))
-# install.packages(c("AER", "minpack.lm", "knitr", "matlab"))
-
-# for working with other tools
-# install.packages(c("reticulate"))
-
-# Install my package, need to prepare package to work for ubuntu
-# if install does not work, load locally
-devtools::install_github("fanwangecon/REconTools")
-
-# Present
-install.packages("revealjs")
-# Kernel
-# install.packages(c('repr', 'IRdisplay', 'evaluate', 'crayon', 'pbdZMQ', 'devtools', 'uuid', 'digest'))
-# IRkernel::installspec()
+# Stata in Rmd
+devtools::install_github("Hemken/Statamarkdown")
 ```
 
-## Install R (inside Conda)
-
-Key packages are generally available in conda's default channel (official distribution) and also the more frequently updated conda-forge channel.
-Prioritize conda-forge to get the latest packages.
-After adding *conda-forge* to channels, that will be prioritized, so when creating a new environment, conda will install first from conda-forge if package exists there.
-Try the *r_env* generation line with and without first adding *conda-forge* to channel, and see that the packages installed will have different versions, reflecting versions in the default channel and in the *conda-forge* channels.
-
-### Set up Conda R environment
-
-Create a Conda Environment called *r_env*, and update its channels.
-
-- **Location**: Installed environments are shown appear in the *envs* folder of *C:/ProgramData/Anaconda3/envs/*.
-Can be easily deleted without disrupting the main base installation for conda.
-This is very important.
-During installation, could easily run into problems, and need to re-install.
-Much better to only re-install a folder.
-Note that when R is installed in *envs*, it will not show up under add or remove programs for uninstallation from there, has to be uninstalled, deleted directly here.
-- **Use only in Env**: Note that if we installed r inside r_env, if we type *r* under the base environment, we can not enter r.
-We can only enter r within r_env.
-With PATH properly set-up, this happens under Conda Prompt, Windows Prompt, etc.
-- **Multiple Pythons**: With the above installation for R, one benefit is that if R requires a different version of Python than what the base environment uses, the r_env could have a different python version.
-So type *python* in the base environment as well as inside the *r_env*.
-This also means potentially there could be duplicated installations I think.
-Look at the python versions under *conda list* in the base and in the r-environment.
-- **File Size**: Note that this creates a large installation folder, *C:/ProgramData/Anaconda3/envs/r_env/*, without additional packages, is 1.3 GB in size
-
-```{bash}
-# outside of conda, install some depencies
-sudo apt-get install libcurl4-openssl-dev
-sudo apt-get install libssl-dev
-sudo apt-get install libxml2-dev
-
-# install key r packages within a r-environment
-conda env remove -n r_env
-# start empty environment
-conda create -n r_env
-# activate env and check, nothing yet
-conda activate r_env
-conda list
-
-# check channel and add env specific channel
-conda config --get channels
-# to get latest r, use conda-forge, which has more recent Rs
-# conda config --env --add channels conda-forge
-# channels for base
-conda config --get channels
-# channels for cur env
-conda config --get channels --env
-
-# see all installed environments
-conda env list
-# activate an environment to use it, if in base, r does not exist, isolated in r_env
-conda activate r_env
-# see packages in environment
-conda list
-# to quit
-conda deactivate
+Temp Installs:
+```
+# 2020-10-19
+# Temp install development version due to but
+# https://github.com/rstudio/reticulate/issues/831
+devtools::install_github("rstudio/reticulate")
 ```
 
-### Install R and Some Packages in Conda
+## Update R on Computer
 
-Either inside a R specific environment, or outside of it, now do additional installations for R and also R packages.
+1. On windows, install the *installr* package, and use *updateR()*
+2. At the end, will ask if want to move all old pacages to new R directory
 
-During installation, the R programs might require downgrading other programs in the Conda environment that Python for example also uses.
-That is why potentially it is safer to install in R environment.
-However, when installing in R enviornment, certain packages could have issues if installer does not realize it is in an environment with special folder structure, so installation could fail.
-
-```{bash}
-# install files
-conda install -n r_env -c r r r-essentials r-tidyverse r-tidymodels -y
-
-# trouble with igraph installation, install here from conda
-# conda install -n r_env r-essentials r-base r-tidyr r-tidyverse r-devtools r-irkernel r-pkgdown r-roxygen2
-conda install -n r_env -c r r-igraph
-conda install -n r_env -c conda-forge igraph
-conda install -n r_env -c r r-rstantools r-rstan r-rstanarm -y
-```
-
-## Install Additional Packages inside the R
-
-These are packages that I use, these should be installed inside the environment.
-Or they could be installed later from inside r-studio.
-Installing inside r-studio is a lot better.
-*tidymodel* has installation issues sometimes.
-
-In *r_env*, type in *R*, and then install from inside terminal's R. For conda env, devtools will be installed and will install packages inside *envs/r_env/Lib/R*.
+New R will have new package directory, could keep all in old, should copy all to new, and not keep old.
 
 ```{r}
-# enter into env
-# conda activate r_env
-# enter R or type in rstudio
-# sicne R is only install inside r_env, has to enter rstudio from r_env
-# R
-# rstudio
-
-# main packagevps
-# tidymodel installation on linux difficult
-install.packages(c("rstantools", "rstan", "rstanarm"))
-install.packages(c("tidyr", "tidyverse", "tidymodels"))
-
-# tidymodels
-# development packages
-install.packages(c("devtools", "IRkernel", "pkgdown", "roxygen2", "kableExtra"))
-# other packages
-install.packages(c("AER", "minpack.lm", "knitr", "matlab"))
-
-# Install my package, need to prepare package to work for ubuntu
-# if install does not work, load locally
-devtools::install_github("fanwangecon/REconTools")
-
-# Present
-install.packages("revealjs")
-# Kernel
-install.packages(c('repr', 'IRdisplay', 'evaluate', 'crayon', 'pbdZMQ', 'devtools', 'uuid', 'digest'))
-IRkernel::installspec()
-```
-
-## R-Studio Set-up Download from Rstudio
-
-1. Download R-studio, and install, as normal (not from conda, directly from rstudio website latest windows version)
-2. Open up anaconda prompt, enter *r_env* environment: *activate r_env*
-3. cd into rstudio exe file folder: cd "C:/Program Files/RStudio/bin"
-4. start r-studio from inside *r_env*: rstudio.exe
-5. inside r-studio, check: *.libPaths()*
-    - "C:/ProgramData/Anaconda3/envs/r_env/Lib/R/library"
-
-```{bash}
-activate r_env
-cd "C:/Program Files/RStudio/bin"
-rstudio.exe
-
-cd "C:/ProgramData/Anaconda3/envs/r_env/Lib/R/library"
-"C:/Program Files/RStudio/bin/rstudio.exe"
-```
-
-For linux, note that rstudio offers Ubuntu as well as Debian versions that can be installed with wget:
-
-```{bash}
-<!-- for ubuntu -->
-wget "https://download1.rstudio.org/desktop/bionic/amd64/rstudio-1.2.5033-amd64.deb"
-<!-- for debian -->
-sudo apt install ./rstudio-1.2.5033-amd64.deb
-wget "https://download1.rstudio.org/desktop/debian9/x86_64/rstudio-1.2.5033-amd64.deb"
-sudo apt install ./rstudio-1.2.5033-amd64.deb
-conda install -c r rstudio
-cd "C:/Program Files/RStudio/bin"
-rstudio.exe
-
-cd "C:/ProgramData/Anaconda3/envs/r_env/Lib/R/library"
-"C:/Program Files/RStudio/bin/rstudio.exe"
-```
-
-Is RSTUDIO pointing to the R installation you want? Note you can open Rstudio from differen conda env command line, that will use different R installations. Or also set:
-
-- *export RSTUDIO_WHICH_R=/usr/bin/R*
-- *export RSTUDIO_WHICH_R=/home/wangfanbsg75/anaconda3/bin/R*
-
-R-studio theme, [VSCode theme](https://github.com/anthonynorth/rscodeio) for Rstudio works very well:
-
-```{r}
-# admin rights
-sudo rstudio --no-sandbox
-remotes::install_github("anthonynorth/rscodeio")
-rscodeio::install_theme()
+# https://www.r-project.org/nosvn/pandoc/installr.html
+install.packages('installr')
+# update R from inside R (not Rstudio)
+require(installr)
+# this will open dialog boxes to take you through the steps.
+updateR()
+# Set Rstudio to the Latest R
 ```
@@
 ```{r}
-# A simple file with summary statistics using tidyverse
-source('C:/Users/fan/R4Econ/summarize/dist/fst_hist_onevar.R')
-# Another simple file with summary statistics using tidyverse
-source('C:/Users/fan/R4Econ/support/tibble/fs_tib_basics.R')
-# A file involving estimation
-source('C:/Users/fan/R4Econ/optimization/cesloglin/fst_ces_plan_linlog.R')
-
+# # A simple file with summary statistics using tidyverse
+# source('C:/Users/fan/R4Econ/summarize/dist/htmlpdfr/fst_hist_onevar.R')
+# # Another simple file with summary statistics using tidyverse
+# source('C:/Users/fan/R4Econ/support/tibble/htmlpdfr/fs_tib_basics.R')
+# # A file involving estimation
+# source('C:/Users/fan/R4Econ/optimization/cesloglin/htmlpdfr/fst_ces_plan_linlog.R')
+#
 # C:/Users/fan/R4Econ/summarize/dist/fst_hist_onevar.Rmd
@@
 ```
-
-# Install Latex and PDF
-
-Use a combination of overleaf and local compile.
-The goal is to have the same installation set-up for windows as well as linux.
-And hopefully, locally compilable file also can be compiled on overleaf (only use packages also available on overleaf).
-
-There are several pieces of things to install:
-
-1. latex compiler: pdflatex, etc
-2. tex distributions: MikTex, texlive
-    + these folders, once various packages are installed, could be very large, many GB
-3. latex packages from distributions
-3. editor (gui): Atom, Sublime text, texStudio, etc
-
-## Uninstall
-
-- uninstall *MiKTeX*: delete from programs, then delete remaining folder in Program Files.
-- uninstall *texlive*: go to *c:/texlive*, delete the folder
-
-## Install
-
-*Install on Windows*
-
-- [Install Texstudio](https://www.texstudio.org/)
-- [Install texlive](https://www.tug.org/texlive/acquire-netinstall.html)
-
-*Install on Ubuntu*
-
-install texlive and texstudio ubuntu/debian.
-
-```{bash}
-sudo apt-get update
-sudo apt-get install texlive-full
-sudo apt-get install texstudio
-```
-
-Test file compilations in TexStudio.
-
-## SumatraPDF
-
-For windows, install [SumatraPDF](https://www.sumatrapdfreader.org/download-free-pdf-viewer.html). Can easily modify colors.
-
-**Settings**
-
-[Kindle Sepia](https://medium.com/greatnote/kindle-sepia-color-code-1fed14b1a5ef) modifications:
-
-- Background color:
-    + Kindle Sepia: *fbf0d9*
-    + Kindle Sepia Light: *fff8e6*
-- Text color:
-    + Kindle Sepia: *5f4b32*
-    + Kindle Sepia Darker: *503f2a*
-    + Kindle Sepia Darkerer: *1e170f*
-
-```
-FixedPageUI [
-	TextColor = #1e170f
-	BackgroundColor = #fff8e6
-	SelectionColor = #f5fc0c
-	WindowMargin = 2 4 2 4
-	PageSpacing = 4 4
-]
-```
-
-## Okular PDF
-
-Linux: *sudo apt-get install okular*
-Windows: install okular from windows app store
-
-### Okular Shortcuts and Features
-
-**Settings**:
-
-- Background color:
-    + background behind pdf: configure okular, general, use custom backgroun color, Gainsboro gray: *DCDCDC*, kindle sepia: *FBF0D9*
-    + pdf background itself: configure okular, accessbility, change color, change paper color, Light Kindle Sepia: *fff8e6*
-
-**Features**:
-
-- Okular 3 pages per row view: view, overview
-- Automatic Update when PDF updated elsewhere: this is one of the key reasons to use okular, when I knit a Rmd file to PDF, the currently open Okular PDF file automatically updates and does not give file is open error like Acrobat.
-- Background color:
-    + background behind pdf: configure okular, general, use custom backgroun color, Gainsboro gray: *DCDCDC*, kindle sepia: *FBF0D9*
-    + pdf background itself: configure okular, accessbility, change color, change paper color, Light Kindle Sepia: *fff8e6*
-
-**Shortcuts**:
-
-+ Okular configure shortcuts: setting, configure shortcuts
-+ Okular if menu bar lost: *Ctrl + m*
-+ Okular comment pane: *F6*
-+ Okular close left pane: *F7*
-+ Okular full scrren: *Ctrl + Shift + F*
-    * unlike acrobat, pdf allows for multiple scrrens
-
-## Adobe PDF
-
-PDF Adobe Acrobat Installation
-  + go to adobe website, log in using fwang26@uh.edu
-  + go to my account, choose view and download my apps, choose acrobat & PDF, download Acrobat DC
-  + UH account can only be activated on two accounts at once, so need to kick other computers out temporarily potentially
-
-# Install Various Editors
-
-Atom, VSCode, Notepad++, Sublime, etc.
-These are essential editors that allows for pleasant programming and writing experiences.
-See here for [fan](http://fanwangecon.github.io/) instructions on [vim](https://fanwangecon.github.io/Tex4Econ/nontex/install/linux/fn_vim.html) installations.
-
-All settings here JSON files here:
-
-- windows: *C:/Users/fan/AppData/Roaming/Code/User*, can be modified here directly
-
-## VSCode Installation
-
-VSCode is much more light-weight than Atom, much faster.
-On Windows, download [here](https://code.visualstudio.com/download).
-VScode settings easy to change for various extensions.
-Very very good Latex Editor, probably the best I have used.
-
-For Linux:
-
-```{bash}
-# Debian Install
-curl https://packages.microsoft.com/keys/microsoft.asc | gpg --dearmor > microsoft.gpg
-sudo install -o root -g root -m 644 microsoft.gpg /usr/share/keyrings/microsoft-archive-keyring.gpg
-sudo sh -c 'echo "deb [arch=amd64 signed-by=/usr/share/keyrings/microsoft-archive-keyring.gpg] https://packages.microsoft.com/repos/vscode stable main" > /etc/apt/sources.list.d/vscode.list'
-sudo apt-get install apt-transport-https
-sudo apt-get update
-sudo apt-get install code # or code-insiders
-
-# Change Font (https://wwFw.reddit.com/r/Crostini/comments/cesxr0/vscode_ui_and_fonts_too_small_heres_how_to_fix_it/)
-# modify: /usr/share/applications/code.desktop
-nvim /usr/share/applications/code.desktop
-#replace this line: Exec=/usr/share/code/code --unity-launch %F
-Exec=sommelier -X --scale=0.8 --dpi=160 /usr/share/code/code "--unity-launch %F"
-#replace this line: Exec=/usr/share/code/code --new-window %F
-Exec=sommelier -X --scale=0.8 --dpi=160 /usr/share/code/code "--new-window %F"
-
-# Open File
-# low density mode to see cleary
-code
-```
-
-### VSCode Extensions
-
-Press *Ctrl + P*, paste the *ext install* commands below to install extensions. Extensions are in: *%USERPROFILE%/.vscode/extensions* for windows. Can change code for extension there.
-
-```{bash}
-# [Microsoft Python Extension](https://marketplace.visualstudio.com/items?itemName=ms-python.python)
-ext install ms-python.python
-# [Latex Workshop](https://marketplace.visualstudio.com/items?itemName=James-Yu.latex-workshop)
-ext install latex-workshop
-# [R](https://marketplace.visualstudio.com/items?itemName=Ikuyadeu.r)
-ext install ikuyadeu.r
-```
-
-### VSCode Shortcuts and Features
-
-**Features**:
-
-1. open a file, if have workspace where the file is in, automatically expand tree and show where file is on left pane.
-
-**Shortcuts** :
-
-- see all shortcuts: *Ctrl + k, ctrl + s*
-- Zen model: *Ctrl + k, z*, this means press control k, then press z
-    + note that z mode can be adjusted by shiftin the bar on the left
-- Open up Settings: *Ctrl + ,*
-- Preview Markdown in VSCode: *Ctrl + Shift + v*
-- Open up left pane: *Ctrl + b*
-- Wrap Text: *alt + z*, switch between wrap or not to save screen space for example.
-- Hide Console Pane (running code): *Ctrl + j*
-
-*personal bindings*
-
-- toggle minimap: *Ctrl + k, ctrl + z*
-
-### VSCode and R
-
-VSCode works pretty well it seems with Rmd files.
-Rmd files are useful to work through algorithm, examples in preparation for writing usable functions.
-Rstudio has been often very slow for me, and I generally feel like can not stretch around and work in RStudio IDE.
-
-In Atom, Hydrogen works, but really only works with very basic line by line testing.
-
-Using VSCode with RMD files seems much quicker, and there is room to breath.
-
-1. Install R following R installation instructions.
-2.
-Then install extension [R](https://marketplace.visualstudio.com/items?itemName=Ikuyadeu.r).
-Microsoft stopped supporting rmd in VSCode: [R Tools for Visual Studio](https://github.com/microsoft/RTVS)
-3. properly set path (might have to call vscode from r env)
-    + *r.rterm.linux*: */home/wangfanbsg75/anaconda3/envs/r_env/bin/R*
-    + *r.rterm.windows*: *C:/Program Files/R/R-3.6.2/bin/x64/R.exe*
-        * note *R.exe* at the end
-4. Run:
-    - ctrl + enter to activate R terminal
-    - VSCode 2019 allows for Knit Rmd: *Ctrl + Shift + K*
-    - also can run code segment: select lines and *ctrl + enter*
-
-### VSCode and Latex
-
-Download [Latex Workshop](https://marketplace.visualstudio.com/items?itemName=James-Yu.latex-workshop).
-
-**Shortcuts**
-
-- compile: *ctrl + alt + b*
-- sync: *ctrl + alt + j*
-- terminate pdflatex compile hang: *ctrl + shift + p; kill latex compiler process*
-- live save
-
-**Settings**
-
-change background border pdf color (not pdf but border): *ctrl + shift + x*, LatexWorkshop, Settings, Configure Extension Settings, Search for background, change color name.
-or enter: *latex-workshop.view.pdf.backgroundColor*.
-use gainsboro gray: *#DCDCDC*, or lightgray *#D3D3D3*.
-
-To take advantage of Okular (where background color can be none-white for example). Go to settings, and:
-1. Change: *latex-workshop.view.pdf.viewer* to external
-2. Change: *latex-workshop.view.pdf.external.viewer.command* to *C:/Program Files/SumatraPDF/SumatraPDF.exe*
- open up *C:/Users/fan/AppData/Roaming/Code/User/settings.json*, and copy these in:
-
-```
-"latex-workshop.view.pdf.external.synctex.command": "C:/Program Files/SumatraPDF/SumatraPDF.exe",
-"latex-workshop.view.pdf.external.synctex.args": [
-  "-forward-search",
-  "%TEX%",
-  "%LINE%",
-  "-reuse-instance",
-  "-inverse-search",
-  "code \"C:\\Users\\fan\\AppData\\Local\\Programs\\Microsoft VS Code\\resources\\app\\out\\cli.js\" -r -g \"%f:%l\"",
-  "%PDF%",
-]
-```
-
-**Features**:
-
-1. upon savings, rebuid file and update pdf (similar to overleaf)
-2. hover offers equation preview
-
-**Shortcuts**:
-
-1. preview: *ctrl + alt + v*
-2. synctex location: *ctrl + alt + j*
-
-### VSCode settings.json
-
-The settings.json file, *%APPDATA%/Code/User/settings.json*:
-
-```
-{
-  "r.rterm.windows": "C:/Program Files/R/R-3.6.2/bin/x64/R.exe",
-  "window.zoomLevel": 0,
-  "latex-workshop.view.pdf.viewer": "external",
-  "latex-workshop.view.pdf.external.synctex.command": "C:/Program Files/SumatraPDF/SumatraPDF.exe",
-  "latex-workshop.view.pdf.external.synctex.args": [
-		"-forward-search",
-		"%TEX%",
-		"%LINE%",
-		"-reuse-instance",
-		"-inverse-search",
-		"code \"C:\\Users\\fan\\AppData\\Local\\Programs\\Microsoft VS Code\\resources\\app\\out\\cli.js\" -r -g \"%f:%l\"",
-		"%PDF%",
-	],
-	"latex-workshop.view.pdf.external.viewer.command": "C:/Program Files/SumatraPDF/SumatraPDF.exe",
-  "editor.minimap.enabled": false,
-  "latex-workshop.latex.clean.fileTypes": [
-    "*.aux",
-    "*.bbl",
-    "*.blg",
-    "*.idx",
-    "*.ind",
-    "*.lof",
-    "*.lot",
-    "*.out",
-    "*.toc",
-    "*.acn",
-    "*.acr",
-    "*.alg",
-    "*.glg",
-    "*.glo",
-    "*.gls",
-    "*.fls",
-    "*.log",
-    "*.fdb_latexmk",
-    "*.snm",
-    "*.synctex(busy)",
-    "*.synctex.gz(busy)",
-    "*.nav",
-    "*.xml",
-    "*.gz",
-    "*.bcf"
-  ]
-}
-```
-
-## Atom Installation
-
-Atom is slow but has clean look and nice git/github integration.
-
-### Atom Extensions
-
-Terminal in windows or linux after installation: *apm install hydrogen*. apm is the atom package manager:
-
-```{bash}
-# Once atom is installed, can use apm to install packages
-apm install hydrogen
-# apm install project-manager
-
-# r-related
-# for me the best r-syntax highlighter I have found
-apm install r-syntax
-
-# latex-related
-apm install language-latex
-apm install latex
-
-# Selection and Overview
-apm install sublime-style-column-selection
-apm install minimap
-apm install highlight-selected
-apm install split-diff
-
-# vim distraction free editing
-apm install vim-mode-plus
-apm install ex-mode
-apm install zen
-
-# support
-apm install date
-
-# Inside Conda open up atom
-atom
-
-```
-
-### Atom Shortcuts and Features
-
-**Features**:
-
-```{bash}
-# open multiple projects from atom at the same time, after repos synced
-atom ~/fanwangecon.github.io ~/Pyfan ~/Teaching ~/Tex4Econ ~/R4Econ ~/M4Econ ~/Py4Econ
-# open up any py from from within, try 1+1, does it work?
-# also use script, try ctrl + shift + b, run whole file (not hydrogen)
-```
-
-**Shortcuts** :
-
-- Git Pane: *Ctrl + 9*, *Ctrl + 8*
-
-### Atom and Python
-
-Having installed Anaconda, now install Atom and Hydrogen to Test with Python. For both Jupyter as well as Atom, always open from command prompt, open from *Anaconda Prompt* with admin rights.
-
-Open up *Jupyter Notebook*, does the python kernel work? If does not, uninstall and re-install Anaconda.
-
-```{bash}
-# start jupyter lab, from prompt
-jupyter lab
-```
-
-Try *1+1*.
-
-### Atom and Latex
-
-Install the following two packages in atom:
-
-1. [latex](https://github.com/thomasjo/atom-latex) package on atom.
-2. [language-latex](https://atom.io/packages/language-latex) package on atom
-
-In Atom Latex setting, note that on different platforms, paths to texlive are different:
-
-- Path:
-    + Windows: *C:/texlive/2019/bin/win32*
-    + Chromebook Linux: */usr/bin/latex*
-- Which PDF viewer to use:
-    + download Okular and use [Okular](https://okular.kde.org/)
-
-```{bash}
-# set TeX path
-# C:/texlive/2019/bin/win32
-
-# Latex, after installation
-# see where texlive appears under root folder directories
-sudo find / -name "texlive"
-# see latex version, if texlive is used
-latex -v
-# see main exe directory
-which latex
-# /usr/bin/latex
-```
-
-**Latex Package Option**
-
-*clean* pattern
-
-```{bash}
-**/*.run.xml, **/*.aux, **/*.aux.bak, **/*.bbl, **/*.bcf, **/*.blg, **/*.dvi, **/*.fdb_latexmk, **/*.fls, **/*.idx, **/*.idx.bak, **/*.ilg, **/*.ind, **/*.lof, **/*.log, **/*.lol, **/*.lot, **/*.nav, **/*.out, **/*.ps, **/*.snm, **/*.synctex.gz, **/*.toc, /**/_minted-{jobname}, /{output_dir}/sage-plots-for-{jobname}.tex, /missfont.log, /texput.log, /texput.aux
-```
-
-### Atom settings file
-
-Atom keymap.cson file:
-
-```
-'atom-text-editor':
-  'ctrl-shift-j': 'pretty-json:prettify'
-  'alt-z':'date:date'
-  'alt-x':'date:time'
-  'alt-c':'date:datetime'
-'body':
-  'ctrl-tab': 'pane:show-next-item'
-  'ctrl-shift-tab': 'pane:show-previous-item'
-'.editor':
-  'ctrl-alt-z': 'atom-beautify:beautify-editor'
-  'ctrl-shift-r': 'hydrogen:restart-kernel'
-'atom-text-editor:not([mini])':
-  'ctrl-*': 'highlight-selected:select-all'
-'atom-text-editor, webview.markdown-preview-plus':
-  'ctrl-shift-X': 'markdown-preview-plus:toggle-render-latex'
-
-# https://github.com/t9md/atom-vim-mode-plus/issues/130
-'atom-text-editor.vim-mode-plus.insert-mode':
-  'j j': 'vim-mode-plus:activate-normal-mode'
-```
-
-## Sublime
-
-[Sublime](https://www.sublimetext.com/3)
-
-there are some issues with atom.
-When a file is edited inside Vim, when changes are saved, a [temp file is created in atom](https://github.com/atom/atom/issues/17186).
-Sublime would, however, still show the file with the changes.
-This makes dual screen editing very difficult.
-Sublime text is used for this situation.
-
-```{bash}
-# Sublime Linux
-wget -qO - https://download.sublimetext.com/sublimehq-pub.gpg | sudo apt-key add -
-sudo apt-get install apt-transport-https
-echo "deb https://download.sublimetext.com/ apt/stable/" | sudo tee /etc/apt/sources.list.d/sublime-text.list
-sudo apt-get update
-sudo apt-get install sublime-text
-# launch from terminal
-subl
-```
-
-*Sublime Setup*:
-
-Put sublime path in windows path for example:
-
-```
-C:\Program Files\Sublime Text 3\
-```
-
-- [r and rmd setup](https://weibeld.net/r/rmd_sublime_package.html)
-
-- [sublime markdown Monokai Extended](https://github.com/jonschlinkert/sublime-monokai-extended), [sublime markdown extended](https://github.com/jonschlinkert/sublime-markdown-extended)
-
-### Sublime and Outline (Markdown)
-
-To get the markdown outline of the current document if it is markdown press *Ctrl + R*, shows tabbed nested outline view.
-
-### Sublime Search and Replace
-
-Append to end of all lines with starting string some suffix.
-We have many lines that start with *print('abc')*, but the printed statements differ in length.
-Within the document, want to change all print statements to message statements, and have: *message(print('abc'))*:
-
-1. cursor select *print(*
-2. *alt + F3*, this selects all occurances
-3. *ctrl + end*, moves cursor to end of each line, any other single cursor point speicifc left right end start operation should work
-4. append new text suffix
-5. *ctrl + home*, move cursor to the start of all print lines, and append prefix as needed.
-
-## PyCharm
-
-[pycharm](https://www.)jetbrains.com/pycharm/)
-
-### PyCharm Short Cuts
-
-- Auto-Indent: *CTRL + SHIFT + ALT + L*
-
-## Other Editors
-
-### Notepad++
-
-[Notepad++](https://notepad-plus-plus.org/downloads/v7.8.2/). Many old projects have xml folder structures for Notepad++.
-
-- Silently update file changes made in other editors: Settings, Preferences, MISC., File Status Auto Detection, Update Silently.
-
-# Other Programs to Install
-
-## Package Managers
-
-To install packages in windows more easily:
-
-- [scoop](https://github.com/lukesampson/scoop/wiki/Quick-Start)
-
-```{bash}
-# in powershell
-# enter cmd
-# type powershell in cmd to enter powershell from cmd
-powershell
-# permission
-set-executionpolicy remotesigned -scope currentuser
-# install
-iwr -useb get.scoop.sh | iex
-```
-
-## Utilities
-
-- [pandoc](https://pandoc.org/installing.html)
-- [nodejs](https://nodejs.org/en/) (revealjs pdf conversion)
-- 7-zip
-- evernote
-
-## Security
-
-- keepass
-- [Proton VPN](https://protonvpn.com/): unlimited usage free version available.
-- Express VPN

### 2020-12-24 _other/symbols/fs_unicode.tex
simple unicode handling example.

\documentclass[12pt,english]{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\DeclareUnicodeCharacter{25FC}{$\blacksquare$}

% for links
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,
    urlcolor=cyan,
}

% Titling and Author
\title{Latex Handling Unicode}
\author{\href{https://fanwangecon.github.io/}{Fan Wang}\thanks{https://fanwangecon.github.io, repository: \href{https://fanwangecon.github.io/Tex4Econ/}{Tex4Econ}}}
\date{\today}
\begin{document}

\maketitle

Dependencies:
\begin{verbatim}
  \usepackage[utf8]{inputenc}
  \usepackage{amsmath}
  \usepackage{amssymb}
  \usepackage{amsthm}
\end{verbatim}

\section{End of Proof as Unicode}

\begin{verbatim}
  \DeclareUnicodeCharacter{25FC}{$\blacksquare$}
\end{verbatim}

Suppose want to directly use unicode 25FC, which is a black-box for end of proof. Pasting ◼ into latex is OK, if we declare 25FC to be a blacksquare. Without this declaration, would have unicode error upon compile when using ◼.

When there are unicode issues, look at the output error message, will say which is the CODE of the unicode character that is having an issue. Search online for what that character looks like add U+ in front of the four letter-numeric code possibly.

\end{document}

### 2021-01-02 _support/reference/biblatex_basic/biblatex_test.tex
parencite date only, possessive citation

@@
 }
+@article{hao_air_2016,
+	title = {Air {Pollution} and {Preterm} {Birth} in the {U}.{S}.
+{State} of {Georgia} (2002–2006): {Associations} with {Concentrations} of 11 {Ambient} {Air} {Pollutants} {Estimated} by {Combining} {Community} {Multiscale} {Air} {Quality} {Model} ({CMAQ}) {Simulations} with {Stationary} {Monitor} {Measurements}},
+	volume = {124},
+	issn = {0091-6765, 1552-9924},
+	shorttitle = {Air {Pollution} and {Preterm} {Birth} in the {U}.{S}. {State} of {Georgia} (2002–2006)},
+	url = {https://ehp.niehs.nih.gov/doi/10.1289/ehp.1409651},
+	doi = {10.1289/ehp.1409651},
+	language = {en},
+	number = {6},
+	urldate = {2020-07-18},
+	journal = {Environmental Health Perspectives},
+	author = {Hao, Hua and Chang, Howard H. and Holmes, Heather A. and Mulholland, James A. and Klein, Mitch and Darrow, Lyndsey A. and Strickland, Matthew J.},
+	month = jun,
+	year = {2016},
+	pages = {875--880}
+}
+@article{westergaard_ambient_2017,
+	title = {Ambient air pollution and low birth weight - are some women more vulnerable than others?},
+	volume = {104},
+	issn = {01604120},
+	url = {https://linkinghub.elsevier.com/retrieve/pii/S0160412017301976},
+	doi = {10.1016/j.envint.2017.03.026},
+	language = {en},
+	urldate = {2020-07-19},
+	journal = {Environment International},
+	author = {Westergaard, Nadja and Gehring, Ulrike and Slama, Rémy and Pedersen, Marie},
+	month = jul,
+	year = {2017},
+	pages = {146--154},
+}
+
 \end{filecontents}
@@
 
-\paragraph{\href{https://papers.ssrn.com/sol3/papers.cfm?abstract_id=3140132}{Data}}
+\section{Possessive Citations}
+
+In this example, using possessive to put apostrophe after author names and before date. Accomplished by using \emph{citeauthor} first then \emph{parentcite}.
+
+\citeauthor{hao_air_2016}'s \parencite*{hao_air_2016} Georgia study
+found that associations of traffic-related pollutants, including NO\textsubscript{2} and
+PM\textsubscript{2.5}, with preterm birth tended to be stronger for mothers with low
+educational attainment.
+
+\section{Cite Only Date}
+
+To write more flexibly, can mention author names explicitly in text and then cite the article with \emph{parentcite} for the date only: Westergaard and her colleagues \parencite*{westergaard_ambient_2017} identified only a small handful of studies that addressed effect modification by dimensions of socioeconomic status.
+
+\section{\href{https://papers.ssrn.com/sol3/papers.cfm?abstract_id=3140132}{Data}}
 

### 2021-06-02 template/fantemplate_image_appendix/draft.tex
Tex4Econ Example Figure only File

\documentclass{article}
\usepackage{geometry}
\geometry{
	a4paper,
	noheadfoot=true,
	left=1.0in,
	right=1.0in,
	top=1.0in,
	bottom=1.0in,
}
\usepackage[export]{adjustbox}
\usepackage[font={Large}]{caption}
\usepackage{hyperref}
\usepackage{xcolor}
\hypersetup{
    colorlinks,
    linkcolor={red!50!black},
    citecolor={blue!50!black},
    urlcolor={blue!80!black}
}

\begin{document}

% no page numbering
\pagenumbering{gobble}

% From: https://tex.stackexchange.com/a/110908/109818
\begin{figure}[h]
\hspace*{-\dimexpr\oddsidemargin+1in\relax}
\makebox[\paperwidth]{%
\includegraphics[width=1.1\textwidth]{template/fantemplate_image_appendix/img/img1.png}
}
\caption{This is a testing file from \href{https://fanwangecon.github.io/Tex4Econ/}{Tex4Econ} for a PDF file including only images, designed as an add-on Appendix to a File Generated Elsewhere, by Word, for example. Font size for capture is controlled by the Caption package's font option. Image can bleed into 1 inch margin, and is centered using makebox. This is the first image. This image is on top with figure \textit{h} option. Note also that this page does not have a page number, deleted with \textit{gobble}. See Figures \ref{fig:image2} and \ref{fig:image3}. \label{fig:image1}}
\hspace*{-\paperwidth}
\end{figure}

\pagebreak
\clearpage

% start page-numbering
\pagenumbering{arabic} 
\setcounter{page}{26}

\begin{figure}[p]
\hspace*{-\dimexpr\oddsidemargin+1in\relax}
\makebox[\paperwidth]{%
\includegraphics[width=1.0\textwidth]{template/fantemplate_image_appendix/img/img2.png}
}
\caption{This is a testing file from \href{https://fanwangecon.github.io/Tex4Econ/}{Tex4Econ} for a PDF file including only images, designed as an add-on Appendix to a File Generated Elsewhere. This is the second image, centered on the page, and does not bleed into 1 inch margin. Note that the page number is set at 26. See Figures \ref{fig:image1} and \ref{fig:image3}. \label{fig:image2}}
\hspace*{-\paperwidth}
\end{figure}

\pagebreak
\clearpage

% start page-numbering
\pagenumbering{arabic} 
\setcounter{page}{1}

\begin{figure}[p]
\caption{This is a testing file from \href{https://fanwangecon.github.io/Tex4Econ/}{Tex4Econ} for a PDF file including only images, designed as an add-on Appendix to a File Generated Elsewhere. This is the third image, with caption on top. And the image bleeds into the margins by matching paperwidth 95 percent. Image also centered on page. Note that the page number is set at 1. See Figures \ref{fig:image1} and \ref{fig:image2}. \label{fig:image3}}
\hspace*{-\dimexpr\oddsidemargin+1in\relax}
\makebox[\paperwidth]{%
\includegraphics[width=0.95\paperwidth]{template/fantemplate_image_appendix/img/img3.png}
}
\hspace*{-\paperwidth}
\end{figure}

\end{document}

### 2021-06-02 template/fantemplate_image_appendix/draft.tex
Figure only Appendix additional caption options and list of figures.

@@
 \documentclass{article}
+
 \usepackage{geometry}
@@
 
+\newcommand\invisiblesection[1]{%
+  \refstepcounter{section}%
+  \addcontentsline{toc}{section}{\protect\numberline{\thesection}#1}%
+  \sectionmark{#1}}
+
+% https://tex.stackexchange.com/a/395713/109818
+\newcommand{\mycaption}[2]{%
+  \caption[#1]{\textbf{#1}\newline\normalsize#2}%
+}
+
+% list of figures spacing between number and caption
+\usepackage{tocloft}
+\setlength{\cftfignumwidth}{4em}
+% spacing in list of figures
+\setlength\cftbeforefigskip{\baselineskip}
+
 \begin{document}
@@
 \pagenumbering{gobble}
+\begingroup
+  \centering
+  \LARGE \href{https://github.com/FanWangEcon/Tex4Econ/tree/master/template/fantemplate_image_appendix}{Tables and Figures Appendix} for \\[1.0em]
+   Template File for Tables and Figures Appendix \\[1.0em]
+  \large \href{http://fanwangecon.github.io/}{Fan Wang} \\[0.5em]
+  \large \today \\[1.0em]\par
+\endgroup
+
+\listoffigures
+
+\pagebreak
+\clearpage
 
@@
 \begin{figure}[h]
-\hspace*{-\dimexpr\oddsidemargin+1in\relax}
-\makebox[\paperwidth]{%
-\includegraphics[width=1.1\textwidth]{template/fantemplate_image_appendix/img/img1.png}
-}
-\caption{This is a testing file from \href{https://fanwangecon.github.io/Tex4Econ/}{Tex4Econ} for a PDF file including only images, designed as an add-on Appendix to a File Generated Elsewhere, by Word, for example.
+\mycaption{Scatter Plot QSEC HP}{This is a testing file from \href{https://fanwangecon.github.io/Tex4Econ/}{Tex4Econ} for a PDF file including only images, designed as an add-on Appendix to a File Generated Elsewhere, by Word, for example.
 Font size for capture is controlled by the Caption package's font option.
@@
 Note also that this page does not have a page number, deleted with \textit{gobble}.
+Also note this has a caption heading and a caption detail.
+The caption details do not appear in the list of figures.
 See Figures \ref{fig:image2} and \ref{fig:image3}.
 \label{fig:image1}}
+\hspace*{-\dimexpr\oddsidemargin+1in\relax}
+\makebox[\paperwidth]{%
+\includegraphics[width=1.1\textwidth]{img/img1.png}
+}
 \hspace*{-\paperwidth}
@@
 \makebox[\paperwidth]{%
-\includegraphics[width=1.0\textwidth]{template/fantemplate_image_appendix/img/img2.png}
+\includegraphics[width=1.0\textwidth]{img/img2.png}
 }
-\caption{This is a testing file from \href{https://fanwangecon.github.io/Tex4Econ/}{Tex4Econ} for a PDF file including only images, designed as an add-on Appendix to a File Generated Elsewhere.
+\mycaption{QSEC and HP Two Lines}{This is a testing file from \href{https://fanwangecon.github.io/Tex4Econ/}{Tex4Econ} for a PDF file including only images, designed as an add-on Appendix to a File Generated Elsewhere.
 This is the second image, centered on the page, and does not bleed into 1 inch margin.
@@
 \begin{figure}[p]
-\caption{This is a testing file from \href{https://fanwangecon.github.io/Tex4Econ/}{Tex4Econ} for a PDF file including only images, designed as an add-on Appendix to a File Generated Elsewhere.
+\caption{A Standard Caption with Hidden Caption Below Text.
+This is a testing file from \href{https://fanwangecon.github.io/Tex4Econ/}{Tex4Econ} for a PDF file including only images.
+\label{fig:image3}}
+\hspace*{-\dimexpr\oddsidemargin+1in\relax}
+\makebox[\paperwidth]{%
+\includegraphics[width=0.95\paperwidth]{img/img3.png}
+}
+\caption*{This is a testing file from \href{https://fanwangecon.github.io/Tex4Econ/}{Tex4Econ} for a PDF file including only images, designed as an add-on Appendix to a File Generated Elsewhere.
 This is the third image, with caption on top.
@@
 Note that the page number is set at 1.
-See Figures \ref{fig:image1} and \ref{fig:image2}.
-\label{fig:image3}}
+Note this is a standard caption.
+See Figures \ref{fig:image1} and \ref{fig:image2}.}
+\hspace*{-\paperwidth}
+\end{figure}
+
+\invisiblesection{One}
+\setcounter{figure}{0}
+\renewcommand{\thefigure}{A.\arabic{section}.\arabic{figure}}
+
+\begin{figure}[p]
+\caption{A standard caption without additional bottom notes.
+Cash-on-Hand Period t and t+1.
+This Figure is number with a section number from an invisible section.
+The A and B might represent Appendix names.
+See Figure \ref{fig:image5}.
+\label{fig:image4}}
 \hspace*{-\dimexpr\oddsidemargin+1in\relax}
 \makebox[\paperwidth]{%
-\includegraphics[width=0.95\paperwidth]{template/fantemplate_image_appendix/img/img3.png}
+\includegraphics[width=1.0\textwidth]{img/img4.png}
+}
+\hspace*{-\paperwidth}
+\end{figure}
+
+\invisiblesection{Two}
+\renewcommand{\thefigure}{B.\arabic{section}.\arabic{figure}}
+\setcounter{figure}{0}
+
+\begin{figure}[p]
+\mycaption{Asset Choice Grids}{This Figure is number with a different section number from an invisible section.
+The A and B might represent Appendix names.
+See Figure \ref{fig:image4}.
+\label{fig:image5}}
+\hspace*{-\dimexpr\oddsidemargin+1in\relax}
+\makebox[\paperwidth]{%
+\includegraphics[width=1.0\textwidth]{img/img5.png}
 }

### 2022-03-09 template/fantemplate_acceptedsubmit/manuscript_main.tex
Submitted Accepted file template

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Main Text
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}

Insufficient height and weight growth still affect many children around the globe. Estimates are that about 150 million (22 percent) of children under five years of age are stunted \autocite{fao_state_2019}.\footnote{Stunted children have height-for-age more than two standard deviations below the median for a well-nourished population. In 2018, 59 million (30 percent) and 82 million (23 percent) of African and (non-Japanese) Asian children under five years of age were stunted, respectively \autocite{fao_state_2019}.} Studies suggest that these children are at risk of not developing their full human capital potential \autocite{behrman_nutritional_2009, black_early_2017, hoddinott_effect_2008, hoddinott_adult_2013, hoddinott_economic_2013, maluccio_impact_2009, richter_investing_2017, victora_maternal_2008}. Our paper contributes to a growing literature that investigates how interventions in early childhood can contribute to foster human-capital formation for at-risk children \autocite[e.g.,][]{carneiro_heckman_2003, cunha_heckman_2007, cunha_heckman_jeea, cunha_heckman_schennach_2010, heckman_etal_jpube2010, heckman_etal_qe2010, heckman_etal_aer2010, campbell_etal_2014, gertler_etal_2014}.

\section{The Model}

Following our discussions on parental beliefs, given $\Omega_{y,v} = \big(Y, p^{N}_{yv}, \delta, X, \epsilon, \mu_{R_{y,v}}, \sigma_{R_{y,v}}^{2} \big)$, each household solves the following maximization problem:

\begin{equation}
\label{eq:optimain}
\max_{C,N} \Bigg\{C+\rho\cdot C^{2}+  \left\{ \gamma\cdot H^{24}+\lambda \cdot \int_{R_{yv}} \left(H^{24}-R_{yv}\right)\mathbbm{1}\left\{ H^{24}\ge R_{yv}\right\}\phi \left(R_{yv};\mu_{R_{yv}}, \sigma_{R_{yv}}^{2} \right) dR_{yv} \right\} \Bigg\}
\end{equation}

subject to the budget constraint \eqref{eq:budget_constraint}, the production function \eqref{eq:prod_function}, the equation that determines mean \eqref{eq:mean_belief}, and some measure of variance beliefs $\sigma^2_{R_{y,v}}$. Let $N\left(\Omega_{y,v}\right)$ denote the policy function for nutrition. If $\sigma^2_{R_{y,v}}=0$, preferences for health would be piecewise linear with a kink at $\mu_{R_{yv}}$. If $\sigma^2_{R_{y,v}}>0$, preferences for health are continuously differentiable; if additionally $\gamma>0$ and $\lambda<0$, preferences for health are concave.

The optimization problem in Equation \eqref{eq:optimain} does not permit analytical solutions.\footnote{In Appendix Section \ref{sec:apprefsd}, we discuss the first-order condition for the optimal nutritional choice problem. In Appendix Section \ref{sec:modelsolu}, we describe the procedures for numerical solutions.} To illustrate how changes in key parameters impact optimal choices, we present in Figure \ref{fig:indiff} the consumption-health possibility frontier along with several indifference curves for an individual, using estimated parameters from our model.\footnote{The consumption-health possibility frontier is jointly determined by the household budget and the child height production function.} In each panel, solid dots indicate optimal choices (i.e., the combination of height and household consumption where indifference curves are tangent to the consumption-health possibility frontier).

Panel a shows several indifference curves and the consumption-health possibility frontier. The figure clearly shows the asymmetry in indifference curves. To the left of the mean reference height, parents are willing to sacrifice a large amount of consumption for a small increase in the child's height. In contrast, to the right of the mean reference height, parents are willing to forego only a small amount of consumption for a large increment in height.

In panel b, we vary the $\lambda$ parameter. Marginal benefits of additional nutritional intakes on expected utility are increasing in $\lambda$. Additionally, reference points matter more when $\lambda$ deviates more from zero. Visually, at more negative values of $\lambda$, the curvature of the indifference curve increases. The greater the curvature of the indifference curve, the more critical the role of reference height in determining parental nutritional choices and, consequently, the child's height at age 24 months.

In panel b, we fix $\lambda$ and vary $\mu_{R_{y,v}}$. When $\lambda<0$, the marginal benefits of additional nutritional intakes are increasing in $\mu_{R_{y,v}}$. The greater the value of $\mu_{R_{y,v}}$, the lower the household consumption and the taller the child at age 24 months.

Finally, panel d of Figure \ref{fig:indiff} presents the effect of increasing uncertainty about the parental estimates of mean height, $\sigma^2_{R_{y,v}}$. Given the estimated parameters from the empirical model, higher values of $\sigma^2_{R_{y,v}}$ increase the marginal benefits of additional nutrition when expected height exceeds $\mu_{R_{y,v}}$ and reduces the curvature of the indifference curves. These lead to an increase in nutritional choices. In the limit, as $\sigma^2_{R_{y,v}}$ approaches infinity, preferences become linear in height, and predictions from models with and without reference points become empirically indistinguishable.

We use the estimated parameters to produce Figure \ref{fig:indiff}. However, in general, the household response to an increase in uncertainty depends on the values of $\gamma$ and $\lambda$. When marginal utility gains from additional investment in health are positive after the mean reference point $\mu_{R}$ -- which means $-\gamma < \lambda < 0$ -- an increase in $\sigma_{R}$ will lead to an increase in investments in health. In contrast, if marginal utility from additional investment in health is negative after the mean reference point $\mu_{R}$ -- which generates backward bending indifference curves -- a similar increase of $\sigma_{R}$ could reduce investment in health. Ceteris paribus, there is a threshold level of $\lambda$ where increases in $\sigma_{R}$ have no impact on health investments. In Appendix Section \ref{sec:apprefsd}, we discuss the intuition behind these results and provide graphical illustrations.

\section{Data}

The data we use in this paper comes from an experimental intervention conducted by The Institute of Nutrition of Central America and Panama (INCAP), which started a nutritional-supplementation trial in 1969. Four villages from eastern Guatemala were selected, one pair of villages that was relatively populous (\textasciitilde900 residents each) and one pair that was less populous (\textasciitilde500 residents each). The villages were similar in child nutritional status, measured as the height at three years of age \autocite{habicht_nutritional_1995}. Over 50\% of children lacked proper nutrition and were severely stunted, measured as height-for-age z-scores less than -3.\footnote{Guatemalan children continue to suffer from severe malnutrition. In 2015, among Guatemalan households in the lowest quintile of wealth, approximately 70 percent of children younger than five were stunted. In middle-quintile Guatemalan households, 45 percent of children younger than five were stunted \autocite{fao_state_2019}.} The intervention consisted of randomly assigning nutritional supplements. One large and one small village were selected to receive a high-protein drink called Atole, and the other two were selected to receive an alternative supplement called Fresco. Each serving of Atole (180 ml) contained 11.5 grams of protein and 163 kcal. Fresco had no proteins, and each serving (180 ml) had 59 kcal. The central hypothesis was that the protein supplementation would accelerate physical and mental development \autocite{habicht_nutritional_1995}. The intervention started in February 1969 in the larger villages and in May 1969 in the smaller villages and lasted until the end of February 1977, with data collection taking place until September 1977 \autocite{maluccio_impact_2009,islam_evidence_2009}. The nutritional supplements were distributed in feeding centers located centrally in each village. The centers were open twice a day, two to three hours in the mid-morning and two to three hours in the mid-afternoon. All village members had access to the supplements at the feeding centers.

Table \ref{summcovarmain} presents summary statistics for the variables that we use in our analysis. In Panels a and b, we show statistics on gender, income, and prices for our main sample of 503 individuals (panel a) and gender and income for the fuller sample of 1155 individuals (panel b). In Panels c and d, we show statistics on heights and nutritional intakes, respectively. Table \ref{summcovarmain} has five columns. The first column presents the overall means and standard deviations in Atole and Fresco villages combined. The second and third columns present Atole and Fresco village-specific means and standard deviations. Column four shows the gaps in means between Atole and Fresco villages for each variable, and column five presents the p-values for the statistical significance of these gaps.

As mentioned before, the intervention took place in four villages, two Atole or treatment villages and two Fresco or control villages. In the rest of the paper, when we refer to Atole and Fresco villages, we merge the information of the two villages that received the same supplement. The limited number of villages might impact the descriptive statistics' standard errors since villages can share common unobserved shocks. We follow the methods developed by \textcite{donald2007inference} and \textcite{cameron2015practitioner} to study how robust our results are to this clustering. The method proposed by \textcite{donald2007inference} consists of estimating averages by clusters, controlling for individual variables, and using those averages in the regressions. This method greatly reduces the number of observations. We define cluster year-village pairs and half-year-village pairs to implement this procedure. Following \textcite{cameron2015practitioner} we also implement a pair-cluster bootstrap, using the same cluster definition as in the \textcite{donald2007inference} method. Table \ref{summcovarmain} and Figure \ref{fig:PortHgtGap} report the results without using the clusters corrections, but the results are robust to those methods.

\section{Results}

We present estimated parameters in Table \ref{tab:paramestitwo}, with standard errors shown in parentheses. For preferences, $\rho$ is -0.047, indicating that preferences are concave in $c$. $\gamma$ and $\lambda$ are $0.033$ and $-0.026$, respectively. Therefore, preferences are also concave in height, and the curvature of the indifference curves indicates the asymmetry in responses. Parents prefer taller to shorter children, but the marginal benefit from an additional centimeter of height beyond the reference comparison height is close to zero (albeit positive).

The price discount parameter $\delta$ is $0.376$, representing a $38\%$ discount in protein prices in Atole villages. The production-function parameters are $\beta=0.073$, $\alpha_{H_0}=0.022$, $\alpha_{male}=0.009$, $A=4.144$, and $\sigma_{\epsilon}=0.010$. Given these parameters, we show the consumption- and height-possibility frontier along with indifference curves for an individual in panel a of Figure \ref{fig:indiff}.

The measurement-error estimates are $\sigma_{\eta}=0.382$ and $\sigma_{\iota}=0.043$. These findings indicate that measurement error is more severe for nutritional intake than height, which is intuitive.

We use the estimated model to decompose the relative contributions of prices and reference points to the height dynamics in Atole and Fresco villages. In Appendix \ref{sec:targetuniversal}, we discuss additional counterfactuals in which we compare the relative impacts of poor-targeted and universal policy experiments given reference points.

\section{Conclusion}

In this paper, we build and estimate a child-nutritional investment model. The model considers reference-dependent preferences, where the reference is with respect to the heights of the previous cohort of children who live in the same village. Reference points shift endogenously as households observe children’s heights from earlier birth cohorts changing.

For researchers interested in the impact of price subsidies and income transfers, we have introduced a long-term secondary channel -- endogenous changes in reference points -- that might affect the impacts of these policies. For the protein-supplement experiment implemented in Guatemala, which we interpret as a price-discount policy, by 1975 -- six years after the start of the policy – 57\% to 65\% of the policy’s impact are due to its impact on shifting reference points.

Our paper also shows significant height increases might be realized from shifting reference points for highly-stunted populations. It is an open question how to exogenously shift these reference points in the short run, although the Peruvian experience mentioned in the introduction indicates that educational campaigns could be effective on a large scale over time. The cost of an educational campaign to inform households about alternative reference heights well might be lower compared to income transfers and price subsidies with similar effects on heights.

We recognize that our analysis requires a crucial assumption: parents use the data on a selected group of children to estimate mean and variance beliefs about the reference height. We argued that our assumption is consistent with research in economics, medicine, and anthropology, but we recognize that there are many other alternatives, such as rational expectations, Bayesian updating, or social learning models. Unfortunately, the literature in economics knows very little about such a critical element of the model we propose in this paper. Therefore, it is necessary to encourage research that elicits parental subjective distributions of reference points as part of parent-directed interventions to reduce stunting. Within a randomized controlled trial, the availability of such data would shed light on the process parents use to update critical moments of the subjective distribution. With such evidence, one could have a more robust representation of our model that would better inform the design of public policies to improve children’s health.

\clearpage
\pagebreak

### 2022-03-09 template/fantemplate_acceptedsubmit/manuscript_online_appendix.tex
Submitted Accepted file template

% reset page numbers
\pagenumbering{arabic}
\setcounter{page}{1}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Title Page for Appendix
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% special footnote symbols
\renewcommand*{\thefootnote}{\fnsymbol{footnote}}
\begingroup
  \doublespacing
  \centering
  \Large ONLINE APPENDIX \\[1.5em]
  \LARGE \PAPERTITLE \\[0.75em]
  \large
    Fan Wang,\footnote[1]{\AUTHORWANG}\\[1.0em]
\endgroup
\clearpage

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Appendix A, Solution and Estimation Details
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Set equation, figure, table indexing
\renewcommand{\thefigure}{A.\arabic{figure}}
\setcounter{figure}{0}
\renewcommand{\thetable}{A.\arabic{table}}
\setcounter{table}{0}
\renewcommand{\theequation}{A.\arabic{equation}}
\setcounter{equation}{0}
\renewcommand{\thefootnote}{A.\arabic{footnote}}
\setcounter{footnote}{0}

\section{Solution and Estimation Details (Online Publication)}

\subsection{Reference Point and Preference for Height \label{sec:apprefsd}}

\subsubsection{The Optimal Nutritional-Choice Problem\label{sec:fullproblem}}
Given Equation \eqref{eq:budget_constraint} for the budget constraint, Equation \eqref{eq:prod_function} for the production function, Equation \eqref{eq:preferences} for preferences, and the reference points distributions discussed in Section \ref{sec:information}, the nutritional-choice problem is:
\begin{align}
    \begin{gathered}\label{eq:optimization}
        \max_{N}
        \left\{
            C + \rho\cdot C^{2} +
            \gamma \cdot H^{24} +
            \lambda \cdot \int_{R_{yv}} \left(H^{24}-R_{yv}\right)\mathbbm{1}\left\{ H^{24}\ge R_{yv}\right\}dF(R_{yv})
        \right\}
        \\
        C + p^{N}_{yv}\cdot(1-\delta\cdot\mathbbm{1}\left(v=Atole\right))\cdot N = Y\\
        H^{24} = \exp(A+ X\cdot\alpha+\epsilon)\cdot N^{\beta}
    \end{gathered}
\end{align}
For notational convenience, we drop subscripts, let $\hat{A}=\exp\left(A + X\cdot\alpha + \epsilon\right)$, replace $H^{24}$ and $C$ as functions of $N$, and rewrite Equation \eqref{eq:optimization} as:
\begin{align}
    \begin{gathered}\label{eq:optimization:single}
        \max_{N}
        \left\{
        \begin{array}{c}
            \left(Y - p \cdot N\right) +
            \rho\cdot\left(Y - p \cdot N\right)^{2} \\
            + \gamma \cdot \hat{A} \cdot N^{\beta} \\
            + \lambda \cdot \left(\hat{A} \cdot N^{\beta}-\mu_R\right)
                    \Phi\left(\frac{\hat{A} \cdot N^{\beta}-\mu_R}{\sigma_R}
                \right) \\
            + \lambda \cdot \sigma_R \cdot \phi\left(
                \frac{\hat{A} \cdot N^{\beta}-\mu_R}{\sigma_R}
                \right) \\
        \end{array}
        \right\}
    \end{gathered}
\end{align}
In Equation \eqref{eq:optimization:single}, we analytically integrate the integral from Equation \eqref{eq:optimization}.\footnote{The expected utility function contained the expectation of a truncated normal random variable:
\begin{multline}
	\int_{R_{yv}} \left(H^{24}-R_{yv}\right)\mathbbm{1}\left\{ H^{24}\ge R_{yv}\right\}dF(R_{yv})=  \left(H^{24}-\mu_{R_{yv}}\right)\cdot\left(\Phi\left(\frac{H^{24}-\mu_{R_{yv}}}{\sigma_{R_{yv}}}\right)\right)+\sigma_{R_{yv}}\phi\left(\frac{H^{24}-\mu_{R_{yv}}}{\sigma_{R_{yv}}}\right) \label{eq:truncatedNormal}
\end{multline}}

\subsubsection{Optimal Nutritional Choices and $\sigma_R$\label{sec:sigmaopti}}

Panels a, c, and e of Figure \ref{fig:refpointhgtutil} show health (height) at age 24 months along the x-axis and household consumption along the y-axis. We plot the shape of indifference curves for a given value of $\gamma$ and different values of $\lambda$ and $\sigma_R$ together with the consumption-health possibility frontier, which combines the budget constraint with the production function for height.

Panels b, d, and f show the difference between height at age 24 months and the mean beliefs about the reference height along the x-axis, and the component of utility that  includes the reference point for height along the y-axis. We believe it is helpful to zero in on this component because it is the primary driver of our empirical analysis, and it shows the role that the parameters $\lambda$ and $\sigma_R$ play in our study of the determinants of height at age 24 months.

In panels a and b, we use our estimated values of $\gamma$ and $\lambda$ for the scenario in which $\sigma_R = 0.5$. In panels c and d, we set $\lambda$ to be negative $1.5$ times the estimated value of $\gamma$. In panels e and f, the $\lambda$ value is lowered to be negative $2.5$ times the estimated value of $\gamma$.

For the configuration of values of $\gamma$ and $\lambda$ in panel a, an increase in $\sigma_R$ increases optimal height because the marginal benefits of height levels that exceed $\mu_{R}$ remains positive as panel b shows. However, for the configuration of values of $\gamma$ and $\lambda$ in panel c, we have a bliss point for height that varies just a little as we increase the value of $\sigma_R$. In panel e, as the value of $\lambda$ continues to decrease, the disutility of height beyond the mean reference point decreases so fast that the uncertainty becomes costly. As a result, an exogenous increase in $\sigma_R$ reduces the optimal level of height.

\newcommand{\subFigWidthApp}{0.50}
\begin{figure}[hbt!]
    \centering
    \begin{subfigure}[b]{\subFigWidthApp\textwidth}
        \centering
        \includegraphics[width=\linewidth]{\string"fig_main/fig1d_Tester_Indiff_person_495_refsd_increasem3_20210130".eps}
        \caption{Choices with $\gamma=0.0325$, $\lambda=-0.0257$}
    \end{subfigure}~
	\begin{subfigure}[b]{\subFigWidthApp\textwidth}
	    \centering
    	\includegraphics[width=\linewidth]{\string"tab_fig_online_appendix/fig_a1b_Tester_UHgt_moresd_higherH".eps}
    	\caption{Health preference with $\gamma=0.0325$, $\lambda=-0.0257$}
	\end{subfigure}
	\par\medskip
	\begin{subfigure}[b]{\subFigWidthApp\textwidth}
        \centering
        \includegraphics[width=\linewidth]{\string"tab_fig_online_appendix/fig_a1c_Tester_Indiff_person_495_refsd_noimpactm3_20210130".eps}
        \caption{Choices with $\gamma=0.0325$, $\lambda=-\gamma\cdot1.5$}
    \end{subfigure}~
	\begin{subfigure}[b]{\subFigWidthApp\textwidth}
	    \centering
	    \includegraphics[width=\linewidth]{\string"tab_fig_online_appendix/fig_a1d_Tester_UHgt_moresd_noimpact".eps}
	    \caption{Health preference with $\gamma=0.0325$, $\lambda=-\gamma\cdot1.5$}
	\end{subfigure}
	\par\medskip
	\begin{subfigure}[b]{\subFigWidthApp\textwidth}
        \centering
        \includegraphics[width=\linewidth]{\string"tab_fig_online_appendix/fig_a1e_Tester_Indiff_person_495_refsd_decreasem3_20210130".eps}
        \caption{Choices with $\gamma=0.0325$, $\lambda=-\gamma\cdot2.5$}
    \end{subfigure}~
	\begin{subfigure}[b]{\subFigWidthApp\textwidth}
	    \centering
	    \includegraphics[width=\linewidth]{\string"tab_fig_online_appendix/fig_a1f_Tester_UHgt_moresd_lowerH".eps}
	    \caption{Health preference with $\gamma=0.0325$, $\lambda=-\gamma\cdot2.5$}
	\end{subfigure}
	\caption{Reference points distribution standard deviation ($\sigma_R$) and health outcomes}
	\label{fig:refpointhgtutil}
\end{figure}
\pagebreak

\clearpage
\pagebreak

\subsection{Alternative Assumptions about Variance Beliefs} \label{sec:appsecalter}

Our model assumes that parents adopt the expected height of two-year-old children in their village as the reference point. Parents estimate the expected height using the observations of the children in their village. We assume that their estimation of the expected height follows a normal distribution with mean belief parameter $\mu_{R_{y,v}}$ and variance belief parameter $\sigma_{R{y,v}}^{2}$. In our empirical analysis, we assume that $\mu_{R_{y,v}}$  captures the uncertainty about the mean belief, so  $\sigma_{R{y,v}} = 0.5$.

In our sensitivity analysis, we adopt the assumption that the variance belief is equal to the variance of height. We argue that this approach is an upper bound for variance beliefs. Under this assumption, $\sigma_{R{y,v}} = 3.5$. To complete our sensitivity analysis, we also investigate our model's decomposition findings for scenarios in which $\sigma_{R{y,v}} = 1.5$ and $\sigma_{R{y,v}} = 2.5$.

\subsection{Data for Estimation \label{sec:estidata}}

We include in the estimation children who were born between 1970 and 1975. We show summary statistics for these children in Sections \ref{sec:stat} and \ref{sec:gap}. As discussed earlier, we do not observe both initial heights and heights at month 24 for children born before or after these years.

We use the months 15 to 24 average protein intakes, heights at month 24, protein prices, incomes, gender, and initial height variables shown in Table \ref{summcovarmain} and described in Section \ref{sec:stat} as $N$, $H^{24}$, $p_{yv}^{N}$, $Y$, and components of $X$. We use protein intakes because \textcite{puentes_early_2016} shows that proteins rather than non-protein components of calories matter for height growth in these INCAP data. Ideally, our intake variable should be averaged from month 0 to month 24. However, we do not observe protein values from month 0 to month 12 for close to half of our sample because data collection for this age group started in 1973. Also, it is not easy to estimate the protein component of breastmilk for children who rely on breastfeeding in the first year of life.

\subsection{Additional Estimation Information \label{sec:estimorer}}

\subsubsection{Additional Model fit}
\input{tab_fig_online_appendix/tab_a1_modelfitmulti}

In Table \ref{tab:paramfitmulti}, we provide additional information on the fits of the estimated model under varying assumptions about $\sigma_{R_{y,v}}$. Model fits with respect to protein choices and height outcomes are presented across the columns, and model fits with respect to overall averages in Atole and Fresco villages, as well as average by gender and time are presented in separate rows.

Estimated models across $\sigma_{R_{y,v}}$ assumptions -- with estimates shown in Table \ref{tab:paramesti} -- are all able to provide similarly good fits between model predictions and key data moments.

\subsubsection{Additional Estimates}

\begin{figure}[htbp]
\makebox[\textwidth][c]{\includegraphics[width=1.10\textwidth]{tab_fig_online_appendix/fig_a2_estimates_final.png}}
\caption{Preference parameter estimates from estimating the model under different assumptions about the standard deviation of reference points distribution $\sigma_{R_{y,v}}$}
\label{fig:estimatesmulti}
\end{figure}

In Table \ref{tab:paramesti}, we present parameter estimates under four assumptions for $\sigma_{R_{y,v}}$ from 0.5 cm to 3.5 cm. In this section, for additional information, we provide key estimates from estimating the model at $\sigma_{R_{y,v}}$ values from 0.25 cm to 3.75 cm at 0.05 cm intervals. In Figure \ref{fig:estimatesmulti}, we visualize the point-estimates results for the core preference parameters of $\rho$, $\gamma$ and $\lambda$ in three sub-figures. We mark with dashed blue lines values of $\sigma_{R_{y,v}}$ along the x-axis where $\sigma_{R_{y,v}}=0.5$ and $\sigma_{R_{y,v}}=3.5$.

For $\rho$, the quadratic coefficient on non-nutritional consumptions, the estimated coefficient becomes more negative as $\sigma_{R_{y,v}}$ increases. This finding implies lower marginal gains from additional non-nutritional consumption at higher $\sigma_{R_{y,v}}$.

\clearpage
\pagebreak

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Appendix Bibliography
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Bibliography
\begingroup
\setstretch{1.0}
\setlength\bibitemsep{0pt}
\printbibliography[title=References for Online Appendix]
\endgroup
\pagebreak

### 2022-03-09 template/fantemplate_acceptedsubmit/manuscript_tab_fig.tex
Submitted Accepted file template

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Figures
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Figure 1
\newcommand{\subFigWidth}{0.50}
\begin{figure}[H]
    \centering
    \begin{subfigure}[b]{\subFigWidth\textwidth}
        \centering
        \includegraphics[width=\linewidth]{\string"fig_main/fig1a_Tester_Indiff_person_495_med_2021".eps}
        \caption{Contours of indifference curves at given estimates}
    \end{subfigure}~
	\begin{subfigure}[b]{\subFigWidth\textwidth}
	    \centering
    	\includegraphics[width=\linewidth]{\string"fig_main/fig1b_Tester_Indiff_person_495_lambdam3_20210130".eps}
    	\caption{Vary $\lambda$}
	\end{subfigure}
	\par\medskip
	\begin{subfigure}[b]{\subFigWidth\textwidth}
        \centering
        \includegraphics[width=\linewidth]{\string"fig_main/fig1c_Tester_Indiff_person_495_refmeanm3_20210130".eps}
        \caption{Vary $\mu_{R}$}
    \end{subfigure}~
	\begin{subfigure}[b]{\subFigWidth\textwidth}
	    \centering
	    \includegraphics[width=\linewidth]{\string"fig_main/fig1d_Tester_Indiff_person_495_refsd_increasem3_20210130".eps}
	    \caption{Vary $\sigma_{R}$}
	\end{subfigure}
	\caption{Consumption and height outcome indifference curves and choice frontiers. \emph{Note}: Health possibility frontier and indifference curves are visualized in blue (solid-line) given estimated parameters and characteristics for one particular child. The consumption and expected height outcome frontier is determined by the budget constraint as well as the production function. Panels b, c and d show results from varying one parameter at a time in red (dashed-line) and orange (dotted-line). See Section \ref{sec:maximize} for discussions.}
	\label{fig:indiff}
\end{figure}
\pagebreak

% Figure 2
\begin{figure}[H]
    \centering
    \begin{subfigure}[t]{.43\textwidth}
        \centering
        \includegraphics[width=\linewidth]{\string"fig_main/fig2a_ss_mean_hgt24_yr_trimmed".eps}
        \caption{Height}
    \end{subfigure}~
	\begin{subfigure}[t]{0.57\textwidth}
	    \centering
    	\includegraphics[width=\linewidth]{\string"fig_main/fig2b_ss_mean_prot_15t24_yr".eps}
    	\caption{Protein}
	\end{subfigure}
	\caption{Increasing protein and height gaps across cohorts. \emph{Note}: See Section \ref{sec:gap} for discussions.}
	\label{fig:PortHgtGap}
\end{figure}
\pagebreak

\clearpage

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Tables
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Table 1
\input{"tab_main/tab1_summ_stats_covar_main_keep.tex"}
\clearpage
% Table 2
\input{tab_main/tab2_estimates_2018}
\clearpage
% Table 3
\input{"tab_main/tab3_modelfit.tex"}
\clearpage
% Table 4
\input{"tab_main/tab4_frescoatoledecompose.tex"}
\clearpage
% Table 5
\input{tab_main/tab5_estimates_2021}
\clearpage
\pagebreak

### 2022-03-09 template/fantemplate_acceptedsubmit/manuscript_title_etc.tex
Submitted Accepted file template

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 1. Define Keywords, JEL
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand{\PAPERKEYWORDS}{\textbf{Keywords}: Early Childhood, Height, Reference Points, Nutrition, Anthropometrics}
\newcommand{\PAPERJEL}{\textbf{JEL}: I15, D8, D9, O15}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 2. Define Title
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand{\PAPERTITLE}{\href{https://papers.ssrn.com/sol3/papers.cfm?abstract_id=3167023}{You are What Your Parents Expect: Height and Local Reference Points}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 3. Define Authors contact information
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand{\AUTHORWANG}{Fan Wang: Department of Economics, University of Houston, Houston, Texas, USA (email: fwang26@uh.edu)}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 4. Define Thanks
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand{\ACKNOWLEDGMENTS}{
We thank \blindtext}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 5. Define Abstract
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand{\PAPERABSTRACT}{
Recent estimates are that about 150 million children under five years of age are stunted, with substantial negative consequences for their schooling, cognitive skills, health, and economic productivity. Therefore, understanding what determines such growth retardation is significant for designing public policies that aim to address this issue. We build a model for nutritional choices and health with reference-dependent preferences. Parents care about the health of their children relative to some reference population. In our empirical model, we use height as the health outcome that parents target. Reference height is an equilibrium object determined by earlier cohorts' parents' nutritional choices in the same village. We explore the exogenous variation in reference height produced by a protein-supplementation experiment in Guatemala to estimate our model’s parameters. We use our model to decompose the impact of the protein intervention on height into price and reference-point effects. We find that the changes in reference points account for 65\% of the height difference between two-year-old children in experimental and control villages in the sixth annual cohort born after the initiation of the intervention.
\PAPERJEL}

### 2022-03-09 template/fantemplate_acceptedsubmit/tab_fig_online_appendix/tab_a1_modelfitmulti.tex
Submitted Accepted file template

\begin{table}[htbp]
\renewcommand{\arraystretch}{1.3}
\centering
{\small
\def\sym#1{\ifmmode^{#1}\else\(^{#1}\)\fi}
\caption{Model Predictions from estimating the model under different assumptions about the standard deviation of reference points distribution $\sigma_{R}$.\label{tab:paramfitmulti}}
\begin{adjustbox}{max width=1\textwidth}
\begin{tabular}{lcccc|cccc}
\toprule
& \multicolumn{4}{C{6cm}}{\hspace*{-10mm}\textbf{Average protein choices}} & \multicolumn{4}{C{6cm}}{\hspace*{-15mm}\textbf{Average height outcome}} \\
\cmidrule(l{5pt}r{5pt}){2-5} \cmidrule(l{5pt}r{5pt}){6-9}
& \multicolumn{1}{C{1.5cm}}{\textit{\small$\sigma_R=0.5$}} & \multicolumn{1}{C{1.5cm}}{\textit{\small$\sigma_R=1.5$}} & \multicolumn{1}{C{1.5cm}}{\textit{\small$\sigma_R=2.5$}} & \multicolumn{1}{C{1.5cm}}{\textit{\small$\sigma_R=3.5$}} & \multicolumn{1}{C{1.5cm}}{\textit{\small$\sigma_R=0.5$}} & \multicolumn{1}{C{1.5cm}}{\textit{\small$\sigma_R=1.5$}} & \multicolumn{1}{C{1.5cm}}{\textit{\small$\sigma_R=2.5$}} & \multicolumn{1}{C{1.5cm}}{\textit{\small$\sigma_R=3.5$}} \\      
\midrule
\multicolumn{9}{l}{\hspace*{0mm}\textbf{\normalsize Panel a: Average}} \\
Fresco          &  19.38&   19.24&   19.25&   19.29&   76.77&   76.77&   76.78&   76.77\\
Atole           &  25.10&   25.30&   25.30&   25.47&   78.19&   78.32&   78.33&   78.39\\
\midrule
\multicolumn{9}{l}{\hspace*{0mm}\textbf{\normalsize Panel b: Averages across genders}} \\
Fresco Female   &  18.15&   18.14&   18.16&   18.15&   76.07&   76.11&   76.12&   76.11\\
Fresco Male     &  23.96&   24.17&   24.17&   24.24&   77.60&   77.74&   77.75&   77.81\\
Atole Female    &  20.48&   20.23&   20.23&   20.30&   77.40&   77.36&   77.36&   77.35\\
Atole Male      &  26.16&   26.34&   26.33&   26.60&   78.74&   78.85&   78.86&   78.93\\
\midrule
\multicolumn{9}{l}{\hspace*{0mm}\textbf{\normalsize Panel c: Averages across years}} \\
Fresco 1970-71  &  18.43&   18.61&   18.63&   18.61&   76.52&   76.59&   76.60&   76.57\\
Atole  1970-71  &  23.13&   23.52&   23.46&   23.46&   77.71&   77.85&   77.85&   77.88\\
Fresco 1972-73  &  19.30&   19.22&   19.24&   19.25&   76.80&   76.79&   76.79&   76.79\\
Atole  1972-73  &  24.51&   24.76&   24.76&   24.92&   78.07&   78.20&   78.20&   78.27\\
Fresco 1974-75  &  19.97&   19.61&   19.61&   19.69&   76.89&   76.86&   76.86&   76.85\\
Atole  1974-75  &  27.13&   27.13&   27.15&   27.46&   78.65&   78.78&   78.80&   78.87\\
\bottomrule
\addlinespace[0.5em]
\multicolumn{9}{p{1\textwidth}}{\parbox[t]{1\textwidth}{}}\\
\end{tabular}\end{adjustbox}
}
\end{table}

### 2022-03-09 template/fantemplate_acceptedsubmit/tab_main/tab1_summ_stats_covar_main_keep.tex
Submitted Accepted file template

\begin{table}[t!]
{\small
\centering                                 \def\sym#1{\ifmmode^{#1}\else\(^{#1}\)\fi}                                 \caption{Summary statistics for various variables\label{summcovarmain}}                                 \begin{adjustbox}{max width=1\textwidth}                                 \begin{tabular}{m{6.9cm} >{\centering\arraybackslash}m{1.8cm} >{\centering\arraybackslash}m{1.8cm} >{\centering\arraybackslash}m{1.8cm} >{\centering\arraybackslash}m{1.8cm} >{\centering\arraybackslash}m{1.8cm}}                                 \toprule                                                                                         & \multicolumn{5}{C{9cm}}{Atole and Fresco villages differences} \\                                                 \cmidrule(l{5pt}r{5pt}){2-6}                                                   & \multicolumn{1}{C{1.8cm}}{\small \textbf{All}} & \multicolumn{2}{C{3.6cm}}{\small \textbf{Group averages}} & \multicolumn{2}{C{3.6cm}}{\small \textbf{p-values testing}} \\                                                  \cmidrule(l{5pt}r{5pt}){2-2} \cmidrule(l{5pt}r{5pt}){3-4} \cmidrule(l{5pt}r{5pt}){5-6}                                                  & \multicolumn{1}{C{1.8cm}}{\textit{\small mean (sd)}} & \multicolumn{1}{C{1.8cm}}{\textit{\small Fresco}} & \multicolumn{1}{C{1.8cm}}{\textit{\small Atole}} & \multicolumn{1}{C{1.8cm}}{\textit{\small gap}} & \multicolumn{1}{C{1.8cm}}{\textit{\small p-value}} \\
\midrule
\multicolumn{6}{l}{\vspace*{-3mm}\hspace*{-0mm}\textbf{\normalsize Panel a: Gender income price (N=503, main sample)}} \\                                          &            &            &            &            &            \\
Male                &        0.52&        0.52&        0.52&       -0.00&        0.92\\
                    &\vspace*{-2mm}{\footnotesize (0.50) }&\vspace*{-2mm}{\footnotesize (0.50) }&\vspace*{-2mm}{\footnotesize (0.50) }&            &            \\
Income (quetzale)       &      515.57&      503.68&      526.00&       22.32&        0.59\\
                    &\vspace*{-2mm}{\footnotesize (460.9) }&\vspace*{-2mm}{\footnotesize (464.4) }&\vspace*{-2mm}{\footnotesize (458.4) }&            &            \\
Mth 15-24 protein price (quetzale/10k grams)&       52.58&       52.47&       52.68&        0.21&        0.54\\
                    &\vspace*{-2mm}{\footnotesize (3.87) }&\vspace*{-2mm}{\footnotesize (3.93) }&\vspace*{-2mm}{\footnotesize (3.81) }&            &            \\
\midrule
\multicolumn{6}{l}{\vspace*{-3mm}\hspace*{-0mm}\textbf{\normalsize Panel b: Gender income (N=1115, height observed once in first 24 months)}} \\                                          &            &            &            &            &            \\
Male                &        0.53&        0.53&        0.53&        0.00&        0.98\\
                    &\vspace*{-2mm}{\footnotesize (0.50) }&\vspace*{-2mm}{\footnotesize (0.50) }&\vspace*{-2mm}{\footnotesize (0.50) }&            &            \\
Income (quetzale)       &      449.49&      444.63&      454.06&        9.43&        0.72\\
                    &\vspace*{-2mm}{\footnotesize (432.3) }&\vspace*{-2mm}{\footnotesize (446.4) }&\vspace*{-2mm}{\footnotesize (419.0) }&            &            \\
\midrule
\multicolumn{6}{l}{\vspace*{-3mm}\hspace*{-0mm}\textbf{\normalsize Panel c: Height}} \\                                          &            &            &            &            &            \\
Month 0 (cm)  {\footnotesize N=503}&       49.64&       49.79&       49.52&       -0.27&        0.19\\
                    &\vspace*{-2mm}{\footnotesize (2.29) }&\vspace*{-2mm}{\footnotesize (2.29) }&\vspace*{-2mm}{\footnotesize (2.29) }&            &            \\
Month 6 (cm)  {\footnotesize N=463}&       62.72&       62.49&       62.93&        0.44&        0.05\\
                    &\vspace*{-2mm}{\footnotesize (2.46) }&\vspace*{-2mm}{\footnotesize (2.50) }&\vspace*{-2mm}{\footnotesize (2.42) }&            &            \\
Month 12 (cm) {\footnotesize N=475}&       68.81&       68.45&       69.13&        0.68&        0.01\\
                    &\vspace*{-2mm}{\footnotesize (2.99) }&\vspace*{-2mm}{\footnotesize (3.13) }&\vspace*{-2mm}{\footnotesize (2.83) }&            &            \\
Month 18 (cm) {\footnotesize N=482}&       73.37&       72.88&       73.80&        0.92&        0.00\\
                    &\vspace*{-2mm}{\footnotesize (3.23) }&\vspace*{-2mm}{\footnotesize (3.26) }&\vspace*{-2mm}{\footnotesize (3.15) }&            &            \\
Month 24 (cm) {\footnotesize N=503}&       77.66&       76.97&       78.30&        1.33&        0.00\\
                    &\vspace*{-2mm}{\footnotesize (3.47) }&\vspace*{-2mm}{\footnotesize (3.49) }&\vspace*{-2mm}{\footnotesize (3.33) }&            &            \\
\midrule
\multicolumn{6}{l}{\vspace*{-3mm}\hspace*{-0mm}\textbf{\normalsize Panel d: Average daily nutritional intake}} \\                                          &            &            &            &            &            \\
Month 15 (grams/day) {\footnotesize N=464}&       17.43&       14.29&       20.07&        5.78&        0.00\\
                    &\vspace*{-2mm}{\footnotesize (10.5) }&\vspace*{-2mm}{\footnotesize (9.14) }&\vspace*{-2mm}{\footnotesize (10.9) }&            &            \\
Month 18 (grams/day) {\footnotesize N=461}&       21.52&       18.27&       24.41&        6.14&        0.00\\
                    &\vspace*{-2mm}{\footnotesize (11.4) }&\vspace*{-2mm}{\footnotesize (9.61) }&\vspace*{-2mm}{\footnotesize (12.0) }&            &            \\
Month 21 (grams/day) {\footnotesize N=475}&       24.45&       20.17&       27.99&        7.82&        0.00\\
                    &\vspace*{-2mm}{\footnotesize (11.4) }&\vspace*{-2mm}{\footnotesize (9.03) }&\vspace*{-2mm}{\footnotesize (11.9) }&            &            \\
Month 24 (grams/day) {\footnotesize N=462}&       26.99&       22.51&       31.07&        8.56&        0.00\\
                    &\vspace*{-2mm}{\footnotesize (12.0) }&\vspace*{-2mm}{\footnotesize (9.02) }&\vspace*{-2mm}{\footnotesize (13.0) }&            &            \\
Avg mth 15-24 (grams/day) {\footnotesize N=503}&       22.54&       18.78&       25.84&        7.06&        0.00\\
                    &\vspace*{-2mm}{\footnotesize (8.98) }&\vspace*{-2mm}{\footnotesize (6.43) }&\vspace*{-2mm}{\footnotesize (9.62) }&            &            \\
Avg mth 15-24 (kcal/day)   {\footnotesize N=503}&      691.78&      681.78&      700.55&       18.77&        0.38\\
                    &\vspace*{-2mm}{\footnotesize (236.5) }&\vspace*{-2mm}{\footnotesize (236.2) }&\vspace*{-2mm}{\footnotesize (236.9) }&            &            \\
\bottomrule
\addlinespace[0.5em]
\multicolumn{6}{p{1\textwidth}}{\parbox[t]{1.0\textwidth}{\footnotesize{\emph{Note}: See Section \ref{sec:stat} for discussions.}}}\\
\addlinespace
\end{tabular}
\end{adjustbox}
}
\end{table}

### 2022-03-09 template/fantemplate_acceptedsubmit/tab_main/tab4_frescoatoledecompose.tex
Submitted Accepted file template

\begin{table}[htbp]
\centering                                 \def\sym#1{\ifmmode^{#1}\else\(^{#1}\)\fi}                                 \caption{Decompose the protein gap between Atole and Fresco villages\label{frescoatoledecompose}}                                 \begin{adjustbox}{max width=1\textwidth}                                 \begin{tabular}{m{2.5cm} >{\centering\arraybackslash}m{1.8cm} >{\centering\arraybackslash}m{1.8cm} >{\centering\arraybackslash}m{1.8cm} >{\centering\arraybackslash}m{1.8cm} >{\centering\arraybackslash}m{1.8cm}}                                 \toprule
& \multicolumn{5}{C{9cm}}{Average protein choice across birth years} \\
\cmidrule(l{5pt}r{5pt}){2-6}
& \multicolumn{1}{C{1.8cm}}{\small \textbf{Fresco}} & \multicolumn{3}{C{5.4cm}}{\small \textbf{Fresco counterfactuals}} & \multicolumn{1}{C{1.8cm}}{\small \textbf{Atole}} \\
\cmidrule(l{5pt}r{5pt}){2-2} \cmidrule(l{5pt}r{5pt}){3-5} \cmidrule(l{5pt}r{5pt}){6-6}
& \multicolumn{1}{C{1.8cm}}{\textit{\small simulated without counterfactuals}} & \multicolumn{1}{C{1.8cm}}{\textit{\small Fresco with Atole price discount}} & \multicolumn{1}{C{1.8cm}}{\textit{\small Fresco with Atole ref. point}} & \multicolumn{1}{C{1.8cm}}{\textit{\small Fresco with both Atole price and ref. point}} & \multicolumn{1}{C{1.8cm}}{\textit{\small simulated without counterfactuals}} \\                                         
\midrule
\multicolumn{6}{L{13.3cm}}{\vspace*{-5mm}\hspace*{-5mm}\textbf{\normalsize Panel a: Height across birth cohorts}} \\
&            &            &            &            &            \\
1970-71             &       76.52&       77.20&       77.09&       77.68&       77.71\\
1972-73             &       76.80&       77.35&       77.57&       78.08&       78.07\\
1974-75             &       76.89&       77.48&       77.86&       78.43&       78.65\\
% \midrule
% Observations        &        7050&        7050&        7050&        7050&        8070\\
\midrule
\multicolumn{6}{L{13.3cm}}{\vspace*{-5mm}\hspace*{-5mm}\textbf{\normalsize Panel b: Protein across birth cohorts}} \\                                          &            &            &            &            &            \\
1970-71             &       18.43&       20.80&       20.48&       22.69&       23.13\\
1972-73             &       19.30&       21.35&       22.27&       24.33&       24.51\\
1974-75             &       19.97&       22.13&       23.95&       26.32&       27.13\\
% \midrule
% Observations        &        7050&        7050&        7050&        7050&        8070\\
\bottomrule
\addlinespace[0.5em]
\multicolumn{6}{l}{\footnotesize{\emph{Note}: See Section \ref{sec:decompose} for discussions.}}\\
\addlinespace
\end{tabular}
\end{adjustbox}
\end{table}

### 2022-03-09 _support/reference/biblatex_basic/biblatex_test.tex
Full article title citation in-text

@@
 \usepackage[bottom]{footmisc}
+% setspace: for spacing gap in references
+\usepackage{setspace}
 
@@
 \begin{filecontents}{ref.bib}
+@book{becker_human_1994,
+  title = {Human {{Capital}}: {{A Theoretical}} and {{Empirical Analysis}}, with {{Special Reference}} to {{Education}}, 3rd {{Edition}}},
+  author = {Becker, Gary S.},
+  date = {1994-03-14},
+  edition = {3rd edition},
+  publisher = {{University of Chicago Press}},
+  location = {{Chicago}},
+  isbn = {978-0-226-04120-9},
+  pagetotal = {412}
+}
 @article{becker_human_1986,
@@
 
+\section{Full Article Title In-Text Citation}
+
+To cite the entire title of the the paper, we can use \emph{citetitle}: The article, \citetitle{conti_understanding_2010}, by \citeauthor{conti_understanding_2010}, published in year \cite*{conti_understanding_2010}, is been discussed in this sentence.
+
+We can also cite the full title of a book or an article, rather then using \emph{textcite}, we use \emph{citetitle} first, followed by \emph{autocite}: 
+\begin{itemize}
+    \item \citetitle{conti_understanding_2010} \autocite{conti_understanding_2010} is an article published in a journal.
+    \item \citetitle{becker_human_1994} \autocite{becker_human_1994} is a book we are reading today.
+\end{itemize}
+
 \section{\href{https://papers.ssrn.com/sol3/papers.cfm?abstract_id=3140132}{Data}}
@@
 \begingroup
-%\setstretch{1.1}
-\setlength\bibitemsep{0pt}
+\setstretch{1.1}
+\setlength\bibitemsep{6pt}
 \printbibliography

### 2022-03-18 template/fantemplate_acceptedsubmit/manuscript_tab_fig.tex
Accepted Template preprint + journal submit tex/pdf

@@
 The consumption and expected height outcome frontier is determined by the budget constraint as well as the production function.
-Panels b, c and d show results from varying one parameter at a time in red (dashed-line) and orange (dotted-line).
-See Section \ref{sec:maximize} for discussions.}
+Panels b, c and d show results from varying one parameter at a time in red (dashed-line) and orange (dotted-line).}
 	\label{fig:indiff}
@@
 	\end{subfigure}
-	\caption{Increasing protein and height gaps across cohorts. \emph{Note}: See Section \ref{sec:gap} for discussions.}
+	\caption{Increasing protein and height gaps across cohorts.}
 	\label{fig:PortHgtGap}
@@
 \clearpage
-% Table 4
-\input{"tab_main/tab4_frescoatoledecompose.tex"}
-\clearpage
-% Table 5
-\input{tab_main/tab5_estimates_2021}
-\clearpage
 \pagebreak

### 2022-03-18 template/fantemplate_acceptedsubmit/manuscript_title_etc.tex
Accepted Template preprint + journal submit tex/pdf

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\newcommand{\AUTHORWANG}{Fan Wang: Department of Economics, University of Houston, Houston, Texas, USA (email: fwang26@uh.edu)}
+\newcommand{\AUTHORWANG}{Fan Wang}
+\newcommand{\AUTHORWANGINFO}{\AUTHORWANG: Department of Economics, University of Houston, Houston, Texas, USA (email: fwang26@uh.edu)}
 
@@
 We use our model to decompose the impact of the protein intervention on height into price and reference-point effects.
-We find that the changes in reference points account for 65\% of the height difference between two-year-old children in experimental and control villages in the sixth annual cohort born after the initiation of the intervention.
+We find that the changes in reference points account for 65\% of the height difference between two-year-old children in experimental and control villages in the sixth annual cohort born after the initiation of the intervention.\\
 \PAPERJEL}

### 2022-04-15 _support/reference/biblatex_basic/biblatex_test.tex
ref: Working paper biblatex formats; display url if no doi

--- 2019-12-03 _support/reference/biblatex_basic/biblatex_test.tex
@@
 \usepackage[bottom]{footmisc}
+% setspace: for spacing gap in references
+\usepackage{setspace}
+
+\usepackage[
+  authordate,
+  backend=biber,
+  isbn=false,
+  sorting=nyt,
+  maxbibnames=10,
+  maxcitenames=3,
+  sortcites=true]{biblatex-chicago}
 
@@
 }
+@article{hao_air_2016,
+	title = {Air {Pollution} and {Preterm} {Birth} in the {U}.{S}.
+{State} of {Georgia} (2002–2006): {Associations} with {Concentrations} of 11 {Ambient} {Air} {Pollutants} {Estimated} by {Combining} {Community} {Multiscale} {Air} {Quality} {Model} ({CMAQ}) {Simulations} with {Stationary} {Monitor} {Measurements}},
+	volume = {124},
+	issn = {0091-6765, 1552-9924},
+	shorttitle = {Air {Pollution} and {Preterm} {Birth} in the {U}.{S}. {State} of {Georgia} (2002–2006)},
+	url = {https://ehp.niehs.nih.gov/doi/10.1289/ehp.1409651},
+	doi = {10.1289/ehp.1409651},
+	language = {en},
+	number = {6},
+	urldate = {2020-07-18},
+	journal = {Environmental Health Perspectives},
+	author = {Hao, Hua and Chang, Howard H. and Holmes, Heather A. and Mulholland, James A. and Klein, Mitch and Darrow, Lyndsey A. and Strickland, Matthew J.},
+	month = jun,
+	year = {2016},
+	pages = {875--880}
+}
+@article{westergaard_ambient_2017,
+	title = {Ambient air pollution and low birth weight - are some women more vulnerable than others?},
+	volume = {104},
+	issn = {01604120},
+	url = {https://linkinghub.elsevier.com/retrieve/pii/S0160412017301976},
+	doi = {10.1016/j.envint.2017.03.026},
+	language = {en},
+	urldate = {2020-07-19},
+	journal = {Environment International},
+	author = {Westergaard, Nadja and Gehring, Ulrike and Slama, Rémy and Pedersen, Marie},
+	month = jul,
+	year = {2017},
+	pages = {146--154},
+}
+@report{cavounidis_2022,
+  title = {Estimating the Nature of Technological Change:
+    Exploiting Shifts in Skill Use Within and Between Occupations},
+  author = {Cavounidis, Costas and
+    Dicandia, Vittoria and
+    Lang, Kevin and
+    Malhotra, Raghav},
+  date = {2022},
+  institution = {Mimeo,
+    Department of Economics,
+    Univerity of Warwick}
+}
+@report{morchio_moser_2021,
+  title = {The Gender Pay Gap: Micro Sources and Macro Consequences},
+  author = {Morchio, Iacopo and Moser, Christian},
+  date = {2021},
+  series = {CEPR Discussion Papers},
+  number = {15283},
+  url = {https://ideas.repec.org/p/cpr/ceprdp/16383.html}
+}
 \end{filecontents}
 
-\usepackage[authordate,
-backend=bibtex,
-doi=false,
-isbn=false,
-sorting=nyt,
-maxbibnames=10,
-maxcitenames=3,
-sortcites=False]{biblatex-chicago}
-\bibliography{ref}
+% https://tex.stackexchange.com/a/424775/109818
+\DeclareSourcemap{
+  \maps[datatype=bibtex]{
+    \map[overwrite]{
+      \step[fieldsource=doi, final]
+      \step[fieldset=url, null]
+      \step[fieldset=eprint, null]
+    }
+  }
+}
+\addbibresource{ref.bib}
 
@@
 
-\paragraph{\href{https://papers.ssrn.com/sol3/papers.cfm?abstract_id=3140132}{Data}}
+\section{biblatex Settings}
+
+\subsection{Chicago Author-Date}
+
+To use authordate chicago stye, cite up to three authors in text, more than three authors use `et al.', and cite in the references at most ten author names.
+
+\begin{verbatim}
+  \usepackage[
+    authordate,
+    backend=biber,
+    isbn=false,
+    sorting=nyt,
+    maxbibnames=10,
+    maxcitenames=3,
+    sortcites=true]{biblatex-chicago}
+\end{verbatim}
+
+\subsection{DOI or URL if DOI does not Exist}
+
+Using \textbf{biber} as backend, can use the `sourcemap' feature to control: (1) print doi if exists; (2) print url if doi does not exist; (3) print eprint if no doi and also no url.
+See \url{https://tex.stackexchange.com/a/424799/109818}.
+
+\begin{verbatim}
+\DeclareSourcemap{
+  \maps[datatype=bibtex]{
+    \map[overwrite]{
+      \step[fieldsource=doi, final]
+      \step[fieldset=url, null]
+      \step[fieldset=eprint, null]
+    }
+  }
+}
+\end{verbatim}
+
+\section{Citations}
+\subsection{Possessive Citations}
+
+In this example, using possessive to put apostrophe after author names and before date. Accomplished by using \emph{citeauthor} first then \emph{parentcite}.
+
+\citeauthor{hao_air_2016}'s \parencite*{hao_air_2016} Georgia study
+found that associations of traffic-related pollutants, including NO\textsubscript{2} and
+PM\textsubscript{2.5}, with preterm birth tended to be stronger for mothers with low
+educational attainment.
+
+\subsection{Cite Only Date}
+
+To write more flexibly, can mention author names explicitly in text and then cite the article with \emph{parentcite} for the date only: Westergaard and her colleagues \parencite*{westergaard_ambient_2017} identified only a small handful of studies that addressed effect modification by dimensions of socioeconomic status.
+
+\subsection{Full Article Title In-Text Citation}
+
+To cite the entire title of the the paper, we can use \emph{citetitle}: The article, \citetitle{conti_understanding_2010}, by \citeauthor{conti_understanding_2010}, published in year \cite*{conti_understanding_2010}, is been discussed in this sentence.
+
+We can also cite the full title of a book or an article, rather then using \emph{textcite}, we use \emph{citetitle} first, followed by \emph{autocite}:
+\begin{itemize}
+    \item \citetitle{conti_understanding_2010} \autocite{conti_understanding_2010} is an article published in a journal.
+    \item \citetitle{becker_human_1994} \autocite{becker_human_1994} is a book we are reading today.
+\end{itemize}
+
+\section{BIB Entries}
+
+\subsection{BIB Entry for non-public Working Paper}
+
+For working papers that have not been shared on public repositories. Here we cite \textcite{cavounidis_2022}.
+
+\begin{verbatim}
+  @report{cavounidis_2022,
+    title = {Estimating the Nature of Technological Change:
+      Exploiting Shifts in Skill Use Within and Between Occupations},
+    author = {Cavounidis, Costas and
+      Dicandia, Vittoria and
+      Lang, Kevin and
+      Malhotra, Raghav},
+    date = {2022},
+    institution = {Mimeo,
+      Department of Economics,
+      Univerity of Warwick}
+  }
+\end{verbatim}
+
+\subsection{BIB Entry for Working Paper in Series}
+
+For working paper in various working paper series. \textcite{morchio_moser_2021} is a CEPR Discussion Paper.
+
+\begin{verbatim}
+@report{morchio_moser_2021,
+  title = {The Gender Pay Gap: Micro Sources and Macro Consequences},
+  author = {Morchio, Iacopo and Moser, Christian},
+  date = {2021},
+  series = {CEPR Discussion Papers},
+  number = {15283},
+  url = {https://ideas.repec.org/p/cpr/ceprdp/16383.html}
+}
+\end{verbatim}
+
+\section{\href{https://papers.ssrn.com/sol3/papers.cfm?abstract_id=3140132}{Data}}
 
@@
 \begingroup
-%\setstretch{1.1}
-\setlength\bibitemsep{0pt}
+\setstretch{1.0}
+\setlength\bibitemsep{3pt}
 \printbibliography

### 2022-04-21 nontex/git/g_basics/fs_git_bash.Rmd
git basics and git bash pull single repo

---
title: "BASH Pull and Push From GIT Remote Repository"
output:
  pdf_document: default
  word_document: default
  html_document: default
  html_notebook: default
urlcolor: blue
always_allow_html: yes
---

Go back to [Fan](http://fanwangecon.github.io/)'s [Tex4Econ and Miscellaneous Repository](http://fanwangecon.github.io/Tex4Econ/).

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval = FALSE)
```

### Basic BASH

#### Pull from Remote Repo and Create a New Local Directory

[Sample pull bash file](https://fanwangecon.github.io/Tex4Econ/nontex/git/g_basics/fs_git_bash_pull_one) is shown below.

```{}
#!/usr/bin/bash

# This bash file, after making the appropriate adjustments pulls from a remote
# project and creates a new local folder.

# ADJUT 1 STRREPO
# STRREPO='Py4Econ'
STRREPO='PrjHealthProductionCGW'

if [ -d "/g/repos/" ]
then
  echo "Computer has g drive, on precision"
  STRREPOWTHPATH="/g/repos/${STRREPO}"
else
  echo "Computer has c drive, on vostro"
  STRREPOWTHPATH="/c/Users/fan/${STRREPO}"
fi
echo "${STRREPOWTHPATH}"

echo pull single repository
echo going to pull from $STRREPOWTHPATH

# generate all needed key repositories
mkdir $STRREPOWTHPATH

# Initialize
cd $STRREPOWTHPATH

# ADJUT 2.1 ACCOUNT
# Set global config settings, in ~/.gitconfig
git config --global user.name "Fan Wang"
git config --global user.email wangfanbsg75@live.com

# Initialize
git init
# ADJUT 2.2 ACCOUNT
git remote add github git@github.com:fanwangecon/$STRREPO

# Secure
eval "$(ssh-agent)"
# ssh-add ~/.ssh/id_rsa_yy
ssh-add ~/.ssh/id_rsa

# Pull
cd $STRREPOWTHPATH
# ADJUT 3 root name
git pull github main
# git pull github master

# Open Repository in Atom
atom $STRREPOWTHPATH
```

### 2022-05-15 template/fantemplate_acceptedsubmit/manuscript_online_appendix.tex
Accepted Template preprint + journal submit tex/pdf

@@
-% reset page numbers
-\pagenumbering{arabic}
-\setcounter{page}{1}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% Title Page for Appendix
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% special footnote symbols
-\renewcommand*{\thefootnote}{\fnsymbol{footnote}}
-\begingroup
-  \doublespacing
-  \centering
-  \Large ONLINE APPENDIX \\[1.5em]
-  \LARGE \PAPERTITLE \\[0.75em]
-  \large
-    Fan Wang,\footnote[1]{\AUTHORWANG}\\[1.0em]
-\endgroup
-\clearpage
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 We include in the estimation children who were born between 1970 and 1975.
-We show summary statistics for these children in Sections \ref{sec:stat} and \ref{sec:gap}.
-As discussed earlier, we do not observe both initial heights and heights at month 24 for children born before or after these years.
+We show summary statistics for these children in Sections \ref{sec:stat} and \ref{sec:gap}.\footnote{As discussed earlier, we do not observe both initial heights and heights at month 24 for children born before or after these years.}
 
@@
 We use protein intakes because \textcite{puentes_early_2016} shows that proteins rather than non-protein components of calories matter for height growth in these INCAP data.
-Ideally, our intake variable should be averaged from month 0 to month 24.
-However, we do not observe protein values from month 0 to month 12 for close to half of our sample because data collection for this age group started in 1973.
-Also, it is not easy to estimate the protein component of breastmilk for children who rely on breastfeeding in the first year of life.
+Ideally, our intake variable should be averaged from month 0 to month 24.\footnote{However, we do not observe protein values from month 0 to month 12 for close to half of our sample because data collection for this age group started in 1973.
+Also, it is not easy to estimate the protein component of breastmilk for children who rely on breastfeeding in the first year of life.}
 
@@
 
-For $\rho$, the quadratic coefficient on non-nutritional consumptions, the estimated coefficient becomes more negative as $\sigma_{R_{y,v}}$ increases.
-This finding implies lower marginal gains from additional non-nutritional consumption at higher $\sigma_{R_{y,v}}$.
-
-\clearpage
-\pagebreak
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% Appendix Bibliography
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-% Bibliography
-\begingroup
-\setstretch{1.0}
-\setlength\bibitemsep{0pt}
-\printbibliography[title=References for Online Appendix]
-\endgroup
-\pagebreak
+For $\rho$, the quadratic coefficient on non-nutritional consumptions, the estimated coefficient becomes more negative as $\sigma_{R_{y,v}}$ increases.\footnote{This finding implies lower marginal gains from additional non-nutritional consumption at higher $\sigma_{R_{y,v}}$.}

### 2022-05-15 template/fantemplate_acceptedsubmit/manuscript_title_etc.tex

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\newcommand{\PAPERTITLE}{\href{https://papers.ssrn.com/sol3/papers.cfm?abstract_id=3167023}{You are What Your Parents Expect: Height and Local Reference Points}}
+\newcommand{\PAPERTITLE}{\href{https://doi.org/10.1016/j.red.2021.09.001}{An equilibrium model of formal and informal credit markets in developing countries}}
 
@@
 \newcommand{\AUTHORWANG}{Fan Wang}
-\newcommand{\AUTHORWANGINFO}{\AUTHORWANG: Department of Economics, University of Houston, Houston, Texas, USA (email: fwang26@uh.edu)}
+\newcommand{\AUTHORWANGURL}{https://orcid.org/0000-0003-2640-5420}
+\newcommand{\AUTHORWANGINFO}{\href{\AUTHORWANGURL}{\AUTHORWANG}: Department of Economics, University of Houston, Houston, Texas, USA (email: fwang26@uh.edu)}
+
+\newcommand{\AUTHORTEXFORECON}{Tex4Econ}
+\newcommand{\AUTHORTEXFORECONURL}{https://fanwangecon.github.io/Tex4Econ/}
+\newcommand{\AUTHORTEXFORECONINFO}{\href{\AUTHORTEXFORECONURL}{\AUTHORTEXFORECON}: Github repository, San Francisco, CA, USA (email: fanwecon@gmail.com)}
 
@@
 \PAPERJEL}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% 6. Define citation or availability of latest draft
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\newcommand{\PAPERDOIURL}{https://doi.org/10.1086/711654}
+\newcommand{\PAPERINFO}{
+This paper has been accepted for publication: Hannum, Emily, Xiaoying Liu, and Fan Wang.
+“Estimating the Effects of Educational System Consolidation: The Case of China’s Rural School Closure Initiative.” Economic Development and Cultural Change 70, no.
+1 (October 1, 2021): 485–528.
+\url{\PAPERDOIURL}.
+}

### 2022-05-18 _other/tikz/tree/fs_tikz_nodediagram.tex
Tikz node-based diagrams

\documentclass{article}

\usepackage{blindtext}
\usepackage{multicol}
\usepackage{caption}
\usepackage{amsmath}
\usepackage{tikz}
\usepackage{pgfplots}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,
    urlcolor=cyan,
}
\usepackage{geometry}
\geometry{
	a4paper,
	noheadfoot=true,
	left=1.0in,
	right=1.0in,
	top=1.0in,
	bottom=1.0in
}

% url package
\usepackage{hyperref}
\usepackage{subcaption}
\usepackage{relsize} % make some math large
\usepackage{bm} % make some math bold

% Itemize formating
\usepackage{enumitem}

% Figure positioning
\usepackage{float}

% Titling and Author
\title{Latex Tikz Examples, Node-based Diagrams}
\author{\href{https://fanwangecon.github.io/}{Fan Wang}\thanks{\url{https://fanwangecon.github.io}, repository: \href{https://fanwangecon.github.io/Tex4Econ/}{Tex4Econ}}}
\date{\today}

\begin{document}

\maketitle

\section{Connecting Nodes with Arrows}

In the following example, there are three sets of data, relevant for three research objectives:

\begin{verbatim}
    \begin{tikzpicture}[thick]
        \node(1) at (-1,-1) [rectangle,draw=blue!50,fill=blue!20] {Data 1};
        \node(2) at (7 ,-2) [rectangle,draw=blue!50,fill=blue!20] {Data 2};
        \node(3) at (-1,-4) [rectangle,draw=blue!50,fill=blue!20] {Data 3};

        \node(4) at (3,-1) [rectangle,draw=black!50] {Analysis Objective 1};
        \node(5) at (3,-2) [rectangle,draw=black!50] {Analysis Objective 2};
        \node(6) at (3,-3) [rectangle,draw=black!50] {Analysis Objective 3};

        \draw [->] (1) edge (4);
        \draw [->] (1) |- (5);
        \draw [->] (1) |- (6);

        \draw [->] (2) edge (5);
        \draw [->] (2) |- (6);

        \draw [->] (3) -| (6);
    \end{tikzpicture}    
\end{verbatim}

\medskip
\begin{center}
    \begin{tikzpicture}[thick]
        \node(1) at (-1,-1) [rectangle,draw=blue!50,fill=blue!20] {Data 1};
        \node(2) at (7 ,-2) [rectangle,draw=blue!50,fill=blue!20] {Data 2};
        \node(3) at (-1,-4) [rectangle,draw=blue!50,fill=blue!20] {Data 3};

        \node(4) at (3,-1) [rectangle,draw=black!50] {Analysis Objective 1};
        \node(5) at (3,-2) [rectangle,draw=black!50] {Analysis Objective 2};
        \node(6) at (3,-3) [rectangle,draw=black!50] {Analysis Objective 3};

        \draw [->] (1) edge (4);
        \draw [->] (1) |- (5);
        \draw [->] (1) |- (6);

        \draw [->] (2) edge (5);
        \draw [->] (2) |- (6);

        \draw [->] (3) -| (6);
    \end{tikzpicture}
\end{center}
\clearpage

\section{Connecting Blocks of Nodes and with Blocks of Nodes}

To present the relationship between data and research analysis, show visually how several research aim will be achieved with different data structures and analysis.

\begin{verbatim}
    \begin{tikzpicture}[thick, font=\small]
        \node(100) at (2.5,10) [rectangle] {Research Aim I};
        \node(101) at (-3,8.5) [rectangle, draw=blue!50, fill=blue!20] {Data 1};
        \node(102) at (-3,7.5) [rectangle, draw=black!50, fill=red!20] {Data 2};
        \node(111) at (0,8) [rectangle, draw=black!50] {Combine};
        \draw [->] (101) edge (111);
        \draw [->] (102) edge (111);
        \node(121) at (3,9) [rectangle, draw=black!50] {Analysis I};
        \node(122) at (3,8) [rectangle, draw=black!50] {Analysis II};
        \node(123) at (3,7) [rectangle, draw=black!50] {Analysis III};
        \draw [->] (111) |- (121);
        \draw [->] (111) |- (122);
        \draw [->] (111) |- (123);
        \node(131) at (8,8) [rectangle, draw=black!50, text width=5cm] {Some Text.};
    \end{tikzpicture}    
\end{verbatim}

\begin{center}
\begin{tikzpicture}[thick, font=\small]
    % Objective I
    \node(100) at (2.5,10) [rectangle] {Research Aim I};
    \node(101) at (-3,8.5) [rectangle, draw=blue!50, fill=blue!20] {Data 1};
    \node(102) at (-3,7.5) [rectangle, draw=black!50, fill=red!20] {Data 2};

    \node(111) at (0,8) [rectangle, draw=black!50] {Combine};
    \draw [->] (101) edge (111);
    \draw [->] (102) edge (111);

    \node(121) at (3,9) [rectangle, draw=black!50] {Analysis I};
    \node(122) at (3,8) [rectangle, draw=black!50] {Analysis II};
    \node(123) at (3,7) [rectangle, draw=black!50] {Analysis III};
    \draw [->] (111) |- (121);
    \draw [->] (111) |- (122);
    \draw [->] (111) |- (123);

    \node(131) at (8,8) [rectangle, draw=black!50, text width=5cm] {specimen book. It has survived not only five centuries, but also the leap into electronic typesetting, remaining essentially unchanged.};

    % Objective II
    \node(200) at (2.5,5) [rectangle] {Research Aim II};
    \node(201) at (-3,3.5) [rectangle, draw=blue!50, fill=blue!20] {Data 1};
    \node(202) at (-3,2.5) [rectangle, draw=black!50, fill=green!20] {Data 3};

    \node(211) at (0,3) [rectangle, draw=black!50] {Combine};
    \draw [->] (201) edge (211);
    \draw [->] (202) edge (211);

    \node(221) at (3,4) [rectangle, draw=black!50] {Analysis I};
    \node(222) at (3,3) [rectangle, draw=black!50] {Analysis II};
    \node(223) at (3,2) [rectangle, draw=black!50] {Analysis III};
    \draw [->] (211) |- (221);
    \draw [->] (211) |- (222);
    \draw [->] (211) |- (223);

    \node(231) at (8,3) [rectangle, draw=black!50, text width=5cm] {specimen book. It has survived not only five centuries, but also the leap into electronic typesetting, remaining essentially unchanged.};

    % Objective III
    \node(300) at (2.5,0) [rectangle] {Research Aim III};
    \node(301) at (-3,-1.5) [rectangle, draw=blue!50, fill=blue!20] {Data 1};
    \node(302) at (-3,-2.5) [rectangle, draw=black!50, fill=brown!20] {Data 4};

    \node(311) at (0,-2) [rectangle, draw=black!50] {Combine};
    \draw [->] (301) edge (311);
    \draw [->] (302) edge (311);

    \node(321) at (3,-1.5) [rectangle, draw=black!50] {Analysis I};
    \node(322) at (3,-2.5) [rectangle, draw=black!50] {Analysis II};
    \draw [->] (311) |- (321);
    \draw [->] (311) |- (322);

    \node(331) at (8,-2) [rectangle, draw=black!50, text width=5cm] {specimen book. It has survived not only five centuries, but also the leap into electronic typesetting, remaining essentially unchanged.};

\end{tikzpicture}
\end{center}
\clearpage
\newpage

\section{Rows of Data and Analysis Connected Nodes}

\subsection{Research Plan Diagram Example One}

To present the relationship between data and research analysis, show visually how several research aim will be achieved with different data structures and analysis.

\begin{figure}[H]
\centering
\caption{Research Aim I---Inequality in Ambient Environmental Exposures}
\begin{tikzpicture}[thick, font=\small]
% A. Sizing for tikz
\def\fstdata{4.2cm}
\def\fstanalysis{5.2cm}
\def\fstunequal{3.0cm}
\def\fstnote{13.2cm}
% B.1 Text for tikz group 1
\newcommand{\dataone}{\textbf{Environmental Data} $Z_{l,y}$: ambient exposure in location $l$, period $y$.}
\newcommand{\datatwo}{\textbf{Population Data} $P_{i,l,t}$: size of demographic group $i$ in location $l$, period $y$.}
% B.2 Text for tikz group 2
\newcommand{\analysisone}{\emph{Analysis I}: Excess pollution burden in each (or combined) location $l$ and over time.}
\newcommand{\analysistwo}{\emph{Analysis II}: Excess pollution burden for demographic group $i$ over time.}
\newcommand{\analysisthree}{\emph{Analysis III}: Excess pollution burden for demographic group $i$ in each (or combined) location $l$ over time.}
% B.3 Text for tikz group 3
\newcommand{\inequalitymeasure}{Exposure inequality: 
\begin{enumerate}[leftmargin=0cm,itemindent=.3cm,labelwidth=\itemindent,labelsep=0.0cm, itemsep=-0.1cm, topsep=0cm, align=left]
    \item Overall
    \item Across groups
    \item Within group
\end{enumerate}}
% C Tikz Draw
    % Objective I
    % \node(100) at (2.5,10.75) [rectangle] {};
    \node(101) at (-3,8.8) [rectangle, draw=blue!50, fill=blue!20, text width=\fstdata] {\dataone};
    \node(102) at (-3,7.2) [rectangle, draw=black!50, fill=red!20, text width=\fstdata] {\datatwo};

    \node(111) at (0.5,8) [circle, draw=black!50] {Merge};
    \draw [->] (101) edge (111);
    \draw [->] (102) edge (111);

    \node(121) at (4.5,9.5) [rectangle, draw=black!50, text width=\fstanalysis] {\analysisone};
    \node(122) at (4.5,8) [rectangle, draw=black!50, text width=\fstanalysis] {\analysistwo};
    \node(123) at (4.5,6.5) [rectangle, draw=black!50, text width=\fstanalysis] {\analysisthree};
    \draw [->] (111.north) |- (121);
    \draw [->] (111.east) |- (122);
    \draw [->] (111.south) |- (123);

    \node(131) at (9.5,8) [rectangle, draw=black!50, text width=\fstunequal] {\inequalitymeasure};
    \draw [->] (121) to [bend left=45] (131);
    \draw [->] (122) to (131);
    \draw [->] (123) to [bend right=45] (131);

    \node(141) at (2.5,2.25) [rectangle, draw=black!50, text width=\fstnote, label={Inequality distributional percentile calculations}, align=center] {
Given $M$ locations and $N$ demographic groups, let $\mathcal{P}_{i,y}=\sum_{l=1}^{M}
P_{l,i,y}$ be group $i$'s population and $\mathcal{Z}_{i,y}$ be group $i$'s mean exposure. The quantile function $Q_{x}(\tau)$ with $\tau\in[0,1)$ is:\\
$\begin{aligned}   
\text{Overall: } &Q_{Z_{y}}(\tau) =
\max_{l\in\left\{1, \dots, M \right\}}
\left(
    \text{Z}_{l,y}
    \times
    \mathbf{1}\left\{
    \tau \ge
      \sum_{\tilde{l}=1}^{M} P_{\tilde{l},y}
      \times
      \mathbf{1}\left\{
        Z_{\tilde{l},y} \le Z_{l,y}
        \right\}
    \right\}
\right)\\
\text{Across: } &Q_{\mathcal{Z}_{y}}(\tau) =
\max_{i\in\left\{1, \dots, N \right\}}
\left(
    \mathcal{Z}_{i,y}
    \times
    \mathbf{1}\left\{
    \tau \ge
      \sum_{\tilde{i}=1}^{N} \mathcal{P}_{\tilde{i},y}
      \times
      \mathbf{1}\left\{
        \mathcal{Z}_{\tilde{i},y} \le \mathcal{Z}_{i,y}
        \right\}
    \right\}
\right)\\
\text{Within: } &Q_{Z_{i,y}}(\tau) =
\max_{l\in\left\{1, \dots, M \right\}}
\left(
    \text{Z}_{l,y}
    \times
    \mathbf{1}\left\{
    \tau \ge
      \sum_{\tilde{l}=1}^{M}
      \frac{P_{i, \tilde{l}, y}}{\mathcal{P}_{i,y}}
      \times
      \mathbf{1}\left\{
        Z_{\tilde{l},y} \le Z_{l,y}
        \right\}
    \right\}
\right)
% , \forall i\in\left\{1,\dots,N\right\}
\end{aligned}$    
    };
\draw [->] (131.east) to [bend left=45] (141.east);

\end{tikzpicture}
\end{figure}
\clearpage

\subsection{Research Plan Diagram Example Two}

\begin{figure}[H]
\centering
\caption{Research Aim II---Inequality in Ambient Environmental Exposures}
\begin{tikzpicture}[thick, font=\small]
% A. Sizing for tikz
\def\fstdata{4.2cm}
\def\fstanalysis{4.5cm}
\def\fstunequal{3.5cm}
\def\fstnote{16.2cm}
% B.1 Text for tikz group 1
\newcommand{\dataone}{\textbf{Environmental Data} $Z_{l,y}$: ambient exposure in location $l$ during period $y$.}
\newcommand{\datatwo}{\textbf{Human Capital Data} $Y_{j,i,l,y}$: human capital outcomes for individual $j$ of demographic group $i$ in location $l$ during period $y$.}
\newcommand{\datathree}{\textbf{SES Status Data} $X_{j}$: Parental/household SES and other attributes for $j$.}
% B.2 Text for tikz group 2
\newcommand{\analysisone}{\emph{Analysis I}: Explain average variations in $Y_{j,i,l,t}$ with variations in $Z_{l,y}$ across $l$ and $y$.}
\newcommand{\analysistwo}{\emph{Analysis II}: Explain quantiles of residual variations in $Y_{j,i,l,t}$ with variations in $Z_{l,y}$ across $l$ and $y$.}
\newcommand{\analysisthree}{\emph{Analysis III}: Explain variations in the quantiles of $Y_{j,i,l,t}$ with variations in $Z_{l,y}$ across $l$ and $y$.}
% B.3 Text for tikz group 3
\newcommand{\inequalitymeasure}{
\textbf{Allow for}: 
\begin{enumerate}[leftmargin=0cm,itemindent=.3cm,labelwidth=\itemindent,labelsep=0cm, itemsep=-0.05cm, topsep=0cm, align=left]
    \item Multiple $Z_{l,y}$ 
    \item $Z_{ly} \cdot X_{i}$ interaction
    % \item Instruments (e.g. thermal inversion)
\end{enumerate}
\medskip
\textbf{Control for}: 
\begin{enumerate}[leftmargin=0cm,itemindent=.3cm,labelwidth=\itemindent,labelsep=0cm, itemsep=-0.05cm, topsep=0cm, align=left]
    \item Location $\times$ time trends
    \item Invariant demo. group attributes
    \item Pre-determined parental attributes
\end{enumerate}}
% C Tikz Draw
    % Objective I
    % \node(100) at (2.5,10.75) [rectangle] {};
    \node(101) at (-3,10) [rectangle, draw=blue!50, fill=blue!20, text width=\fstdata] {\dataone};
    \node(102) at (-3,8) [rectangle, draw=black!50, fill=green!20, text width=\fstdata] {\datatwo};
    \node(103) at (-3,6) [rectangle, draw=black!50, fill=yellow!20, text width=\fstdata] {\datathree};

    \node(111) at (0.5,8) [circle, draw=black!50] {Merge};
    \draw [->] (101.east) to (111);
    \draw [->] (102) edge (111);
    \draw [->] (103.east) to (111);

    \node(121) at (4.5,9.75) [rectangle, draw=black!50, text width=\fstanalysis] {\analysisone};
    \node(122) at (4.5,8) [rectangle, draw=black!50, text width=\fstanalysis] {\analysistwo};
    \node(123) at (4.5,6.1) [rectangle, draw=black!50, text width=\fstanalysis] {\analysisthree};
    \draw [->] (111.north) |- (121);
    \draw [->] (111.east) |- (122);
    \draw [->] (111.south) |- (123);

    \node(131) at (9.5,8) [rectangle, draw=black!50, text width=\fstunequal] {\inequalitymeasure};
    \draw [->] (121) to [bend left=45] (131);
    \draw [->] (122) to (131);
    \draw [->] (123) to [bend right=45] (131);

    \node(141) at (3.00,2.8) [rectangle, draw=black!50, text width=\fstnote, label={Mean and quantile estimations}, align=left] {To illustrate, assume an additive model, and let $\widehat{Y}_{jily}= 
\alpha_0 \cdot \widehat{Z}_{ly}
+ \alpha_1 \cdot \widehat{Z}_{ly} \cdot X_{j}
+ \alpha_2 \cdot X_{j}
+ \theta_{i}
+ \phi_{l}
+ \psi_{ly}$, 
where $\widehat{Z}$ are SES dimensions of parental characteristics and $\theta_{i}
+ \phi_{l}
+ \psi_{ly}$ are demographic group, location, and location-specific time fixed effects.
Analysis I minimizes 
$\sum_{j,i,l,y} \left(Y_{jily} - \widehat{Y}_{jily}\right)^2$. 
Analysis II minimizes 
$\sum_{j,i,l,y} 
\left(\tau-
\mathbf{1}
\left\{ Y_{jily} - \widehat{Y}_{jily} \le 0\right\}
\right) \cdot \left(Y_{jily} - \widehat{Y}_{jily}\right)
$, where $\mathbf{1}\left\{\cdot\right\}$ denotes the indicator function.
Analysis III minimizes 
$\sum_{j,i,l,y} 
\left(\widehat{RIF}\left(\widehat{Q(\tau)}, Y_{jily}\right) - 
\widehat{Y}_{jily}\right)^2$, where $\widehat{RIF}$ is the quantile-specific recentered influence function.
};
\draw [->] (131.east) to [bend left=45] (141.east);

\end{tikzpicture}
\end{figure}

\clearpage

\subsection{Research Plan Diagram Example Three}

\begin{figure}[H]
\centering
\caption{Research Aim III---Inequality in Ambient Environmental Exposures}
\begin{tikzpicture}[thick, font=\small]
% A. Sizing for tikz
\def\fstdata{4.2cm}
\def\fstanalysis{4.75cm}
\def\fstunequal{3.90cm}
\def\fstnote{16.2cm}
% B.1 Text for tikz group 1
\newcommand{\dataone}{\textbf{Environmental Data} $Z_{l,y}$: Ambient exposure in location $l$ during period $y$.}
\newcommand{\datatwo}{\textbf{Home Inputs} $H_{j,i,l,y}$: Home/parental human capital inputs for child $j$ of demo-SES group $i$ in location $l$ during period $y$.}
\newcommand{\datathree}{\textbf{Community Inputs} $S_{l,y}$: Community inputs (e.g. schools, health clinics) in location $l$ during period $y$.}
% B.2 Text for tikz group 2
\newcommand{\analysisone}{\emph{Analysis I}: In period $y$, explain variations in $H_{j,i,l,t}$ and $S_{l,y}$ with variations in $Z_{l,y}$ across $l$.}
\newcommand{\analysistwo}{\emph{Analysis II}:
Explain variations in $H_{j,i,l,y}$ and $S_{l,y}$ with the path of variations in $\left\{Z_{l,\widehat{y}}\right\}_{\widehat{y}=y-\tau}^{y}$ from period $y-\tau$ to $y$.
% Evaluate the persistence of the association between $Y_{j,i,l,y}$ and $Z_{l,y-\tau}$ from $\tau$ periods ago, considering $Z_{l,y}$.
}
\newcommand{\analysisthree}{\emph{Analysis III}: Explain variations in $Y_{j,i,l,y}$ (Human capital outcomes) with variations in $Y_{j,i,l,y-1}$, $H_{j,i,l,t}$, $S_{l,y}$, and $Z_{l,y}$ across $j$ and $l$.}
% B.3 Text for tikz group 3
\newcommand{\inequalitymeasure}{
\textbf{Endogeneity}: 
\begin{enumerate}[leftmargin=0cm,itemindent=.3cm,labelwidth=\itemindent,labelsep=0cm, itemsep=-0.05cm, topsep=0cm, align=left]
    % \item Multiple $Z_{l,y}$ 
    % \item $Z_{ly} \cdot X_{i}$ interaction
    % \item Isolate unpredictable components of $Z_{l,y}$ 
    \item $\mathrm{cov}\left(Z_{l,y},\text{Inputs}\right)\neq 0$ 
    \item $\mathrm{P}\left(Z_{l,y}|Z_{l,y-\tau}\right)\neq \mathrm{P}\left(Z_{l,y}\right)$
    % \item Instruments (e.g. thermal inversion)
\end{enumerate}
\medskip
\textbf{Identification}: 
\begin{enumerate}[leftmargin=0cm,itemindent=.3cm,labelwidth=\itemindent,labelsep=0cm, itemsep=-0.05cm, topsep=0cm, align=left]
    \item Consider multiple $Z_{l,y}$ and inputs
    \item Consider current and lagged inputs
    \item Instruments (e.g. thermal inversion)
\end{enumerate}}
% C Tikz Draw
    % Objective I
    % \node(100) at (2.5,10.75) [rectangle] {};
    \node(101) at (-3,9.9) [rectangle, draw=blue!50, fill=blue!20, text width=\fstdata] {\dataone};
    \node(102) at (-3,8.0) [rectangle, draw=black!50, fill=brown!20, text width=\fstdata] {\datatwo};
    \node(103) at (-3,5.9) [rectangle, draw=black!50, fill=orange!20, text width=\fstdata] {\datathree};

    \node(111) at (0.5,8) [circle, draw=black!50] {Merge};
    \draw [->] (101.east) to (111);
    \draw [->] (102) edge (111);
    \draw [->] (103.east) to (111);

    \node(121) at (4.3,9.7) [rectangle, draw=black!50, text width=\fstanalysis] {\analysisone};
    \node(122) at (4.3,8.0) [rectangle, draw=black!50, text width=\fstanalysis] {\analysistwo};
    \node(123) at (4.3,5.9) [rectangle, draw=black!50, text width=\fstanalysis] {\analysisthree};
    \draw [->] (111.north) |- (121);
    \draw [->] (111.east) to (122);
    \draw [->] (111.south) |- (123);

    \node(131) at (9.5,8) [rectangle, draw=black!50, text width=\fstunequal] {\inequalitymeasure};
    \draw [->] (121) to [bend left=45] (131);
    \draw [->] (122) to (131);
    \draw [->] (123) to [bend right=45] (131);

    \node(141) at (3.00,2.4) [rectangle, draw=black!50, text width=\fstnote, label={Production function estimations}, align=left] {To illustrate, suppose that $Y_{j,i,l,y}=f\left(
    Y_{j,i,l,y-1},
    H_{j,i,l,y}\left(\left\{Z_{l,\widehat{y}}\right\}_{\widehat{y}=y-\tau}^{y}\right),
    S_{l,y}\left(\left\{Z_{l,\widehat{y}}\right\}_{\widehat{y}=y-\tau}^{y}\right),
    \left\{Z_{l,\widehat{y}}\right\}_{\widehat{y}=y-\tau}^{y},
    \epsilon_{j,i,l,y}
    \right)$, where $f(\cdot)$ is the human capital production function and $\epsilon_{j,i,l,y}$ is unobserved shock. Analysis I and II focus on understanding the relationship between environmental shocks and home and community input choices $H_{j,i,l,y}\left(\left\{Z_{l,\widehat{y}}\right\}_{\widehat{y}=y-\tau}^{y}\right)$ and $S_{l,y}\left(\left\{Z_{l,\widehat{y}}\right\}_{\widehat{y}=y-\tau}^{y}\right)$. Analysis I assumes $\tau =0$. Analysis II considers $\tau >0$, accounting for the persistent effects of past shocks. Analysis III estimates function $f(\cdot)$; potential endogeneity of inputs and unobserved shocks $\epsilon_{j,i,l,y}$ is considered, and the inclusion of $\left\{Z_{l,\widehat{y}}\right\}_{\widehat{y}=y-\tau}^{y}$ accounts for key inputs that are normally unobserved.
};
\draw [->] (131.east) to [bend left=45] (141.east);

\end{tikzpicture}
\end{figure}

\clearpage
\section{Multi-stage Choice Diagram}

Three nodes, two in a row.

\tikzset{
    % Two node styles for game trees: solid and hollow
    solid node/.style={circle,draw,inner sep=1.5,fill=black},
    hollow node/.style={circle,draw,inner sep=1.5,fill=white}
}
\begin{center}
\begin{tikzpicture}[scale=1.5,font=\footnotesize]

% A.2 Level Styles
    % Specify spacing for each level of the tree
    \tikzstyle{level 1}=[level distance=17mm,sibling distance=25mm]
    \tikzstyle{level 2}=[level distance=15mm,sibling distance=15mm]

% B Level 1 point
\node(0)[solid node,label=above:{$P1$}]{}

% C Level 2 Node (child nodes)
% C.1 First child node, left
child{
    % C.1.a Node line color
    [red]
    % C.1.b Node dot
    node(1)[solid node, label=below:{red dot}]{}
    % C.1.c now go to edge
    edge from parent
        % C.1.c Node along edge
        node[sloped, above, black, text width=3cm]{Minimum Choice showing up along this red line}
    }
% C.2 Middle Child node, do not show line, invisible
child{
    % Main node of level 2 middle node, same y-axis height as node left and right
    % Y-shift to move level 3 child node lower
    [red]  % this is the style of the line middle line
        node(2)[solid node, xshift=30, yshift=-50, label=right:{hello}]{} % this is the style of the middle point that would have matched up the middle line
    % D.1 Left level 3 (from middle level 2)
    child{
        [black]
        node[hollow node,label=below:{$(a,b)$}]{}
        edge from parent
            node[left]{$C$}
        }
    child{
        [black]
        node[hollow node,label=below:{$(c,d)$}]{}
        edge from parent
            node[right]{$D$}
        }
    edge from parent
        % draw none here prevents the middle line extending rom P1 to hello to be drawn
        [draw=none]
        %note that you need to adjust the yshift if you change the level distance
        node[left, black, xshift=-5, yshift=0, text width = 1mm]{$\alpha$\\$\beta$\\$\sigma$}
    }
child{
    [black]
    node(3)[solid node, label=right:{hi there}, green]{}
    edge from parent
        node[right, xshift=0, yshift=15, text width=2cm]{Some text for this edge}
    };
% information set
\draw[dashed, bend right]
    (1) to (3);
\draw[dashed, bend left, line width=0.5mm, blue]
    (0) to
        node[right, text width=1.25cm, xshift=5, yshift=-10]
            {\tiny{label right of blue dashed line}}
        (2);
\end{tikzpicture}
\end{center}

\end{document}

### 2022-05-19 _tab/text/fs_tab_text.tex
Text only tables, and restructure home-page

\documentclass[12pt,english]{article}

\usepackage{blindtext}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{color}
% \usepackage[monochrome]{xcolor}
\usepackage{babel}
\usepackage{csquotes}
\usepackage{setspace}
\usepackage{graphicx}
\usepackage{booktabs,dcolumn}
\usepackage{array}
\usepackage{multirow}
\usepackage[font=singlespacing, skip=3pt]{caption}
\usepackage[usenames,dvipsnames,svgnames,table]{xcolor}
\usepackage{float}
\usepackage[export]{adjustbox}[2011/08/13]
\usepackage{subfig}
\usepackage{float}
\usepackage[colorlinks=true, linkcolor=blue, citecolor=blue, plainpages=false, pdfpagelabels=true, urlcolor=blue]{hyperref}
\usepackage{geometry}
\usepackage{ragged2e}

% rotate table
\usepackage{lscape}

% Thicker lines in table
\usepackage{hhline}

\geometry{
	a4paper,
	noheadfoot=true,
	left=1.0in,
	right=1.0in,
	top=1.0in,
	bottom=1.0in,
}

% \setlength{\parindent}{0pt}
\makeatletter
%\doublespacing
\onehalfspacing
\date{January 16, 2019}
\newcommand{\rowgroup}[1]{\hspace{-0.5em}#1}
\newcommand*\samethanks[1][\value{footnote}]{\footnotemark[#1]}
\newcommand{\sym}[1]{\ifmmode^{#1}\else\(^{#1}\)\fi}

\usepackage{array}
\usepackage{makecell}
\renewcommand\theadalign{bc}
\renewcommand\theadfont{\bfseries}
\renewcommand\theadgape{\Gape[4pt]}
\renewcommand\cellgape{\Gape[4pt]}
\newcolumntype{L}[1]{>{\raggedright\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\newcolumntype{C}[1]{>{\centering\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\newcolumntype{R}[1]{>{\raggedleft\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}

\usepackage{colortbl}

% Titling and Author
\title{Latex Tables, All Text Table Examples}
\author{\href{https://fanwangecon.github.io/}{Fan Wang}\thanks{\url{https://fanwangecon.github.io}, repository: \href{https://fanwangecon.github.io/Tex4Econ/}{Tex4Econ}}}
\date{\today}
\begin{document}

\maketitle

\section{Double Panel Three Columns, Centered}

\begin{table}[!ht]
\centering{}
{\small
	\caption{\label{tab:paramesti}Comparison of Production and Commercial Units}
	\begin{tabular}{>{\centering\arraybackslash}L{4cm} >{\centering\arraybackslash}L{4cm} >{\centering\arraybackslash}L{4cm}}
		\toprule
		\midrule
		\multicolumn{3}{c}{\textbf{Panel A: Urban areas}}\\
		\midrule
		\textbf{\textit{Before}} & \textbf{\textit{After}} & \textbf{\textit{In Charge}}\\
		\cmidrule(l){1-3}
		A&B&C\\
		\cmidrule(l){1-3}
		E&F&G\\
		\cmidrule(l){1-3}
		State-owned retailers, state-owned wholesale companies&E&F\\
		\cmidrule(l){1-3}
		Z&Z&Q\\
		\toprule
		\midrule
		\multicolumn{3}{c}{\textbf{Panel B: Rural areas}}\\
		\midrule
		\textbf{\textit{Before}} & \textbf{\textit{After}} & \textbf{\textit{In Charge}}\\
		\cmidrule(l){1-3}
		D&D&D\\
		Z&Rural handicraft cooperative groups, Agriculture collectives and transportation cooperatives &Z\\
		V&V&V\\
		\bottomrule
	\end{tabular}
}
\end{table}
\clearpage

\section{All Text Colored Table With Two Columns}

In the table below, there are two columns, the left-side column contains a single cell. Each cell has a heading. The cells are separated by lines. There is extra padding/spacing. The cells have colors.

Furthermore, we allow for thicker border lines via the \textbf{hhline} package. Additionally, we use the \textbf{hhline} package to draw horizontal hhline that is on top of background colors, it uses the same color as the background color in the first column, and uses black to show border in the second column.

\begin{scriptsize}
\begin{verbatim}
\begin{table}[h] \bgroup
\centering{}
    \def\arraystretch{2}%
    \fontsize{9}{9}\selectfont
    \caption{\label{tab:paramesti}Key sources of global}
    \arrayrulewidth=1.5mm
    \begin{tabular}{|p{6cm}|p{8cm}|}
    \hline
    \cellcolor{gray!20} 
    & \cellcolor{orange!5} \textbf{Heading Col 2 A}\newline ices augue, a dignissim nibh \\
    \hhline{|>{\arrayrulecolor{gray!20}}->{\arrayrulecolor{black}}|-|}
    \cellcolor{gray!20}
    & \cellcolor{blue!5} \textbf{Heading Col 2 B}\newline ices augue, a dignissim nibh lec \\
    \hhline{|>{\arrayrulecolor{gray!20}}->{\arrayrulecolor{black}}|-|}
    \multirow{-9.5}{6cm}{\cellcolor[gray]{.9}
    \textbf{Heading Col 1}\newline ipiscing elit. Etiam lobortis facilisis sem.}
    & \cellcolor{purple!5} \textbf{Heading Col 2 C}\newline ices augue, a dignissim nibh lec \\
    \hline
    \end{tabular}
\egroup\end{table}    
\end{verbatim}
\end{scriptsize}

\begin{table}[h]
\centering{}
\bgroup
\def\arraystretch{2}%
\fontsize{9}{9}\selectfont
\caption{\label{tab:paramesti}Key sources of global, comparative data on children's outcomes}
% arrayrulewidth controls with table outter boundary and vertical lines
\arrayrulewidth=1.5mm
\begin{tabular}{|p{6cm}|p{8cm}|} % centered columns (4 columns) 
\hline
\cellcolor{gray!20}
&
\cellcolor{orange!5}
\textbf{Heading Col 2 A}\newline
ices augue, a dignissim nibh lec-
tus placerat pede. Vivamus nunc nunc, mo-
lestie ut, ultricies vel, semper in, velit. Ut
porttitor. Praesent in sapien. Lorem ip-
sum dolor sit amet, consectetuer adipiscing
elit. Duis fringilla tristiq  ultricies vel, semper in, velit. Ut
porttitor. Praesent in sapien. Lorem ip-
sum dolor sit amet, consectetuer adipiscing
elit. Duis fringilla tristiq
\\
% https://tex.stackexchange.com/a/65235/109818
\hhline{|>{\arrayrulecolor{gray!20}}->{\arrayrulecolor{black}}|-|}
\cellcolor{gray!20}
&
\cellcolor{blue!5}
\textbf{Heading Col 2 B}\newline
ices augue, a dignissim nibh lec-
tus placerat pede. Vivamus nunc nunc, mo-
lestie ut, ultricies vel, semper in, velit. Ut
porttitor. Praesent in sapien. Lorem ip-
sum dolor sit amet, consectetuer adipiscing
elit. Duis fringilla tristiq
\\
% https://tex.stackexchange.com/a/65235/109818
\hhline{|>{\arrayrulecolor{gray!20}}->{\arrayrulecolor{black}}|-|}
\multirow{-9.5}{6cm}{\cellcolor[gray]{.9}\textbf{Heading Col 1}\newline
ipiscing elit. Etiam lobortis facilisis sem.
Nullam nec mi et neque pharetra sollicitudin.
Praesent imperdiet mi nec ante. Donec ul-
lamcorper, felis non sodales commodo, lec-
tus velit ultrices augue, a dignissim nibh lec-
tus placerat pede. Vivamus nunc nunc, mo-
lestie ut, ultricies vel, semper in, velit. Ut
porttitor. Praesent in sapien. Lorem ip-
sum dolor sit amet, consectetuer adipiscing
elit. Duis fringilla tristique neque. Sed in-
terdum libero ut metus. Pellentesque plac-
erat. Nam rutrum augue a leo. Morbi sed
elit sit amet ante lobortis s
}
&
\cellcolor{purple!5}
\textbf{Heading Col 2 C}\newline
ices augue, a dignissim nibh lec-
tus placerat pede. Vivamus nunc nunc, mo-
lestie ut, ultricies vel, semper in, velit. Ut
porttitor. Praesent in sapien. Lorem ip-
sum dolor sit amet, consectetuer adipiscing
elit. Duis fringilla tristiq \\
% \addlinespace[0.15cm]
\hline
\end{tabular}
\egroup
\end{table}

\clearpage

\section{Center-aligned Multiple Heading Landscape Table}

A table with nine columns, all center aligned. There are three heading columns. Using \textbf{multicolumn} as well as \textbf{multirow} to generate heading groupings.

\begin{tiny}
\begin{verbatim}
\begin{landscape}
\begin{table}[p]
\centering{}
{\fontsize{8}{8}\selectfont
	\caption{\label{tab:paramesti}Key sources of global, comparative data on children's outcomes}
	\begin{tabular}{
	>{\centering\arraybackslash}L{2cm} >{\centering\arraybackslash}L{3.25cm} >{\centering\arraybackslash}L{1.3cm}
	>{\centering\arraybackslash}L{1.3cm}
	>{\centering\arraybackslash}L{1.7cm}
	>{\centering\arraybackslash}L{1.4cm}
	>{\centering\arraybackslash}L{2.0cm}
	>{\centering\arraybackslash}L{1.9cm}
	>{\centering\arraybackslash}L{1.3cm}
	}
		\toprule
% 		\midrule
		&\multicolumn{3}{c}{Climate and pollution hazard measures}
		&\multicolumn{5}{c}{Child outcome measures}
		\\
		\cmidrule(lr){2-4}\cmidrule(lr){5-9}
		&\multicolumn{1}{c}{\multirow{2}{3.25cm}{\centering Directly asked within population survey/census}}
		&\multicolumn{2}{c}{Via GPS link}
		&\multicolumn{1}{c}{\multirow{2}{1.7cm}{\centering Prenatal/birth outcomes}}
		&\multicolumn{1}{c}{\multirow{2}{1.40cm}{\centering Physical health}}
		&\multicolumn{1}{c}{\multirow{2}{2.0cm}{\centering Developmental or behavioral measures}}
		&\multicolumn{2}{c}{Education}
		\\
		\cmidrule(lr){3-4}\cmidrule(lr){8-9}
		&\multicolumn{1}{c}{}
		&\emph{Available}
		&\emph{Planned}
		&\multicolumn{1}{c}{}
		&\multicolumn{1}{c}{}
		&\multicolumn{1}{c}{}
		&\multicolumn{1}{c}{\multirow{1}{1.9cm}{\centering\emph{Enrollment or Attainment}}}
		&\multicolumn{1}{c}{\multirow{1}{1.3cm}{Learning}}\\
		\addlinespace[0.05cm]
		\\
		\cmidrule(lr){1-9}
		\addlinespace[0.15cm]
		\textbf{Demographic and Health Surveys}
		& &x& &x&x& &x&
		\\
		\addlinespace[0.15cm]
		\cmidrule(lr){1-9}
		\addlinespace[0.15cm]
		\textbf{Multiple Indicator Cluster Surveys}
		& x [Child's school closed in last year due to natural disaster]
		& &x& & &x&x&x
		\\
		\addlinespace[0.15cm]
		\cmidrule(lr){1-9}
		\addlinespace[0.15cm]
		\textbf{Young Lives Surveys}
		& x [Community reports natural disasters]
		& &x&x&x&x&x&x
		\\
		\addlinespace[0.15cm]
		\cmidrule(lr){1-9}
		\addlinespace[0.15cm]
		\textbf{IPUMS-Terra Census Data}
		& & &x& & & &x&
		\\
		\addlinespace[0.15cm]
		\bottomrule
	\end{tabular}
}
\end{table}
\end{landscape}    
\end{verbatim}
\end{tiny}

\begin{landscape}
\begin{table}[p]
\centering{}
{\fontsize{8}{8}\selectfont
	\caption{\label{tab:paramesti}Key sources of global, comparative data on children's outcomes}
	\begin{tabular}{
	>{\centering\arraybackslash}L{2cm} >{\centering\arraybackslash}L{3.25cm} >{\centering\arraybackslash}L{1.3cm}
	>{\centering\arraybackslash}L{1.3cm}
	>{\centering\arraybackslash}L{1.7cm}
	>{\centering\arraybackslash}L{1.4cm}
	>{\centering\arraybackslash}L{2.0cm}
	>{\centering\arraybackslash}L{1.9cm}
	>{\centering\arraybackslash}L{1.3cm}
	}
		\toprule
% 		\midrule
		&\multicolumn{3}{c}{Climate and pollution hazard measures}
		&\multicolumn{5}{c}{Child outcome measures}
		\\
		\cmidrule(lr){2-4}\cmidrule(lr){5-9}
		&\multicolumn{1}{c}{\multirow{2}{3.25cm}{\centering Directly asked within population survey/census}}
		&\multicolumn{2}{c}{Via GPS link}
		&\multicolumn{1}{c}{\multirow{2}{1.7cm}{\centering Prenatal/birth outcomes}}
		&\multicolumn{1}{c}{\multirow{2}{1.40cm}{\centering Physical health}}
		&\multicolumn{1}{c}{\multirow{2}{2.0cm}{\centering Developmental or behavioral measures}}
		&\multicolumn{2}{c}{Education}
		\\
		\cmidrule(lr){3-4}\cmidrule(lr){8-9}
		&\multicolumn{1}{c}{}
		&\emph{Available}
		&\emph{Planned}
		&\multicolumn{1}{c}{}
		&\multicolumn{1}{c}{}
		&\multicolumn{1}{c}{}
		&\multicolumn{1}{c}{\multirow{1}{1.9cm}{\centering\emph{Enrollment or Attainment}}}
		&\multicolumn{1}{c}{\multirow{1}{1.3cm}{Learning}}\\
		\addlinespace[0.05cm]
		\\
		\cmidrule(lr){1-9}
		\addlinespace[0.15cm]
		\textbf{Demographic and Health Surveys}
		& &x& &x&x& &x&
		\\
		\addlinespace[0.15cm]
		\cmidrule(lr){1-9}
		\addlinespace[0.15cm]
		\textbf{Multiple Indicator Cluster Surveys}
		& x [Child's school closed in last year due to natural disaster]
		& &x& & &x&x&x
		\\
		\addlinespace[0.15cm]
		\cmidrule(lr){1-9}
		\addlinespace[0.15cm]
		\textbf{Young Lives Surveys}
		& x [Community reports natural disasters; households report natural disasters; child reports child reports natural hazard/flood as a difficulty in getting to school]
		& &x&x&x&x&x&x
		\\
		\addlinespace[0.15cm]
		\cmidrule(lr){1-9}
		\addlinespace[0.15cm]
		\textbf{IPUMS-Terra Census Data}
		& & &x& & & &x&
		\\
		\addlinespace[0.15cm]
		\bottomrule
	\end{tabular}
}
\end{table}
\end{landscape}

\end{document}

### 2025-11-09 _other/tikz/distribution/latent_health.tex
Updates from Overleaf

% create a standalone latex file for generating a tikz figure.
% generate the following tikz visualization with two plots (added with \addplot), and several nodes. 
% 0. make the overall plot wide so that there is plenty of space.
% 1. create an x-axis and an y-axis.
% 2. the values along the x-axis should range from -5 to 5, and the values along the y-axis should range from 0 to 0.5.
% 3. first, plot the standard normal distribution curve on the graph, labeling it "normal (\mu=0, \sigma=1)", using a solid blue line, this has name path = mu0sigma1
% 4. second, plot the normal distribution curve on the graph with mean +1 and standard deviation 1, labeling it "normal (\mu=1, \sigma=1)", using a solid red line, this has name path = mu1sigma1
% 5. the legend position should be to the south of the plot, outside the plot area.
% 6. now we draw a vertical line that connects the x-axis to the mu0sigma1 curve at x = -0.3853205, this is node 101, no label value printed.
% 7. between the mu0sigma1 curve and the x-axis, we shade the area to the left of node 101 with a light blue color. this has name path = mu0sigma1area. We create a node outside of the shaded area, and label it as $P(H(h^{\text{base}}, d^{\text{base}}) \leq \zeta_{\text{good}}) = 0.350$, this points towards the shaded area mu0sigma1area. The label text should be fully visible in the plot. This node has node value 102.
% 8. between the mu1sigma1 curve and the x-axis, we shade the area to the left of node 101 with a light red color. this has name path = mu1sigma1area. We create a node outside of the shaded area, and label it as $P(H(h^{\text{base}}+1, d^{\text{base}}+1) \leq \zeta_{\text{good}}) = 0.083$, this points towards the shaded area mu1sigma1area. The label text should be fully visible in the plot. This node has node value 101.
% 9. We draw an extra x-axis tic at the x position of node 101. we then create a node with the value of -0.3853205 to 2 decimals, printed below the x-axis below the tic mark, and with an arrow pointing to the tic mark. This new node is named node 203. The label text should be fully visible in the plot.

\documentclass{article}
\usepackage{geometry}
\geometry{
	a4paper,
	noheadfoot=true,
	left=1.0in,
	right=1.0in,
	top=1.0in,
	bottom=1.0in
}
\usepackage{amsmath}
\usepackage{float}
\usepackage{pgfplots}
\usepackage{subcaption}
\pgfplotsset{compat=1.17}
\usepgfplotslibrary{fillbetween}
\usetikzlibrary{decorations.pathreplacing}

\begin{document}

\begin{figure}[H]
    \centering
    \captionsetup{width=1.0\textwidth}
	\caption{Illustration of the identification of latent health thresholds and marginal effects given elicited subjective health probabilities across input scenarios and health status levels.}
	\label{fig:vert}
	\begin{subfigure}[t]{1.0\textwidth}
        % Sub-caption
        \centering
    		\caption{Baseline subjective health probabilities and thresholds}	
        \begin{tikzpicture}
            \begin{axis}[
                width=16cm,
                height=8cm,
                font=\footnotesize,
                xlabel={$x$},
                ylabel={Density},
                xmin=-5, xmax=5,
                ymin=0, ymax=0.47,
                samples=200,
                domain=-5:5,
                legend style={at={(1.0, 1.0)}, anchor=north east, align=left},
                extra x ticks={-0.3853205},
                extra x tick labels={},
                clip=false
            ]

            % Plot standard normal distribution

            \addplot[blue, thick, name path=mu0sigma1] {1/sqrt(2*pi)*exp(-0.5*x^2)};
            \addlegendentry{
                Standardized latent health\\
                distribution at $(d^{\text{base}}, e^{\text{base}})$\\
                $H(d^{\text{base}}, e^{\text{base}}) \sim \mathcal{N}\left(\mu=0, \sigma=1\right)$
                }
            % Create path for x-axis
            \path[name path=axis] (axis cs:-5,0) -- (axis cs:5,0);

            % Shade area under mu0sigma1 to the left of x=-0.3853205
            \addplot[blue!20, name path=mu0sigma1area] fill between[of=mu0sigma1 and axis, soft clip={domain=-5:-0.3853205}];

            % Draw vertical line at x=-0.3853205 (node 101)
            \draw[solid, blue!50, very thick] (axis cs:-0.3853205,0) -- (axis cs:-0.3853205,{1/sqrt(2*pi)*exp(-0.5*(-0.3853205)^2)});

            % Node 102 for mu0sigma1 area
            \node[anchor=north west, align=left] at (axis cs:-4.8,0.40) (102) {
            % \node[anchor=north west, align=left] at (axis cs:-4.7, 0.50) (102) {
                % Elicit baseline $(d^{\text{base}}, e^{\text{base}})$ subjective\\ 
                % probability of less than good health: \\
                $P(H(d^{\text{base}}, e^{\text{base}}) < \zeta_{\text{good}}) = 0.350$\\
                % Given normalization, identify\\
                % latent health threshold for\\
                % good health: $\zeta_{\text{good}}=-0.385$.
                };
            \draw[->, thick] ( [xshift=0.0cm] 102.south) -- (axis cs:-0.85,0.12);

            % \draw[densely dashdotted, blue, very thick] (axis cs:0,0) -- (axis cs:0,{1/sqrt(2*pi)*exp(-0.5*(0)^2)});

            % Node 203 for x-axis label
            \node[anchor=north] at (axis cs:-0.3853205,-0.08) (103) {$\zeta_{\text{good}} = -0.385$};
            \draw[->, thick] (103) -- (axis cs:-0.3853205,-0.01);

            \end{axis}
        \end{tikzpicture}
    \end{subfigure}

	\par\smallskip % this line generates two rows

	\begin{subfigure}[t]{1.0\textwidth}
	    % Sub-caption
	    \centering
        \caption{Subjective health probabilities at alternative input scenarios and marginal effects}   
            \begin{tikzpicture}
            \begin{axis}[
                width=16cm,
                height=8cm,
                font=\footnotesize,
                xlabel={$x$},
                ylabel={Density},
                xmin=-5, xmax=5,
                ymin=0, ymax=0.47,
                samples=200,
                domain=-5:5,
                legend style={at={(1.0, 1.0)}, anchor=north east, align=left},
                extra x ticks={-0.3853205},
                extra x tick labels={},
                clip=false
            ]

            % Plot standard normal distribution
            \addplot[blue!30, thick, name path=mu0sigma1] {1/sqrt(2*pi)*exp(-0.5*x^2)};
            % \addlegendentry{
            %     $H(d^{\text{base}}, e^{\text{base}}) \sim \mathcal{N}\left(\mu=0, \sigma=1)\right)$
            %     }

            % Plot normal distribution with mu=1, sigma=1
            \addplot[red, thick, name path=mu1sigma1] {1/sqrt(2*pi)*exp(-0.5*(x-1.259533)^2)};
            \addlegendentry{
                $H(d^{\text{base}}+1, e^{\text{base}}+1)$\\
                $\sim \mathcal{N}\left(\mu=\lambda_{\left(++\right)}, \sigma=1\right)$
                }

            % Create path for x-axis
            \path[name path=axis] (axis cs:-5,0) -- (axis cs:5,0);

            % Shade area under mu0sigma1 to the left of x=-0.3853205
            \addplot[blue!07, name path=mu0sigma1area] fill between[of=mu0sigma1 and axis, soft clip={domain=-5:-0.3853205}];

            % Shade area under mu1sigma1 to the left of x=-0.3853205
            \addplot[red!20, name path=mu1sigma1area] fill between[of=mu1sigma1 and axis, soft clip={domain=-5:-0.3853205}];

            % Draw vertical line at x=-0.3853205 (node 101)
            \draw[solid, red!50, very thick] (axis cs:-0.3853205,0) -- (axis cs:-0.3853205,{1/sqrt(2*pi)*exp(-0.5*(-0.3853205-1.259533)^2)});

            % % Node 102 for mu0sigma1 area
            % \node[anchor=east] at (axis cs:-1,0.425) (202) {$P(H(d^{\text{base}}, e^{\text{base}}) \leq \zeta_{\text{good}}) = 0.350$};
            % \draw[->, thick] ( [xshift=1cm] 202.south) -- (axis cs:-0.85,0.15);

            % Node 101 for mu1sigma1 area (note: description says node value 101)
            \node[anchor=north west, align=left] at (axis cs:-4.8,0.40) (202) {
            % \node[anchor=north west, align=left] at (axis cs:-4.8,0.52) (202) {
                % Elicit scenario-specific ($d^{\text{base}}+1, e^{\text{base}}+1$)\\
                % subjective probability of less than good health: \\
                $P(H(d^{\text{base}}+1, e^{\text{base}}+1) < \zeta_{\text{good}}) = 0.050$\\
                % Given $\zeta_{\text{good}}$ and the same uncertainty\\
                % distribution ($\sigma=1$) identify\\
                % the marginal shift in\\
                % latent health: $\lambda_{\left(++\right)}=1.260$\\
                };
            \draw[->, thick] ([xshift=0.0cm, yshift=+0cm] 202.south) -- (axis cs:-0.65,0.035);

            % draw a node 
            \draw[densely dashdotted, blue!30, very thick] (axis cs:0,0) -- (axis cs:0,{1/sqrt(2*pi)*exp(-0.5*(0)^2)});
            \draw[densely dashdotted, red, very thick] (axis cs:1.259533,0) -- (axis cs:1.259533,{1/sqrt(2*pi)*exp(-0.5*(0)^2)});
            % draw a underbrace between the two dashdotted lines
            \draw[decorate,decoration={brace,mirror,amplitude=6pt},thick,align=center]
                (axis cs:0,0.15) -- (axis cs:1.259533,0.15) node[midway,below=6pt] {
                    $\lambda_{\left(++\right)}$\\
                    $=1.260$
                    };

            % solve for lambda, such that:
            % qnorm(zeta, mean=lambda, sd=1) = 0.15

            % We have:
            % F_Y(zeta) = P(Y <= zeta) = prob2
            % Y = X + lambda

            % Therefore:
            % F_Y(zeta)
            % = P(Y <= zeta) 
            % = P(X + lambda <= zeta)
            % = P(X <= zeta - lambda)
            % = F_X(zeta - lambda)
            % = prob2

            % zeta - qnorm(prob2)
            % zeta = qnorm(prob1)

            % Node 203 for x-axis label
            \node[anchor=north] at (axis cs:-0.3853205,-0.08) (203) {$\zeta_{\text{good}} = -0.385$};
            \draw[->, thick] (203) -- (axis cs:-0.3853205,-0.01);

            \end{axis}
            \end{tikzpicture}

	\end{subfigure}    
	\par\smallskip
    \parbox[t]{1.0\textwidth}{\footnotesize \emph{Note:}
    Next period latent health is a random variable. 
    The latent health random variable at baseline input levels is $H(d^{\text{base}}, e^{\text{base}})$. 
    The latent health random variable given increases in both input levels is 
    $H(d^{\text{base}}+1, e^{\text{base}}+1)$.
    We elicit subjective probabilities that next period latent health is worse than ``good'' at the baseline and alternative input scenarios.
    We assume that latent health is a mixture of normals (in this case one normal).
    Since the scale and location of latent variables can not be identified, we normalize $H(d^{\text{base}}, e^{\text{base}}) \sim \mathcal{N}\left(\mu=0, \sigma=1\right)$.
    The normalized latent threshold for good health, $\zeta_{\text{good}}$, can be identified by inverting the survey-elicited cumulative probability of having less than good health: 
    $\Phi^{-1}\left(P\left(H\left(d^{\text{base}}, e^{\text{base}}\right) < \zeta_{\text{good}} \right)\right) = \zeta_{\text{good}}$. 
    The marginal effect of increasing inputs is $\lambda_{\left(++\right)}$, where $\lambda_{\left(++\right)}$ provides a mean-shift of the baseline latent health random variable: $H(d^{\text{base}}+1, e^{\text{base}}+1) = H(d^{\text{base}}, e^{\text{base}}) + \lambda_{\left(++\right)}$.
    The marginal effect can be identified as the difference of inverted cdfs:
    We have $
    P\left(H\left(d^{\text{base}}+1, e^{\text{base}}+1\right) < \zeta_{\text{good}} \right) = 
    P\left(H\left(d^{\text{base}}, e^{\text{base}}\right) + \lambda_{\left(++\right)} < \zeta_{\text{good}} \right) = 
    \Phi\left(\zeta_{\text{good}} - \lambda_{\left(++\right)}\right)
    $, and hence $
    \lambda_{\left(++\right)} = \zeta_{\text{good}} - 
    \Phi^{-1}\left(
        P\left(H\left(d^{\text{base}}+1, e^{\text{base}}+1\right) < \zeta_{\text{good}} \right)
    \right)
    $.
    }
\end{figure}
\end{document}

### 2025-11-09 _other/tikz/tree/fs_tikz_nodediagram.tex

@@
 \usepackage{tikz}
+\usetikzlibrary{decorations.text}
+
 \usepackage{pgfplots}
@@
 \newpage
+
+\section{Concentric Circle Diagrams}
+
+\subsection{Single Set of Concentric Circles}
+
+We have three circles concentric, with word on top. Here is the code:
+\begin{verbatim}
+\begin{tikzpicture}[thick, font=\small]
+\def\sizechd{1cm}
+\def\sizehum{3cm}
+\def\sizefac{4.5cm}
+    % Objective I
+    \node(101) at (0,0) [fill, circle, 
+        draw=black!50, fill=yellow!40, 
+        minimum size=\sizefac] {};
+    \node(102) at (0,0) [fill, circle, 
+        draw=blue!50, fill=blue!20, 
+        minimum size=\sizehum, label=above:Home] {};
+    \node(103) at (0,0) [circle, 
+        draw=black!50, fill=white!20, 
+        scale=1, minimum size=\sizechd, label=above:Caretakers] {Children};
+\end{tikzpicture}
+\end{verbatim}
+
+Here is the figure:
+\begin{center}
+\begin{tikzpicture}[thick, font=\small]
+\def\sizechd{1cm}
+\def\sizehum{3cm}
+\def\sizefac{4.5cm}
+    % Objective I
+    \node(101) at (0,0) [fill, circle, draw=black!50, fill=yellow!40, minimum size=\sizefac] {Data 3};
+    \node(102) at (0,0) [fill, circle, draw=blue!50, fill=blue!20, minimum size=\sizehum, label=above:Home] {Data 2};
+    \node(103) at (0,0) [circle, draw=black!50, fill=white!20, scale=1, minimum size=\sizechd, label=above:Caretakers] {Children};
+\end{tikzpicture}
+\end{center}
+
+\subsection{Three Sets of Concentric Circles}
+
+We have three sets of three circles concentric, with word on top.
+\begin{center}
+\begin{tikzpicture}[thick, font=\small]
+\def\sizechd{1cm}
+\def\sizehum{3cm}
+\def\sizefac{4.5cm}
+\def\xcira{-2.15}
+\def\xcirb{2.15}
+\def\xcirc{0}
+\def\ycira{0}
+\def\ycirb{0}
+\def\ycirc{-3.75}
+
+% Circle A
+\node(101) at (\xcira, \ycira) [fill, circle, draw=black!50, fill=yellow!40, minimum size=\sizefac] {};
+\node(102) at (\xcira, \ycira) [fill, circle, draw=blue!50, fill=blue!20, minimum size=\sizehum, label=above:Home] {};
+\node(103) at (\xcira, \ycira) [circle, draw=black!50, fill=white!20, scale=1, minimum size=\sizechd, label=above:Caretakers] {Children};
+% \path   [thin, draw=blue, text=black,    % <--- new
+%          postaction={decorate},           % <--- changed
+%          text effects={text along path}]  % <--- new
+%         (4,0) arc [start angle=-60,end angle=80,radius=4];
+
+% Circle B
+\node(101) at (\xcirb, \ycirb) [fill, circle, draw=black!50, fill=yellow!40, minimum size=\sizefac] {Data 3};
+\node(102) at (\xcirb, \ycirb) [fill, circle, draw=blue!50, fill=blue!20, minimum size=\sizehum, label=above:Home] {Data 2};
+\node(103) at (\xcirb, \ycirb) [circle, draw=black!50, fill=white!20, scale=1, minimum size=\sizechd, label=above:Caretakers] {Children};
+
+% Circle C
+\node(101) at (\xcirc, \ycirc) [fill, circle, draw=black!50, fill=yellow!40, minimum size=\sizefac] {Data 3};
+\node(102) at (\xcirc, \ycirc) [fill, circle, draw=blue!50, fill=blue!20, minimum size=\sizehum, label=above:Home] {Data 2};
+\node(103) at (\xcirc, \ycirc) [circle, draw=black!50, fill=white!20, scale=1, minimum size=\sizechd, label=above:Caretakers] {Children};
+\end{tikzpicture}
+\end{center}
+
+\subsection{Circle with Circular Text}
+
+We have three circles concentric, with concentric text.
+The text starts from 180 degree and goes to 0 degree, covering half a circle.
+The text is centered, so if there is less text, the text appears in the center.
+
+\begin{center}
+\begin{tikzpicture}[thick, font=\small]
+\def\sizechd{1cm}
+\def\sizehum{3cm}
+\def\sizefac{4.5cm}
+\def\xcira{0}
+\def\ycira{0}
+
+% Circle A
+\node(101) at (\xcira, \ycira) [fill, circle, draw=black!50, fill=yellow!40, minimum size=\sizefac] {};
+\node(102) at (\xcira, \ycira) [fill, circle, draw=blue!50, fill=blue!20, minimum size=\sizehum] {};
+\node(103) at (\xcira, \ycira) [circle, draw=black!50, fill=white!20, scale=1, minimum size=\sizechd] {Children};
+
+\draw[decoration={
+    text along path,
+    text={Caretakers are here.},
+    text align={center},
+    raise=0cm},decorate] (-1, 0) arc (180:0:1);
+\draw[decoration={
+    text along path,
+    text={This is our home!},
+    text align={center},
+    raise=0cm},decorate] (-1.8, 0) arc (180:0:1.8);
+
+\end{tikzpicture}
+\end{center}
+
+\subsection{Three Sets of Concentric Circles with Circular Text}
+
+We have three sets of three circles concentric, with word on top.
+
+\begin{center}
+\begin{tikzpicture}[thick, font=\normalsize]
+\def\sizechd{1.5cm}
+\def\sizehum{3.5cm}
+\def\sizefac{5cm}
+% Cirlce x and y
+\def\xcira{-2.4}
+\def\xcirb{2.4}
+\def\xcirc{0}
+\def\ycira{0}
+\def\ycirb{0}
+\def\ycirc{-4.2}
+
+% Circle A
+\node(101) at (\xcira, \ycira) [fill, circle, draw=black!50, fill=yellow!40, minimum size=\sizefac] {};
+\node(102) at (\xcira, \ycira) [fill, circle, draw=blue!50, fill=blue!20, minimum size=\sizehum] {};
+\node(103) at (\xcira, \ycira) [circle, draw=black!50, fill=white!20, scale=1, minimum size=\sizechd] {Children};
+\draw[decoration={
+    text along path,
+    text={Child health professionals},
+    text align={center},
+    raise=0cm},decorate] (-3.60, 0) arc (180:0:1.22);
+\draw[decoration={
+    text along path,
+    text={Health facilities},
+    text align={center},
+    raise=0cm},decorate] (-4.4, 0) arc (180:0:2);
+
+% Circle B
+\node(101) at (\xcirb, \ycirb) [fill, circle, draw=black!50, fill=yellow!40, minimum size=\sizefac] {Data 3};
+\node(102) at (\xcirb, \ycirb) [fill, circle, draw=blue!50, fill=blue!20, minimum size=\sizehum] {Data 2};
+\node(103) at (\xcirb, \ycirb) [circle, draw=black!50, fill=white!20, scale=1, minimum size=\sizechd] {Children};
+\draw[decoration={
+    text along path,
+    text={Teachers Teachers Teachers Teachers Teachers.},
+    text align={center},
+    raise=0cm},decorate] (1.20, 0) arc (180:-179:1.22);
+\draw[decoration={
+    text along path,
+    text={Schools Schools Schools Schools Schools Schools Schools Schools Schools.},
+    text align={center},
+    raise=0cm},decorate] (0.4, 0) arc (180:-179:2);
+
+% Circle C
+\node(101) at (\xcirc, \ycirc) [fill, circle, draw=black!50, fill=yellow!40, minimum size=\sizefac] {Data 3};
+\node(102) at (\xcirc, \ycirc) [fill, circle, draw=blue!50, fill=blue!20, minimum size=\sizehum] {Data 2};
+\node(103) at (\xcirc, \ycirc) [circle, draw=black!50, fill=white!20, scale=1, minimum size=\sizechd] {Children};
+\draw[decoration={
+    text along path,
+    text={Teachers Teachers Teachers Teachers Teachers.},
+    text align={center},
+    raise=0cm},decorate] (-1.22, -4.20) arc (180:-179:1.22);
+\draw[decoration={
+    text along path,
+    text={Schools Schools Schools Schools Schools Schools Schools Schools Schools.},
+    text align={center},
+    raise=0cm},decorate] (-2.02, -4.20) arc (180:-179:2);
+
+\end{tikzpicture}
+\end{center}
+\clearpage
+
+\subsection{Three Sets of Concentric Circles with Circular Text and Big Eclipse}
+
+We have three sets of three circles concentric, with word on top.
+
+\begin{center}
+\begin{tikzpicture}[thick, font=\normalsize]
+\def\sizechd{1.5cm}
+\def\sizehum{3.5cm}
+\def\sizefac{5cm}
+% Cirlce x and y
+\def\xcira{-2.4}
+\def\xcirb{2.4}
+\def\xcirc{0}
+\def\ycira{0}
+\def\ycirb{0}
+\def\ycirc{-4.2}
+
+\draw [black, fill=gray!20] (0, -1.7) ellipse (6.75cm and 5.5cm);
+
+% Circle A
+\node(101) at (\xcira, \ycira) [fill, circle, draw=black!50, fill=yellow!40, minimum size=\sizefac] {};
+\node(102) at (\xcira, \ycira) [fill, circle, draw=blue!50, fill=blue!20, minimum size=\sizehum] {};
+\node(103) at (\xcira, \ycira) [circle, draw=black!50, fill=white!20, scale=1, minimum size=\sizechd] {Children};
+\draw[decoration={
+    text along path,
+    text={Child health professionals},
+    text align={center},
+    raise=0cm},decorate] (-3.60, 0) arc (180:0:1.22);
+\draw[decoration={
+    text along path,
+    text={Health facilities},
+    text align={center},
+    raise=0cm},decorate] (-4.4, 0) arc (180:0:2);
+
+% Circle B
+\node(101) at (\xcirb, \ycirb) [fill, circle, draw=black!50, fill=yellow!40, minimum size=\sizefac] {Data 3};
+\node(102) at (\xcirb, \ycirb) [fill, circle, draw=blue!50, fill=blue!20, minimum size=\sizehum] {Data 2};
+\node(103) at (\xcirb, \ycirb) [circle, draw=black!50, fill=white!20, scale=1, minimum size=\sizechd] {Children};
+\draw[decoration={
+    text along path,
+    text={Teachers Teachers Teachers Teachers Teachers.},
+    text align={center},
+    raise=0cm},decorate] (1.20, 0) arc (180:-179:1.22);
+\draw[decoration={
+    text along path,
+    text={Schools Schools Schools Schools Schools Schools Schools Schools Schools.},
+    text align={center},
+    raise=0cm},decorate] (0.4, 0) arc (180:-179:2);
+
+% Circle C
+\node(101) at (\xcirc, \ycirc) [fill, circle, draw=black!50, fill=yellow!40, minimum size=\sizefac] {Data 3};
+\node(102) at (\xcirc, \ycirc) [fill, circle, draw=blue!50, fill=blue!20, minimum size=\sizehum] {Data 2};
+\node(103) at (\xcirc, \ycirc) [circle, draw=black!50, fill=white!20, scale=1, minimum size=\sizechd] {Children};
+\draw[decoration={
+    text along path,
+    text={Teachers Teachers Teachers Teachers Teachers.},
+    text align={center},
+    raise=0cm},decorate] (-1.22, -4.20) arc (180:-179:1.22);
+\draw[decoration={
+    text along path,
+    text={Schools Schools Schools Schools Schools Schools Schools Schools Schools.},
+    text align={center},
+    raise=0cm},decorate] (-2.02, -4.20) arc (180:-179:2);
+
+% Text 
+% \node[below] at (0, 3.5) {
+% Climatic environment, extreme weather, etc.};
+\node[below] at (0, 3.5) [rectangle, draw=gray!50, fill=gray!10, text width=3cm] {Climate shocks environmental crisis.};
+
+\end{tikzpicture}
+\end{center}
+\clearpage
+
+\subsection{Three Sets of Concentric Circles with Circular Text and Big Eclipse and Arrows Outcomes}
+
+We have three sets of three circles concentric, with word on top. Edges and centered text below.
+
+\begin{center}
+\begin{tikzpicture}[thick, font=\small]
+\tikzstyle{every node}=[draw,shape=ellipse];
+\def\sizechd{1.5cm}
+\def\sizehum{3.5cm}
+\def\sizefac{5cm}
+% Cirlce x and y
+\def\xcira{-2.4}
+\def\xcirb{2.4}
+\def\xcirc{0}
+\def\ycira{0}
+\def\ycirb{0}
+\def\ycirc{-4.2}
+
+% Background gray
+\draw [black, fill=gray!20] (0, -1.4) ellipse (5.75cm and 5.75cm);
+
+% Circle A
+\node(101) at (\xcira, \ycira) [fill, circle, draw=black!50, fill=yellow!40, minimum size=\sizefac] {};
+\node(102) at (\xcira, \ycira) [fill, circle, draw=blue!50, fill=blue!20, minimum size=\sizehum] {};
+\node(103) at (\xcira, \ycira) [circle, draw=black!50, fill=white!20, scale=1, minimum size=\sizechd] {Children};
+\draw[decoration={
+    text along path,
+    text={Child health professionals},
+    text align={center},
+    raise=0cm},decorate] (-3.60, 0) arc (180:0:1.22);
+\draw[decoration={
+    text along path,
+    text={Health facilities},
+    text align={center},
+    raise=0cm},decorate] (-4.4, 0) arc (180:0:2);
+
+% Circle B
+\node(201) at (\xcirb, \ycirb) [fill, circle, draw=black!50, fill=yellow!40, minimum size=\sizefac] {};
+\node(202) at (\xcirb, \ycirb) [fill, circle, draw=blue!50, fill=blue!20, minimum size=\sizehum] {};
+\node(203) at (\xcirb, \ycirb) [circle, draw=black!50, fill=white!20, scale=1, minimum size=\sizechd] {Children};
+\draw[decoration={
+    text along path,
+    text={Teachers Teachers Teachers Teachers Teachers.},
+    text align={center},
+    raise=0cm},decorate] (1.20, 0) arc (180:-179:1.22);
+\draw[decoration={
+    text along path,
+    text={Schools Schools Schools Schools Schools Schools Schools Schools Schools.},
+    text align={center},
+    raise=0cm},decorate] (0.4, 0) arc (180:-179:2);
+
+% Circle C
+\node(301) at (\xcirc, \ycirc) [fill, circle, draw=black!50, fill=yellow!40, minimum size=\sizefac] {};
+\node(302) at (\xcirc, \ycirc) [fill, circle, draw=blue!50, fill=blue!20, minimum size=\sizehum] {};
+\node(303) at (\xcirc, \ycirc) [circle, draw=black!50, fill=white!20, scale=1, minimum size=\sizechd] {Children};
+\draw[decoration={
+    text along path,
+    text={Teachers Teachers Teachers Teachers Teachers.},
+    text align={center},
+    raise=0cm},decorate] (-1.22, -4.20) arc (180:-179:1.22);
+\draw[decoration={
+    text along path,
+    text={Schools Schools Schools Schools Schools Schools Schools Schools Schools.},
+    text align={center},
+    raise=0cm},decorate] (-2.02, -4.20) arc (180:-179:2);
+
+% Text 
+% \node[below] at (0, 3.5) {
+% Climatic environment, extreme weather, etc.};
+% \node[below] at (0, 3.5) [rectangle, draw=gray!50, fill=gray!10, text width=3.5cm] {\textbf{{\normalsize \textcolor{blue}{Extreme Weather Crisis}}}};
+\draw[decoration={
+    text along path,
+    text={Extreme Weather Crisis Extreme Weather Crisis Extreme Weather Crisis Extreme Weather Crisis.},
+    text align={center},
+    raise=0cm},decorate] (-6, -1.45) arc (180:0:6);
+
+\node(898) at (-4, -3.75) [rectangle, draw=gray!20, fill=gray!20, text width=0cm] {};
+\node(899) at (+4, -3.75) [rectangle, draw=gray!20, fill=gray!20, text width=0cm] {};
+
+\node at (0, 3.5) [rectangle, draw=blue!20, fill=gray!20, minimum width=3.8cm] {\textcolor{blue}{Extreme temperature}};
+\node at (0, 2.9) [rectangle, draw=blue!20, fill=gray!20, minimum width=3.8cm] {\textcolor{blue}{Pollution}};
+\node(998) at (0, -7.75) [rectangle, draw=gray!10, fill=gray!0, minimum width=3.8cm] {\textcolor{red}{Human Capital Formation}};
+\node(999) at (0, -8.25) [rectangle, draw=gray!10, fill=gray!0, minimum width=7.1cm] {\textcolor{black}{Learning, psychological, socio-emotional, physical outcomes}};
+
+\path[->] (101.south west) edge [double, out=-1200, 
+    in=100, draw=red,line width=1pt] (898.north);
+\path[->] (301.west) edge [double, out=-1200, 
+    in=0, draw=red,line width=1pt] (898.east);
+\path[->] (898.south west) edge [double, out=-1200, 
+    in=150, draw=red,line width=1pt] (998.west);
+
+\path[->] (201.south east) edge [double, out=-70, 
+    in=100, draw=red,line width=1pt] (899.north);
+\path[->] (301.east) edge [double, out=0, 
+    in=-200, draw=red,line width=1pt] (899.west);
+\path[->] (899.south east) edge [double, out=0, 
+    in=20, draw=red,line width=1pt] (998.east);
+
+\end{tikzpicture}
+\end{center}
+% \clearpage
+
+\subsection{Three Sets of Concentric Circles with Circular Text and Big Eclipse and Arrows Outcomes and Outside Arrows and Central Circle}
+
+We have three sets of three circles concentric, with word on top. Edges and centered text below. Additional circle inside, and centered areas. We also resize the area the make it smaller
+% VSPACE reduction needed after adding the outside dashed lines, which somehow added extra spaces
+\begin{center}
+\vspace*{-1cm}
+\hspace*{-0.5cm}
+\resizebox{8cm}{!}{
+\begin{tikzpicture}[font=\small]
+\tikzstyle{every node}=[draw,shape=ellipse];
+\def\sizechd{1.5cm}
+\def\sizehum{3.5cm}
+\def\sizefac{5cm}
+% Cirlce x and y
+\def\xcira{-2.4}
+\def\xcirb{2.4}
+\def\xcirc{0}
+\def\ycira{0}
+\def\ycirb{0}
+\def\ycirc{-4.2}
+
+% Background gray
+\draw [black, fill=gray!20] (0, -1.4) ellipse (5.75cm and 5.75cm);
+
+% Circle A
+\node(101) at (\xcira, \ycira) [fill, circle, draw=black!50, fill=yellow!40, minimum size=\sizefac] {};
+\node(102) at (\xcira, \ycira) [fill, circle, draw=blue!50, fill=blue!20, minimum size=\sizehum] {};
+\node(103) at (\xcira, \ycira) [circle, draw=black!50, fill=white!20, scale=1, minimum size=\sizechd] {Children};
+\draw[decoration={
+    text along path,
+    text={Child health professionals},
+    text align={center},
+    raise=0cm},decorate] (-3.60, 0) arc (180:0:1.22);
+\draw[decoration={
+    text along path,
+    text={Maternal/Child health facilities},
+    text align={center},
+    raise=0cm},decorate] (-4.4, 0) arc (180:0:2);
+
+% Circle B
+\node(201) at (\xcirb, \ycirb) [fill, circle, draw=black!50, fill=yellow!40, minimum size=\sizefac] {};
+\node(202) at (\xcirb, \ycirb) [fill, circle, draw=blue!50, fill=blue!20, minimum size=\sizehum] {};
+\node(203) at (\xcirb, \ycirb) [circle, draw=blue!50, fill=white!20, scale=1, minimum size=\sizechd] {Children};
+\draw[decoration={
+    text along path,
+    text={Teachers and curriculum},
+    text align={center},
+    raise=0cm},decorate] (1.20, 0) arc (180:0:1.22);
+\draw[decoration={
+    text along path,
+    text={Pre-school, primary/secondary schools},
+    text align={center},
+    raise=0cm},decorate] (0.4, 0) arc (180:0:2);
+
+% Circle C
+\node(301) at (\xcirc, \ycirc) [fill, circle, draw=black!50, fill=yellow!40, minimum size=\sizefac] {};
+\node(302) at (\xcirc, \ycirc) [fill, circle, draw=blue!50, fill=blue!20, minimum size=\sizehum] {};
+\node(303) at (\xcirc, \ycirc) [circle, draw=blue!50, fill=white!20, scale=1, minimum size=\sizechd] {Children};
+\draw[decoration={
+    text along path,
+    text={Parents and caretakers},
+    text align={center},
+    raise=0cm},decorate] (-1.3, -4.20) arc (-180:0:1.3);
+\draw[decoration={
+    text along path,
+    text={Living environment and housing},
+    text align={center},
+    raise=0cm},decorate] (-2.2, -4.20) arc (-180:0:2.2);
+
+% Circle D
+\path [draw=red!50, fill=red!30, fill opacity = 1.0, line width=1pt, even odd rule] (0,-1.42) circle (1.5) (0,-1.42) circle (0.8);
+\node(403) at (0,-1.42) [circle, draw=red!50, fill=white!20, scale=1, minimum size=\sizechd] {Children};
+\draw[decoration={
+    text along path,
+    text={Policies and community},
+    text align={center},
+    raise=0cm},decorate] (-1.30, -1.35) arc (-180:0:1.25);
+
+% Text 
+% \node[below] at (0, 3.5) {
+% Climatic environment, extreme weather, etc.};
+% \node[below] at (0, 3.5) [rectangle, draw=gray!50, fill=gray!10, text width=3.5cm] {\textbf{{\normalsize \textcolor{blue}{Extreme Weather Crisis}}}};
+\draw[decoration={
+    text along path,
+    text={Climatic ambient environmental exposures during childhood that condition human capital growth and development},
+    text align={center},
+    raise=0cm},decorate] (-6, -1.45) arc (180:0:6);
+
+\node(898) at (-4, -3.75) [rectangle, draw=gray!20, fill=gray!20, text width=0cm] {};
+\node(899) at (+4, -3.75) [rectangle, draw=gray!20, fill=gray!20, text width=0cm] {};
+
+\node(996) at (0, 3.5) [rectangle, draw=black!20, fill=gray!20, minimum width=3.8cm, font=\bfseries] {\textcolor{black}{Extreme temperature}};
+\node(997) at (0, 3.0) [rectangle, draw=black!20, fill=gray!20, minimum width=3.8cm, font=\bfseries] {\textcolor{black}{Pollution}};
+\node(998) at (0, -7.75) [rectangle, draw=gray!10, fill=gray!0, minimum width=3.8cm] {\textcolor{red}{Human Capital Formation}};
+\node(999) at (0, -8.25) [rectangle, draw=gray!10, fill=gray!0, minimum width=7.1cm] {\textcolor{black}{Learning, psychological, socio-emotional, physical outcomes}};
+
+% to and out
+% https://tikz.dev/library-edges
+% out = The angle at which the curve leaves the start coordinate.
+If the start coordinate is a node, the start coordinate is the point on the border of the node at the given ⟨angle⟩.
+The control point will, thus, lie at a certain distance in the direction ⟨angle⟩ from the start coordinate.
+% in = The angle at which the curve reaches the target coordinate.
+\path[->] (101.south west) edge [double, out=-105, 
+    in=100, draw=blue,line width=1pt] (898.north);
+\path[->] (301.west) edge [double, out=-105, 
+    in=0, draw=blue,line width=1pt] (898.east);
+\path[->] (898.south west) edge [double, out=-105, 
+    in=150, draw=blue,line width=1pt] (998.west);
+
+\path[->] (201.south east) edge [double, 
+    out=-70, in=100, 
+    draw=blue,line width=1pt] (899.north);
+\path[->] (301.east) edge [double, 
+    out=0, in=-200, 
+    draw=blue,line width=1pt] (899.west);
+\path[->] (899.south east) edge [double, 
+    out=-75, in=30, 
+    draw=blue,line width=1pt] (998.east);        
+\path[dashed, ->] (999.north east) edge [
+    out=30, in=35, looseness=1
+    ] (996.north east);
+\path[dashed, ->] (999.north west) edge [
+    out=150, in=145, looseness=1
+    ] (996.north west);
+
+\path[<->] (103.east) edge [double, draw=black, line width=1pt] (403.north west);
+\path[<->] (203.west) edge [double, draw=black, line width=1pt] (403.north east);
+\path[<->] (303.north) edge [double, draw=black, line width=1pt] (403.south);
+
+\end{tikzpicture}
+}
+\end{center}
+Above we have the picture we are interested in including.
+\clearpage
 
@@
 
+\section{Consumption, cash, and other spending}
+
+\subsection{Diagram with box edge color and box fill color and parameterized layer gaps}
+
+\def\txbwa{50}
+\def\linewa{2.5}
+
+\def\xsft{-25}
+\def\lvla{0}
+\def\lvlb{\lvla -1.25}
+\def\lvlc{\lvlb -1.75}
+\def\lvld{\lvlc -1.5}
+\def\lvle{\lvld -2.25}
+
+\def\clrsavings{orange}
+\def\clrresource{gray}
+\def\clrother{gray}
+\def\clrcash{red}
+\def\clrbank{black}
+
+\begin{center}
+\begin{tikzpicture}[thick]
+    % \tikz[align=center]
+    % level 1
+    % \draw (0,0) rectangle (2,2) node[pos=.5, text width=2cm,  align=center] {Test sdkf ljlkdjfa lkdsjf };
+
+    \node(101) at (0,\lvla) [rectangle,draw=\clrcash!50,fill=\clrresource!20,align=center,line width=\linewa, text width=\txbwa, xshift=\xsft, align=center] {
+        Cash earn
+        };
+    \node(102) at (5,\lvla) [rectangle,draw=\clrcash!50,fill=\clrsavings!20, align=center, line width=\linewa, text width=\txbwa, xshift=\xsft, align=center] {
+        Cash save
+        };
+    % level 2
+    \node(201) at (2.5,\lvlb) [rectangle,draw=\clrresource!50,fill=\clrresource!20, align=center, text width=\txbwa, xshift=\xsft, align=center] {
+        Resources (all cash)
+        };
+    % level 3
+    \node(301) at (-1.5,\lvlc) [rectangle,draw=\clrother!50, fill=blue!20, align=center, text width=\txbwa, xshift=\xsft, align=center] {
+        Cash consumption
+        };
+    \node(302) at (+2.5,\lvlc) [rectangle,draw=\clrother!50,fill=blue!20, align=center, text width=\txbwa, xshift=\xsft, align=center] {
+        Non-cash cons.
+        };
+    \node(303) at (+6.5,\lvlc) [rectangle,draw=\clrother!50,fill=\clrsavings!20, align=center, text width=\txbwa, xshift=\xsft, align=center] {
+        Savings
+        };
+    % level 3.5
+    \node(351) at (0.075,\lvld) [rectangle,draw=\clrbank!50,fill=blue!20, line width=\linewa, text width=\txbwa, xshift=\xsft, align=center] {
+        Deposit to bank
+        };
+    % level 4
+    \node(401) at (-3.5,\lvle) [rectangle,draw=\clrcash!50,fill=blue!20, line width=\linewa, text width=\txbwa, xshift=\xsft, align=center] {
+        Cash pay: Pocket-in-Pocket-out
+        };
+    \node(402) at (-1.1,\lvle) [rectangle,draw=\clrcash!50,fill=blue!20, line width=\linewa, text width=\txbwa, xshift=\xsft, align=center] {
+        Cash pay: ATM-to-cons.
+        };
+    \node(403) at (1.3,\lvle) [rectangle,draw=\clrbank!50,fill=blue!20, line width=\linewa, text width=\txbwa, xshift=\xsft, align=center] {
+        Bank pay: Bank-card cons.
+        };
+    \node(404) at (3.7,\lvle) [rectangle,draw=\clrbank!50,fill=blue!20, line width=\linewa, text width=\txbwa, xshift=\xsft, align=center] {
+        Bank pay: Digital cons.
+        };
+    \node(405) at (6.1,\lvle) [rectangle,draw=\clrcash!50,fill=\clrsavings!20, line width=\linewa, text width=\txbwa, xshift=\xsft, align=center] {
+        Cash save: Savings in pocket
+        };
+    \node(406) at (8.5,\lvle) [rectangle, draw=\clrbank!50, fill=\clrsavings!20, line width=\linewa, text width=\txbwa, xshift=\xsft, align=center] {
+        Bank save: Savings at bank
+        };
+
+    \draw [->] (101.south) to (201.north west); 
+    \draw [->] (102.south) to (201.north east);
+
+    \draw [->] (201.south) to (301.north); 
+    \draw [->] (201.south) to (302.north);
+    \draw [->] (201.south) to (303.north);
+
+    \draw [->] (301.south) to (401.north); 
+    \draw [->] (301.south) to (351.north west);
+    \draw [->] (302.south) to (351.north east);
+    \draw [->] (351.south) to (402.north); 
+    \draw [->] (351.south) to (403.north); 
+    \draw [->] (351.south) to (404.north);
+
+    \draw [->] (303.south) to (405.north);
+    \draw [->] (303.south) to (406.north);
+
+\end{tikzpicture}
+\end{center}
+\clearpage
+
 \end{document}
